### 2015-09-21 Docs/Proposal/patents.tex
first commit

\input{header.tex}

\title{Mining Patents Data through Semantic Network Analysis\bigskip\\
\textit{Project Proposal}
}
\author{\noun{J. Raimbault}}
\date{September 19th}

\maketitle

\justify

\begin{abstract}
Patents are a central proxy in the study of the economy of innovation. Indeed, the information contained in relations between patents reflects the underlying structure of the socio-technological system of research and development in innovative companies. Whereas recent focus was mainly on the study of patterns in the inter-patent citation network, taking technological fields as externally fixed, we propose a novel approach based on semantic analysis of patents textual contents. Indeed, measures such as co-occurences and repetitions of keywords should contain a slightly different information than the one extracted from the citation network, as for example links between domains, or informal domains that could appear as communities in the semantic network. The aim of this project is to investigate the nature and extent of this information, by the mining of regular patterns in features that should be established. We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, datamining techniques. Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and identify innovatives
\end{abstract}

%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

% state-of-the-art and recent works.

The study of innovation through the lens of technological patents is not a novel idea~\cite{}%old paper studying patents
but the recent rise of new methods and computational abilities, including datamining and network analysis~\cite{}%newman networks
has shed a new light on the approach. With methods relatively close to applied epistemology studies such as science mapping~\cite{}
or autorships networks analysis~\cite{}
, recent works have studied patents citation network to understand the processes of technological innovation.

%%%%%%%%%%%%%%%%%%%%
\section{Research objectives}

The identification of so-called \emph{emerging research fronts} was done in the case of scientific publications in~\cite{shibata2008detecting}. In the same spirit, our guiding research objective is to identify such fronts for patents, i.e. to be able to classify patents in order to distinguish the ``real innovations'' from

% cross domains ? -> Youn paper. \cite{Youn:2015fk}

%%%%%%%%%%%%%%%%%%%%
\section{Proposed approach}

%%%%%%%%%%%%%%%%%%%%
\subsection{General description}

%%%%%%%%%%%%%%%%%%%%
\subsection{Technical details}

%%%%%%%%%%%%%%%%%%%%
\section{Project organisation}

%%%%%%%%%%%%%%%%%%%%
%% Biblio
%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{apalike}
\bibliography{../../Biblio/patents}

\end{document}

### 2015-09-21 Docs/Proposal/patents.tex
more_bib_textmining

@@
 We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, datamining techniques.
-Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and identify innovatives
+Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and be able to systematically differentiate innovatives from imitating patents.
 \end{abstract}
@@
 
-The study of innovation through the lens of technological patents is not a novel idea~\cite{}%old paper studying patents
-but the recent rise of new methods and computational abilities, including datamining and network analysis~\cite{}%newman networks
-has shed a new light on the approach. With methods relatively close to applied epistemology studies such as science mapping~\cite{}
-or autorships networks analysis~\cite{}
-, recent works have studied patents citation network to understand the processes of technological innovation.
+The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including datamining and network analysis~\cite{newman2010networks} has shed a new light on the approach.
+With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation.
 
@@
 
+\subsection{Research question}
+
 The identification of so-called \emph{emerging research fronts} was done in the case of scientific publications in~\cite{shibata2008detecting}.
 In the same spirit, our guiding research objective is to identify such fronts for patents, i.e.
-to be able to classify patents in order to distinguish the ``real innovations'' from
+to be able to classify patents in order to distinguish the ``real innovations'' from imitations of existing technologies.
+That is relatively close to the issue of defining a relevant measure of innovation~\cite{archibugi1988search}
 
 % cross domains ? -> Youn paper. \cite{Youn:2015fk}
+
+\subsection{Link with previous work}
+
+% particular state-of-the-art ; how are we positioned ?
+
+A consequent amount of research already proposed to use semantic networks to study technological domains.
+One of the first works to enhance the approach was~\cite{yoon2004text}, where the idea of visualizing keywords network was introduced and illustrated on a small technological domain.
+
+The novelty of our project relies on various points, including the systematic unsupervized research of patterns, the possibility to build hybrid features from both semantic and citation networks, the combination of various techniques from datamining to network analysis.
 
@@
 
+This project is based on the assumption that semantic relations between patents contents must include some information on the underlying technological innovation processes.
+The idea is strongly inspired from the semantic science mapping proposed in~\cite{chavalarias2013phylomemetic}, where dynamics of scientific fields was reconstructed by keywords co-occurence networks analysis.
+The assets of such an approach include
+
 %%%%%%%%%%%%%%%%%%%%
@@
 \section{Project organisation}
+
+\begin{itemize}
+\item Project definition, litterature review - AB, JR, PA - ETA 10h
+\item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h
+\item Technical aspects (database management, text-mining implementation) - JR - ETA 10h
+\item Empirical datamining - AB, JR - ETA 20h
+\item Theoretical feedback, revision of mining techniques - AB, JR, PA - ETA 10h
+\item Theoretical modeling, results interpretation, perspectives - AB, PA - ETA ?
+\end{itemize}
 

### 2015-10-18 Models/TextProcessing/test.py
test_nw_file

@@ -1,14 +1,20 @@
 
-import nltk,sqlite3,time,locale
+import nltk,sqlite3,time,locale,datetime
+
+# issue with multithreading
+#from multiprocessing import Pool
 
 
 
 # tests
 
 def test():
-    # test_kw()
-    test_db()
+    #test_kw()
+    #test_db()
+    test_dico()
 
+def test_dico():
+    construct_occurrence_dico(2000,100)
 
 def test_db():
     for patent in get_patent_data(2000,100):
@@ -16,12 +22,59 @@ def test_db():
 
 
 def test_kw():
-    for patent in res :
-        print(extract_keywords(patent[1]+". "+patent[2],patent[0]))
+    def f(patent):
+        return extract_keywords(patent[1]+". "+patent[2],patent[0])
+
+    p = Pool(4)
+    print(p.map(f, get_patent_data(2000,1000)))
 
 
 
 ## Functions
+
+def construct_occurrence_dico(year,limit) :
+    data = get_patent_data(year,limit)
+    p_kw_dico = dict()
+    kw_p_dico = dict()
+    for patent in data :
+        patent_id = patent[0].encode('ascii','ignore')
+        keywords = extract_keywords(patent[1]+". "+patent[2],patent_id)
+        print(keywords)
+
+        for w in keywords :
+            k = reduce(lambda s1,s2 : s1+' '+s2,w)
+            # add to p_kw dico
+            if k in kw_p_dico :
+                kw_p_dico[k].append(patent_id)
+            else :
+                kw_p_dico[k]= [patent_id]
+
+            #
+            if patent_id in p_kw_dico :
+                p_kw_dico[patent_id].append(k)
+            else :
+                p_kw_dico[patent_id] = [k]
+
+
+    print(p_kw_dico.keys())
+    print(p_kw_dico.values())
+    #print(map(lambda l : len(l),dico.values()))
+
+    # write to file
+    p_kw = open('../../Data/processed/test_pkw_'+str(year)+'_'+str(limit)+'_'+str(datetime.datetime.now())+'.csv','w')
+    kw_p = open('../../Data/processed/test_kwp_'+str(year)+'_'+str(limit)+'_'+str(datetime.datetime.now())+'.csv','w')
+
+    for k in p_kw_dico.keys():
+        p_kw.write(k)
+        for kw in p_kw_dico[k]:
+            p_kw.write(kw)
+        p_kw.write('\n')
+
+    for k in kw_p_dico.keys():
[…]

### 2015-10-19 Models/Test/graphs.R
Rscript_graphfile_construction

@@ -1,0 +1,43 @@
+library(rgexf)
+
+source('Models/Test/utils.R')
+
+# reconstruct maps 
+p_kw <- readMappingFile('Data/processed/test_pkw_2000_1000_2015-10-19 09:40:23.085621.csv',sep=";")
+kw_p <- readMappingFile('Data/processed/test_kwp_2000_1000_2015-10-19 09:40:23.368437.csv',sep=";")
+
+# test gexf export
+
+# patent graph, link if same kw
+pids=list();id=1;for(n in names(p_kw)){pids[[n]]=id;id=id+1;}
+nodes = data.frame(id=1:length(pids),label=names(p_kw))
+
+# edges
+rawedges=c();k=1;
+edgeLabels = c();
+keywords=names(kw_p);
+for(kw in kw_p){
+  show(k)
+  if(length(kw)>1){
+    for(i in 1:(length(kw)-1)){
+      for(j in (i+1):length(kw)){
+        rawedges=append(rawedges,pids[[kw[i]]],pids[[kw[j]]])
+        edgeLabels=append(edgeLabels,keywords[k])
+      }
+    }
+  }
+  k=k+1;
+}
+
+# quite slow ; may be not that powerful on larger dataset ? -> filter keywords before in python script ; by score on subcorpuses
+
+# construct the edges dataframe
+edgesmat=matrix(data=rawedges,ncol=2,byrow=TRUE)
+colnames(edgesmat)<-c('source','target')
+
+write.gexf(nodes=nodes,
+           edges=edgesmat,
+           output='Data/processed/test_patentNW.gexf')
+
+
+

### 2015-10-19 Models/Test/utils.R

@@ -1,0 +1,16 @@
+
+# utils functions
+
+readMappingFile <- function(file,sep){
+  lines = readLines(file)
+  res=list()
+  for(l in lines){
+    words = strsplit(l,sep)[[1]]
+    # reconstruct a hashtable in the res list
+    res[[words[1]]]=words[2:length(words)]
+  }
+  return(res)
+}
+
+
+

### 2015-10-19 Models/TextProcessing/test.py

@@ -14,7 +14,7 @@ def test():
     test_dico()
 
 def test_dico():
-    construct_occurrence_dico(2000,100)
+    construct_occurrence_dico(2000,1000)
 
 def test_db():
     for patent in get_patent_data(2000,100):
@@ -65,15 +65,15 @@ def construct_occurrence_dico(year,limit) :
     kw_p = open('../../Data/processed/test_kwp_'+str(year)+'_'+str(limit)+'_'+str(datetime.datetime.now())+'.csv','w')
 
     for k in p_kw_dico.keys():
-        p_kw.write(k)
+        p_kw.write(k+";")
         for kw in p_kw_dico[k]:
-            p_kw.write(kw)
+            p_kw.write(kw+";")
         p_kw.write('\n')
 
     for k in kw_p_dico.keys():
-        kw_p.write(k)
+        kw_p.write(k+";")
         for kw in kw_p_dico[k]:
-            kw_p.write(kw)
+            kw_p.write(kw+";")
         kw_p.write('\n')
 
 

### 2015-10-19 Docs/Proposal/patents.tex
Update patents.tex

@@
 
+Every patent is associated with many details that have been made available by national and international patent offices.
+First, each patent is associated with one or several technological fields which are chosen from a list by patent office specialists after careful review of the content of the patent (see IPC class).
+Second, every patent has to make a list of citations to all the patents used in the process, this naturally define a network between entities that have some technologies in common.
+From these two features innovation economists have created various indices to measure the quality of a patent ( number of citations, scope of technological field...).
+
+Two other indicators are of particular interest for us: originality and radicalness. The originality measure is
+defined by Hall \textit{et al.} (2001) \cite{Hall2001} as $Ori_{i}%
+=1-\displaystyle\sum_{j=1}^{n_{i}}{cit_{i,j}^{2}}$ where $cit_{i,j}$ is the
+percentage of citations made by patent $i$ to a patent in class $j$ out of
+$n_{i}$ technological classes to which patent $i$ belongs. If the scope of
+technologies which the patent uses and cites is large, then the originality
+measure will be high. Radicalness is more difficult to define. It is
+constructed in the same way as the originality index but here we only consider
+the technology classes of patents cited by patent $i$ but to which patent $i$
+does not belong.
+
 %%%%%%%%%%%%%%%%%%%%

### 2015-10-19 Docs/Proposal/patents.tex
Update patents.tex

@@
 to be able to classify patents in order to distinguish the ``real innovations'' from imitations of existing technologies.
-That is relatively close to the issue of defining a relevant measure of innovation~\cite{archibugi1988search}
+That is relatively close to the issue of defining a relevant measure of innovation~\cite{archibugi1988search}.
+The goal of the study is therefore to build a new database based on USPTO patent applications from 1975 to 2014 where each patent would be link with an index between 0 and 1, 1 being a patent corresponding to a new product and 0 being a patent corresponding to an improvment on an existing product.
+This question is of major importance in mordern growth theories (see Klenow et al.
+(forthcoming) especially to measure growth induced by incumbent improving on their own innovations \cite{KletteKortum2002}.
+% Klenow: How destructive is innovation
 
@@
 the technology classes of patents cited by patent $i$ but to which patent $i$
-does not belong.
+does not belong. These two indicators are good proxies and great start to estimate if a patent is protecting a new product that can hardly be classified into the official technological field space.
+
+Our strategy will rely on differences between our network based on semantic comparison and the two existing network defined above.
+The underlying assumption being that highly innovative new product are not well classified by the technological class space and should struggle to cite previous related patents.
+Hence, we expect such patent to have a large distance in terms of semantic analysis with patents it cite and patents in the same technological class.
 

### 2015-10-20 Docs/Proposal/patents.tex
Update patents.tex
small_update_proposal

@@
 
-\title{Mining Patents Data through Semantic Network Analysis\bigskip\\
+\title{
+% faut trouver un titre choc ^^
+%Mining Patents Data through Semantic Network Analysis
+An Hypernetwork Approach to Accurately Measure Technological Innovation
+\bigskip\\
 \textit{Project Proposal}
 }
-\author{\noun{J. Raimbault}}
-\date{September 19th}
+\author{\noun{J. Raimbault}$^{1,2}$ and \noun{A. Bergeaud}$^{3,4}$\medskip\\
+$^{1}$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\\
+$^{2}$ UMR-T IFSTTAR 9403 LVMT\\
+$^{3}$ London School of Economics\\
+$^{4}$ Coll{\`e}ge de France
+}
+\date{}
 
@@
 With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation.
+As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
+in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.
+% TODO
+% Est-ce qu'il y a déjà un papier d'Aghion qui fait le lien entre croissance et connaissance de l'innovation ?
+Genre Aghion, P., & Howitt, P.
+(2005).
+Growth with quality-improving innovations: an integrated framework.
+Handbook of economic growth, 1, 67-110.
+?
+% si oui est-ce que c'est intéressant de le citer à cet endroit ?
 
@@
 The goal of the study is therefore to build a new database based on USPTO patent applications from 1975 to 2014 where each patent would be link with an index between 0 and 1, 1 being a patent corresponding to a new product and 0 being a patent corresponding to an improvment on an existing product.
-This question is of major importance in mordern growth theories (see Klenow et al.
+This question is of major importance in modern growth theories (see Klenow et al.
 (forthcoming) especially to measure growth induced by incumbent improving on their own innovations \cite{KletteKortum2002}.
 % Klenow: How destructive is innovation
-
-% cross domains ? -> Youn paper. \cite{Youn:2015fk}
 
@@
 One of the first works to enhance the approach was~\cite{yoon2004text}, where the idea of visualizing keywords network was introduced and illustrated on a small technological domain.
+We will also be interested in measures based on technological classification, as in~\cite{Youn:2015fk} where the study of the distribution of classes within patents leads to confirm the combinatory nature of the innovation process.
 
-The novelty of our project relies on various points, including the systematic unsupervized research of patterns, the possibility to build hybrid features from both semantic and citation networks, the combination of various techniques from datamining to network analysis.
+The novelty of our project relies on various points, including the systematic unsupervized research of patterns, the possibility to build hybrid features from both semantic and citation networks, the combination of various techniques from datamining to multi-layer network analysis.
 
@@
 The idea is strongly inspired from the semantic science mapping proposed in~\cite{chavalarias2013phylomemetic}, where dynamics of scientific fields was reconstructed by keywords co-occurence networks analysis.
-The assets of such an approach include
+The assets of such an approach include the fact to be not dependant on predefined fields or domains, what allows specifically to uncover effective domains by community detection.
+Extracting significant keywords (see technical details) from titles and abstracts
 
@@
 Two other indicators are of particular interest for us: originality and radicalness. The originality measure is
-defined by Hall \textit{et al.} (2001) \cite{Hall2001} as $Ori_{i}%
-=1-\displaystyle\sum_{j=1}^{n_{i}}{cit_{i,j}^{2}}$ where $cit_{i,j}$ is the
+defined by Hall \textit{et al.} (2001) \cite{Hall2001} as
+\[
+O_{i}%
+=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}}\] where $c_{i,j}$
+is the
 percentage of citations made by patent $i$ to a patent in class $j$ out of
@@
 
+\paragraph{Citation Network}
+
+% TBW : useful ?
+
+\paragraph{Technological Class Network}
+
+% idem
+
+\paragraph{Semantic Network}
+
+\paragraph{Possible Features}
+
 %%%%%%%%%%%%%%%%%%%%
@@
 \item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h
-\item Technical aspects (database management, text-mining implementation) - JR - ETA 10h
-\item Empirical datamining - AB, JR - ETA 20h
+\item Technical aspects (database management, text-mining implementation) - JR - ETA 15h
+\item Empirical datamining - AB, JR - ETA 25h
 \item Theoretical feedback, revision of mining techniques - AB, JR, PA - ETA 10h

### 2015-10-20 Docs/Proposal/patents.tex
dialy
filled missing parts in proposal ; more refs

@@
 $^{2}$ UMR-T IFSTTAR 9403 LVMT\\
-$^{3}$ London School of Economics\\
-$^{4}$ Coll{\`e}ge de France
+$^{3}$ London School of Economics
 }
@@
 in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.
-% TODO
-% Est-ce qu'il y a déjà un papier d'Aghion qui fait le lien entre croissance et connaissance de l'innovation ?
+% TODO Est-ce qu'il y a déjà un papier d'Aghion qui fait le lien entre croissance et connaissance de l'innovation ?
 Genre Aghion, P., & Howitt, P.
@@
 % si oui est-ce que c'est intéressant de le citer à cet endroit ?
+This project aims thus to fullfill the objective of exploring the potentialities of a precise measure of innovation through the mining of different aspects of patents data.
 
@@
 One of the first works to enhance the approach was~\cite{yoon2004text}, where the idea of visualizing keywords network was introduced and illustrated on a small technological domain.
+Semantic analysis has already proved its efficiency in various fields, such as~\cite{choi2014patent,fattori2003text} for technology studies, or~\cite{2015arXiv151003797G} in political science for example.
 We will also be interested in measures based on technological classification, as in~\cite{Youn:2015fk} where the study of the distribution of classes within patents leads to confirm the combinatory nature of the innovation process.
+Advanced citation-based measures have been proposed in order to gain an order of information extracted from the citation network~\cite{2015arXiv150907285A}, but we will stay to rather simple indicators concerning this network as we will cross it with other type of data.
+Concerning dynamic analysis, models of citation processes have been proposed and fit to data such as in~\cite{valverde2007topology}, and depending on temporal patterns we observe on features, we may propose to use dynamic models for network evolution.
 
@@
 The assets of such an approach include the fact to be not dependant on predefined fields or domains, what allows specifically to uncover effective domains by community detection.
-Extracting significant keywords (see technical details) from titles and abstracts
+Extracting significant keywords (see technical details) from titles and abstracts allows to construct semantic networks between patents or keywords, in which community detection e.g.
+should reveal patterns of ``effective'' technological fields.
 
@@
 Second, every patent has to make a list of citations to all the patents used in the process, this naturally define a network between entities that have some technologies in common.
-From these two features innovation economists have created various indices to measure the quality of a patent ( number of citations, scope of technological field...).
+From these two features innovation economists have created various indices to measure the quality of a patent (number of citations, scope of technological field, etc.
+).
+Two other indicators are of particular interest for us: originality and radicalness, their definition and expression being detailed in the next section.
 
-Two other indicators are of particular interest for us: originality and radicalness. The originality measure is
-defined by Hall \textit{et al.} (2001) \cite{Hall2001} as
+Our strategy will rely on comparisons between our network based on semantic comparison and the two existing network defined above.
+Simple correlations and diachronic dynamic analysis for time-dependant networks, combined with unsupervised datamining for rough data exploration, should be conducted first, and then completed by more refined datamining, using supervised learning if needed, i.e.
+if no significant pattern has emerged in the features constructed.
+The underlying assumption driving our work is that highly innovative new product are not well classified by the technological class space and should struggle to cite previous related patents.
+% TODO Ref thématique possible là-dessus ou c'est un feeling ?
+Hence, we expect such patent to have a large distance in terms of semantic analysis with patents it cites and patents in the same technological class.
+
+%%%%%%%%%%%%%%%%%%%%
+\subsection{Technical details}
+
+\paragraph{Originality Measures}
+
+The originality measure is
+defined by Hall \textit{et al.} (2001)~\cite{Hall2001} as
 \[
@@
 
-Our strategy will rely on differences between our network based on semantic comparison and the two existing network defined above.
-The underlying assumption being that highly innovative new product are not well classified by the technological class space and should struggle to cite previous related patents.
-Hence, we expect such patent to have a large distance in terms of semantic analysis with patents it cite and patents in the same technological class.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Technical details}
-
 \paragraph{Citation Network}
@@
 
+We first assign to a patent $p$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted following a similar procedure to the one detailed in~\cite{chavalarias2013phylomemetic} :
+\begin{itemize}
+\item Text parsing and tokenizing.
+\item Part-of-speech tagging, normalization.
+\item Stem extraction and multi-stems constructions.
+\item Relevant multi-stems filtering.
+\end{itemize}
+
+Text processing operations will be implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{} % cite nltk
+which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
+
 \paragraph{Possible Features}
@@
 \section{Project organisation}
+
+Proposed research agenda :
 

### 2015-10-20 Docs/Proposal/patents.tex
Update patents.tex

--- 2015-10-20 Docs/Proposal/patents.tex
@@
 O_{i}%
-=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}}\] where $c_{i,j}$
+=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}} where $c_{i,j}$
 is the
@@
 
-% TBW : useful ?
+We define a binary relation between each pair of patents $Cit(i, j)$ = 1 if j cites i or i cites j.
 
@@
 
-% idem
+For each patent i, let $B_i$ be the set of technological class of i.
+We then define a relationship between each pair i and j as 2 times the number of technological class in common divided by the total number of class of i and j.
+\[
+Class(i,j) = 2\frac{\left\vert{B_i\cap B_j}\right\vert}{\frac{\left\vert{B_i}\right\vert}+\frac{\left\vert{B_j}\right\vert}}
+\]
+
+Thus, if two patents have no class in common, $Class(i,j)=0$ while if the two patents are exactly identical in terms of their sets of technologial class $Class(i,j)=1$.
 
 \paragraph{Semantic Network}
+
+We first assign to a patent $p$ a set of significant keywords $K(p)\in $
 

### 2015-10-20 Docs/Proposal/patents.tex
Update patents.tex

--- 2015-10-20 Docs/Proposal/patents.tex
@@
 
-% TBW : useful ?
+We define a binary relationship between each pair of patents $Cit(i, j) = 1$ if j cites i or i cites j, otherwise $Cit(i, j) = 0.
 
@@
 
-% idem
+For each patent i, let $B_i$ be the set of technological class of i.
+We then define a relationship between each pair i and j as 2 times the number of technological class in common divided by the total number of class of i and j.
+\[
+Class(i,j) = 2\frac{\left\vert{B_i\cap B_j}\right\vert}{\frac{\left\vert{B_i}\right\vert}+\frac{\left\vert{B_j}\right\vert}}
+\]
+
+Thus, if two patents have no class in common, $Class(i,j)=0$ while if the two patents are exactly identical in terms of their sets of technologial class $Class(i,j)=1$.
 

### 2015-10-20 Docs/Proposal/patents.tex
merge_conflict_solved

@@
 \[
-O_{i}%
-=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}} where $c_{i,j}$
-is the
-percentage of citations made by patent $i$ to a patent in class $j$ out of
+O_{i}=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}}
+\]
+where $c_{i,j}$is the percentage of citations made by patent $i$ to a patent in class $j$ out of
 $n_{i}$ technological classes to which patent $i$ belongs. If the scope of
@@
 
-We define a binary relationship between each pair of patents $Cit(i, j) = 1$ if j cites i or i cites j, otherwise $Cit(i, j) = 0.
+We define a binary relationship between each pair of patents $Cit(i, j) = 1$ if j cites i or i cites j, otherwise $Cit(i, j) = 0$.
 

### 2015-10-25 Models/TextProcessing/test.py
added_relevant_kw_extraction

@@ -32,6 +32,64 @@ def test_kw():
 
 ## Functions
 
+
+def extract_relevant_keywords(year,limit,kwLimit):
+    [p_kw_dico,kw_p_dico]=construct_occurrence_dico(year,limit)
+    # compute unithoods
+    unithoods = dict()
+    for k in kw_p_dico.keys():
+        # TODO
+        l = 1 # l = len(strsplit(k,' '))
+        unithoods[k]=log(l+1)*len(kw_p_dico[k])
+    # sort and keep K*N keywords
+    ## TODO
+    selected_kws = dict()
+    # dictionary : kw -> index in matrix
+
+    # compute termhoods :: coocurrence matrix -> in \Theta(16 N^2) - N must thus stay 'small'
+    cooccs = []
+    for i in range(len(selected_kws.keys())):
+        cooccs.append(([0]*len(selected_kws.keys())))
+    # fill the cooc matrix
+    # for each patent : kws are coocurring if selected.
+    # Beware to filter BEFORE launching O(n^2) procedure
+
+    for p in p_kw_dico.keys() :
+        sel = []
+        for k in p_kw_dico[p] :
+            if k in selected_kws : sel.append(k)
+        for i in range(1,len(sel)-1):
+            for j in range(i+1,len(sel)):
+                ii = selected_kws[sel[i]] ; jj= selected_kws[sel[j]] ;
+                cooccs[ii][jj] = cooccs[ii][jj] + 1
+                cooccs[jj][ii] = cooccs[jj][ii] + 1
+
+    # compute termhoods
+    colSums = [sum(row) for row in cooccs]
+
+    termhoods = [0]*len(cooccs)
+    for i in range(len(coocs)):
+        s = 0;
+        for j in range(len(coocs)):
+            if j != i : s = s + (cooccs[i][j]-colSums[i]*colSums[j])^2/(colSums[i]*colSums[j])
+        termhoods[i]=s
+
+    # sort and filter on termhoods
+    # TODO
+    tselected = dict()
+
+    # reconstruct the patent -> tselected dico, finally necessary to build kw nw
+    p_tsel_dico = dict()
+    for p in p_kw_dico.keys() :
+        sel = []
+        for k in p_kw_dico[p] :
+            if k in selected_kws : sel.append(k)
+        p_tsel_dico[p] = sel
+
+    # eventually write to file ? -> do that in other proc (! atomicity)
[…]

### 2015-10-25 Models/TextProcessing/test.py
skeleton_bootstrap

@@ -33,8 +33,24 @@ def test_kw():
 ## Functions
 
 
-def extract_relevant_keywords(year,limit,kwLimit):
-    [p_kw_dico,kw_p_dico]=construct_occurrence_dico(year,limit)
+# tests for a bootstrap technique to avoid subcorpus relevance bias
+def bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bSize):
+    N = len(corpus)
+
+    # generate bSize extractions
+    #extractions =
+
+    # for each extraction, extract subcorpus and get relevant kws
+
+    # then for each patent, mean termhoods, and recompute relevant keywords ?
+
+
+
+
+
+# extract relevant keywords, using unithood and termhood
+def extract_relevant_keywords(corpus,kwLimit):
+    [p_kw_dico,kw_p_dico]=construct_occurrence_dico(corpus)
     # compute unithoods
     unithoods = dict()
     for k in kw_p_dico.keys():
@@ -90,8 +106,9 @@ def extract_relevant_keywords(year,limit,kwLimit):
     return(p_tsel_dico)
 
 
-def construct_occurrence_dico(year,limit) :
-    data = get_patent_data(year,limit)
+#
+def construct_occurrence_dico(data) :
+    #data = get_patent_data(year,limit)
     p_kw_dico = dict()
     kw_p_dico = dict()
     for patent in data :

### 2015-10-26 Docs/WorkingPapers/methods.tex
skeleton_workingpaper_methodsandResults

--- 2015-10-20 Docs/Proposal/patents.tex
@@
 \title{
-% faut trouver un titre choc ^^
-%Mining Patents Data through Semantic Network Analysis
 An Hypernetwork Approach to Accurately Measure Technological Innovation
 \bigskip\\
-\textit{Project Proposal}
+\textit{Methods and Results}
 }
-\author{\noun{J. Raimbault}$^{1,2}$ and \noun{A. Bergeaud}$^{3,4}$\medskip\\
+\author{\noun{J. Raimbault}$^{1,2}$ and \noun{A. Bergeaud}$^{3}$\medskip\\
 $^{1}$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\\
@@
 \begin{abstract}
-Patents are a central proxy in the study of the economy of innovation.
-Indeed, the information contained in relations between patents reflects the underlying structure of the socio-technological system of research and development in innovative companies.
-Whereas recent focus was mainly on the study of patterns in the inter-patent citation network, taking technological fields as externally fixed, we propose a novel approach based on semantic analysis of patents textual contents.
-Indeed, measures such as co-occurences and repetitions of keywords should contain a slightly different information than the one extracted from the citation network, as for example links between domains, or informal domains that could appear as communities in the semantic network.
-The aim of this project is to investigate the nature and extent of this information, by the mining of regular patterns in features that should be established.
-We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, datamining techniques.
-Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and be able to systematically differentiate innovatives from imitating patents.
+This working paper details technical methods used in the project and gives a first overview of results.
 \end{abstract}
@@
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%
 
-% state-of-the-art and recent works.
-
-The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including datamining and network analysis~\cite{newman2010networks} has shed a new light on the approach.
-With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation.
-As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
-in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.
-% TODO Est-ce qu'il y a déjà un papier d'Aghion qui fait le lien entre croissance et connaissance de l'innovation ?
-Genre Aghion, P., & Howitt, P.
-(2005).
-Growth with quality-improving innovations: an integrated framework.
-Handbook of economic growth, 1, 67-110.
-?
-% si oui est-ce que c'est intéressant de le citer à cet endroit ?
-This project aims thus to fullfill the objective of exploring the potentialities of a precise measure of innovation through the mining of different aspects of patents data.
+\textit{See project Proposal}
 
 %%%%%%%%%%%%%%%%%%%%
-\section{Research objectives}
+\section{Methods}
+%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Research question}
-
-The identification of so-called \emph{emerging research fronts} was done in the case of scientific publications in~\cite{shibata2008detecting}.
-In the same spirit, our guiding research objective is to identify such fronts for patents, i.e.
-to be able to classify patents in order to distinguish the ``real innovations'' from imitations of existing technologies.
-That is relatively close to the issue of defining a relevant measure of innovation~\cite{archibugi1988search}.
-The goal of the study is therefore to build a new database based on USPTO patent applications from 1975 to 2014 where each patent would be link with an index between 0 and 1, 1 being a patent corresponding to a new product and 0 being a patent corresponding to an improvment on an existing product.
-This question is of major importance in modern growth theories (see Klenow et al.
-(forthcoming) especially to measure growth induced by incumbent improving on their own innovations \cite{KletteKortum2002}.
-% Klenow: How destructive is innovation
-
-\subsection{Link with previous work}
-
-% particular state-of-the-art ; how are we positioned ?
-
-A consequent amount of research already proposed to use semantic networks to study technological domains.
-One of the first works to enhance the approach was~\cite{yoon2004text}, where the idea of visualizing keywords network was introduced and illustrated on a small technological domain.
-Semantic analysis has already proved its efficiency in various fields, such as~\cite{choi2014patent,fattori2003text} for technology studies, or~\cite{2015arXiv151003797G} in political science for example.
-We will also be interested in measures based on technological classification, as in~\cite{Youn:2015fk} where the study of the distribution of classes within patents leads to confirm the combinatory nature of the innovation process.
-Advanced citation-based measures have been proposed in order to gain an order of information extracted from the citation network~\cite{2015arXiv150907285A}, but we will stay to rather simple indicators concerning this network as we will cross it with other type of data.
-Concerning dynamic analysis, models of citation processes have been proposed and fit to data such as in~\cite{valverde2007topology}, and depending on temporal patterns we observe on features, we may propose to use dynamic models for network evolution.
-
-The novelty of our project relies on various points, including the systematic unsupervized research of patterns, the possibility to build hybrid features from both semantic and citation networks, the combination of various techniques from datamining to multi-layer network analysis.
-
-%%%%%%%%%%%%%%%%%%%%
-\section{Proposed approach}
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{General description}
-
-This project is based on the assumption that semantic relations between patents contents must include some information on the underlying technological innovation processes.
-The idea is strongly inspired from the semantic science mapping proposed in~\cite{chavalarias2013phylomemetic}, where dynamics of scientific fields was reconstructed by keywords co-occurence networks analysis.
-The assets of such an approach include the fact to be not dependant on predefined fields or domains, what allows specifically to uncover effective domains by community detection.
-Extracting significant keywords (see technical details) from titles and abstracts allows to construct semantic networks between patents or keywords, in which community detection e.g.
-should reveal patterns of ``effective'' technological fields.
-
-Every patent is associated with many details that have been made available by national and international patent offices.
-First, each patent is associated with one or several technological fields which are chosen from a list by patent office specialists after careful review of the content of the patent (see IPC class).
-Second, every patent has to make a list of citations to all the patents used in the process, this naturally define a network between entities that have some technologies in common.
-From these two features innovation economists have created various indices to measure the quality of a patent (number of citations, scope of technological field, etc.
-).
-Two other indicators are of particular interest for us: originality and radicalness, their definition and expression being detailed in the next section.
-
-Our strategy will rely on comparisons between our network based on semantic comparison and the two existing network defined above.
-Simple correlations and diachronic dynamic analysis for time-dependant networks, combined with unsupervised datamining for rough data exploration, should be conducted first, and then completed by more refined datamining, using supervised learning if needed, i.e.
-if no significant pattern has emerged in the features constructed.
-The underlying assumption driving our work is that highly innovative new product are not well classified by the technological class space and should struggle to cite previous related patents.
-% TODO Ref thématique possible là-dessus ou c'est un feeling ?
-Hence, we expect such patent to have a large distance in terms of semantic analysis with patents it cites and patents in the same technological class.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Technical details}
+% Taken from Technical Details section of proposal 
+% -> develop more precisely if needed
 
@@
 \[
-Class(i,j) = 2\frac{\left\vert{B_i\cap B_j}\right\vert}{\frac{\left\vert{B_i}\right\vert}+\frac{\left\vert{B_j}\right\vert}}
+Class(i,j) = 2\frac{\left\vert{B_i\cap B_j}\right\vert}{\left\vert{B_i}\right\vert+\left\vert{B_j}\right\vert}
 \]
@@
 
+\paragraph{Multilayer Network Analysis}
+Check out the method proposed in~\cite{iacovacci2015mesoscopic}. $\rightarrow$ Interesting for some kind of ``between-layers correlation'' ?
+
 %%%%%%%%%%%%%%%%%%%%
-\section{Project organisation}
-
-Proposed research agenda :
-
-\begin{itemize}
-\item Project definition, litterature review - AB, JR, PA - ETA 10h
-\item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h
-\item Technical aspects (database management, text-mining implementation) - JR - ETA 15h
-\item Empirical datamining - AB, JR - ETA 25h
-\item Theoretical feedback, revision of mining techniques - AB, JR, PA - ETA 10h
-\item Theoretical modeling, results interpretation, perspectives - AB, PA - ETA ?
-\end{itemize}
+\section{Results}
+%%%%%%%%%%%%%%%%%%%%
 

### 2015-10-26 Models/TextProcessing/test.py

@@ -45,7 +45,7 @@ def bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bSize):
     # then for each patent, mean termhoods, and recompute relevant keywords ?
 
 
-
+ bvbm
 
 
 # extract relevant keywords, using unithood and termhood

### 2015-10-26 Docs/WorkingPapers/methods.tex
methods_paper

@@
 
-\paragraph{Semantic Network}
+%%%%%%%%%%%%%%%%%%%%
+\subsection{Semantic Network}
 
-We first assign to a patent $p$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted following a similar procedure to the one detailed in~\cite{chavalarias2013phylomemetic} :
-\begin{itemize}
+\paragraph{Significant Keywords extraction procedure}
+
+We first assign to a patent $p \in \mathcal{P}$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted through a procedure similar to the one detailed in~\cite{chavalarias2013phylomemetic}, consisting in the following steps
+\begin{enumerate}
 \item Text parsing and tokenizing.
@@
 \item Relevant multi-stems filtering.
-\end{itemize}
+\end{enumerate}
 
-Text processing operations will be implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{} % cite nltk
+Text processing operations are implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{} % cite nltk
 which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
+Source code is openly available on the repository of the project\footnote{at \texttt{url}}.
+% TODO je suis pour ouvrir le repo une fois qu'on aura la majorité du taf faite, je sais pas ce que t'en penses ?
+c'est une nécessité pour ouverture et reproducibilité ; sans ça aucune valeur à ce qu'on prétend dans le papelard.
+Steps one to three are directly done using built-in functions of the library.
+Step four needs a particular treatment that we propose as an extension of the original method for large corpuses, which is detailed in the following.
+
+\paragraph{Bootstrap on random subcorpuses for relevance estimation}
+
+Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words.
+Let $K_w$ the maximal number of relevant keywords per patent.
+If $N$ is the total number of relevant keywords extracted
+The heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus.
+More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the termhood score as
+\[
+t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
+\]
 

### 2015-11-02 Docs/Proposal/patents.tex
compile_ok
Update patents.tex
proposal ok for me

@@
 }
-\author{\noun{J. Raimbault}$^{1,2}$ and \noun{A. Bergeaud}$^{3,4}$\medskip\\
+\author{\noun{J. Raimbault}$^{1,2}$ and \noun{A. Bergeaud}$^{3}$\medskip\\
 $^{1}$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\\
@@
 
-We first assign to a patent $p$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted following a similar procedure to the one detailed in~\cite{chavalarias2013phylomemetic} :
+We first assign to a patent $p\in \mathcal{P}$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted following a similar procedure to the one detailed in~\cite{chavalarias2013phylomemetic} :
 \begin{itemize}
@@
 
-Text processing operations will be implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{} % cite nltk
-which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
+The semantic network is then constructed by co-occurrences analysis : nodes are keywords, i.e.
+$V=\bigcup_{p\in\mathcal{P}}K(p)$, and edges represent co-occurrences : $E = \{(k,k') | \exists p \textrm{ s.t.
+} k, k' \in K(p)\}$.
+This specification aims to capture semantic communities that do necessarily have a thematic meaning and that should correspond to a specific domain, field, technology or technique.
+
+Text processing operations will be implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{nltk} which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
 
 \paragraph{Possible Features}
+
+Content of the hypernetwork analysis is rather open at this stage of the project, as techniques used will depend on patterns found in the first explorations of each network alone and of first order structural correlations.
+From an unsupervised datamining perspective, relevant features to distinguish real innovation may for example include :
+\begin{itemize}
+\item Citation relative centrality regarding technological or semantic classes : given a partition of $\mathcal{P}$ represented by a classification function $C$ (constructed for example by clustering or community detection within technological or semantic networks), a vector feature is for patent $i$
+\[
+\left(\frac{\sum_{j\in c}Cit^{out}(i,j)}{\sum_{j\in c}Cit^{in}(i,j)}\right)_{c\in C(\mathcal{P})}
+\]
+\item Dynamic evolution of classification vector : if $C_t$ is stratified over successive time periods indexed by time $t$, either $\Delta \vec{C}_t (i)$ if $\vec{C}_t$ is a vector of probabilities to belong to each class (in case of a Bayesian approach), or $\Delta (C_t(j))_{Cit(i,j,t)\neq 0}$ in case of a deterministic approach, could both be interesting features.
+\item Deviation from the expected classes given position in other layers of the hypernetwork (it would need explorations if these conditional probabilities first can be well estimated, then if they contain relevant information).
+\end{itemize}
 
@@
 \item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h
-\item Technical aspects (database management, text-mining implementation) - JR - ETA 15h
+\item Technical aspects (database management, text-mining implementation : JR ; citation network, technological class network : AB) - AB, JR - ETA 20h
 \item Empirical datamining - AB, JR - ETA 25h

### 2015-11-04 Docs/Proposal/patents.tex
data_class_techno

@@
 if no significant pattern has emerged in the features constructed.
-The underlying assumption driving our work is that highly innovative new product are not well classified by the technological class space and should struggle to cite previous related patents.
+The underlying assumption driving our work is that highly innovative new products are not well classified within the technological class space.
 % TODO Ref thématique possible là-dessus ou c'est un feeling ?

### 2015-11-28 Docs/WorkingPapers/methods.tex
tests_classes_nw

@@
 
+\paragraph{Computation of the Technological Network}
+
+With a number of patents of magnitude $10^6$, it is not considerable in memory and in time to compute pairwise distances on all patents.
+Fortunately, distance matrix is relatively sparse and non trivial proximities  (i.e.
+where patents have more than one class in common) can be computed through an efficient set intersection and difference implementation.
+
+More precisely, let $n = \left|\mathcal{P}\right|$ the number of patents.
+classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes.
+The number of classes $K$ being fixed, it simplifies into a $O(n\log{n})$.
+
 %%%%%%%%%%%%%%%%%%%%

### 2015-11-28 Models/Techno/overlap.R

@@ -22,5 +22,26 @@ for(i in 1:nrow(overlap)){
 
 o <- read.csv('overlap_snd_order_different.csv',sep=';')
 
+hist(diag(as.matrix(overlap)))
 diag(overlap) <- 0
 max(overlap)
+
+
+###########
+##
+# stats on class sizes -> power law ?
+
+classSizes = diag(as.matrix(overlap))
+hist(classSizes[classSizes> 100],breaks=200)
+
+# rank-size law for classes size ?
+plot(log(1:length(classSizes)),log(sort(classSizes,decreasing=TRUE)))
+plot(log(1:length(classSizes[classSizes> 10000])),log(sort(classSizes[classSizes> 10000],decreasing=TRUE)))
+plot(sort(classSizes,decreasing=TRUE))
+
+
+###
+# nw of non trivial techno distances
+
+
+

### 2015-11-29 Models/TextProcessing/test.py
kw_export_ok

@@ -9,7 +9,8 @@ import nltk,sqlite3,time,locale,datetime,operator,math
 # tests
 
 def test():
-    test_termhood_extract()
+    test_dico()
+    #import_kw_dico('../../data/processed/keywords.sqlite3')
 
 
 def test_termhood_extract():
@@ -20,9 +21,16 @@ def test_termhood_extract():
     export_dico_csv(relevant_dico,'../../data/processed/relevantDico_y2000_size1000_kwLimit200')
     export_list(relevantkw,'../../data/processed/relevantkw_y2000_size1000_kwLimit200')
 
+def extract_all_keywords() :
+    corpus = get_patent_data(-1,-1)
+    [p_kw_dico,kw_p_dico] = construct_occurrence_dico(corpus)
+    export_kw_dico('../../data/processed/keywords.sqlite3',p_kw_dico)
 
 def test_dico():
-    construct_occurrence_dico(2000,1000)
+    # with export
+    corpus = get_patent_data(2007,1000)
+    [p_kw_dico,kw_p_dico] = construct_occurrence_dico(corpus)
+    export_kw_dico('../../data/processed/keywords_y2007_1000.sqlite3',p_kw_dico)
 
 def test_db():
     for patent in get_patent_data(2000,100):
@@ -42,24 +50,46 @@ def test_kw():
 
 
 # tests for a bootstrap technique to avoid subcorpus relevance bias
-def bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bSize):
+def bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bootstrapSize):
     N = len(corpus)
 
+    # compute occurence_dicos
+    #  TODO : store results in db or file to not recompute them at each step.
+    occurence_dicos = construct_occurrence_dico(corpus)
+
     # generate bSize extractions
-    #extractions =
+    #   -> random subset of 1:N of size subCorpusSize
+    # TODO
+    extractions = []
 
+    mean_termhoods = dict() # mean termhoods progressively updated
+    p_kw_dico = dict() # patent -> kw dico : cumulated on repetitions. if a kw is relevant a few time, counted as 0 in mean.
     # for each extraction, extract subcorpus and get relevant kws
+    # for each patent, mean termhoods computed cumulatively, ; recompute relevant keywords later
+    for extraction in extractions :
[…]

### 2015-11-29 Models/TextProcessing/test.py
all_kw_extract

@@ -9,9 +9,9 @@ import nltk,sqlite3,time,locale,datetime,operator,math
 # tests
 
 def test():
-    test_dico()
+    #test_dico()
     #import_kw_dico('../../data/processed/keywords.sqlite3')
-
+    extract_all_keywords()
 
 def test_termhood_extract():
     corpus = get_patent_data(2000,3000)
@@ -24,13 +24,13 @@ def test_termhood_extract():
 def extract_all_keywords() :
     corpus = get_patent_data(-1,-1)
     [p_kw_dico,kw_p_dico] = construct_occurrence_dico(corpus)
-    export_kw_dico('../../data/processed/keywords.sqlite3',p_kw_dico)
+    export_kw_dico('../../Data/processed/keywords.sqlite3',p_kw_dico)
 
 def test_dico():
     # with export
     corpus = get_patent_data(2007,1000)
     [p_kw_dico,kw_p_dico] = construct_occurrence_dico(corpus)
-    export_kw_dico('../../data/processed/keywords_y2007_1000.sqlite3',p_kw_dico)
+    export_kw_dico('../../Data/processed/keywords_y2007_1000.sqlite3',p_kw_dico)
 
 def test_db():
     for patent in get_patent_data(2000,100):
@@ -279,7 +279,8 @@ def get_patent_data(year,limit) :
 
     #cursor.execute('SELECT patdesc.patent,patent.patent FROM patent,patdesc WHERE patent.patent=patdesc.patent LIMIT 10;')
     # retrieve records
-    query='SELECT patent.patent,title,abstract,GYear FROM patdesc,patent WHERE patdesc.patent = patent.patent AND abstract!=\'\' AND GYear = '+str(year)
+    query='SELECT patent.patent,title,abstract,GYear FROM patdesc,patent WHERE patdesc.patent = patent.patent AND abstract!=\'\''
+    if year != -1 : query = query +' AND GYear = '+str(year)
     if limit != -1 :
         query = query+' LIMIT '+str(limit)+";"
     else :

### 2015-11-30 Docs/WorkingPapers/methods.tex
kw_export_ok
test_parallel_procesisng

@@
 More precisely, let $n = \left|\mathcal{P}\right|$ the number of patents.
-classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes.
+Classes are constructed in $O(n)$ from file giving patents classes, and then sorted in $\Theta (\sum_k{\left|\mathcal{C}_k\right|\cdot \log{\left|\mathcal{C}_k\right|}})$ with $\mathcal{C}_k$ the classes.
 The number of classes $K$ being fixed, it simplifies into a $O(n\log{n})$.
+This sorting allows to compute overlaps and differences between classes in linear time by a direct comparison.
+To compute higher order overlaps, we have an exponential complexity in the overlap order $o$ (in $O(K^o)$) but order three appears experimentally to have cardinals smaller enough for a reasonable one-to-one technological distance computation.
+A class partition strategy allows to know any distance : if $o (\mathcal{C}_i,\mathcal{C}_j)$ is first order overlap between classes $i$ and $j$ and $o_2 (\mathcal{C}_i,\mathcal{C}_j,\mathcal{C}_k)$ second order overlap (i.e.
+$o(\mathcal{C}_k,o(\mathcal{C}_i,\mathcal{C}_j))$, then for any class $i$,
+\begin{itemize}
+\item between any $p\in \mathcal{C}_i \\ \cup_{k}{o(i,k)}$, proximity is necessarily 1 (one class in common for one-class patents)
+\item for any $j \neq i$
+\end{itemize}
 

### 2015-11-30 Models/Techno/overlap.R

@@ -15,7 +15,8 @@ for(i in 1:nrow(overlap)){
   #}
 }
 
-
+write.table(x=cbind(0:832,rbind(1:832,overlap)),
+            file='overlap_adjacency.csv',row.names=FALSE,col.names=FALSE,sep=";")
 
 #########
 ##
@@ -42,6 +43,21 @@ plot(sort(classSizes,decreasing=TRUE))
 
 ###
 # nw of non trivial techno distances
+
+d <- read.csv('distances_2nd_order_extended.csv',sep=';',header=FALSE)
+summary(d)
+hist(d[,6],breaks=50)
+
+# try a 'by-hand' hclust to avoid computing dist matrix
+
+# first construct a table to get distances quickly
+distances=list()
+for(i in 1:nrow(d)){
+  distances[paste0(d[i,1],d[i,2])]=d[i,6]
+  distances[paste0(d[i,2],d[i,1])]=d[i,6]
+  if(i %% 10000 == 0 ){show(i)}
+}
+# very slow
 
 
 

### 2015-11-30 Models/Test/parallel.py

@@ -1,0 +1,17 @@
+
+# test python multiprocessing
+
+from multiprocessing import Pool
+import math,time
+
+def f(x):
+    return(math.sqrt(x)*math.cos(x))
+
+start = time.time()
+
+pool = Pool(4)
+#print(pool.map(f,range(1000000)))
+res = map(f,range(100000000))
+#res = pool.map(f,range(10000000))
+
+print('Ellapsed Time : '+str(time.time() - start))

### 2016-01-25 Models/TextProcessing/test.py
res_bootstrap_100

@@ -49,11 +49,11 @@ def test_kw():
 
 
 def test_bootstrap():
-    year = 2000
-    N = 10000
-    kwLimit=1000
-    subCorpusSize=1000
-    bootstrapSize=10
+    year = -1
+    N = -1
+    kwLimit=10000
+    subCorpusSize=50000
+    bootstrapSize=100
     corpus = get_patent_data(year,N,False)
     [relevantkw,relevant_dico] = bootstrap_subcorpuses(corpus,1000,subCorpusSize,bootstrapSize)
     export_dico_csv(relevant_dico,'res/bootstrap_relevantDico_y'+str(year)+'_size'+str(N)+'_kwLimit'+str(kwLimit)+'_subCorpusSize'+str(subCorpusSize)+'_bootstrapSize'+str(bootstrapSize))

### 2016-01-25 Docs/Proposal/patents.tex

@@
 The aim of this project is to investigate the nature and extent of this information, by the mining of regular patterns in features that should be established.
-We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, datamining techniques.
-Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and be able to systematically differentiate innovatives from imitating patents.
+We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, data-mining techniques.
+Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and be able to systematically differentiate innovative from imitating patents.
 \end{abstract}
@@
 
-The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including datamining and network analysis~\cite{newman2010networks} has shed a new light on the approach.
+The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including data-mining and network analysis~\cite{newman2010networks} has shed a new light on the approach.
 With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation.
@@
 \begin{itemize}
-\item Project definition, litterature review - AB, JR, PA - ETA 10h
+\item Project definition, literature review - AB, JR, PA - ETA 10h
 \item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h

### 2016-01-25 Docs/WorkingPapers/methods.tex

@@
 
-Text processing operations are implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{} % cite nltk
-which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
+Text processing operations are implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{bird2006nltk} which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
 Source code is openly available on the repository of the project\footnote{at \texttt{url}}.
@@
 
-\paragraph{Bootstrap on random subcorpuses for relevance estimation}
+\paragraph{Bootstrap on random sub-corpuses for relevance estimation}
 
@@
 Let $K_w$ the maximal number of relevant keywords per patent.
-If $N$ is the total number of relevant keywords extracted
-The heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus.
-More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the termhood score as
+If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus.
+More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as
 \[
@@
 
+Let $X = \{x_1,\ldots ,x_N\}$ a discrete set and $X_1,\ldots ,X_K \in \mathcal{P}(X)$.
+We write $X_k = \{x_1^{(k)},\ldots ,x_{N_k}^{(k)}\}$.
+Exact probability distributions within sets are determined directly in $O(\sum_{k=1}^{K}{N_k})$.
+
 \paragraph{Possible Features}
+
+\textit{From proposal : }
+
+\begin{itemize}
+\item Citation relative centrality regarding technological or semantic classes : given a partition of $\mathcal{P}$ represented by a classification function $C$ (constructed for example by clustering or community detection within technological or semantic networks), a vector feature is for patent $i$
+\[
+\left(\frac{\sum_{j\in c}Cit^{out}(i,j)}{\sum_{j\in c}Cit^{in}(i,j)}\right)_{c\in C(\mathcal{P})}
+\]
+\item Dynamic evolution of classification vector : if $C_t$ is stratified over successive time periods indexed by time $t$, either $\Delta \vec{C}_t (i)$ if $\vec{C}_t$ is a vector of probabilities to belong to each class (in case of a Bayesian approach), or $\Delta (C_t(j))_{Cit(i,j,t)\neq 0}$ in case of a deterministic approach, could both be interesting features.
+\item Deviation from the expected classes given position in other layers of the hypernetwork (it would need explorations if these conditional probabilities first can be well estimated, then if they contain relevant information).
+\end{itemize}
 

### 2016-01-25 Models/TextProcessing/test.py
rm_irrelevant_res

@@ -51,11 +51,11 @@ def test_kw():
 def test_bootstrap():
     year = -1
     N = -1
-    kwLimit=10000
-    subCorpusSize=50000
+    kwLimit=50000
+    subCorpusSize=100000
     bootstrapSize=100
     corpus = get_patent_data(year,N,False)
-    [relevantkw,relevant_dico] = bootstrap_subcorpuses(corpus,1000,subCorpusSize,bootstrapSize)
+    [relevantkw,relevant_dico] = bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bootstrapSize)
     export_dico_csv(relevant_dico,'res/bootstrap_relevantDico_y'+str(year)+'_size'+str(N)+'_kwLimit'+str(kwLimit)+'_subCorpusSize'+str(subCorpusSize)+'_bootstrapSize'+str(bootstrapSize))
     export_list(relevantkw,'res/relevantkw_y'+str(year)+'_size'+str(N)+'_kwLimit'+str(kwLimit)+'_subCorpusSize'+str(subCorpusSize)+'_bootstrapSize'+str(bootstrapSize))
 

### 2016-02-08 Models/Techno/TechnoClasses/src/patents/Citation.java
originalityu

@@ -1,0 +1,39 @@
+/**
+ * 
+ */
+package patents;
+
+/**
+ * @author Raimbault Juste <br/> <a href="mailto:juste.raimbault@polytechnique.edu">juste.raimbault@polytechnique.edu</a>
+ *
+ */
+public class Citation {
+	
+	public Patent citing;
+	
+	public Patent cited;
+	
+	public long date;
+	
+	// simple constructor is ok, no need to do hashconsing on citation structure
+	
+	public Citation(Patent citi,Patent cite,long d){
+		citing=citi;cited=cite;date=d;
+	}
+	
+	public Citation(String citi,String cite,long d){
+		citing=Patent.construct(citi);cited=Patent.construct(cite);date=d;
+	}
+	
+	@Override
+	public int hashCode(){
+		return(citing.hashCode()+cited.hashCode());
+	}
+	
+	@Override
+	public boolean equals(Object o){
+		return (o instanceof Citation)&&(((Citation)o).citing.equals(citing))&&(((Citation)o).cited.equals(cited));
+	}
+	
+	
+}

### 2016-02-08 Models/Techno/TechnoClasses/src/patents/CitationNetwork.java

@@ -1,0 +1,56 @@
+/**
+ * 
+ */
+package patents;
+
+import java.text.DateFormat;
+import java.text.SimpleDateFormat;
+import java.util.HashMap;
+import java.util.LinkedList;
+
+/**
+ * @author Raimbault Juste <br/> <a href="mailto:juste.raimbault@polytechnique.edu">juste.raimbault@polytechnique.edu</a>
+ *
+ */
+public class CitationNetwork {
+
+	
+	
+	public static void computeOriginalities(String classFile,String patentFile,String dateType,String[] citationFiles,String outDir,int sizeThreshold){
+		HashMap<String,LinkedList<Patent>> classes = Classes.constructTimelySortedClasses(classFile,patentFile,dateType);
+		for(String citationFile:citationFiles){
+		   fillCitationNetwork(citationFile);
+		}
+		for(String className:classes.keySet()){
+			if(classes.get(className).size()>sizeThreshold){
+				LinkedList<String[]> c = new LinkedList<String[]>();
+				String[] header = {"id","ts","originality"};
+				c.add(header);
+				for(Patent p:classes.get(className)){
+					String[] d = {p.id,p.dates.get(dateType).toString(),new Double(p.originality()).toString()};c.add(d);
+				}
+				Writer.writeCSV(c, outDir+"/"+className);
+			}
+		}
+		
+	}
+	
+	/**
+	 * Fill citation network from a csv citation file.
+	 * 
+	 * @param citationFile
+	 */
+	public static void fillCitationNetwork(String citationFile){
+		System.out.println("filling it network from file "+citationFile);
+		LinkedList<String[]> data = Reader.readCSV(citationFile, ",");
+		for(String[] row:data){
+			String cited = row[0];String citing = row[5];
+			DateFormat dfm = new SimpleDateFormat("yyyy-MM-dd");
+			long date = 0;try{date=dfm.parse(row[1]).getTime();}catch(Exception e){}
+			//Citation citation = new Citation(citing,cited,date);
+			Patent pcited = Patent.construct(cited);Patent pciting = Patent.construct(citing);
+			Citation citation = new Citation(pciting,pcited,date);
+			pciting.cited.add(citation);pcited.cited.add(citation);
+		}
+	}
+}

### 2016-02-08 Models/Techno/TechnoClasses/src/patents/Main.java

@@ -26,8 +26,11 @@ public class Main {
 		//computeDistanceOnOverlap(sortedClasses);
 		//computeSecondOrderOverlaps(sortedClasses);
 		//Distances.computeDistancesOnSecondOrderOverlaps(sortedClasses);
-		Classes.exportClassesTimeSeries("../../../Data/raw/classesTechno/class.csv",
-				"../../../Data/raw/patent/patent.csv", "AppDate", 1000, "res/sizes_appdate");
+		//Classes.exportClassesTimeSeries("../../../Data/raw/classesTechno/class.csv",
+		//		"../../../Data/raw/patent/patent.csv", "AppDate", 1000, "res/sizes_appdate");
+		String[] citFiles = {"../../../Data/raw/citation/citation75_99.csv","../../../Data/raw/citation/citation00_10.csv"};
+		CitationNetwork.computeOriginalities("../../../Data/raw/classesTechno/class.csv", 
+				"../../../Data/raw/patent/patent.csv", "AppDate", citFiles, "res/originalities_appdate", 1000);
 		
 		
 	}

### 2016-02-08 Models/Techno/TechnoClasses/src/patents/Reader.java

@@ -78,4 +78,19 @@ public class Reader {
 		return res;
 	}
 	
+	
+	public static LinkedList<String[]> readCSV(String file,String delimiter){
+		LinkedList<String[]> res = new LinkedList<String[]>();
+		try{
+		   BufferedReader r = new BufferedReader(new FileReader(new File(file)));
+		   String currentLine = r.readLine();
+		   while(currentLine != null){
+			   res.add(currentLine.split(delimiter));
+			   currentLine=r.readLine();
+		   }
+		}catch(Exception e){e.printStackTrace();}
+		return(res);
+	}
+	
+	
 }

### 2016-02-08 Docs/WorkingPapers/methods.tex
Organisation::timeLog_tableur

@@
 \begin{itemize}
-\item between any $p\in \mathcal{C}_i \\ \cup_{k}{o(i,k)}$, proximity is necessarily 1 (one class in common for one-class patents)
-\item for any $j \neq i$
+\item between any $p\in \mathcal{C}_i - \cup_{k}{o(\mathcal{C}_i,\mathcal{C}_k)}$, proximity is necessarily 1 (one class in common for one-class patents)
+\item for any $j \neq i$, let $\mathcal{S}_{i,j} = o(\mathcal{C}_i,\mathcal{C}_j) - \cup_{k\neq i,j} o(\mathcal{C}_i,\mathcal{C}_j,\mathcal{C}_k)$.
+Then distance within $\mathcal{S}_{i,j}$ and with non-overlapping part of the classes is straightforward computed as constant among patents
+\item Remaining patents within second order overlap are few enough for a reasonable computation of their respective distances.
 \end{itemize}
+
+\paragraph{Inter-class network}
+
+The definition of a time-dependent relation between classes as size of overlap normalized by classes sizes, by $w_{i\rightarrow j} = \frac{\left| o(\mathcal{C}_i,\mathcal{C}_j) \right|}{\left| \mathcal{C}_i\right|}$, similar to the technological distance between patents with the distinction that it is here not symmetric and captures the part of class $i$ in interaction with class $j$, allows to build an inter-class network.
+The evolution of network structure over time may contain useful information and reinforce e.g.
+a typology of classes that one can obtain by classifying temporal class trajectories.
 
@@
 Let $K_w$ the maximal number of relevant keywords per patent.
-If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus.
+If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $k\cdot N$ keywords on the whole corpus (and take a fixed value $k=4)$, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of cooccurrences of the stem, compared to an uniform distribution within the whole corpus.
 More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as
@@
 
-Let $X = \{x_1,\ldots ,x_N\}$ a discrete set and $X_1,\ldots ,X_K \in \mathcal{P}(X)$.
+One issue arising when working with large corpuses is the square complexity for determining cooccurrences, that can be simplified at best to the sum of squared sizes of pre-relevant keywords for each patent.
+
+%Let $X = \{x_1,\ldots ,x_N\}$ a discrete set and $X_1,\ldots ,X_K \in \mathcal{P}(X)$.
 We write $X_k = \{x_1^{(k)},\ldots ,x_{N_k}^{(k)}\}$.

### 2016-02-08 Models/TextProcessing/bootstrap.py
semantic::bootstrap_ready

@@ -3,11 +3,6 @@ import utils,io,keywords
 
 
 
-def run_bootstrap(kwLimit,subCorpusSize,bootstrapSize):
-    corpus = io.get_patent_data(-1,-1,False)
-    bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bootstrapSize)
-
-
 
 
 def test_bootstrap():
@@ -26,6 +21,70 @@ def test_bootstrap():
 
 
 
+# creates databases for bootstrap run
+def init_bootstrap(res_folder):
+    conn = utils.configure_sqlite(res_folder+'/bootstrap.sqlite3')
+    c = conn.cursor()
+    c.execute('CREATE TABLE relevant (keyword text, cumtermhood real, ids text);')
+    c.execute('CREATE TABLE params (key text, value real);')
+    c.execute('CREATE TABLE dico (id text, keywords text);')
+    conn.commit()
+    conn.close()
+
+
+##
+#   assumed to be run in //
+#     - run by packet for intermediate filtering -
+def run_bootstrap(res_folder,kwLimit,subCorpusSize,bootstrapSize) :
+    corpus = io.get_patent_data(-1,-1,False)
+    occurence_dicos = io.import_kw_dico('data/keywords.sqlite3')
+    database = res_folder+'/bootstrap.sqlite3'
+    #while True :
+    for i in range(10):
+        [relevantkw,relevant_dico,allkw] = bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrapSize)
+        # update bases iteratively (ok for concurrency ?)
+        for kw in relevantkw.keys():
+            update_kw_tm(kw,relevantkw[kw],database)
+        for i in relevant_dico.keys():
+            update_kw_dico(i,relevant_dico[i],database)
+
+
+def update_kw_tm(kw,incr,database):
+    prev = utils.fetchone_sqlite('SELECT cumtermhood,ids FROM relevant WHERE keyword=\''+kw+'\';',database)
+    t = 0
+    ids=''
+    if len(prev > 0):
+        t = prev[0][0]
+        ids = prev[0][1]
+    t = t + incr
+    # insert
+    utils.insert_sqlite('INSERT INTO cumtermhood VALUES (\''+kw+'\','+str(t)+',\''+ids+'\');',database)
+
+
+def update_kw_dico(i,kwlist,database):
+    # update id -> kws dico
[…]

### 2016-02-08 Models/TextProcessing/utils.py

@@ -19,3 +19,26 @@ def read_csv(file,delimiter):
     f=open(file,'r')
     lines = f.readlines()
     return([s.split(delimiter) for s in lines])
+
+
+# returns sqlite connection
+def configure_sqlite(database):
+    return(sqlite3.connect(database))
+
+
+def fetchone_sqlite(query,database):
+    conn = configure_sqlite(database)
+    cursor = conn.cursor()
+    cursor.execute(query)
+    res = cursor.fetchone()
+    conn.commit()
+    conn.close()
+    return(res)
+
+
+def insert_sqlite(query,database):
+    conn = configure_sqlite(database)
+    cursor = conn.cursor()
+    cursor.execute(query)
+    conn.commit()
+    conn.close()

### 2016-02-08 Models/TextProcessing/bootstrap.py
running

@@ -1,5 +1,5 @@
 import numpy
-import utils,io,keywords
+import utils,data,keywords
 
 
 
@@ -36,8 +36,8 @@ def init_bootstrap(res_folder):
 #   assumed to be run in //
 #     - run by packet for intermediate filtering -
 def run_bootstrap(res_folder,kwLimit,subCorpusSize,bootstrapSize) :
-    corpus = io.get_patent_data(-1,-1,False)
-    occurence_dicos = io.import_kw_dico('data/keywords.sqlite3')
+    corpus = data.get_patent_data(-1,-1,False)
+    occurence_dicos = data.import_kw_dico('data/keywords.sqlite3')
     database = res_folder+'/bootstrap.sqlite3'
     #while True :
     for i in range(10):
@@ -106,7 +106,7 @@ def bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bootstrapSize):
 
     for eind in range(len(extractions)) :
         print("bootstrap : run "+str(eind))
-	    extraction = extractions[eind]
+	extraction = extractions[eind]
         subcorpus = [corpus[i] for i in extraction]
         [keywords,p_kw_local_dico] = keywords.extract_relevant_keywords(subcorpus,kwLimit,occurence_dicos)
 

### 2016-02-08 Models/TextProcessing/keywords.py

@@ -1,5 +1,5 @@
 import nltk,operator
-import io,keywords,utils
+import data,keywords,utils
 
 
 
@@ -80,7 +80,7 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     for i in range(len(coocs)):
         s = 0;
         for j in range(len(coocs)):
-            if j != i : s = s + ()(coocs[i][j]-colSums[i]*colSums[j])*(coocs[i][j]-colSums[i]*colSums[j]))/(colSums[i]*colSums[j])
+            if j != i : s = s + ((coocs[i][j]-colSums[i]*colSums[j])*(coocs[i][j]-colSums[i]*colSums[j]))/(colSums[i]*colSums[j])
         termhoods[i]=s
 
     # sort and filter on termhoods

### 2016-02-08 Models/TextProcessing/main.py

@@ -9,8 +9,8 @@ def run():
     #extract_all_keywords()
     #termhood_extraction()
     #bootstrap.test_bootstrap()
-    bootstrap.init_bootstrap('test')
-    bootstrap.run_bootstrap('test',100,100,100)
+    #bootstrap.init_bootstrap('bootstrap/test')
+    bootstrap.run_bootstrap('bootstrap/test',100,100,100)
 
 
 def main():

### 2016-02-08 Models/TextProcessing/utils.py

@@ -1,4 +1,4 @@
-import datetime
+import datetime,sqlite3
 
 # Exports a dictionary to a generalized csv, under the form key;val1;val2;...;valN
 def export_dico_csv(dico,fileprefix):

### 2016-02-08 Models/TextProcessing/bootstrap.py
run_zeb

@@ -90,7 +90,7 @@ def update_kw_dico(i,kwlist,database):
 
 
 # tests for a bootstrap technique to avoid subcorpus relevance bias
-def bootstrap_subcorpuses(corpus,kwLimit,subCorpusSize,bootstrapSize):
+def bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrapSize):
     N = len(corpus)
 
     print('Bootstrapping on corpus of size '+str(N))

### 2016-02-08 Models/TextProcessing/data.py

@@ -49,7 +49,7 @@ def import_kw_dico(database) :
 
     for row in res :
         patent_id = row[0].encode('ascii','ignore')
-        print(patent_id)
+        #print(patent_id)
         keywords = row[1].encode('ascii','ignore').split(';')
         p_kw_dico[patent_id] = keywords
         for kw in keywords :

### 2016-02-08 Models/TextProcessing/main.py

@@ -9,7 +9,7 @@ def run():
     #extract_all_keywords()
     #termhood_extraction()
     #bootstrap.test_bootstrap()
-    #bootstrap.init_bootstrap('bootstrap/test')
+    bootstrap.init_bootstrap('bootstrap/test')
     bootstrap.run_bootstrap('bootstrap/test',100,100,100)
 
 

### 2016-02-08 Models/TextProcessing/bootstrap.py
parallel_run_sh_script

@@ -108,12 +108,12 @@ def bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrap
         print("bootstrap : run "+str(eind))
 	extraction = extractions[eind]
         subcorpus = [corpus[i] for i in extraction]
-        [keywords,p_kw_local_dico] = keywords.extract_relevant_keywords(subcorpus,kwLimit,occurence_dicos)
+        [kws,p_kw_local_dico] = keywords.extract_relevant_keywords(subcorpus,kwLimit,occurence_dicos)
 
         # add termhoods
-        for kw in keywords.keys() :
+        for kw in kws.keys() :
             if kw not in mean_termhoods : mean_termhoods[kw] = 0
-            mean_termhoods[kw] = mean_termhoods[kw] + keywords[kw]
+            mean_termhoods[kw] = mean_termhoods[kw] + kws[kw]
 
         # update p->kw dico
         for p in p_kw_local_dico.keys() :

### 2016-02-08 Models/TextProcessing/keywords.py

@@ -1,4 +1,4 @@
-import nltk,operator
+import nltk,operator,math
 import data,keywords,utils
 
 
@@ -123,7 +123,7 @@ def extract_sub_dicos(corpus,occurence_dicos) :
     kw_p_dico = dict()
 
     for patent in corpus :
-        patent_id = io.get_patent_id(patent)
+        patent_id = data.get_patent_id(patent)
         keywords = []
 	if patent_id in p_kw_dico_all : keywords = p_kw_dico_all[patent_id]
         p_kw_dico[patent_id] = keywords
@@ -147,7 +147,7 @@ def construct_occurrence_dico(data) :
     p_kw_dico = dict()
     kw_p_dico = dict()
     for patent in data :
-        patent_id = io.get_patent_id(patent)
+        patent_id = data.get_patent_id(patent)
         keywords = extract_keywords(patent[1]+". "+patent[2],patent_id)
         #print(keywords)
 

### 2016-02-08 Models/TextProcessing/main.py

@@ -9,7 +9,7 @@ def run():
     #extract_all_keywords()
     #termhood_extraction()
     #bootstrap.test_bootstrap()
-    bootstrap.init_bootstrap('bootstrap/test')
+    #bootstrap.init_bootstrap('bootstrap/test')
     bootstrap.run_bootstrap('bootstrap/test',100,100,100)
 
 

### 2016-02-08 Models/TextProcessing/bootstrap.py
fixed_db_insertion

@@ -40,44 +40,62 @@ def run_bootstrap(res_folder,kwLimit,subCorpusSize,bootstrapSize) :
     occurence_dicos = data.import_kw_dico('data/keywords.sqlite3')
     database = res_folder+'/bootstrap.sqlite3'
     #while True :
-    for i in range(10):
+    for i in range(2):
         [relevantkw,relevant_dico,allkw] = bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrapSize)
         # update bases iteratively (ok for concurrency ?)
         for kw in relevantkw.keys():
             update_kw_tm(kw,relevantkw[kw],database)
         for i in relevant_dico.keys():
             update_kw_dico(i,relevant_dico[i],database)
-
+        update_count(bootstrapSize,database)
 
 def update_kw_tm(kw,incr,database):
     prev = utils.fetchone_sqlite('SELECT cumtermhood,ids FROM relevant WHERE keyword=\''+kw+'\';',database)
     t = 0
     ids=''
-    if len(prev > 0):
-        t = prev[0][0]
-        ids = prev[0][1]
-    t = t + incr
-    # insert
-    utils.insert_sqlite('INSERT INTO cumtermhood VALUES (\''+kw+'\','+str(t)+',\''+ids+'\');',database)
+    #print(prev)
+    if prev is not None:
+        t = prev[0]+incr
+        ids = prev[1]
+        utils.insert_sqlite('UPDATE relevant SET keyword=\''+kw+'\',cumtermhood='+str(t)+',ids=\''+ids+'\' WHERE keyword=\''+kw+'\';',database)
+    else :
+        # insert
+        utils.insert_sqlite('INSERT INTO relevant VALUES (\''+kw+'\','+str(incr)+',\'\');',database)
+
+
 
 
 def update_kw_dico(i,kwlist,database):
     # update id -> kws dico
-    prev = utils.fetchone_sqlite('SELECT keywords FROM relevant WHERE id=\''+i+'\';',database)
+    prev = utils.fetchone_sqlite('SELECT keywords FROM dico WHERE id=\''+i+'\';',database)
     kws = set()
-    if len(prev > 0):
-        kws = set(prev[0][0].split(";"))
+    if prev is not None: kws = set(prev[0].split(";"))
     for kw in kwlist :
         kws.add(kw)
[…]

### 2016-02-08 Models/TextProcessing/main.py

@@ -10,7 +10,8 @@ def run():
     #termhood_extraction()
     #bootstrap.test_bootstrap()
     bootstrap.init_bootstrap('bootstrap/test')
-    bootstrap.run_bootstrap('bootstrap/test',100,100,100)
+    bootstrap.run_bootstrap('bootstrap/test',10,10,2)
+    #bootstrap.run_bootstrap('bootstrap/run_kw1000_csize2000_b20',1000,2000,20)
 
 
 def main():

### 2016-02-09 Models/TextProcessing/bootstrap.py
fixed_b_return

@@ -122,11 +122,15 @@ def bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrap
     # for each extraction, extract subcorpus and get relevant kws
     # for each patent, mean termhoods computed cumulatively, ; recompute relevant keywords later
 
+    allkw = []
+
     for eind in range(len(extractions)) :
         print("bootstrap : run "+str(eind))
-	extraction = extractions[eind]
+	    extraction = extractions[eind]
         subcorpus = [corpus[i] for i in extraction]
         [kws,p_kw_local_dico] = keywords.extract_relevant_keywords(subcorpus,kwLimit,occurence_dicos)
+
+        allkw.append(kws)
 
         # add termhoods
         for kw in kws.keys() :
@@ -137,7 +141,8 @@ def bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrap
         for p in p_kw_local_dico.keys() :
             if p not in p_kw_dico : p_kw_dico[p] = set()
             for kw in p_kw_local_dico[p] :
-		p_kw_dico[p].add(kw)
+		        p_kw_dico[p].add(kw)
 
-    # sort on termhoods (no need to normalize) adn returns
-    return(extract_from_termhood(mean_termhoods,p_kw_dico,kwLimit))
+    res = kwFunctions.extract_from_termhood(mean_termhoods,p_kw_dico,kwLimit)
+    res.append(allkw)
+    return(res)

### 2016-02-09 Models/TextProcessing/bootstrap.py
remote

@@ -93,9 +93,9 @@ def update_count(bootstrapSize,database):
     prev = utils.fetchone_sqlite('SELECT value FROM params WHERE key=\'count\'',database)
     if prev is not None:
         t=prev[0]+bootstrapSize
-	    utils.insert_sqlite('UPDATE params SET value='+str(t)+' WHERE key=\'count\';',database)
+	utils.insert_sqlite('UPDATE params SET value='+str(t)+' WHERE key=\'count\';',database)
     else :
-	    utils.insert_sqlite('INSERT INTO params VALUES (\'count\','+str(bootstrapSize)+')',database)
+	utils.insert_sqlite('INSERT INTO params VALUES (\'count\','+str(bootstrapSize)+')',database)
 
 
 
@@ -140,4 +140,4 @@ def bootstrap_subcorpuses(corpus,occurence_dicos,kwLimit,subCorpusSize,bootstrap
 		p_kw_dico[p].add(kw)
 
     # sort on termhoods (no need to normalize) adn returns
-    return(extract_from_termhood(mean_termhoods,p_kw_dico,kwLimit))
+    return(keywords.extract_from_termhood(mean_termhoods,p_kw_dico,kwLimit))

### 2016-04-20 Models/DataCollection/dataExport.py
kw_extrac_finished

@@ -25,7 +25,7 @@ def export_redbook_as_csv(fields,file) :
 
     for row in data :
         print row
-	    for i in range(len(fields)) :
+	for i in range(len(fields)) :
             if fields[i] in row : writer.write(row[fields[i]])
             if i < len(fields)-1:
                 writer.write(";")
@@ -35,7 +35,7 @@ def export_redbook_as_csv(fields,file) :
 def export_classes_as_csv(file,max_year):
     mongo = pymongo.MongoClient('localhost', 29019)
     database = mongo['redbook']
-    data = database.raw.find({"id":{"$regex":"[0-9]*"},"year":{"$lt":max_year}},{"id":1,"classes":1})
+    data = database.raw.find({"id":{"$regex":r'^[0-9]'},"year":{"$lt":max_year}},{"id":1,"classes":1})
 
     writer = open(file,'w')
 
@@ -61,4 +61,4 @@ def export_classes_as_csv(file,max_year):
 
 #export_redbook_as_csv(['id','grant_date','app_date'],'export/redbook.csv')
 
-export_classes_as_csv('export/classes_76-01.csv',2002)
+export_classes_as_csv('export/classes_76-01.csv',"2002")

### 2016-04-20 Models/DataCollection/parser.py

@@ -83,7 +83,7 @@ def read_dat_as_raw(f) :
     currentLine = r.readline()
     currentPatent = []
     while currentLine != '':
-	currentLine = currentLine.replace('\n','').rstrip(' ')
+	currentLine = currentLine.replace('\n','').replace('\r','').rstrip(' ')
         if currentLine.startswith('PATN'):
             res.append(currentPatent)
             currentPatent = []
@@ -151,7 +151,7 @@ def split_field(row) :
     if len(s)>1 :
         return([s[0],s[1].lstrip()])
     else :
-        return(s[0],'') # returning empty string here causes exception when ABST is empty : should return {} ?
+        return(s[0],{}) # returning empty string here causes exception when ABST is empty : should return {} ?
 
 
 def append_dico(dico,key,value):

### 2016-04-20 Models/TextProcessing/data.py

@@ -107,7 +107,13 @@ def get_patent_data(year,limit):
     res=[]
     for row in data :
         #print row
-	res.append([row['id'],row['title'],row['abstract']])
+	i=""
+	if 'id' in row : i = row['id']
+	title = ""
+	if 'title' in row : title = row['title']
+	abstract = ""
+	if 'abstract' in row : abstract = row['abstract']
+	res.append([i,title,abstract])
     return(res)
 
 

### 2016-04-20 Docs/Papers/Technical/local/paper.tex
run_full_corpus_relevant_all_years

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{An Hypernetwork Approach to Measure Technological Innovation - Submission to PLOS Journals}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Antonin Bergeaud\textsuperscript{1,\Yinyang},
Yoann Potiron\textsuperscript{2,\Yinyang},
Juste Raimbault\textsuperscript{3,\Yinyang}
\\
\bigskip
\bf{1} Department of Economics, London School of Economics, London, UK
\\
\bf{2} Department of Statistics, University of Chicago, Chicago, US
\\
\bf{3} UMR 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* le.corresponding@polytechnique.edu

\end{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the abstract below 300 words
\section*{Abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author Summary}

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}

The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including data-mining and network analysis~\cite{newman2010networks} has shed a new light on the approach. With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation. As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g. in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.

A consequent amount of research already proposed to use semantic networks to study technological domains. One of the first works to enhance the approach was~\cite{yoon2004text}, where the idea of visualizing keywords network was introduced and illustrated on a small technological domain. Semantic analysis has already proved its efficiency in various fields, such as~\cite{choi2014patent,fattori2003text} for technology studies, or~\cite{2015arXiv151003797G} in political science for example. We will also be interested in measures based on technological classification, as in~\cite{Youn:2015fk} where the study of the distribution of classes within patents leads to confirm the combinatory nature of the innovation process. Advanced citation-based measures have been proposed in order to gain an order of information extracted from the citation network~\cite{2015arXiv150907285A}, but we will stay to rather simple indicators concerning this network as we will cross it with other type of data. Concerning dynamic analysis, models of citation processes have been proposed and fit to data such as in~\cite{valverde2007topology}, and depending on temporal patterns we observe on features, we may propose to use dynamic models for network evolution.

%%%%%%%%%%%%%%%%%%%%%
% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

\subsection*{Raw Data}

% cite and describe datasets

\subsection*{Semantic Network Construction}

We first assign to a patent $p\in \mathcal{P}$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted following a similar procedure to the one detailed in~\cite{chavalarias2013phylomemetic} :
\begin{itemize}
\item Text parsing and tokenizing.
\item Part-of-speech tagging, normalization.
\item Stem extraction and multi-stems constructions.
\item Relevant multi-stems filtering.
\end{itemize}

The semantic network is then constructed by co-occurrences analysis : nodes are keywords, i.e. $V=\bigcup_{p\in\mathcal{P}}K(p)$, and edges represent co-occurrences : $E = \{(k,k') | \exists p \textrm{ s.t. } k, k' \in K(p)\}$. This specification aims to capture semantic communities that do necessarily have a thematic meaning and that should correspond to a specific domain, field, technology or technique.

Text processing operations will be implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{nltk} which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations. Source code is openly available on the repository of the project\footnote{at \texttt{url}}. Steps one to three are directly done using built-in functions of the library. Step four needs a particular treatment that we propose as an extension of the original method for large corpuses, which is detailed in the following.

\paragraph{Bootstrap on random sub-corpuses for relevance estimation}

Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words. Let $K_w$ the maximal number of relevant keywords per patent. If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $k\cdot N$ keywords on the whole corpus (and take a fixed value $k=4)$, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of cooccurrences of the stem, compared to an uniform distribution within the whole corpus. More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as

\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
\]

One issue arising when working with large corpuses is the square complexity for determining cooccurrences, that can be simplified at best to the sum of squared sizes of pre-relevant keywords for each patent.

%% Convergence of bootstrap estimator / parameter values for estimation -> sensitivity analysis in supplementary information.

%% construction of semantic nw from cooccurrences
%  -> sensitivity analysis in supplementary info also

%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}

%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semantic Communities Dynamics}

% this section describes semantic communities reconstruction and their temporal dynamics

%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Layer Structure Comparison}

% comparison of techno classes / semantic communities / citation communities

\cite{iacovacci2015mesoscopic}

\subsection*{Unsupervised Data Mining}

\paragraph{Features}

\begin{itemize}
\item Citation relative centrality regarding technological or semantic classes : given a partition of $\mathcal{P}$ represented by a classification function $C$ (constructed for example by clustering or community detection within technological or semantic networks), a vector feature is for patent $i$
\[
\left(\frac{\sum_{j\in c}Cit^{out}(i,j)}{\sum_{j\in c}Cit^{in}(i,j)}\right)_{c\in C(\mathcal{P})}
\]
\item Dynamic evolution of classification vector : if $C_t$ is stratified over successive time periods indexed by time $t$, either $\Delta \vec{C}_t (i)$ if $\vec{C}_t$ is a vector of probabilities to belong to each class (in case of a Bayesian approach), or $\Delta (C_t(j))_{Cit(i,j,t)\neq 0}$ in case of a deterministic approach, could both be interesting features.
\item Deviation from the expected classes given position in other layers of the hypernetwork (it would need explorations if these conditional probabilities first can be well estimated, then if they contain relevant information).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}

%\section*{Supporting Information}
% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.

%\section*{Acknowledgments}

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%

\bibliographystyle{plos2015}
\bibliography{../../../Biblio/patents}

%%%%%%%%%%%%%%%%%%%%
%%  Templates
%%%%%%%%%%%%%%%%%%%%

% For figure citations, please use "Fig." instead of "Figure".
%\begin{figure}[h]
%\caption{{\bf Figure Title first bold sentence}
%Figure Caption}
%\label{fig1}
%\end{figure}

%
%
%
%\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
%\caption{
%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
%\begin{tabular}{|l|l|l|l|l|l|l|l|}
%\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
%\end{tabular}
%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
%\end{flushleft}
%\label{table1}
%\end{adjustwidth}
%\end{table}
%
%

%
%\subsection*{S1 Video}
%\label{S1_Video}
%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Text}
%\label{S1_Text}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Fig}
%\label{S1_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S2 Fig}
%\label{S2_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Table}
%\label{S1_Table}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%

%\begin{thebibliography}{10}
%\bibitem{bib1}
%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005

%\bibitem{bib2}
%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.

%\end{thebibliography}

\end{document}

### 2016-04-20 Models/TextProcessing/bootstrap.py

@@ -28,15 +28,15 @@ def test_bootstrap():
 
 def relevant_full_corpus(year,kwLimit):
     corpus = data.get_patent_data(year,-1,False)
-    occurence_dicos = data.import_kw_dico('data/keywords.sqlite3','data/patent.sqlite3',year)
+    occurence_dicos = data.import_kw_dico('patent','keywords',year)
     if len(corpus) > 0 and len(occurence_dicos) > 0 :
-        relevant = 'relevant_'+str(year)
-        mongo = pymongo.MongoClient('localhost', 29019)
-        database = mongo['relevant_full_'+str(kwLimit)]
+        relevant = 'relevant_'+str(year)+'_full_'+str(kwLimit)
+        mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
+        database = mongo['relevant']
         database[relevant].create_index('keyword')
-        [rel_kws,dico] = keywords.extract_relevant_keywords(corpus,kwLimit,occurence_dicos)
-        for kw in rel_kws.keys():
-            update_kw_tm(kw,rel_kws[kw],database,relevant)
+        #[rel_kws,dico] = keywords.extract_relevant_keywords(corpus,kwLimit,occurence_dicos)
+        #for kw in rel_kws.keys():
+        #    update_kw_tm(kw,rel_kws[kw],database,relevant)
 
 
 

### 2016-04-20 Models/TextProcessing/main.py

@@ -4,9 +4,11 @@ import sys
 
 def run():
     f=open(sys.argv[1])
+    kwLimit = 100000
     for year in f.readlines():
-	print year
-        keywords.extract_keywords_year(str(year).replace('\n',''))
+	    print year
+        bootstrap.relevant_full_corpus(year,kwLimit)
+        #keywords.extract_keywords_year(str(year).replace('\n',''))
     #year=2005;limit=-1;kwLimit=3000;subCorpusSize=20000;bootstrapSize=10;nruns=2
     #year=2005;
     #kwLimit=20000

### 2016-04-21 Models/TextProcessing/data.py
relevant_fail_memory

@@ -18,7 +18,8 @@ def test_db():
 ##
 #  export to mongo
 def export_kw_dico(database,collection,p_kw_dico,year):
-    mongo = pymongo.MongoClient('localhost', 29019)
+    #mongo = pymongo.MongoClient('localhost', 29019)
+    mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
     database = mongo[database]
     col = database[collection]
     col.create_index("id")
@@ -32,7 +33,8 @@ def export_kw_dico(database,collection,p_kw_dico,year):
 
 
 def import_kw_dico(database,collection,year):
-    mongo = pymongo.MongoClient('localhost', 29019)
+    #mongo = pymongo.MongoClient('localhost', 29019)
+    mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
     database = mongo[database]
     col = database[collection]
 
@@ -100,10 +102,14 @@ def get_patent_id(cursor_raw):
 
 
 def get_patent_data(year,limit):
-    mongo = pymongo.MongoClient('localhost', 29019)
+    #mongo = pymongo.MongoClient('localhost', 29019)
+    mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
     database = mongo['redbook']
     col = database['raw']
     data = col.find({"year":year,"id":{"$regex":r'^[0-9]'},"abstract":{"$regex":r'.'}},{"id":1,"title":1,"abstract":1})#.limit(limit)
+    #print(len(data))
+    #print(col.count())
+    #data = col.find()
     res=[]
     for row in data :
         #print row
@@ -113,6 +119,7 @@ def get_patent_data(year,limit):
 	if 'title' in row : title = row['title']
 	abstract = ""
 	if 'abstract' in row : abstract = row['abstract']
+	#if 'id' in row and 'title' in row and 'abstract' in row : print [i,title,abstract]
 	res.append([i,title,abstract])
     return(res)
 

### 2016-04-21 Models/TextProcessing/main.py

@@ -6,8 +6,8 @@ def run():
     f=open(sys.argv[1])
     kwLimit = 100000
     for year in f.readlines():
-	    print year
-        bootstrap.relevant_full_corpus(year,kwLimit)
+	print year
+        bootstrap.relevant_full_corpus(str(year).replace('\n',''),kwLimit)
         #keywords.extract_keywords_year(str(year).replace('\n',''))
     #year=2005;limit=-1;kwLimit=3000;subCorpusSize=20000;bootstrapSize=10;nruns=2
     #year=2005;

### 2016-04-22 Models/TextProcessing/keywords.py
sparse_matric_coocs_computation

@@ -66,9 +66,10 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     # computing cooccurrences
     print('Computing cooccurrences...')
     # compute termhoods :: coocurrence matrix -> in \Theta(16 N^2) - N must thus stay 'small'
-    coocs = []
-    for i in range(len(selected_kws.keys())):
-        coocs.append(([0]*len(selected_kws.keys())))
+    coocs = {}
+
+    #for i in range(len(selected_kws.keys())):
+    #    coocs.append(([0]*len(selected_kws.keys())))
     # fill the cooc matrix
     # for each patent : kws are coocurring if selected.
     # Beware to filter BEFORE launching O(n^2) procedure
@@ -81,18 +82,33 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
         for k in p_kw_dico[p] :
             if k in selected_kws : sel.append(k)
         for i in range(len(sel)-1):
+            ii = selected_kws[sel[i]]
+            if ii not in coocs : coocs[ii] = {}
             for j in range(i+1,len(sel)):
-                ii = selected_kws[sel[i]] ; jj= selected_kws[sel[j]] ;
-                coocs[ii][jj] = coocs[ii][jj] + 1
-                coocs[jj][ii] = coocs[jj][ii] + 1
+                jj= selected_kws[sel[j]]
+                if jj not in coocs : coocs[jj] = {}
+                if jj not in coocs[ii] :
+                    coocs[ii][jj] = 1
+                else :
+                    coocs[ii][jj] = coocs[ii][jj] + 1
+                if ii not in coocs[jj] :
+                    coocs[jj][ii] = 1
+                else :
+                    coocs[jj][ii] = coocs[jj][ii] + 1
+                #coocs[ii][jj] = coocs[ii][jj] + 1
+                #coocs[jj][ii] = coocs[jj][ii] + 1
 
     # compute termhoods
-    colSums = [sum(row) for row in coocs]
+    #colSums = [sum(row) for row in coocs]
+    colSums = {}
+    for i in coocs.keys():
+        colSums[i] = sum(coocs[i].values())
 
-    termhoods = [0]*len(coocs)
-    for i in range(len(coocs)):
+    #termhoods = [0]*len(coocs.keys())
+    termhoods = {}
+    for i in coocs.keys():
         s = 0;
-        for j in range(len(coocs)):
[…]

### 2016-04-22 Models/TextProcessing/bootstrap.py
added_tidf_stat

@@ -34,10 +34,12 @@ def relevant_full_corpus(year,kwLimit):
         relevant = 'relevant_'+str(year)+'_full_'+str(kwLimit)
         mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
         database = mongo['relevant']
+        # clean the collection first
+        database[relevant].delete_many({"cumtermhood":{"$gt":0}})
         database[relevant].create_index('keyword')
-        [rel_kws,dico] = keywords.extract_relevant_keywords(corpus,kwLimit,occurence_dicos)
+        [rel_kws,dico,frequencies] = keywords.extract_relevant_keywords(corpus,kwLimit,occurence_dicos)
         for kw in rel_kws.keys():
-            update_kw_tm(kw,rel_kws[kw],database,relevant)
+            update_kw_tm(kw,rel_kws[kw],frequencies[kw],rel_kws[kw]/frequencies[kw],database,relevant)
 
 
 
@@ -66,13 +68,14 @@ def run_bootstrap(year,limit,kwLimit,subCorpusSize,bootstrapSize,nruns) :
 
 
 
-def update_kw_tm(kw,incr,database,table):
+def update_kw_tm(kw,incr,frequency,tidf,database,table):
     prev = database[table].find_one({'keyword':kw})
     if prev is not None:
         prev['cumtermhood']=prev['cumtermhood']+incr
+        prev['frequency'] = frequency;prev['tidf']=tidf
         database[table].replace_one({'keyword':kw},prev)
     else :
-        database[table].insert_one({'keyword':kw,'cumtermhood':incr,'ids':[]})
+        database[table].insert_one({'keyword':kw,'cumtermhood':incr,'docfrequency':frequency,'tidf':tidf})
 
 
 

### 2016-04-22 Models/TextProcessing/keywords.py

@@ -50,6 +50,12 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
 
     [p_kw_dico,kw_p_dico] = extract_sub_dicos(corpus,occurence_dicos)
 
+    # compute frequencies
+    print('Compute frequencies...')
+    frequencies = {}
+    for k in kw_p_dico.keys():
+        frequencies[k] = len(kw_p_dico[k])
+
     # compute unithoods
     print('Compute unithoods...')
     unithoods = dict()
@@ -117,15 +123,19 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     for k in selected_kws.keys():
         sorting_termhoods[k]=termhoods[selected_kws[k]]
 
-    return(extract_from_termhood(sorting_termhoods,p_kw_dico,kwLimit))
+    [rel_kws,dico,freqselected] = extract_from_termhood(sorting_termhoods,p_kw_dico,kwLimit)
+
+    return([rel_kws,dico,freqselected])
 
 
-def extract_from_termhood(termhoods,p_kw_dico,kwLimit):
+def extract_from_termhood(termhoods,p_kw_dico,frequencies,kwLimit):
     sorted_termhoods = sorted(termhoods.items(), key=operator.itemgetter(1),reverse=True)
 
-    tselected = dict()
+    tselected = {}
+    freqselected = {}
     for i in range(kwLimit):
         tselected[sorted_termhoods[i][0]] = sorted_termhoods[i][1]
+        freqselected[sorted_termhoods[i][0]] = frequencies[sorted_termhoods[i][0]]
 
     # reconstruct the patent -> tselected dico, finally necessary to build kw nw
     p_tsel_dico = dict()
@@ -136,7 +146,7 @@ def extract_from_termhood(termhoods,p_kw_dico,kwLimit):
         p_tsel_dico[p] = sel
 
     # eventually write to file ? -> do that in other proc (! atomicity)
-    return([tselected,p_tsel_dico])
+    return([tselected,p_tsel_dico,freqselected])
 
 ##
 #  Given large occurence dico, extracts corresponding subdico

### 2016-04-22 Models/TextProcessing/keywords.py
remote

@@ -123,7 +123,7 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     for k in selected_kws.keys():
         sorting_termhoods[k]=termhoods[selected_kws[k]]
 
-    [rel_kws,dico,freqselected] = extract_from_termhood(sorting_termhoods,p_kw_dico,kwLimit)
+    [rel_kws,dico,freqselected] = extract_from_termhood(sorting_termhoods,p_kw_dico,frequencies,kwLimit)
 
     return([rel_kws,dico,freqselected])
 

### 2016-04-22 Models/TextProcessing/keywords.py
edge_list

@@ -64,7 +64,9 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
         unithoods[k]=math.log(l+1)*len(kw_p_dico[k])
 
     # sort and keep K*N keywords ; K = 4 for now ?
-    selected_kws = dict() # dictionary : kw -> index in matrix
+    selected_kws = {} # dictionary : kw -> index in matrix
+    #selected_kws_indexes = {} # dico index -> kw.  Q : use kw as keys in cooc matrix ?
+    #  seems to be even more performant
     sorted_unithoods = sorted(unithoods.items(), key=operator.itemgetter(1),reverse=True)
     for i in range(4*kwLimit):
         selected_kws[sorted_unithoods[i][0]] = i
@@ -123,9 +125,15 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     for k in selected_kws.keys():
         sorting_termhoods[k]=termhoods[selected_kws[k]]
 
-    [rel_kws,dico,freqselected] = extract_from_termhood(sorting_termhoods,p_kw_dico,kwLimit)
+    [tselected,dico,freqselected] = extract_from_termhood(sorting_termhoods,p_kw_dico,frequencies,kwLimit)
 
-    return([rel_kws,dico,freqselected])
+    # construct graph edge list
+    edge_list = []
+    for kw in tselected.keys():
+        ii = selected_kws[kw]
+        edge_list.append()
+
+    return([tselected,dico,freqselected])
 
 
 def extract_from_termhood(termhoods,p_kw_dico,frequencies,kwLimit):

### 2016-04-22 Models/TextProcessing/keywords.py
docfreq

@@ -52,9 +52,9 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
 
     # compute frequencies
     print('Compute frequencies...')
-    frequencies = {}
+    docfrequencies = {}
     for k in kw_p_dico.keys():
-        frequencies[k] = len(kw_p_dico[k])
+        docfrequencies[k] = len(kw_p_dico[k])
 
     # compute unithoods
     print('Compute unithoods...')
@@ -125,7 +125,7 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     #for k in selected_kws.keys():
     #    sorting_termhoods[k]=termhoods[selected_kws[k]]
 
-    [tselected,dico,freqselected] = extract_from_termhood(termhoods,p_kw_dico,frequencies,kwLimit)
+    [tselected,dico,freqselected] = extract_from_termhood(termhoods,p_kw_dico,docfrequencies,kwLimit)
 
     # construct graph edge list (! undirected)
     edge_list = []

### 2016-04-22 Models/TextProcessing/bootstrap.py
remote

@@ -38,9 +38,11 @@ def relevant_full_corpus(year,kwLimit):
         database[relevant].delete_many({"cumtermhood":{"$gt":0}})
         database[relevant].create_index('keyword')
         [rel_kws,dico,frequencies,edge_list] = keywords.extract_relevant_keywords(corpus,kwLimit,occurence_dicos)
-        for kw in rel_kws.keys():
+        print('insert relevant...')
+	for kw in rel_kws.keys():
             update_kw_tm(kw,rel_kws[kw],frequencies[kw],math.log(rel_kws[kw])*math.log(len(corpus)/frequencies[kw]),database,relevant)
-        database['network_'+str(year)+'_full_'+str(kwLimit)].insert_many(edge_list)
+        print('insert edges...')
+	database['network_'+str(year)+'_full_'+str(kwLimit)].insert_many(edge_list)
 
 
 

### 2016-04-22 Models/TextProcessing/bootstrap.py
edge_filtering

@@ -32,6 +32,7 @@ def relevant_full_corpus(year,kwLimit):
     print('corpus : '+str(len(corpus))+' ; dico : '+str(len(occurence_dicos[0]))+' , '+str(len(occurence_dicos[1])))
     if len(corpus) > 0 and len(occurence_dicos) > 0 :
         relevant = 'relevant_'+str(year)+'_full_'+str(kwLimit)
+        network = 'network_'+str(year)+'_full_'+str(kwLimit)+'_eth10'
         mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
         database = mongo['relevant']
         # clean the collection first
@@ -39,10 +40,11 @@ def relevant_full_corpus(year,kwLimit):
         database[relevant].create_index('keyword')
         [rel_kws,dico,frequencies,edge_list] = keywords.extract_relevant_keywords(corpus,kwLimit,occurence_dicos)
         print('insert relevant...')
-	for kw in rel_kws.keys():
+	    for kw in rel_kws.keys():
             update_kw_tm(kw,rel_kws[kw],frequencies[kw],math.log(rel_kws[kw])*math.log(len(corpus)/frequencies[kw]),database,relevant)
         print('insert edges...')
-	database['network_'+str(year)+'_full_'+str(kwLimit)].insert_many(edge_list)
+        database[network].delete_many({"weight":{"$gt":0}})
+	    database[network].insert_many(edge_list)
 
 
 

### 2016-04-22 Models/TextProcessing/keywords.py

@@ -132,7 +132,8 @@ def extract_relevant_keywords(corpus,kwLimit,occurence_dicos):
     for kw in tselected.keys():
         for ki in coocs[kw].keys():
             if ki in tselected :
-                edge_list.append({'edge' : kw+";"+ki, 'weight' : coocs[kw][ki]})
+                if coocs[kw][ki] >= 10 :
+                    edge_list.append({'edge' : kw+";"+ki, 'weight' : coocs[kw][ki]})
 
 
     return([tselected,dico,freqselected,edge_list])

### 2016-05-08 Models/Semantic/networkConstruction.R
fung_them_probas

@@ -5,6 +5,49 @@ library(dplyr)
 library(igraph)
 library(rmongodb)
 
+
+
+##
+# Compute thematic probability matrix
+#
+computeThemProbas<-function(gg,com,keyword_dico){
+  # construct kw -> thematic dico
+  thematics = list()
+  for(i in 1:length(V(gg))){
+    thematics[[V(gg)$name[i]]]=com$membership[i]
+  }
+  
+  them_probas = matrix(0,length(names(keyword_dico)),length(unique(com$membership)))
+  for(i in 1:length(names(keyword_dico))){
+    if(i%%100==0){show(i)}
+    kwcount=0
+    for(kw in keyword_dico[[names(keyword_dico)[i]]]){if(kw %in% names(thematics)){
+      j=thematics[[kw]]
+      them_probas[i,j]=them_probas[i,j]+1;kwcount=kwcount+1
+    }}
+    if(kwcount>0){them_probas[i,]=them_probas[i,]/kwcount}
+  }
+  return(them_probas)
+}
+
+
+
+
+
+##
+# extract subgraph communities for given parameters
+extractSubGraphCommunities<-function(ggiant,kmin,kmax,freqmin,freqmax,edge_th){
+  dd = V(ggiant)$docfreq
+  d = degree(ggiant)
+  gg=induced_subgraph(ggiant,which(d>kmin&d<kmax&dd>freqmin&dd<freqmax))
+  gg=subgraph.edges(gg,which(E(gg)$weight>edge_th))
+  clust = clusters(gg);cmax = which(clust$csize==max(clust$csize))
+  gg = induced.subgraph(gg,which(clust$membership==cmax))
+  com = cluster_louvain(gg)
+  return(list(gg=gg,com=com))
+}
+
+
 ##
 # construct network from mongo
 importNetwork<-function(relevantcollection,kwcollection,kwyear,nwcollection,edge_th,target){
@@ -83,107 +126,107 @@ filterGraph<-function(graph,file){
 }
 
 
-
-##
-#  generic function to create and export nw
-#  also compute kws dictionary (used later in originality computation)
-exportNetwork<-function(data,
-                        kwthreshold = 2000,
-                        linkthreshold =15,
-                        connex=TRUE,
-                        export=FALSE,
-                        exportPrefix="",
-                        filterFile="",
[…]

### 2016-05-08 Models/Semantic/semsensitivity.R

@@ -6,9 +6,9 @@ library(dplyr)
 library(igraph)
 source('networkConstruction.R')
 
+#years = c("1998","1999","2000","2005","2006","2007","2008","2009","2010")
+years = read.csv(file=commandArgs(trailingOnly = TRUE)[1])
 
-
-years = c("1998","1999","2000","2005","2006","2007","2008","2009","2010")
 
 for(year in years){
   
@@ -72,15 +72,26 @@ for(year in years){
 
 #############################
 # 
-# load('sensitivity/relevant_full_100000.RData')
-# names(d)[ncol(d)-2]="balance"
-# g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0) 
-# plots=list()
-# for(indic in c("modularity","communities","components","vertices","density","balance")){
-#   plots[[indic]] = g+geom_raster(aes_string("degree_max","edge_th",fill=indic))+facet_grid(freqmax~freqmin)
-# }
-# multiplot(plotlist = plots,cols=3)
 # 
+# library(ggplot2)
+load('sensitivity/relevant_2010_full_100000.RData')
+names(d)[ncol(d)-2]="balance"
+objdec=c(7,45,90,162,253,372,598,1023,2209)/length(res$keyword_dico)
+# load from classes file
+
+msesizes=c()
+for(i in 1:length(comsizes)){
+  msesizes=append(msesizes,sum((log(quantile(comsizes[[i]],(1:9)/10)/d$vertices[i])-log(objdec))^2))
+}
+d=cbind(msesizes,d)
+
+g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0)
+plots=list()
+for(indic in c("modularity","communities","components","vertices","msesizes","balance")){
+  plots[[indic]] = g+geom_raster(aes_string("degree_max","edge_th",fill=indic))+facet_grid(freqmax~freqmin)
+}
+multiplot(plotlist = plots,cols=3)
+
 
 
 

### 2016-05-08 Models/Semantic/semthemprobas.R

@@ -1,0 +1,38 @@
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/Cybergeo/cybergeo20/HyperNetwork/Models/Analysis'))
+library(dplyr)
+library(igraph)
+source('networkConstruction.R')
+
+years = read.csv(file=commandArgs(trailingOnly = TRUE)[1])
+for(year in years){
+  graph=paste0('relevant_',year,'_full_100000')
+  load(paste0('processed/',graph,'.RData'))
+  g=res$g;
+  
+  g = filterGraph(g,'data/filter.csv')
+  
+  clust = clusters(g);cmax = which(clust$csize==max(clust$csize))
+  ggiant = induced.subgraph(g,which(clust$membership==cmax))
+  
+  
+  kmin = 0
+  freqmax = 10000
+  freqmin = 50
+  for(kmax in c(800,1200,2000)){
+    for(edge_th in c(50,100)){
+      sub = extractSubGraphCommunities(ggiant,kmin,kmax,freqmin,freqmax,edge_th)
+      probas = computeThemProbas(sub$gg,sub$com,res$keyword_dico)
+      save(sub,probas,file=paste0('probas/fung_',graph,'_kmin',kmin,'_kmax',kmax,'_freqmin',freqmin,'_freqmax',freqmax,'_eth',edge_th,'.RData'))
+    }
+  }
+  
+}
+
+#################
+#################
+
+#dbparams = 'relevant_full_50000_eth50_nonfiltdico_kmin0_kmax1000_freqmin100_freqmax10000_eth150'
+#load(paste0('probas/',dbparams,'.RData'))
+#them_probas = probas
+

### 2016-05-08 Models/Semantic/allYears.R
zeb

@@ -6,8 +6,11 @@
 setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
 source('networkConstruction.R')
 
-years = read.csv(file=commandArgs(trailingOnly = TRUE)[1])
+years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE)
 
-for(year in years){
-  importNetwork(paste0('relevant.relevant_',year,'_full_100000'),'patent.keywords',year,paste0('network_',year,'_full_100000_eth10'),10,paste0('processed/relevant_',year,'_full_100000'))
+show(years)
+
+for(year in years[,1]){
+  show(paste0("year:",year))
+  importNetwork(paste0('relevant.relevant_',year,'_full_100000'),'patent.keywords',year,paste0('relevant.network_',year,'_full_100000_eth10'),10,paste0('processed/relevant_',year,'_full_100000'))
 }

### 2016-05-08 Models/Semantic/networkConstruction.R

@@ -9,11 +9,15 @@ library(rmongodb)
 # construct network from mongo
 importNetwork<-function(relevantcollection,kwcollection,kwyear,nwcollection,edge_th,target){
   show(paste0('Constructing network for year ',kwyear,' with eth ',edge_th))
-  mongo <- mongo.create(host="mongodb://root:root@127.0.0.1:29019")
+  mongo <- mongo.create(host="127.0.0.1:29019")
+  #mongo.authenticate(mongo,"root","root")
   # 
   relevant <- mongo.find.all(mongo,relevantcollection)
-  dico <- mongo.find.all(mongo,kwcollection,query=list(year=kwyear))
-  
+  dico <- mongo.find.all(mongo,kwcollection,query=list(year=as.character(kwyear)))
+ 
+  show(paste0('dico size : ',length(dico)))
+  show(paste0('relevant : ',length(relevant)))
+ 
   relevant = data.frame(keyword=sapply(relevant,function(d){d$keyword}),
                         cumtermhood=sapply(relevant,function(d){d$cumtermhood}),
                         docfreq=sapply(relevant,function(d){d$docfrequency}),

### 2016-05-09 Models/Semantic/semthemprobas.R
first_res_fung_probas

@@ -1,11 +1,12 @@
 
-setwd(paste0(Sys.getenv('CS_HOME'),'/Cybergeo/cybergeo20/HyperNetwork/Models/Analysis'))
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
 library(dplyr)
 library(igraph)
 source('networkConstruction.R')
 
-years = read.csv(file=commandArgs(trailingOnly = TRUE)[1])
+years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE)
 for(year in years){
+  show(paste0('computing probas for year ',year))
   graph=paste0('relevant_',year,'_full_100000')
   load(paste0('processed/',graph,'.RData'))
   g=res$g;

### 2016-05-09 Models/Semantic/semsensitivity.R
sens_alldata

@@ -7,10 +7,10 @@ library(igraph)
 source('networkConstruction.R')
 
 #years = c("1998","1999","2000","2005","2006","2007","2008","2009","2010")
-years = read.csv(file=commandArgs(trailingOnly = TRUE)[1])
+years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE)
 
 
-for(year in years){
+for(year in years[,1]){
   
   graph=paste0('relevant_',year,'_full_100000')
   load(paste0('processed/',graph,'.RData'))
@@ -75,23 +75,23 @@ for(year in years){
 # 
 # 
 # library(ggplot2)
-load('sensitivity/relevant_2010_full_100000.RData')
-names(d)[ncol(d)-2]="balance"
-objdec=c(7,45,90,162,253,372,598,1023,2209)/length(res$keyword_dico)
+#load('sensitivity/relevant_2010_full_100000.RData')
+#names(d)[ncol(d)-2]="balance"
+#objdec=c(7,45,90,162,253,372,598,1023,2209)/length(res$keyword_dico)
 # load from classes file
 
-msesizes=c()
-for(i in 1:length(comsizes)){
-  msesizes=append(msesizes,sum((log(quantile(comsizes[[i]],(1:9)/10)/d$vertices[i])-log(objdec))^2))
-}
-d=cbind(msesizes,d)
+#msesizes=c()
+#for(i in 1:length(comsizes)){
+#  msesizes=append(msesizes,sum((log(quantile(comsizes[[i]],(1:9)/10)/d$vertices[i])-log(objdec))^2))
+#}
+#d=cbind(msesizes,d)
 
-g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0)
-plots=list()
-for(indic in c("modularity","communities","components","vertices","msesizes","balance")){
-  plots[[indic]] = g+geom_raster(aes_string("degree_max","edge_th",fill=indic))+facet_grid(freqmax~freqmin)
-}
-multiplot(plotlist = plots,cols=3)
+#g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0)
+#plots=list()
+#for(indic in c("modularity","communities","components","vertices","msesizes","balance")){
[…]

### 2016-05-11 Models/Citation/constructNW.R
cit_nw_construction

@@ -1,0 +1,19 @@
+
+# construct citation network
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/citation'))
+
+library(igraph)
+library(Matrix)
+
+edf1 = read.csv(file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/raw/citation/citation75_99/citation75_99.csv'),stringsAsFactors = FALSE)
+edf2 = read.csv(file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/raw/citation/citation00_10.csv'),stringsAsFactors = FALSE)
+
+edf = rbind(edf1[,c(1,6)],edf2[,c(1,6)])
+names(edf)<-c("from","to")
+
+gcitation = graph_from_data_frame(edf)
+citadjacency = get.adjacency(gcitation,sparse=TRUE)
+
+save(gcitation,file='network/citationNetwork.RData')
+save(citadjacency,file='network/adjacency.RData')

### 2016-05-11 Docs/Communications/CCS2016/ccs2016.tex

\input{WPHeader.tex}

\title{Unveiling Patterns of Technological Innovation through Data-mining\\\bigskip
\textit{Communication Proposal, CCS 2016}
}
\author{\small\noun{Juste Raimbault}$^{1,2}$\\
\small(1) UMR CNRS 8504 Géographie-cités and (2) UMR-T IFSTTAR 9403 LVMT
}
%\date{15 octobre 2015}
\date{}

\maketitle

\justify

\pagenumbering{gobble}

%\vspace{-0.5cm}
\textbf{Keywords : }\textit{}

The understanding of patterns of technological innovation is crucial for both economical growth theories and practical application in research and developments. Yet a precise characterization of breakthrough inventions has not been fully investigated. We propose a large-scale data-mining approach on technological patents.

\bigskip

\bigskip

%%%%%%%%%%%%%%%%%%%%
%% Biblio
%%%%%%%%%%%%%%%%%%%%

%\begin{multicols}{2}

%\setstretch{0.3}
%\setlength{\parskip}{-0.4em}

%\bibliographystyle{apalike}
%\bibliography{/Users/Juste/Documents/ComplexSystems/CityNetwork/Biblio/Bibtex/CityNetwork}

%\end{multicols}

\end{document}

### 2016-05-11 Models/Semantic/semthemprobas.R
compute_probas

@@ -16,15 +16,16 @@ for(year in years){
   clust = clusters(g);cmax = which(clust$csize==max(clust$csize))
   ggiant = induced.subgraph(g,which(clust$membership==cmax))
   
-  
   kmin = 0
-  freqmax = 10000
   freqmin = 50
-  for(kmax in c(800,1200,2000)){
-    for(edge_th in c(50,100)){
+  edge_th = 50
+  for(kmaxdec in c(0.15,0.2,0.25)){
+    for(freqmaxdec in c(0.15,0.2,0.25)){
+      kmax=kmaxdec*max(degree(ggiant))
+      freqmax=freqmaxdec*length(res$keyword_dico)
       sub = extractSubGraphCommunities(ggiant,kmin,kmax,freqmin,freqmax,edge_th)
       probas = computeThemProbas(sub$gg,sub$com,res$keyword_dico)
-      save(sub,probas,file=paste0('probas/fung_',graph,'_kmin',kmin,'_kmax',kmax,'_freqmin',freqmin,'_freqmax',freqmax,'_eth',edge_th,'.RData'))
+      save(sub,probas,file=paste0('probas/',graph,'_kmin',kmin,'_kmaxdec',kmaxdec,'_freqmin',freqmin,'_freqmaxdec',freqmaxdec,'_eth',edge_th,'.RData'))
     }
   }
   

### 2016-05-13 Models/Citation/constructNW.R
probas_all

@@ -6,7 +6,7 @@ setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/citation'))
 library(igraph)
 library(Matrix)
 
-edf1 = read.csv(file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/raw/citation/citation75_99/citation75_99.csv'),stringsAsFactors = FALSE)
+edf1 = read.csv(file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/raw/citation/citation75_99.csv'),stringsAsFactors = FALSE)
 edf2 = read.csv(file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/raw/citation/citation00_10.csv'),stringsAsFactors = FALSE)
 
 edf = rbind(edf1[,c(1,6)],edf2[,c(1,6)])

### 2016-05-13 Models/Semantic/semthemprobas.R

@@ -5,7 +5,7 @@ library(igraph)
 source('networkConstruction.R')
 
 years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE)
-for(year in years){
+for(year in years[,1]){
   show(paste0('computing probas for year ',year))
   graph=paste0('relevant_',year,'_full_100000')
   load(paste0('processed/',graph,'.RData'))

### 2016-05-13 Models/Semantic/semanalysis.R
techno_probas

@@ -1,0 +1,32 @@
+
+############
+#  Analysis of semantic communities
+############
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
+
+years = 1976:2012
+
+kmin = 0;freqmin = 50;edge_th = 50;kmaxdec=0.15;freqmaxdec=0.15
+prefix = paste0('_full_100000_kmin',kmin,'_kmaxdec',kmaxdec,'_freqmin',freqmin,'_freqmaxdec',freqmaxdec,'_eth',edge_th,'.RData')
+
+##
+#  1) First order interdisciplinarity
+
+overlaps = c();cyears=c()
+for(year in years){
+  show(year)
+  load(paste0('probas/relevant_',year,prefix))
+  probas=probas[,3:ncol(probas)]
+  for(i in 1:(ncol(probas)-1)){for(j in (i+1):ncol(probas)){
+    overlaps=append(overlaps,sum(probas[,i]*probas[,j])/nrow(probas));cyears=append(cyears,year)
+  }}
+}
+
+inds=1:length(overlaps)#overlaps>0
+overlaps[overlaps==0]=1e-10
+g=ggplot(data.frame(overlaps=overlaps[inds],years=as.character(cyears[inds])))
+g+geom_density(aes(x=overlaps,colour=years),alpha=0.25,adjust=0.75)+scale_x_log10()+xlab("overlap")+ylab("density")#+scale_y_log10()
+
+
+

### 2016-05-13 Models/Semantic/semoptimprobas.R

@@ -1,0 +1,44 @@
+
+# optim params on patent level
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
+
+years = 1976:2012
+
+objdf = read.csv(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/distrib_class_grantdate.csv'),sep=";")
+objdf = objdf[,1:10]
+
+kmin = 0
+freqmin = 50
+edge_th = 50
+
+#kmaxs = c();freqmaxs=c();vals=c();indics=c();
+vals = data.frame()
+for(kmaxdec in c(0.15,0.2,0.25)){
+  for(freqmaxdec in c(0.15,0.2,0.25)){
+    
+    for(y in 1:length(years)){
+      year = years[y]
+      show(year)
+      load(paste0('probas/relevant_',year,'_full_100000_kmin',kmin,'_kmaxdec',kmaxdec,'_freqmin',freqmin,'_freqmaxdec',freqmaxdec,'_eth',edge_th,'.RData'))
+      obj=objdf[y,2:ncol(objdf)]/nrow(probas)
+      #show(summary(probas$kwproportion))
+      #show(summary(colSums(probas[,3:ncol(probas)])/sum(probas[,3:ncol(probas)])))
+      #vals=rbind(vals,c(kmaxdec,freqmaxdec,year,0,sum((log(quantile(colSums(probas[,3:ncol(probas)])/sum(probas[,3:ncol(probas)]),(1:9)/10))-log(obj))^2)))
+      #vals=rbind(vals,c(kmaxdec,freqmaxdec,year,1,quantile(probas$kwproportion,0.5)))
+      vals=rbind(vals,c(kmaxdec,freqmaxdec,year,1,ncol(probas)-2))
+    }
+  }
+}
+
+names(vals)<-c("kmaxdec","freqmaxdec","year","indic","val")
+g = ggplot(vals[vals$indic==1,]) + scale_fill_gradient(low="yellow",high="red")
+g+geom_raster(aes(kmaxdec,freqmaxdec,fill=val))#+facet_wrap(~year)
+
+# -> take params 0.25,0.25 ? less coms
+# whereas 0.15,0.15 : better on coms. <==
+
+
+
+
+

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Classes.java

@@ -17,36 +17,80 @@ import java.util.LinkedList;
 public class Classes {
 
 	
-	public static void exportClassesTimeSeries(String classFile,String patentFile,String dateType,int sizeThreshold,String outDir){
-		(new File(outDir)).mkdir();
+	
+	public static void exportYearlyClasses(String classFile,String patentFile,String dateType,int[] years,int sizeThreshold,String outdir){
+		(new File(outdir)).mkdir();
+		for(int year:years){
+			System.out.println("Exporting year "+year);
+			HashMap<String,HashSet<Patent>> classes = getYearlyClasses(classFile,patentFile,dateType,year,sizeThreshold);
+			int clind = 0;HashMap<String,Integer> clinds = new HashMap<String,Integer>();
+			HashSet<Patent> uniquePatents = new HashSet<Patent>();
+			for(String cl:classes.keySet()){
+				clinds.put(cl, new Integer(clind));clind++;
+				for(Patent p:classes.get(cl)){uniquePatents.add(p);}
+			}
+			LinkedList<String[]> c = new LinkedList<String[]>();
+			String[] header = new String[classes.keySet().size()+1];
+			for(String cl:classes.keySet()){header[clinds.get(cl).intValue()+1]=cl;};header[0]="ID";
+			c.add(header);
+			for(Patent p:uniquePatents){
+				String[] row = new String[classes.keySet().size()+1];
+				row[0]=p.id;
+				for(String pcl:p.classes){row[clinds.get(pcl).intValue()+1]=(new Double(1.0/p.classes.size())).toString();}
+				c.add(row);
+			}
+			Writer.writeCSV(c, outdir+"/technoProbas_"+year+"_sizeTh"+sizeThreshold);
+		}
+		
+	}
+	
+	
+	
+	public static void exportClassesTimeSeries(String classFile,String patentFile,String dateType,int sizeThreshold,String outdir){
+		(new File(outdir)).mkdir();
 		HashMap<String,LinkedList<Patent>> sclasses = constructTimelySortedClasses(classFile,patentFile,dateType);
 		for(String className:sclasses.keySet()){
 			if(sclasses.get(className).size()>sizeThreshold){
 				LinkedList<String[]> c = new LinkedList<String[]>();
 				for(Patent p:sclasses.get(className)){String[] d = {p.id,p.dates.get(dateType).toString()};c.add(d);}
-				Writer.writeCSV(c, outDir+"/"+className);
[…]

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Main.java

@@ -28,11 +28,13 @@ public class Main {
 		//Distances.computeDistancesOnSecondOrderOverlaps(sortedClasses);
 		//Classes.exportClassesTimeSeries("../../../Data/raw/classesTechno/class.csv",
 		//		"../../../Data/raw/patent/patent.csv", "AppDate", 1000, "res/sizes_appdate");
-		String[] citFiles = {"../../../Data/raw/citation/citation75_99.csv","../../../Data/raw/citation/citation00_10.csv"};
-		CitationNetwork.computeOriginalities("../../../Data/raw/classesTechno/class.csv", 
-				"../../../Data/raw/patent/patent.csv", "AppDate", citFiles, "res/originalities_appdate", 1000);
+		//String[] citFiles = {"../../../Data/raw/citation/citation75_99.csv","../../../Data/raw/citation/citation00_10.csv"};
+		//CitationNetwork.computeOriginalities("../../../Data/raw/classesTechno/class.csv", 
+		//		"../../../Data/raw/patent/patent.csv", "AppDate", citFiles, "res/originalities_appdate", 1000);
 		
-		
+		int[] years=new int[37];for(int i = 0;i<38;i++){years[i]=i+1976;}
+		Classes.exportYearlyClasses("../../../Data/raw/classesTechno/class.csv",
+				"../../../Data/raw/patent/patent.csv", "GDate",years,10,"res/technoPerYear");
 	}
 
 }

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Patent.java

@@ -38,6 +38,9 @@ public class Patent implements Comparable<Patent>{
 	 */
 	public HashMap<String,Long> dates;
 	
+	// corresponding years
+	public HashMap<String,Integer> years;
+	
 	
 	/**
 	 * Citing patents.
@@ -60,6 +63,7 @@ public class Patent implements Comparable<Patent>{
 		}else{
 			newP.classes = new HashSet<String>();
 			newP.dates = new HashMap<String,Long>();
+			newP.years = new HashMap<String,Integer>();
 			newP.citing = new HashSet<Citation>();newP.cited = new HashSet<Citation>();
 			patents.put(newP, newP);
 			return(newP);
@@ -80,7 +84,9 @@ public class Patent implements Comparable<Patent>{
 					// parse date
 					DateFormat dfm = new SimpleDateFormat("yyyy-MM-dd");
 					Long date = new Long(dfm.parse(sdate).getTime());
+					Integer year = new Integer(dfm.parse(sdate).getYear()+1900);
 					dates.put(field,date);
+					years.put(field, year);
 				}catch(Exception e){
 					e.printStackTrace();
 				}

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Main.java
bis

@@ -32,7 +32,7 @@ public class Main {
 		//CitationNetwork.computeOriginalities("../../../Data/raw/classesTechno/class.csv", 
 		//		"../../../Data/raw/patent/patent.csv", "AppDate", citFiles, "res/originalities_appdate", 1000);
 		
-		int[] years=new int[37];for(int i = 0;i<38;i++){years[i]=i+1976;}
+		int[] years=new int[37];for(int i = 0;i<37;i++){years[i]=i+1976;}
 		Classes.exportYearlyClasses("../../../Data/raw/classesTechno/class.csv",
 				"../../../Data/raw/patent/patent.csv", "GDate",years,10,"res/technoPerYear");
 	}

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Classes.java
ter

@@ -20,21 +20,22 @@ public class Classes {
 	
 	public static void exportYearlyClasses(String classFile,String patentFile,String dateType,int[] years,int sizeThreshold,String outdir){
 		(new File(outdir)).mkdir();
+		HashMap<String,HashSet<Patent>> allclasses = classesWithDates(classFile,patentFile,dateType);
 		for(int year:years){
 			System.out.println("Exporting year "+year);
-			HashMap<String,HashSet<Patent>> classes = getYearlyClasses(classFile,patentFile,dateType,year,sizeThreshold);
+			HashMap<String,HashSet<Patent>> yearlyclasses = getYearlyClasses(allclasses,dateType,year,sizeThreshold);
 			int clind = 0;HashMap<String,Integer> clinds = new HashMap<String,Integer>();
 			HashSet<Patent> uniquePatents = new HashSet<Patent>();
-			for(String cl:classes.keySet()){
+			for(String cl:yearlyclasses.keySet()){
 				clinds.put(cl, new Integer(clind));clind++;
-				for(Patent p:classes.get(cl)){uniquePatents.add(p);}
+				for(Patent p:yearlyclasses.get(cl)){uniquePatents.add(p);}
 			}
 			LinkedList<String[]> c = new LinkedList<String[]>();
-			String[] header = new String[classes.keySet().size()+1];
-			for(String cl:classes.keySet()){header[clinds.get(cl).intValue()+1]=cl;};header[0]="ID";
+			String[] header = new String[yearlyclasses.keySet().size()+1];
+			for(String cl:yearlyclasses.keySet()){header[clinds.get(cl).intValue()+1]=cl;};header[0]="ID";
 			c.add(header);
 			for(Patent p:uniquePatents){
-				String[] row = new String[classes.keySet().size()+1];
+				String[] row = new String[yearlyclasses.keySet().size()+1];
 				row[0]=p.id;
 				for(String pcl:p.classes){row[clinds.get(pcl).intValue()+1]=(new Double(1.0/p.classes.size())).toString();}
 				c.add(row);
@@ -60,8 +61,8 @@ public class Classes {
 	
 	
 	
-	public static HashMap<String,HashSet<Patent>> getYearlyClasses(String classFile,String patentFile,String dateType,int year,int sizeThreshold){
-		HashMap<String,HashSet<Patent>> classes = classesWithDates(classFile,patentFile,dateType);
[…]

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Classes.java
null_pointer

@@ -37,7 +37,13 @@ public class Classes {
 			for(Patent p:uniquePatents){
 				String[] row = new String[yearlyclasses.keySet().size()+1];
 				row[0]=p.id;
-				for(String pcl:p.classes){row[clinds.get(pcl).intValue()+1]=(new Double(1.0/p.classes.size())).toString();}
+				if(p.classes.size()>0){
+					for(String pcl:p.classes){
+						if(clinds.containsKey(pcl)){
+							row[clinds.get(pcl).intValue()+1]=(new Double(1.0/p.classes.size())).toString();
+						}
+					}
+				}
 				c.add(row);
 			}
 			Writer.writeCSV(c, outdir+"/technoProbas_"+year+"_sizeTh"+sizeThreshold);

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Classes.java
empty_classes

@@ -37,6 +37,7 @@ public class Classes {
 			for(Patent p:uniquePatents){
 				String[] row = new String[yearlyclasses.keySet().size()+1];
 				row[0]=p.id;
+				for(int i=1;i<row.length;i++){row[i]=(new Double(0.0)).toString();}
 				if(p.classes.size()>0){
 					for(String pcl:p.classes){
 						if(clinds.containsKey(pcl)){

### 2016-05-13 Models/Techno/TechnoClasses/src/patents/Writer.java

@@ -45,7 +45,7 @@ public class Writer {
 			BufferedWriter w = new BufferedWriter(new FileWriter(new File(file)));
 			for(T[] t:data){
 				for(int j = 0;j<t.length;j++){
-					w.write(t[j].toString());;if(j<t.length-1){w.write(";");}
+					w.write(t[j].toString());if(j<t.length-1){w.write(";");}
 				}
 				
 				w.write("\n");

### 2016-05-13 Models/Techno/prepareData.R

@@ -1,0 +1,10 @@
+
+# import and saving as RData of yearly techno classes structures
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Techno/TechnoClasses/res/technoPerYear'))
+
+years = 1976:2012
+
+for(year in years){
+  d = read.table('',sep=";",row.names = TRUE,header=TRUE)
+}

### 2016-05-13 Models/Techno/prepareData.R
convert_to_R

@@ -5,6 +5,10 @@ setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Techno/TechnoClasses/r
 
 years = 1976:2012
 
+sizeTh = 10
+
 for(year in years){
-  d = read.table('',sep=";",row.names = TRUE,header=TRUE)
+  show(year)
+  d = read.table(file=paste0('technoProbas_',year,'_sizeTh',sizeTh),sep=";",row.names = TRUE,header=TRUE)
+  save(d,file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/technoPerYear/technoProbas_',year,'_sizeTh',sizeTh,'.RData'))
 }

### 2016-05-13 Models/Techno/prepareData.R
sparse_mats

@@ -3,12 +3,14 @@
 
 setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Techno/TechnoClasses/res/technoPerYear'))
 
+library(Matrix)
+
 years = 1976:2012
 
 sizeTh = 10
 
 for(year in years){
   show(year)
-  d = read.table(file=paste0('technoProbas_',year,'_sizeTh',sizeTh),sep=";",row.names = TRUE,header=TRUE)
+  d = Matrix(read.table(file=paste0('technoProbas_',year,'_sizeTh',sizeTh),sep=";",row.names = TRUE,header=TRUE),sparse=TRUE)
   save(d,file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/technoPerYear/technoProbas_',year,'_sizeTh',sizeTh,'.RData'))
 }

### 2016-05-13 Models/Techno/prepareData.R
sparse_techno_matrices_probas

@@ -11,6 +11,10 @@ sizeTh = 10
 
 for(year in years){
   show(year)
-  d = Matrix(read.table(file=paste0('technoProbas_',year,'_sizeTh',sizeTh),sep=";",row.names = TRUE,header=TRUE),sparse=TRUE)
-  save(d,file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/technoPerYear/technoProbas_',year,'_sizeTh',sizeTh,'.RData'))
+  d = read.table(file=paste0('technoProbas_',year,'_sizeTh',sizeTh),sep=";",row.names = 1,header=TRUE)
+  #d[is.na(d)]=0
+  m = Matrix(as.matrix(d),sparse=TRUE)
+  save(m,file=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/technoPerYear/technoProbas_',year,'_sizeTh',sizeTh,'.RData'))
 }
+
+

### 2016-05-13 Models/Semantic/semanalysis.R
last_results

@@ -7,26 +7,138 @@ setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
 
 years = 1976:2012
 
-kmin = 0;freqmin = 50;edge_th = 50;kmaxdec=0.15;freqmaxdec=0.15
-prefix = paste0('_full_100000_kmin',kmin,'_kmaxdec',kmaxdec,'_freqmin',freqmin,'_freqmaxdec',freqmaxdec,'_eth',edge_th,'.RData')
+kmin = 0;freqmin = 50;edge_th = 50;kmaxdec=0.25;freqmaxdec=0.25
+sizeTh=10
+semprefix = paste0('_full_100000_kmin',kmin,'_kmaxdec',kmaxdec,'_freqmin',freqmin,'_freqmaxdec',freqmaxdec,'_eth',edge_th,'.RData')
+technoprefix=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/technoPerYear/technoProbas_')
+
+loadProbas<-function(year){
+  show(year)
+  res=list()
+  load(paste0('probas/relevant_',year,semprefix))
+  res$semprobas=probas[,3:ncol(probas)]
+  load(paste0(technoprefix,year,'_sizeTh',sizeTh,'.RData'))
+  rowstoadd=setdiff(rownames(res$semprobas),rownames(m))
+  m=rbind(m,matrix(0,length(rowstoadd),ncol(m)));rownames(m)[(nrow(m)-length(rowstoadd)+1):nrow(m)]=rowstoadd
+  res$technoprobas = m[rownames(res$semprobas),]
+  return(res)
+}
+
 
 ##
 #  1) First order interdisciplinarity
 
+#  1.1) Macro-level
+
 overlaps = c();cyears=c()
 for(year in years){
-  show(year)
-  load(paste0('probas/relevant_',year,prefix))
-  probas=probas[,3:ncol(probas)]
-  for(i in 1:(ncol(probas)-1)){for(j in (i+1):ncol(probas)){
-    overlaps=append(overlaps,sum(probas[,i]*probas[,j])/nrow(probas));cyears=append(cyears,year)
+  res = loadProbas(year);technoprobas=res$technoprobas;semprobas=res$semprobas
+  inds = which(colSums(technoprobas)>50)
+  currentovs = rep(0,ncol(technoprobas)*(ncol(technoprobas)-1)/2)
+  k=1
[…]

### 2016-07-24 Models/Semantic/semthemprobas.R
remote

@@ -18,9 +18,9 @@ for(year in years[,1]){
   
   kmin = 0
   freqmin = 50
-  edge_th = 50
-  for(kmaxdec in c(0.15,0.2,0.25)){
-    for(freqmaxdec in c(0.15,0.2,0.25)){
+  for(edge_th in c(10,25)){
+  for(kmaxdec in c(0.15,0.25)){
+    for(freqmaxdec in c(0.15,0.25)){
       kmax=kmaxdec*max(degree(ggiant))
       freqmax=freqmaxdec*length(res$keyword_dico)
       sub = extractSubGraphCommunities(ggiant,kmin,kmax,freqmin,freqmax,edge_th)
@@ -28,7 +28,7 @@ for(year in years[,1]){
       save(sub,probas,file=paste0('probas/',graph,'_kmin',kmin,'_kmaxdec',kmaxdec,'_freqmin',freqmin,'_freqmaxdec',freqmaxdec,'_eth',edge_th,'.RData'))
     }
   }
-  
+  }
 }
 
 #################

### 2016-07-24 Docs/Communications/CCS2016/ccs2016.tex

@@
 
-\title{Unveiling Patterns of Technological Innovation through Data-mining\\\bigskip
+\title{Investigating Patterns of Technological Innovation\\\bigskip
 \textit{Communication Proposal, CCS 2016}
 }
-\author{\small\noun{Juste Raimbault}$^{1,2}$\\
-\small(1) UMR CNRS 8504 Géographie-cités and (2) UMR-T IFSTTAR 9403 LVMT
+\author{\noun{Antonin Bergeaud}$^{1}$, \noun{Yoann Potiron}$^2$ and \noun{Juste Raimbault}$^{3,4}$\\
+$^1$ Department of Economics, London School of Economics\\
+$^2$ Faculty of Business and Commerce, Keio University\\
+$^3$ UMR CNRS 8504 Géographie-cités\\
+$^4$ UMR-T IFSTTAR 9403 LVMT
 }
@@
 %\vspace{-0.5cm}
-\textbf{Keywords : }\textit{}
+\textbf{Keywords : }\textit{Technological Innovation, Text-mining, Multilayer Network}
 
-The understanding of patterns of technological innovation is crucial for both economical growth theories and practical application in research and developments.
+\bigskip
+
+The understanding of patterns of technological innovation is crucial for both economical growth theories and practical applications in research and development.
 Yet a precise characterization of breakthrough inventions has not been fully investigated.
-We propose a large-scale data-mining approach on technological patents.
+We propose to answer this issue through a large-scale data-mining and network approach on patent data.
+
+We construct from US Patent Office raw data an open consolidated database that includes detailed patent information, technological classifications, citation links, and abstract texts, yielding a database of around $4\cdot 10^6$ patents on a time range from 1976 to 2012.
+Aiming at capturing the semantic information contained in texts, that has been shown to be complementary to classification data, we extract relevant n-gram keywords and obtain for each year a semantic network based on co-occurrences.
+The multi-objective optimization of network modularity and size is performed on network construction parameters (filtering thresholds) through high performance computing.
+We obtain for each year a multi-layer network, containing semantic community relations, technological classes relations and citation relations between patents.
+The mining of network layers yields interesting results, such as an increase in time of patent semantic originality combined with a counter-intuitive loss of class-level interdisciplinarity, what confirms the stylized facts of both invention refinement and specialization in time.
+Citation-level interdisciplinarity is investigated by combining the different layers.
+Further work is planned towards the use of these heterogeneous features produced by multi-layer network analysis into machine learning models to predict success and breakthrough level of inventions.
+
+Our contribution to the study of socio-technical complex systems is on the one hand thematic, with the construction of an open-access large scale consolidated patent database and insights into the temporal evolution of inventions, and on the other hand methodological with a technique that can be generated to any network whose nodes contain a textual description.
 

### 2016-09-03 Models/Semantic/semanalysis.R
git_demo

@@ -56,6 +56,7 @@ for(year in years){
 #save(overlaps,cyears,file='res/techno_overlaps.RData')
 load(file='res/techno_overlaps.RData')
 
+
 inds=overlaps>0#1:length(overlaps)#
 #overlaps[overlaps==0]=1e-10
 g=ggplot(data.frame(overlap=overlaps[inds],year=cyears[inds]),aes(x=overlap,colour=as.character(year)))#aes(x=year,y=overlap))

### 2016-09-06 Models/Semantic/semsensitivity.R
modifiable_fullpipe

@@ -43,7 +43,8 @@ for(i in 1:nrow(years)){
   gsizes=c();
   gdensity=c();
   cbalance=c();
-  freqsmin=c();freqsmax=c()
+  freqsmin=c();freqsmax=c();
+  freqsmaxdec=c();kmaxsdec=c()
   comsizes=list()
   i=1
   
@@ -54,8 +55,9 @@ for(i in 1:nrow(years)){
   for(freqmaxdec in c(0.025,0.05,0.15,0.25)){
     freqmax = freqmaxdec*nPatents
     for(freqmin in c(50,100,200,500)){
-      for(kmax in seq(from=0.05,to=0.6,by=0.05)*max(d)){
-        for(edge_th in seq(from=50,to=250,by=20)){
+      for(kmaxdec in seq(from=0.05,to=0.6,by=0.05)){
+        kmax = kmaxdec*max(d)
+	for(edge_th in seq(from=50,to=250,by=20)){
           show(paste0('kmax : ',kmax,' e_th : ',edge_th,' ; freqmin : ',freqmin,' ; freqmax : ',freqmax))
           gg=induced_subgraph(ggiant,which(d>kmin&d<kmax&dd>freqmin&dd<freqmax))
           gg=subgraph.edges(gg,which(E(gg)$weight>edge_th))
@@ -71,14 +73,15 @@ for(i in 1:nrow(years)){
           cbalance=append(cbalance,sum((sizes(com)/length(V(gg)))^2))
           dmax=append(dmax,kmax);eth=append(eth,edge_th)
           freqsmin=append(freqsmin,freqmin);freqsmax=append(freqsmax,freqmax)
-          comsizes[[i]]=sizes(com)
+          freqsmaxdec=append(freqsmaxdec,freqmaxdec);kmaxsdec=append(kmaxsdec,kmaxdec)
+	  comsizes[[i]]=sizes(com)
           i=i+1
         }
       }
     }
   }
   
-  d = data.frame(degree_max=dmax,edge_th=eth,vertices=gsizes,components=csizes,modularity=modularities,communities=comnumber,density=gdensity,comunitiesbalance=cbalance,freqmin=freqsmin,freqmax=freqsmax)
[…]

### 2016-09-06 Models/fullpipe.sh

@@ -9,7 +9,8 @@ START=1976
 END=2008
 NRUNS=15
 
-
+# tasks : relevant ; network ; sensitivity ; probas
+TASK=probas
 
 
 ##########
@@ -38,8 +39,9 @@ do
 done
 
 # command : python main.py yearfile
-#./parrunnum "python main.py relevantyears/runmv" $NRUNS
-
+if [ "$TASK" == "relevant" ] then
+  ./parrunnum "python main.py relevantyears/runmv" $NRUNS
+fi
 
 
 ############
@@ -68,7 +70,9 @@ done
 # NOTE : for this part, rmongodb fails to authenticate -> relaunch db without auth
 
 # command for graph construction : R -f allYears.R --args yearfile
-./parrunnum "R -f allYears.R --args relevantyears/runmv" $NRUNS
+if [ "$TASK" == "network" ] then
+  ./parrunnum "R -f allYears.R --args relevantyears/runmv" $NRUNS
+fi
 
 # graphs stored in processed
 
@@ -83,7 +87,15 @@ done
 #   -> TODO : check analyses citations (2nd order interdisc).
 #
 
+# semsensitivity
+if [ "$TASK" == "sensitivity" ] then
+  ./parrunnum "R -f semsensitivity.R --args relevantyears/runmv" $NRUNS
+fi
 
+if [ "$TASK" == "probas" ] then
+  # probas
+  ./parrunnum "R -f semthemprobas.R --args relevantyears/runmv" $NRUNS
+fi
 
 
 

### 2016-09-06 Models/fullpipe.sh
sensitivity_full

@@ -10,8 +10,8 @@ END=2008
 NRUNS=15
 
 # tasks : relevant ; network ; sensitivity ; probas
-TASK=probas
-
+#TASK=probas
+TASK=sensitivity
 
 ##########
 ##########

### 2016-09-06 Models/fullpipe.sh
sensitivity_giant

@@ -17,7 +17,6 @@ TASK=sensitivity
 ##########
 
 cd TextProcessing
-echo "Running relevance estimation..."
 
 # generate year files
 #remove old
@@ -39,7 +38,9 @@ do
 done
 
 # command : python main.py yearfile
-if [ "$TASK" == "relevant" ] then
+if [ "$TASK" == "relevant" ]
+then
+  echo "Running relevance estimation..."
   ./parrunnum "python main.py relevantyears/runmv" $NRUNS
 fi
 
@@ -70,7 +71,8 @@ done
 # NOTE : for this part, rmongodb fails to authenticate -> relaunch db without auth
 
 # command for graph construction : R -f allYears.R --args yearfile
-if [ "$TASK" == "network" ] then
+if [ "$TASK" == "network" ]
+then
   ./parrunnum "R -f allYears.R --args relevantyears/runmv" $NRUNS
 fi
 
@@ -88,11 +90,13 @@ fi
 #
 
 # semsensitivity
-if [ "$TASK" == "sensitivity" ] then
+if [ "$TASK" == "sensitivity" ]
+then
   ./parrunnum "R -f semsensitivity.R --args relevantyears/runmv" $NRUNS
 fi
 
-if [ "$TASK" == "probas" ] then
+if [ "$TASK" == "probas" ]
+then
   # probas
   ./parrunnum "R -f semthemprobas.R --args relevantyears/runmv" $NRUNS
 fi

### 2016-09-07 Models/Semantic/semsensitivity.R
sizes_comp

@@ -6,110 +6,93 @@ library(dplyr)
 library(igraph)
 source('networkConstruction.R')
 
-years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE,sep=";")
+#years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE,sep=";")
+years=paste0(1976:2008,"-",1980:2012)
 
 # TODO read kwnum from file
 kwNum = "100000"
 #type="full" # full or giant : take full graph or giant component
 type="giant"
 
-for(i in 1:nrow(years)){
-  yearRange=years[i,]
-  year = paste0(as.character(yearRange[1]),"-",as.character(yearRange[length(yearRange)]))
+sizes=c()
+for(year in years){#i in 1:nrow(years)){
+  #yearRange=years[i,]
+  #year = paste0(as.character(yearRange[1]),"-",as.character(yearRange[length(yearRange)]))
+  show(year)
   
   graph=paste0('relevant_',year,'_full_100000')
   load(paste0('processed/',graph,'.RData'))
   nPatents = length(res$keyword_dico)
-  g=res$g;
-  rm(res);gc()
+  sizes=append(sizes,nPatents)
   
-  g = filterGraph(g,'data/filter.csv')
-  
-  # TODO DO NOT USE giant component ?
-  clust = clusters(g);
-  cmax = which(clust$csize==max(clust$csize))
-  if(type=="full"){ggiant=g}
-  else{ggiant = induced.subgraph(g,which(clust$membership==cmax))}
-
-  dd = V(ggiant)$docfreq
-  d = degree(ggiant)
-  
-  kmin = 0
-  
-  modularities = c();
-  comnumber=c();
-  dmax=c();
-  eth=c();
-  csizes=c();
-  gsizes=c();
-  gdensity=c();
-  cbalance=c();
-  freqsmin=c();freqsmax=c();
-  freqsmaxdec=c();kmaxsdec=c()
-  comsizes=list()
-  i=1
-  
-  #
-  # freqmin and freqmax as proportion of patent number ?
-  #  - freqmin can be independent in a first time ; as edge_th -
-  #    freqmax = c(5000,10000,20000,50000) ; 95 : 144706 patents -> ~ 0.25 max
-  for(freqmaxdec in c(0.025,0.05,0.15,0.25)){
-    freqmax = freqmaxdec*nPatents
-    for(freqmin in c(50,100,200,500)){
[…]

### 2016-09-07 Models/Semantic/semsensitivityplot.R

@@ -1,0 +1,37 @@
+
+#############################
+# 
+# plot sensitivity results
+ 
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
+library(ggplot2)
+
+
+kwNum = "100000"
+type="full"
+years=paste0(1976:2008,"-",1980:2012)
+
+for(year in years){
+  graph=paste0('relevant_',year,'_full_',kwNum)
+  load(file=paste0('sensitivity/',graph,'_',type,'.RData'))
+  names(d)[ncol(d)-5]="balance"
+  objdec=c(7,45,90,162,253,372,598,1023,2209)/length(res$keyword_dico)
+  # # load from classes file
+  # 
+  msesizes=c()
+  for(i in 1:length(comsizes)){
+    msesizes=append(msesizes,sum((log(quantile(comsizes[[i]],(1:9)/10)/d$vertices[i])-log(objdec))^2))
+  }
+  d=cbind(msesizes,d)
+  # 
+  # g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0)
+  # plots=list()
+  # for(indic in c("modularity","communities","components","vertices","msesizes","balance")){
+  #   plots[[indic]] = g+geom_raster(aes_string("degree_max","edge_th",fill=indic))+facet_grid(freqmax~freqmin)
+  # }
+  # multiplot(plotlist = plots,cols=3)
+  # 
+  # ggsave(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Results/Semantic/Sensitivity/allyears/window')) 
+  # 
+}
+

### 2016-09-07 Models/Semantic/semsensitivity.R
sens_plot

@@ -6,8 +6,7 @@ library(dplyr)
 library(igraph)
 source('networkConstruction.R')
 
-#years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE,sep=";")
-years=paste0(1976:2008,"-",1980:2012)
+years = read.csv(file=commandArgs(trailingOnly = TRUE)[1],header=FALSE,sep=";")
 
 # TODO read kwnum from file
 kwNum = "100000"
@@ -15,84 +14,83 @@ kwNum = "100000"
 type="giant"
 
 sizes=c()
-for(year in years){#i in 1:nrow(years)){
-  #yearRange=years[i,]
-  #year = paste0(as.character(yearRange[1]),"-",as.character(yearRange[length(yearRange)]))
+for(i in 1:nrow(years)){
+  yearRange=years[i,]
+  year = paste0(as.character(yearRange[1]),"-",as.character(yearRange[length(yearRange)]))
   show(year)
   
-  graph=paste0('relevant_',year,'_full_100000')
+  graph=paste0('relevant_',year,'_full_',kwNum)
   load(paste0('processed/',graph,'.RData'))
   nPatents = length(res$keyword_dico)
   sizes=append(sizes,nPatents)
-  
-#  g=res$g;
-#   rm(res);gc()
-#   
-#   g = filterGraph(g,'data/filter.csv')
-#   
-#   # TODO DO NOT USE giant component ?
-#   clust = clusters(g);
-#   cmax = which(clust$csize==max(clust$csize))
-#   if(type=="full"){ggiant=g}
-#   else{ggiant = induced.subgraph(g,which(clust$membership==cmax))}
-# 
-#   dd = V(ggiant)$docfreq
-#   d = degree(ggiant)
-#   
-#   kmin = 0
-#   
-#   modularities = c();
-#   comnumber=c();
-#   dmax=c();
-#   eth=c();
-#   csizes=c();
-#   gsizes=c();
-#   gdensity=c();
-#   cbalance=c();
-#   freqsmin=c();freqsmax=c();
-#   freqsmaxdec=c();kmaxsdec=c()
-#   comsizes=list()
-#   i=1
-#   
-#   #
-#   # freqmin and freqmax as proportion of patent number ?
-#   #  - freqmin can be independent in a first time ; as edge_th -
-#   #    freqmax = c(5000,10000,20000,50000) ; 95 : 144706 patents -> ~ 0.25 max
-#   for(freqmaxdec in c(0.025,0.05,0.15,0.25)){
[…]

### 2016-09-07 Models/Semantic/semsensitivityplot.R

@@ -11,11 +11,18 @@ kwNum = "100000"
 type="full"
 years=paste0(1976:2008,"-",1980:2012)
 
-for(year in years){
+# additional data for mse 
+load("processed/sizes-5years.RData")
+objdf = read.csv(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/processed/classes/distrib_class_grantdate.csv'),sep=";")
+
+
+for(y in 1:length(years)){
+  year=years[y]
   graph=paste0('relevant_',year,'_full_',kwNum)
   load(file=paste0('sensitivity/',graph,'_',type,'.RData'))
   names(d)[ncol(d)-5]="balance"
-  objdec=c(7,45,90,162,253,372,598,1023,2209)/length(res$keyword_dico)
+  #objdec=c(7,45,90,162,253,372,598,1023,2209)/sizes[y]
+  objdec=objdf[y,1:9]/sizes[y]
   # # load from classes file
   # 
   msesizes=c()
@@ -23,15 +30,18 @@ for(year in years){
     msesizes=append(msesizes,sum((log(quantile(comsizes[[i]],(1:9)/10)/d$vertices[i])-log(objdec))^2))
   }
   d=cbind(msesizes,d)
-  # 
-  # g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0)
-  # plots=list()
-  # for(indic in c("modularity","communities","components","vertices","msesizes","balance")){
-  #   plots[[indic]] = g+geom_raster(aes_string("degree_max","edge_th",fill=indic))+facet_grid(freqmax~freqmin)
-  # }
-  # multiplot(plotlist = plots,cols=3)
-  # 
-  # ggsave(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Results/Semantic/Sensitivity/allyears/window')) 
-  # 
+   
+   g = ggplot(d) + scale_fill_gradient(low="yellow",high="red")#+ geom_raster(hjust = 0, vjust = 0)
+   plots=list()
+   for(indic in c("modularity","communities","components","vertices","msesizes","balance")){
+     plots[[indic]] = g+geom_raster(aes_string("degree_max","edge_th",fill=indic))+facet_grid(freqmax~freqmin)
+   }
+   multiplot(plotlist = plots,cols=3)
+   
[…]

### 2016-12-25 Models/Semantic/semanalysis.R
tif_figures

@@ -206,7 +206,7 @@ for(year in wyears){
 resdir=paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Results/Semantic/Analysis/window5/overlap/')
 df=data.frame(overlap=overlaps,year=as.character(years),type=as.character(types),measure=measures)#,filter=filters)
 rm(overlaps,years,types);gc()
-save(df,file="res/full-overlaps.RData")
+#save(df,file="res/full-overlaps.RData")
 #load("res/full-overlaps.RData")
 
 plotsIntraOverlap <-function(measure,xlabel){
@@ -270,7 +270,7 @@ plotsIntraOverlap("relative","relative overlap")
 
 plotsInterOverlap <-function(measure,xlabel){
   g=ggplot(df[df$measure==measure&df$type=="inter-classifications",],aes(x=overlap,colour=year))
-  g+geom_density(alpha=0.25)+xlab(xlabel)+ylab("density")+scale_x_log10()
+  g+geom_density(alpha=0.25)+xlab(xlabel)+ylab("density")+scale_x_log10()+
     theme(axis.title = element_text(size = 22), axis.text.x = element_text(size = 15),  axis.text.y = element_text(size = 15))
   ggsave(file=paste0(Sys.getenv("CS_HOME"),'/PatentsMining/Results/Semantic/Analysis/window5/overlap/',measure,'_interclassif_all_density_semcounts.pdf'),width=10,height=5)
   

### 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
submission_and_arxi

\documentclass[12pt,twoside,a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[section]{placeins}
\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{etoolbox}
\usepackage{amsmath,amssymb}
\usepackage{float}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{nameref}
\usepackage{lscape}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
\hypersetup{
    colorlinks, linkcolor={dark-red},
    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
}
\geometry{hmargin=4cm,vmargin=4cm}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\setcounter{secnumdepth}{5}
\textwidth 6.0in
\textheight 8.84in 
\setlength{\topmargin}{-0.3in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{5pt}
\setlength{\textfloatsep}{25pt}  
\setlength{\intextsep}{5pt}   
\fancyhf{}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{1pt}
\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
\fancyfoot[C]{\thepage}

\begin{document}

\title{Classifying Patents Based on their Semantic Content\thanks{%
Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
 \ \ \ \ \ Juste Raimbault \bigskip}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the abstract below 300 words
\begin{abstract}
In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach. This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward. To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly. We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes. Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model. This suggests that our method is a useful tool to extract endogenous information.    
\end{abstract}

\pagebreak
%\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}. \cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation. Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis. Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review. Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}. With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters. Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.

Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies. But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share. Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g. ~\cite{AAKnetwork2016}).

In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it. In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract. Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach. The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence). One can for instance consider the case of the word \textit{optic}. Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic. This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.

Previous research has already proposed to use semantic networks to study technological domains and detect novelty. ~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain. The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}. More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation. Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).

Building on such previous research, we make several contributions by fulfilling some shortcomings of existing studies, such as for example the use of frequency-selected single keywords. First of all, we develop and implement a novel fully-automatized methodology to classify patents according to their semantic abstract content, which is to the best of our knowledge the first of its type. This includes the following refinements for which details can be found in Section \ref{keywords}: (i) use of multi-stems as potential keywords; (ii) filtering of keywords based on a second-order (co-occurrences) relevance measure and on an external independent measure (technological dispersion); (iii) multi-objective optimization of semantic network modularity and size. The use of all this techniques in the context of semantic classification is new and essential from a practical perspective.

Furthermore, most of the existing studies rely on a subsample of patent data, whereas we implement it on the full US Patent database from 1976 to 2013. This way, a general structure of technological innovation can be studied. We draw from this application promising qualitative stylized facts, such as a qualitative regime shift around the end of the 1990s, and a significant improvement of citation modularity for the semantic classification when comparing to the technological classification. These thematic conclusions validate our method as a useful tool to extract endogenous information, in a complementary way to the technological classification.

Finally, the statistical model introduced in Section \ref{statisticalmodel} seems to indicate that patents tend to cite more similar patents in the semantic network  when fitted to data. In particular, this propensity is shown to be significantly bigger than the corresponding propensity for technological classes, and this seems to be consistent over time. On the account of this information, we believe that patent officers could benefit very much from looking at the semantic network when considering potential citation candidates of a patent in review.

The paper is organized as follows. Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process. Section \ref{keywords} explains the construction of the semantic classes. Section \ref{result} tests their relevance by providing exploratory results. Finally, section \ref{discussion} discusses potential further developments and conclude. More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.

%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background \label{data}}
%%%%%%%%%%%%%%%%%%%%%%%%

In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013. A clearer definition of utility patent is given in~\nameref{sectionSI}. Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.

%%%%%%%%%%%%%%%%%%%%%
\subsection{An existing classification: the USPC system}

Each USPTO patent is associated with a non-empty set of technological classes and subclasses. There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system. While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention. A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass. At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes. When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A bibliographical network between patents: citations \label{sub:citation}}

As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art. They therefore indicate the past knowledge which relates to the patented invention. Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent. One can consult~\cite{oecdpatentmanual} for more details about this. Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}). Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves. 
From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations). We can thus build a complete network of citations that we will use later on in the analysis.

Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years. This distribution is highly skewed, the $95^{th}$ percentile is 21 years. We also report 164,000 citations with a negative time lag. This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others.

In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years. We impose this restriction for two reasons. First, the number of citations received peaks 4-5 years after application. Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones. As we are restricting to citations received no later than 5 years after the application date, this effect will only affect patents with an application date after 2007.

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}
Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis. Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size. In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}). The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}. The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.

We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013. When distributed by the year of application, the picture is slightly different. The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007. Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents. These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}. Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window. 270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations. A within class citation is defined as a citation between two patents sharing at least one common technological class. Following this definition, 84\% of the citations are within class citations. 14\% of the citations are between two patents that share the exact same set of technological classes.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Towards a Complementary Classification}

Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}. The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications. The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review). Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}. As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored. One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples. Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies. Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}). Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.

%%%%%%%%%%%%%%%%%%%%%
\section{Semantic Classification Construction \label{keywords}}

In this section, we describe methods and empirical analysis leading to the construction of semantic network and the corresponding classification.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords extraction}
\label{keywordsextraction}

Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
\begin{enumerate}
\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).

\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.

\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens. At this point the abstract text is reduced to a set of stems and their grammatical functions.
\item Multi-stems construction: these are the basic semantic units used in further analysis. They are constructed as groups of successive stems in a sentence which satisfies a simple grammatical function rule. The length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives. We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
\end{enumerate}

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining} 
}

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\label{keywords_est}
\paragraph{Relevance definition}

Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords. We choose to set this parameter to $K_w = 100,000$. We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed. This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$. The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is defined as

\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\]

\paragraph{Moving window estimation}
The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$. Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}. In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.

%%%%%%%%%%%%%%%%%%%%
\subsection{Construction of the semantic network}
\label{construction}

We keep the set of most relevant keywords $\mathcal{K}_W$ and obtain their co-occurrence matrix as defined in Section \ref{keywords_est}. This matrix can be directly interpreted as the weighted adjacency matrix of the semantic network. At this stage, the topology of raw networks does not allow the extraction of clear communities. This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g. \texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant. We therefore introduce an additional measure to correct the network topology: the concentration of keywords across technological classes, defined as:

$$c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2},$$

where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes. The higher $c_{tech}$, the more specific to a technological class the node is. For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field. We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$. In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time. To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$). Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$. At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward. Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities. We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$. Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\hspace{-2.5cm}
\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical. \textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values. The maximum is roughly stable across $\theta_c$ (dashed red line). \textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
\label{fig:networksensitivity}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{striking}
%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$. The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
\label{fig:rawnetwork}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

\subsection{Characteristics of Semantic Classes}
\label{characteristics}
For each year $t$, we define as $N^{(sem)}_t$ the number of semantic classes which have been computed by clustering keywords from patents appeared during the period $\big[ t-T_0, t \big]$ (we recall that we have chosen $T_0=4$). Each semantic class $k =  1, \cdots, N^{(sem)}_t$ is characterized by a set of keywords $K(k,t)$ which is a subset of $\mathcal{K}_W$ selected as described in Section \ref{keywordsextraction} to Section \ref{construction}. The cardinal of $K(k, t)$ distribution across each semantic class $k$ is highly skewed with a few semantic classes containing over $1,000$ keywords, most of them with roughly the same number of keywords. In contrast, there are also many semantic classes with only two keywords. There are around 30 keywords by semantic class on average and the median is 2 for any $t$. Fig.~\ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{meancomsize}
%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
\label{fig:mean_K}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

\paragraph*{Title of semantic classes}
USPC technological classes are defined by a title and a highly accurate definition which help retrieve patents easily. The title can be a single word (e.g.: class 101: ``Printing'') or more complex (e.g.: class 218: ``High-voltage switches with arc preventing or extinguishing devices''). As our goal is to release a comprehensive database in which each patent is associated with a set of semantic classes, it is necessary to give an insight on what these classes represent by associating a short description or a title as in~\cite{tseng2007text}. In our case, such description is taken as a subset of keywords taken from $K(k,t)$. For the vast majority of semantic classes that have less than 5 keywords, we decide to keep all of theses keywords as a description. For the remaining classes which feature around 50 keywords on average, we rely on the topological properties of the semantic network.~\cite{yang2000improving} suggest to retain only the most frequently used terms in $K(k,t)$. Another possibility is to select 5 keywords based on their network centrality with the idea that very central keywords are the best candidates to describe the overall idea captured by a community. For example, the largest semantic class in 2003-2007 is characterized by the keywords: \texttt{Support Packet; Tree Network; Network Wide; Voic Stream; Code Symbol Reader}.

\paragraph*{Size of technological and semantic classes} 
We consider a specific window of observations (for example 2000-2004), and we define $Z$ the number of patents which appeared during that time window. For each patent $i=1, \cdots, Z$ we associate a vector of probability where each component $p_{ij}^{(sem)} \in \big[ 0,1 \big]$, with  $j = 1, \cdots, N{(sem)}$ and where\footnote{When there is no room for confusion, we drop the subscript $t$ in $N_t^{(sem)}$.} 
$$\displaystyle \sum_{j=1}^{N^{(sem)}} p_{ij}^{(sem)} = 1.$$ On average across all time windows, a patent is associated to 1.8 semantic classes with a positive probability. Next we define the size of a semantic class as $$S_j^{(sem)} = \displaystyle \sum_{i=1}^Z p_{ij}^{(sem)}.$$ 
Correspondingly, we aim to provide a consistent definition for technological classes. For that purpose, we follow the so-called ``fractional count'' method, which was introduced by the USPTO and consists in dividing equally the patents between all the classes they belong to. Formally, we define the number of technological classes as
$N^{(tec)}$  (which is not time dependent contrary to the semantic case) and for $j = 1, \cdots, N^{(tec)}$ the corresponding matrix of probability is defined as
\[
 p_{ij}^{(tec)} = \frac{B_{ij}}{\displaystyle \sum_{k=1}^{N^{(tec)}}{B_{ik}}},
\]
where  $B_{ij}$ equals $1$ if the $i$th patent belongs to the $j$th technological class and $0$ if not. When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix. Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Fig.~\ref{fig:class-sizes}. This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-2.5cm}
\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$, 
from the biggest to the smallest. The formal definition of size can be found in Section \ref{characteristics}. Each color corresponds to one specific year. Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications. This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}. Over time, curves are translated and levels of hierarchy stays roughly constant.}
\label{fig:class-sizes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Potential Refinements of the Method}

Our semantic classification method could be refined by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method (e.g.~\cite{blei2003latent}), already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a field rather than distant technological recombination. Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation). Also, depending on the level of orthogonality with our classification, it can potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.

Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis. Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links. \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper. Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.

%%%%%%%%%%%%%%%%%%%%%%
\section{Results \label{result}}
%%%%%%%%%%%%%%%%%%%%%

In this section, we present some key features of our resulting semantic classification showing both complementary and differences with the technological classification. We first present several measures derived from this semantic classification at the patent level: Diversity, Originality, Generality (Section \ref{subsec:orig-gene}) and Overlapping (Section \ref{subsec:overlaps}). We then show that the two classifications show highly
different topological measures and strong statistical evidence that they feature a different model (Sections \ref{citationmodularity} and \ref{statisticalmodel}).

%%%%%%%%%%%%%%%%%%%%%%

\subsection{Patent Level Measures}  \label{subsec:orig-gene}

Given a classification system (technological or semantic classes), and the associated probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ (that were defined in Section \ref{characteristics}), one can define a patent-level diversity measure as one minus the Herfindhal concentration index on $p_{ij}$  by

\[
D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}.
\]

We show in Fig.~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series. This is carried with two different settings, namely including/not including patents with zero diversity (i.e. single class patents). We call other patents ``complicated patents'' in the following. First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes. More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization. This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}. Furthermore, a qualitative regime shift on semantic classification occurs around 1996. This can be seen whether or not we include patents with zero diversity. The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease. This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity. It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents.

More commonly used in the literature are the measures of originality and generality. These measures follow the same idea than the above-defined diversity in quantifying the diversity of classes (whether technological or semantic) associated with a patent. But instead of looking at the patent's classes, they consider the classes of the patents that are cited or citing. Formally, the originality $O_i$ and the generality $G_i$ of a patent $i$ are defined as
\[
O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2} \text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2}, 
\]
where $z \in \{tec, sem\}$, $I_i$ denotes the set of patents that are cited by the $i$th patent within a five year window (i.e. if the $i$th patent appears at year $t$, then we consider patents on $[t-T_0, t]$) when considering the originality and $\tilde{I}_i$ the set of patents that cite patent $i$ after less than five years (i.e. we consider patents on $[t ,t + T_0]$) in the case of generality. Note that the measure of generality is forward looking in the sense that $G_i^{(z)}$ used information that will only be available 5 years after patent applications. Both measures are lower on average based on semantic classification than on technological classification. Fig. \ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%First row : semantic with relevant keywords only - all patents 
\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
%Second row : patents with diversity $> 0$ (more than one class)}
\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
\caption{
\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$). The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e. patents with diversity greater than 0).
}
\label{fig:patent-level-orig}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=0.49\textwidth]{originality.png}
\includegraphics[width=0.49\textwidth]{generality.png}\\
%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}. }
\label{fig:orig-gene}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classes overlaps} \label{subsec:overlaps}

A proximity measure between two classes can be defined by their overlap in terms of patents. 
Such measures could for example be used to construct a metrics between semantic classes. Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{Bloom2005distance}. Formally, recalling the definition of $\left(p_{ij}\right)$ as the probability for the $i$th patent to belong to the $j$th class and $N_P$ as the number of patents it writes 
\begin{eqnarray}
\label{overlap}
Overlap_{jk} = \frac{1}{N_P}\cdot \sum_{i=1}^{N_P} p_{ij} p_{ik}. 
\end{eqnarray}

The overlap is normalized by patent count to account for the effect of corpus size: by convention, we assume the overlap to be maximal when there is only one class in the corpus. A corresponding relative overlap is computed as a set similarity measure in the number of patents common to two classes A and B, given by $o(A,B)=2\cdot \frac{\left|A\cap B\right|}{\left|A\right| + \left|B\right|}$.

\paragraph{Intra-classification overlaps}

The study of distributions of overlaps inside each classification, i.e. between technological classes and between semantic classes separately, reveals the structural difference between the two classification methods, suggesting their complementary nature. Their evolution in time can furthermore give insights into trends of specialization. We show in Fig.~\ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications. The technological classification globally always follow a decreasing trend, corresponding to more and more isolated classes, i.e. specialized inventions, confirming the stylized fact obtained in previous subsection. For semantic classes, the dynamic is somehow more intriguing and supports the story of a qualitative regime shift suggested before. Although globally decreasing as technological overlap, normalized (resp. relative) mean overlap exhibits a peak (clearer for normalized overlap) culminating in 1996 (resp. 1999). Looking at normalized overlaps, classification structure was somewhat stable until 1990, then strongly increased to peak in 1996 and then decrease at a similar pace up to now. Technologies began to share more and more until a breakpoint when increasing isolation became the rule again. An evolutionary perspective on technological innovation~\cite{ziman2003technological} could shed light on possible interpretations of this regime shift: as species evolve, the fitness landscape first would have been locally favorable to cross-insemination, until each fitness reaches a threshold above which auto-specialization becomes the optimal path. It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation. 
%This interpretation is consistent with the dynamics of semantic flows presented in Fig.~\ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
\caption{
\textbf{Intra-classification overlaps.}
\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale). \textit{(Right column)} Corresponding mean time-series. \textit{(First row)} Normalized overlaps. \textit{(Second row)} Relative overlaps.}
\label{fig:intra-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Inter-classification overlaps}

Overlaps \emph{between} classifications are defined as in (\ref{overlap}), but with $j$ standing for the $j$th technological class and $k$ for the $k$th semantic class: $p_{ij}$ are technological probabilities and $p_{ik}$ semantic probabilities. They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Fig.~\ref{fig:inter-classif-overlap}. Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease. Although difficult to interpret directly, this stylized fact clearly unveils a change in the \emph{nature} of inventions, or at least in the relation between content of inventions and technological classification. As the tipping point is at the same time as the ones observed in the previous section and since the two statistics are different, it is unlikely that this is a mere coincidence. Thus, these observations could be markers of a hidden underlying structural changes in processes.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series. The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
\label{fig:inter-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Citation Modularity}
\label{citationmodularity}

An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}. The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\cite{AAKnetwork2016}). This section studies empirically modularities of the citation network regarding the different classifications. To corroborate the obtained results, we propose to look at a more rigorous framework in Section \ref{statisticalmodel}. Modularity is a simple measure of how communities in a network are well clustered (see \cite{clauset2004finding} for the accurate definition). Although initially designed for single-class classifications, this measure can be extended to the case where nodes can belong to several classes at the same time, in our case with different probabilities as introduced in \cite{nicosia2009extending}. The simple directed modularity is given in our case by
\[
Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
\]
with $A_{ij}$ the citation adjacency matrix (i.e. $A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not), $k_i^{in}=\left| I_i\right|$ (resp. $k_i^{out}= \left|\tilde{I}_i \right|$) in-degree (resp. out-degree) of patents (i.e. the number of citations made by the $i$th patent to others and the number of citations received by the $i$th patent). $Q_d$ can be defined for each of the two classification systems: $z \in \{tec, sem\}$. If $z=tec$, $c_i$ is defined as the main patent class, which is taken as the first class whereas if $z=sem$, $c_i$ is the class with the largest probability.

Multi-class modularity in turns is given by

\[
\displaystyle Q_{ov}^{(z)} = \frac{1}{N_P} \sum_{c = 1}^{N^{(z)}} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,c}^{out}k_i^{out}\beta_{j,c}^{in}k_j^{in}}{N_P}\right],
\]
where
\[
 \beta_{i,c}^{out} =   \frac{1}{N_P} \displaystyle \sum_j F(p_{ic},p_{jc}) \text{ and } \beta_{j,c}^{in} =  \frac{1}{N_P} \displaystyle \sum_i F(p_{ic},p_{jc}).
\]
We take $F(p_{ic},p_{jc}) = p_{ic}\cdot p_{jc}$ as suggested in \cite{nicosia2009extending}. Modularity is an aggregated measure of how the network deviates from a null model where links would be randomly made according to node degree. In other words it captures the propensity for links to be inside the classes. Overlapping modularity naturally extends simple modularity by taking into account the fact that nodes can belong simultaneously to many classes.
We document in Fig.~\ref{fig:modularities} both simple and multi-class modularities over time. For simple modularity, $Q_d^{(tec)}$ is low and stable across the years whereas $Q_d^{(sem)}$ is slightly greater and increasing. These values are however low and suggest that single classes are not sufficient to capture citation homophily. Multi-class modularities tell a different story. First of all, both classification modularities have a clear increasing trend, meaning that they become more and more adequate with citation network. The specializations revealed by both patent level diversities and classes overlap is a candidate explanation for this growing modularities. Secondly, semantic modularity dominates technological modularity by an order of magnitude (e.g. 0.0094 for technological against 0.0853 for semantic in 2007) at each time. This discrepancy has a strong qualitative significance. Our semantic classification fits better the citation network when using multiple classes. As technologies can be seen as a combination of different components as shown by~\cite{Youn:2015fk}, this heterogeneous nature is most likely better taken into account by our multi-class semantic classification.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\textwidth]{simplemodularity}
\includegraphics[width=0.49\textwidth]{overlappingmodularity}
%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability). (Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
\label{fig:modularities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical Model}
\label{statisticalmodel}
In this section, we develop a statistical model aimed at quantifying performance of both technological and semantic classification systems. In particular, we aim at corroborating findings obtained in Section \ref{citationmodularity}. The mere difference between this approach and the citation modularity approach lies in the choice of the underlying model, and the according quantities of interest. In addition for the semantic approach, we want to see if when restricting to patents with higher probabilities to belong to a class, we obtain better results. To do that, we choose to look at within class citations proportion (for both technological and semantic approaches). We provide two obvious reasons why we choose this. First, the citations are commonly used as a proxy for performance as mentioned in Section \ref{citationmodularity}. Second, this choice is ``statistically fair'' in the sense that both approaches have focused on various goals and not on maximizing directly the within class proportion. 
Nonetheless, the within class proportion is too sensitive to the distribution of the shape of classes. For example, a dataset where patents for each class account for 10\% of the total number of patents will mechanically have a better within class proportion than if each class accounts for only 1\%. Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed. This effort ressembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth. Furthermore, the parameters fitted here can have a direct interpretation as a citation probability.

We need to introduce and recall some notations. We consider a specific window of observations $\big[t- T_0, t \big]$, and we define $Z$ the number of patents which appeared during that time window. We let $t_1, \cdots, t_Z$ their corresponding appearance date by chronological order, which for simplicity are assumed to be such that $t_1 < \cdots < t_Z$. For each patent $i=1, \cdots, Z$ we consider $C_i$ the number of distinctive couples \{cited patent, cited patent's class\} made by the $i$th patent (for instance if the $i$th patent has only made one citation and that the cited patent is associated with three classes, then $C_i = 3$). Let $z \in \{tec, sem\}$, we define $N_{i}^{(z)}$  the number of patents associated to at least one of the $i$th classes at time $t_{i-1}$. For $l = 1, \cdots, C_i$ we consider the variables $B_{l,i}$, which equal $1$ if the cited patent's class is also common to the $i$th patent. We assume that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables 
$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
where the parameter $0 \leq \theta^{(z)} \leq 1$ indicates the propensity for any patent to cite patents of its own technological or semantic class. When $\theta^{(z)} = 0$, the probability of citing patents from its own class is simply $N_{i}^{(z)}(i-1)^{-1}$, which corresponds to the observed proportion of patents which belong to at least one of the $i$th patent's classes. Thus this corresponds to the estimated probability of citing one patent if we assume that the probability of citing any patent $k=1, \cdots, i-1$ is uniformly distributed, which could be a reasonable assumption if classes were assigned randomly and independently from patent abstract contents. Conversely if $\theta^{(z)} = 1$, we are in the case of a model where there are 100\% of within class citations. A reasonable choice of $\theta^{(z)}$ lies between those two extreme values. Finally, we assume that the number of distinctive couples $C_i$ are a sequence of independent and identically distributed random variables following the discrete distribution $C$, and also independent from the other quantities.

We estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding maximum likelihood estimator (MLE) $\hat{\theta}^{(z)}$. The likelihood function, along with the standard deviation expression and details about the test, can be found in~\nameref{sectionSI}. The fitted values, standard errors and p-values corresponding to the statistical test $\theta^{(sem)} = \theta^{(tec)}$ (with corresponding alternative hypothesis $\theta^{(sem)} > \theta^{(tec)}$) on non-overlapping blocks from the period 1980-2007\footnote{Note that the estimation included patents up until 2010 in the period 2006-2007 and not the patents from 1980 in the period 1980-1985 for homogeneity in size with other periods. This doesn't affect the significativity of the results.} are reported on Table \ref{summary}. Semantic values are reported for four different chosen thresholds $p^{-}=.04, .06, .08, .1$. It means that we restricted to the couples ($i$th patent, $j$th class) such that $p_{ij} \geq p^{-}$.

The choice of considering non-overlapping blocks (instead of overlapping blocks) is merely statistical. Ultimately, our interest is in the significance of the test over the whole period 1980-2007. Thus, we want to compute a global p-value. This can be done considering the local p-values (by local, we mean for instance computed on the period 2001-2005) assuming independence between them. This assumption is reasonable only if the blocks are non-overlapping. All of this can be found in~\nameref{sectionSI}. Finally, note that from a statistical perspective, including overlapping blocks wouldn't yield more information.

The values reported in Table \ref{summary} are overwhelmingly against the null hypothesis. The global estimates of $\theta^{(sem)}$ are significantly bigger than the estimate of $\theta^{(tec)}$ for all the considered thresholds. Although the corresponding p-values (which are also very close to 0) are not reported, it is also quite clear that the bigger the threshold, the higher the corresponding $\theta^{(sem)}$ is estimated. This is consistently seen for any period, and significant for the global period. This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propension to cite patents from its own class $\theta^{(sem)}$ is increasing. We believe that this might provide extra information to patent officers when making their choice of citations. Indeed, they could look first to patents which belong to the same semantic class, especially when patents have high probability semantic values.

Note that the introduced model can be seen as a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g. \cite{decelle2011asymptotic}, \cite{valles2016multilayer}). The parameters are estimated computing the corresponding MLE. In view of~\cite{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.

\begin{table}[!ht]
\centering
\caption{\label{summary} Estimated values of $\theta^{(tec)}$ and $\theta^{(sem)}$ and corresponding standard errors obtained from a Maximum Likelihood estimator as presented in section \ref{statisticalmodel}.}
\label{stdQMLE}
\begin{tabular}{@{}rccccccccc@{}}
\toprule
\toprule
\multicolumn{1}{l}{Approach} & \multicolumn{1}{l}{Estimated Value} & \multicolumn{1}{l}{st. er.} & \multicolumn{1}{l}{p-value} \\ \toprule
\multicolumn{4}{l}{1980-1985 period} \\
technological & .664 &.008&\\
semantic $p^{-} = .04$ & .741 &.047 & .053\\
semantic $p^{-} = .06$ & .799 &.081 & .049\\
semantic $p^{-} = .08$ & .828 &.126 & .097\\
semantic $p^{-} = .10$ & .834 &.166 & .153\\
\multicolumn{4}{l}{1986-1990 period} \\
technological & .634 &.007&\\
semantic $p^{-} = .04$ & .703 &.022 & .001\\
semantic $p^{-} = .06$ & .768 &.040 & .0004\\
semantic $p^{-} = .08$ & .804 &.069 & .007\\
semantic $p^{-} = .10$ & .832 &.114 & .041\\
\multicolumn{4}{l}{1991-1995 period} \\
technological & .619 &.006&\\
semantic $p^{-} = .04$ & .655 &.009 & .0004\\
semantic $p^{-} = .06$ & .713 &.017 & 9e-08\\
semantic $p^{-} = .08$ & .731 &.025 & 7e-06\\
semantic $p^{-} = .10$ & .750 &.037 & 9e-06\\
\multicolumn{4}{l}{1996-2000 period} \\
technological & .551 &.003&\\
semantic $p^{-} = .04$ & .585 &.002 & $\approx 0$\\
semantic $p^{-} = .06$ & .638 &.004 & $\approx 0$\\
semantic $p^{-} = .08$ & .660 &.006 & $\approx 0$\\
semantic $p^{-} = .10$ & .686 &.008 & $\approx 0$\\
\multicolumn{4}{l}{2001-2005 period} \\
technological & .567 &.003&\\
semantic $p^{-} = .04$ & .621 &.004 & $\approx 0$\\
semantic $p^{-} = .06$ & .676 &.007 & $\approx 0$\\
semantic $p^{-} = .08$ & .701 &.010 & $\approx 0$\\
semantic $p^{-} = .10$ & .710 &.013 & $\approx 0$\\
\multicolumn{4}{l}{2006-2007 period} \\
technological & .600 &.007&\\
semantic $p^{-} = .04$ & .683 &.016 & 1e-06\\
semantic $p^{-} = .06$ & .732 &.025 & 2e-07\\
semantic $p^{-} = .08$ & .760 &.036 & 6e-06\\
semantic $p^{-} = .10$ & .782 &.048 &9e-05\\
\multicolumn{4}{l}{1980-2007 global period} \\
technological & .606 &.002&\\
semantic $p^{-} = .04$ & .665 &.009 & 8e-11\\
semantic $p^{-} = .06$ & .721 &.017 & 9e-12\\
semantic $p^{-} = .08$ & .747 &.025 & 9e-09\\
semantic $p^{-} = .10$ & .782 &.035 & 3e-07\\
\bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion \label{discussion}}
%%%%%%%%%%%%%%%%%%%%%

The main contribution of this study was twofold. First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts. We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features. Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...). The availability of these data suggests new avenues for further research.

A first potential application is to use the patents' topological measures inherited from their relevant keywords. The fact that these measures are backward-looking and immediately available after the publication of the patent information is an important asset. It would for example be very interesting to test their predicting power to assess the quality of an innovation, using the number of forward citations received by a patent, and subsequently the future effect on the firm's market value.

Regarding firm innovative strategy, a second extension could be to study trajectories of firms in the two networks: technological and semantic. Merging these information with data on the market value of firms can give a lot of insight about the more efficient innovative strategies, about the importance of technology convergence or about acquisition of small innovative firms. It will also allow to observe innovation pattern over a firm life cycle and how this differ across technology field.

A third extension would be to use dig further into the history of innovation. USPTO patent data have been digitized from the first patent in July 1790. However, not all of them contain a text that is directly exploitable. We consider that the quality of patent's images is good enough to rely on Optical Character Recognition techniques to retrieve plain text from at least 1920. With such data, we would be able to extend our analysis further back in time and to study how technological progress occurs and combines in time. \cite{akcigit2013mechanics} conduct a similar work by looking at recombination and apparition of technological subclasses.
Using the fact that communities are constructed yearly, one can construct a measure of proximity between two successive classes. This could give clear view on how technologies converged over the year and when others became obsolete and replaced by new methods.

%%%%%%%%%%%%%%%%%%%%%

\section*{Supporting Information \label{sectionSI}}
% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.

\subsection*{S1 Text : Definition of utility patent}

\textbf{Describes with more details the definition of patents and  context.}

\subsection*{S2 Text : Data collection procedure}

\textbf{Detailed description of data collection}

\subsection*{S3 File : Semantic Network Visualization}

\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}

\subsection*{S4 Text : Network Sensitivity Analysis\label{app:sensitivity}}

\textbf{Extended figures for Network Sensitivity Analysis}

\subsection*{S5 Text : Statistical definitions and derivations}

\textbf{Extended definitions and derivations for the statistical model}

%%%%%%%%%%%%%%%%%%%%%
%\section*{Acknowledgments}

%\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%

%\bibliographystyle{plos2015}
%\bibliography{patents}

\begin{thebibliography}{10}

\bibitem{aghionhowitt1992}
Aghion P, Howitt P.
\newblock {A Model of Growth through Creative Destruction}.
\newblock Econometrica. 1992 March;60(2):323--51.
\newblock Available from:
  \url{https://ideas.repec.org/a/ecm/emetrp/v60y1992i2p323-51.html}.

\bibitem{romer1990}
Romer PM.
\newblock {Endogenous Technological Change}.
\newblock Journal of Political Economy. 1990 October;98(5):S71--102.
\newblock Available from:
  \url{https://ideas.repec.org/a/ucp/jpolec/v98y1990i5ps71-102.html}.

\bibitem{RePEc:nbr:nberwo:3301}
Griliches Z.
\newblock {Patent Statistics as Economic Indicators: A Survey}.
\newblock National Bureau of Economic Research, Inc; 1990. 3301.
\newblock Available from: \url{https://ideas.repec.org/p/nbr/nberwo/3301.html}.

\bibitem{Hall2001}
Hall BH, Jaffe AB, Trajtenberg M.
\newblock {The NBER Patent Citations Data File: Lessons, Insights and
  Methodological Tools}.
\newblock C.E.P.R. Discussion Papers; 2001. 3094.
\newblock Available from: \url{https://ideas.repec.org/p/cpr/ceprdp/3094.html}.

\bibitem{Youn:2015fk}
Youn H, Strumsky D, Bettencourt LMA, Lobo J.
\newblock Invention as a combinatorial process: evidence from US patents.
\newblock Journal of The Royal Society Interface. 2015;12(106).

\bibitem{2013arXiv1310.8220N}
{Newman} MEJ.
\newblock {Prediction of highly cited papers}.
\newblock ArXiv e-prints. 2013 Oct;.

\bibitem{2014arXiv1402.7268S}
{Sarig{\"o}l} E, {Pfitzner} R, {Scholtes} I, {Garas} A, {Schweitzer} F.
\newblock {Predicting Scientific Success Based on Coauthorship Networks}.
\newblock ArXiv e-prints. 2014 Feb;.

\bibitem{sorenson2006complexity}
Sorenson O, Rivkin JW, Fleming L.
\newblock Complexity, networks and knowledge flow.
\newblock Research policy. 2006;35(7):994--1017.

\bibitem{kay2014patent}
Kay L, Newman N, Youtie J, Porter AL, Rafols I.
\newblock Patent overlay mapping: Visualizing technological distance.
\newblock Journal of the Association for Information Science and Technology.
  2014;65(12):2432--2443.

\bibitem{bruck2016recognition}
Bruck P, R{\'e}thy I, Szente J, Tobochnik J, {\'E}rdi P.
\newblock Recognition of emerging technology trends: class-selective study of
  citations in the US Patent Citation Network.
\newblock Scientometrics. 2016;107(3):1465--1475.

\bibitem{curran2011patent}
Curran CS, Leker J.
\newblock Patent indicators for monitoring convergence--examples from NFF and
  ICT.
\newblock Technological Forecasting and Social Change. 2011;78(2):256--273.

\bibitem{Katz1996remarks}
Katz ML.
\newblock Remarks on the economic implications of convergence.
\newblock Industrial and Corporate Change. 1996;5(4):1079--1095.

\bibitem{Furman2011shoulders}
Furman JL, Stern S.
\newblock Climbing atop the Shoulders of Giants: The Impact of Institutions on
  Cumulative Research.
\newblock American Economic Review. 2011 August;101(5):1933--63.
\newblock Available from:
  \url{http://www.aeaweb.org/articles?id=10.1257/aer.101.5.1933}.

\bibitem{AAKnetwork2016}
Acemoglu AU Daron, Kerr W.
\newblock {Innovation Network}.
\newblock Proceedings of the National Academy of Sciences (forthcoming). 2016;.

\bibitem{preschitschek2013}
Preschitschek N, Niemann H, Leker J, Moehrle MG.
\newblock Anticipating industry convergence: Semantic analyses vs IPC
  co-classification analyses of patents.
\newblock Foresight. 2013 11;15(6):446--464.

\bibitem{yoon2004text}
Yoon B, Park Y.
\newblock A text-mining-based patent network: Analytical tool for
  high-technology trend.
\newblock The Journal of High Technology Management Research.
  2004;15(1):37--50.

\bibitem{park2014semantic}
Park I, Yoon B.
\newblock A semantic analysis approach for identifying patent infringement
  based on a product--patent map.
\newblock Technology Analysis \& Strategic Management. 2014;26(8):855--874.

\bibitem{yoon2011detecting}
Yoon J, Kim K.
\newblock Detecting signals of new technological opportunities using semantic
  patent analysis and outlier detection.
\newblock Scientometrics. 2011;90(2):445--461.

\bibitem{gerken2012new}
Gerken JM, Moehrle MG.
\newblock A new instrument for technology monitoring: novelty in patents
  measured by semantic patent analysis.
\newblock Scientometrics. 2012;91(3):645--670.

\bibitem{choi2014patent}
Choi J, Hwang YS.
\newblock Patent keyword network analysis for improving technology development
  efficiency.
\newblock Technological Forecasting and Social Change. 2014;83:170--182.

\bibitem{fattori2003text}
Fattori M, Pedrazzi G, Turra R.
\newblock Text mining applied to patent mapping: a practical business case.
\newblock World Patent Information. 2003;25(4):335--342.

\bibitem{2015arXiv151003797G}
{Gurciullo} S, {Smallegan} M, {Pereda} M, {Battiston} F, {Patania} A, {Poledna}
  S, et~al.
\newblock {Complex Politics: A Quantitative Semantic and Topological Analysis
  of UK House of Commons Debates}.
\newblock ArXiv e-prints. 2015 Oct;.

\bibitem{lerner2015use}
Lerner J, Seru A.
\newblock The use and misuse of patent data: Issues for corporate finance and
  beyond.
\newblock Booth/Harvard Business School Working Paper. 2015;.

\bibitem{oecdpatentmanual}
OECD.
\newblock OECD Patent Statistics Manual. 2009;Available from:
  \url{/content/book/9789264056442-en}.

\bibitem{martin2015}
Dechezlepretre A, Martin R, Mohnen M.
\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
\newblock Centre for Economic Performance, LSE; 2014. dp1300.
\newblock Available from:
  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.

\bibitem{tseng2007text}
Tseng YH, Lin CJ, Lin YI.
\newblock Text mining techniques for patent analysis.
\newblock Information Processing \& Management. 2007;43(5):1216--1247.

\bibitem{Adams2010text}
Adams S.
\newblock {The text, the full text and nothing but the text: Part 1 - Standards
  for creating textual information in patent documents and general search
  implications}.
\newblock World Patent Information. 2010 March;32(1):22--29.
\newblock Available from:
  \url{https://ideas.repec.org/a/eee/worpat/v32y2010i1p22-29.html}.

\bibitem{abbas2014literature}
Abbas A, Zhang L, Khan SU.
\newblock A literature review on the state-of-the-art in patent analysis.
\newblock World Patent Information. 2014;37:3--13.

\bibitem{chavalarias2013phylomemetic}
Chavalarias D, Cointet JP.
\newblock Phylomemetic patterns in science evolution---the rise and fall of
  scientific fields.
\newblock Plos One. 2013;8(2):e54847.

\bibitem{nltk}
NLTK. Natural Language Toolkit, Stanford University; 2015.

\bibitem{clauset2004finding}
Clauset A, Newman ME, Moore C.
\newblock Finding community structure in very large networks.
\newblock Physical review E. 2004;70(6):066111.

\bibitem{yang2000improving}
Yang Y, Ault T, Pierce T, Lattimer CW.
\newblock Improving text categorization methods for event tracking.
\newblock In: Proceedings of the 23rd annual international ACM SIGIR conference
  on Research and development in information retrieval. ACM; 2000. p. 65--72.

\bibitem{blei2003latent}
Blei DM, Ng AY, Jordan MI.
\newblock Latent dirichlet allocation.
\newblock Journal of machine Learning research. 2003;3(Jan):993--1022.

\bibitem{kaplan2015double}
Kaplan S, Vakili K.
\newblock The double-edged sword of recombination in breakthrough innovation.
\newblock Strategic Management Journal. 2015;36(10):1435--1457.

\bibitem{iacovacci2015mesoscopic}
Iacovacci J, Wu Z, Bianconi G.
\newblock Mesoscopic Structures Reveal the Network Between the Layers of
  Multiplex Datasets.
\newblock arXiv preprint arXiv:150503824. 2015;.

\bibitem{de2015ranking}
De~Domenico M, Sol{\'e}-Ribalta A, Omodei E, G{\'o}mez S, Arenas A.
\newblock Ranking in interconnected multilayer networks reveals versatile
  nodes.
\newblock Nature communications. 2015;6.

\bibitem{ARCHIBUGI199279}
Archibugi D, Pianta M.
\newblock Specialization and size of technological activities in industrial
  countries: The analysis of patent data.
\newblock Research Policy. 1992;21(1):79 -- 93.
\newblock Available from:
  \url{http://www.sciencedirect.com/science/article/pii/0048733392900283}.

\bibitem{Bloom2005distance}
Bloom N, Schankerman M, Reenen JV.
\newblock {Identifying Technology Spillovers and Product Market Rivalry}.
\newblock Econometrica. 2013 07;81(4):1347--1393.
\newblock Available from:
  \url{https://ideas.repec.org/a/ecm/emetrp/v81y2013i4p1347-1393.html}.

\bibitem{ziman2003technological}
Ziman J.
\newblock Technological innovation as an evolutionary process.
\newblock Cambridge University Press; 2003.

\bibitem{holland2012signals}
Holland JH.
\newblock Signals and boundaries: Building blocks for complex adaptive systems.
\newblock Mit Press; 2012.

\bibitem{nicosia2009extending}
Nicosia V, Mangioni G, Carchiolo V, Malgeri M.
\newblock Extending the definition of modularity to directed graphs with
  overlapping communities.
\newblock Journal of Statistical Mechanics: Theory and Experiment.
  2009;2009(03):P03024.

\bibitem{decelle2011asymptotic}
Decelle A, Krzakala F, Moore C, Zdeborov{\'a} L.
\newblock Asymptotic analysis of the stochastic block model for modular
  networks and its algorithmic applications.
\newblock Physical Review E. 2011;84(6):066106.

\bibitem{valles2016multilayer}
Valles-Catala T, Massucci FA, Guimera R, Sales-Pardo M.
\newblock Multilayer stochastic block models reveal the multilayer structure of
  complex networks.
\newblock Physical Review X. 2016;6(1):011036.

\bibitem{2016arXiv160602319N}
{Newman} MEJ.
\newblock {Community detection in networks: Modularity optimization and maximum
  likelihood are equivalent}.
\newblock ArXiv e-prints. 2016 Jun;.

\bibitem{akcigit2013mechanics}
Akcigit U, Kerr WR, Nicholas T.
\newblock The Mechanics of Endogenous Innovation and Growth: Evidence from
  Historical US Patents.
\newblock Citeseer; 2013.

\bibitem{regibeau2010}
R{\'e}gibeau P, Rockett K.
\newblock Innovation cycles and learning at the patent office: does the early
  patent get the delay?
\newblock Journal of Industrial Economics. 2010;58(2):222--246.
\newblock Available from:
  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.

\end{thebibliography}

\newpage

\section*{S1 Text : Definition of utility patent}

A utility patent at the USPTO is a document providing intellectual property and protection of an invention. It excludes others to making, using, or selling the invention the same invention in the United States in exchange for a disclosure of the patent content. The protection is granted for 20 years since 1995 (it was 17 years before that from 1860) starting from the year the patent application was filled, but can be interrupted before if its owner fails to pay the maintenance fees due after 3.5, 7.5 and 11.5 years. Utility patents are by far the most numerous, with more than 90\% of the total universe of USPTO patents.\footnote{Other categories are Plant patents, Design patents and Reissue patents.} According to the Title 35 of the United States Codes (35 USC) section 101: \textit{``Whoever invents or discovers any new and useful process, machine, manufacture, or composition of matter, or any new and useful improvement thereof, may obtain a patent therefor, subject to the conditions and requirements of this title.''}\footnote{%
Patent laws can be found in http://www.uspto.gov/web/offices/pac/mpep/mpep-9015-appx-l.html\#d0e302376} In practice however, other types of invention including algorithms can also be patented.\footnote{A notable example is the patent \textit{US6285999} protecting the Page Rank algorithm invented by Larry Page in 1998 which was the genesis of Google.} The two following sections of the 35 USC defined the condition an invention must meet to be protected by the USPTO: (i) novelty: the claimed invention cannot be already patented or described in a previous publication (35 USC section 102); (ii) obviousness: \textit{``differences between the claimed invention and the prior art must not be such that the claimed invention as a whole would have been obvious before the effective filing date of the claimed invention to a person having ordinary skill in the art to which the claimed invention pertains''}. (35 USC section 103). After review from the USPTO experts, an application satisfying these requirements will be accepted and a patent granted. The average time lag for such a review is on average a little more than 2 years since 1976, with some patents being granted after much more than two years.\footnote{This time lag, sometimes called the grant lag, is highly heterogeneous across technological fields. In addition, it cannot be considered as totally random. For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\cite{regibeau2010}.}

\paragraph{Sample restriction}
As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013. For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below). We restrict attention to patents applied for before 2007. The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO. However, in order to date them as closely as possible to the date of invention, we use the application date as a reference. As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013. Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.

\newpage

\section*{S2 Text : Data collection and Workflow}

\label{supp:data}

\subsubsection*{Data Collection Procedure}

Raw version of USPTO redbook with abstracts are available for years 1976-2014 starting from bulk download page at \url{https://bulkdata.uspto.gov/}. A script first automatically downloads files. Before being automatically processed, a few error in files (corresponding to missing end of records probably due to line dropping during the concatenation of weekly files) had to be corrected manually. Files are then processed with the following filters transforming different format and xml schemes into a uniform dictionary data structure :

\begin{itemize}
\item \texttt{dat} files (1976-2000): handmade parser
\item \texttt{xml} files (2001-2012): xml parser, used with different schemas definitions.
\end{itemize}

Everything is stored into a MongoDB database, which latest dump is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}
\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % anonymize the db for submission

\subsubsection*{Processing Workflow}

The source code for the full workflow is available at \url{https://github.com/JusteRaimbault/PatentsMining}. A simplified shell wrapper is at \texttt{Models/fullpipe.sh}. Note that keywords co-occurrence estimation requires a memory amount in $O(N^2)$ (although optimized using dictionaries) and the operation on the full database requires a consequent infrastructure. Launch specifications are the following :

\paragraph{Setup}

Install the database and required packages.

\begin{itemize}
\item Having a running local mongod instance
\item mongo host, port, user and password to be configured in \texttt{conf/parameters.csv}
\item raw data import from gz file : use mongorestore -d redbook -c raw --gzip {\$}FILE
\item specific python packages required : pymongo, python-igraph, nltk (with resources punkt, averaged{\_}perceptron{\_}tagger,porter{\_}test)
\end{itemize}

\paragraph{Running}

The utility fullpipe.sh launches the successive stages of the processing pipe.

\paragraph{Options}

\textit{this configuration options can be changed in }\texttt{conf/parameters.csv}

\begin{itemize}
\item window size in years
\item beginning of first window
\item beginning of last window
\item number of parallel runs
\item \texttt{kwLimit} : total number of keywords $K_W$
\item \texttt{edge{\_}th} : $\theta_w$ pre-filtering for memory storage purposes
\item \texttt{dispth} : $\theta_c$
\item \texttt{ethunit} : $\theta_w^{(0)}$
\end{itemize}

\paragraph{Tasks}

The tasks to be done in order : keywords extraction, relevance estimation, network construction, semantic probas construction, are launched with the following options :
%!! keywords and kw-consolidation tested with python3 ; rest with python2 (igraph compatibility issues)

\begin{enumerate}
\item \texttt{keywords} : extracts keywords
\item \texttt{kw-consolidation} : consolidate keywords database (techno disp measure)
\item \texttt{raw-network} : estimates relevance, constructs raw network and perform sensitivity analysis
\item \texttt{classification} : classify and compute patent probability, keyword measures and patent measures ; here parameters $(\theta_w,\theta_c)$ can be changed in configuration file.
\end{enumerate}

\paragraph{Classification Data}

The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}. Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window. The format are the following :

\begin{itemize}
\item Keywords files : keyword ; community ; termhood times inverse document frequency ; technological concentration ; document frequency ; termhood ; degree ; weighted degree ; betweenness centrality ; closeness centrality ; eigenvector centrality
\item Patents measures : patent id ; total number of potential keywords ; number of classified keywords ; same topological measures as for keywords
\item Patent probabilities : patent id ; total number of potential keywords ; id of the semantic class ; number of keywords in this class. Probabilities have to be reconstructed by extracting all the lines corresponding to a patent and dividing each count by the total number of classified keywords.
\end{itemize}

\paragraph{Analysis}

The results of classification has to be processed for analysis (construction of sparse matrices for efficiency e.g.), following the steps:
\begin{itemize}
\item from classification files to R variables with \texttt{Semantic/semanalfun.R}
\item from csv technological classes to R-formatted sparse Matrix with \texttt{Techno/prepareData.R} 
\item from csv citation file to citation network in R-formatted graph and adjacency sparse matrix with \texttt{Citation/constructNW.R}
\end{itemize}

Analyses are done in \texttt{Semantic/semanalysis.R}.

\newpage

\section*{S4 Text : Network Sensitivity Analysis \label{app:sensitivity}}

\subsubsection*{Network Sensitivity}

The example of Fig.1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Fig.~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.  We also show an other point of view over the Pareto optimization, that is the third plot giving the values of normalized objectives as a function of $\theta_c$.

% Figures :

%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
\caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
\label{fig:ext-sensitivity-1}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
\caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
\label{fig:ext-sensitivity-2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
\caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
\label{fig:ext-sensitivity-3}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Time-window size sensitivity}

% put some graphs for 3-years time window : same qualitative properties but a bit more noisy

We show in Fig.~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$. The same qualitative behavior is observed (with different quantitative values, as typically $\theta_w^{(0)}$ is for example expected to vary with document number and semantic regime, thus with window size), what confirms that the method is valid across different time windows.

%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
\caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
\label{fig:sensitivity-window3-1}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
\caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
\label{fig:sensitivity-window3-2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
\caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
\label{fig:sensitivity-window3-3}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

\newpage

\section*{S5 Text : Statistical definitions and derivations}
\subsubsection*{Likelihood expression}
We define $\mathcal{F}_i$ the filtration which corresponds to the time $t_i$. With this notation $\mathcal{L}( X | \mathcal{F}_{i-1})$ simply means the likelihood of $X$ conditioned on the past. We consider $\widehat{\theta}^{(z)}$ the MLE\footnote{Apparently, this MLE is a partial MLE, but we will not refer to partial for simplicity.} of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
\begin{eqnarray*}
\sum_{i=2}^Z \sum_{l=1}^{C_i} \log \mathcal{L} \big( B_{l,i} | \mathcal{F}_{i-1} \big).
\end{eqnarray*}
Recalling that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables 
$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
the log-likelihood of the model can be expressed as 
\begin{eqnarray}
\label{loglik}
\sum_{i=2}^Z \sum_{l=1}^{C_i} B_{l,i} \log \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big) +(1 - B_{l,i}) \log \Big(1 - \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big).
\end{eqnarray}
In practice, the user can easily implement the formula (\ref{loglik}) for any $0 \leq \theta^{(z)} \leq 1$, and maximize it over a predefined grid to obtain $\widehat{\theta}^{(z)}$.

\subsubsection*{Standard errors of the estimated values}
Under some assumptions, it is possible to show the asymptotic normality of $\widehat{\theta}^{(z)}$ and to compute the asymptotic variance. For simplicity of exposition, we assume that we restrict to $\theta^{(z)}$ such that we have $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} < 1$ for any $i=2, \cdots, Z$. The central limit theorem can be expressed as 
\begin{eqnarray}
\label{variance}
\sqrt{Z \mathbb{E} [ C ]} (\widehat{\theta}^{(z)} - \theta^{(z)}) \overset{\mathcal{L}}{\rightarrow} MN \Big( 0, \int (p + \theta^{(z)})(1 - (p + \theta^{(z)})) d\pi^{(z)} (p) \Big),
\end{eqnarray}
where MN stands for a multinormal distribution and $\pi^{(z)}$ for the asymptotic limit distribution of the quantity $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)}$. Note that the variance term in (\ref{variance}) is equal to an aggregate version of the Fisher information matrix. The proof of such statement is beyond the scope of this paper. On the basis of (\ref{variance}), we provide a variance estimator as 
$$v^{(z)} = \frac{1}{C_k-1}\sum_{i=2}^{C_k}  \frac{N_{i_k}^{(z)}}{i-1} + \widehat{\theta}^{(z)},$$ 
where $i_k$ is such that the $i_k$th patent corresponds to the $k$th couple. This estimator was used to compute the standard deviation in Table \ref{summary}.
\subsubsection*{Test statistic}
The test statistic used is a mean difference test statistic between $\widehat{\theta}^{(tec)}$ and  $\widehat{\theta}^{(sem)}$, where the formal expression can be found in (\ref{teststat}). We assume independence between both quantities and thus under the null hypothesis, we have that 
$$\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)} {\rightarrow} MN(0,V),$$
where $V= \int (p + \theta^{(tec)})(1 - (p + \theta^{(tec)})) d\pi^{(tec)} (p) + \int (p + \theta^{(sem)})(1 - (p + \theta^{(sem)})) d\pi^{(sem)} (p)$ can be estimated by $\widehat{V} = v^{(sem)} + v^{(tec)}$. Then, we obtain that 
\begin{eqnarray}
\label{teststat}
A = \frac{\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)}}{\widehat{V}} \approx \mathcal{N} (0,1),
\end{eqnarray}
where $A$ is the mean difference test static.

%%%%%%%%%%%%%%%%%%%%
%% Supplementary Information
%%%%%%%%%%%%%%%%%%%%

%\newpage

%\section*{S1 Text : Definition of utility patent}

%%%%%%%%%%%%%%%%%%%%
%\newpage

%\section*{S2 Text : Data collection and Workflow}

%%%%%%%%%%%%%%%%%%%%

%\newpage

%\section*{S4 Text : Network Sensitivity Analysis}

%%%%%%%%%%%%%%%%%%%%
%\bigskip
%\bigskip
%\newpage
%
%
%
%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Additional plots}
%
%% plots that have some info but not included in paper
%
%
%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!ht]
%% figure : interlayer overlap
%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_density_semcounts.png}
%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_ts_semcounts.png}\\
%\caption{Inter-classification effective overlaps (normalized by patent count)}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%
%
%
%

%%%%%%%%%%%%%%%%%%%%%%
%% Junk
%%%%%%%%%%%%%%%%%%%%%%

%Data-mining and network analysis~\cite{newman2010networks} can bring different insights.  As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g. in the recent analysis on 20\textsuperscript{th} century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation necessarily involves complex patterns which understanding must have positive feedback on the economy.\par

%%%%%%%%%%%%%%%%%%%%
%%  Templates
%%%%%%%%%%%%%%%%%%%%

% For figure citations, please use "Fig." instead of "Figure".
%\begin{figure}[h]
%\caption{{\bf Figure Title first bold sentence}
%Figure Caption}
%\label{fig1}
%\end{figure}

%
%
%
%\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
%\caption{
%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
%\begin{tabular}{|l|l|l|l|l|l|l|l|}
%\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
%\end{tabular}
%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
%\end{flushleft}
%\label{table1}
%\end{adjustwidth}
%\end{table}
%
%

%
%\subsection*{S1 Video}
%\label{S1_Video}
%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Text}
%\label{S1_Text}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Fig}
%\label{S1_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S2 Fig}
%\label{S2_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Table}
%\label{S1_Table}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%

%\begin{thebibliography}{10}
%\bibitem{bib1}
%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005

%\bibitem{bib2}
%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.

%\end{thebibliography}

\end{document}

\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}

A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics. Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
\[
\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
\]
It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields. We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}

% eventually do stats on merging/splitting : distribution of kws overlaps in time ?

\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time. Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-2.5cm}
\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes. \comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
\label{fig:semanticflows}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%

### 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
jpegs

@@
 %\hspace{-2.5cm}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
+\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.jpg}
+\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig1.tif}
@@
 \centering
-\includegraphics[width=\textwidth]{striking}
+\includegraphics[width=\textwidth]{striking.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig2.tif}
@@
 \centering
-\includegraphics[width=0.9\textwidth]{meancomsize}
+\includegraphics[width=0.9\textwidth]{meancomsize.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig3.tif}
@@
 \hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
+\includegraphics[width=1.2\textwidth]{all_raw_counts.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig4.tif}
@@
 %First row : semantic with relevant keywords only - all patents 
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
+\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts.jpg}
+\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts.jpg}\\
 %Second row : patents with diversity $> 0$ (more than one class)}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
+\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts.jpg}
+\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig5.tif}
@@
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{originality.png}
-\includegraphics[width=0.49\textwidth]{generality.png}\\
+\includegraphics[width=0.49\textwidth]{originality.jpg}
+\includegraphics[width=0.49\textwidth]{generality.jpg}\\
 %\includegraphics[width=\textwidth]{tiff/Fig6.tif}
@@
 \centering
-\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
-\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
+\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.jpg}
+\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.jpg} \\
+\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.jpg}
+\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig7.tif}
@@
 \begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
+\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.jpg}
+\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig8.tif}
@@
 \centering
-\includegraphics[width=0.49\textwidth]{simplemodularity}
-\includegraphics[width=0.49\textwidth]{overlappingmodularity}
+\includegraphics[width=0.49\textwidth]{simplemodularity.jpg}
+\includegraphics[width=0.49\textwidth]{overlappingmodularity.jpg}
 %\includegraphics[width=\textwidth]{tiff/Fig9.tif}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.jpg}
 \caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.jpg}
 \caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.jpg}
 \caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.jpg}
 \caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.jpg}
 \caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.jpg}
 \caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}

### 2017-04-02 Docs/Papers/Technical/arxiv/v1/main.tex
sub_v2

@@
 \label{keywords_est}
-\paragraph{Relevance definition}
+\paragraph*{Relevance definition}
 
@@
 
-\paragraph{Moving window estimation}
+\paragraph*{Moving window estimation}
 The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past.
@@
 
-\paragraph{Intra-classification overlaps}
+\paragraph*{Intra-classification overlaps}
 
@@
 
-\paragraph{Inter-classification overlaps}
+\paragraph*{Inter-classification overlaps}
 
@@
 
-\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}
+\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at\\
+ \url{http://37.187.242.99/files/public/network.svg}
 
@@
 
-\paragraph{Sample restriction}
+\paragraph*{Sample restriction}
 As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013.
@@
 
-\paragraph{Setup}
+\paragraph*{Setup}
 
@@
 
-\paragraph{Running}
+\paragraph*{Running}
 
@@
 
-\paragraph{Options}
+\paragraph*{Options}
 
@@
 
-\paragraph{Tasks}
+\paragraph*{Tasks}
 
@@
 
-\paragraph{Classification Data}
-
-The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
+\paragraph*{Classification Data}
+
+The data resulting from the classification process with parameters used here is available as \texttt{csv} files at\\
+ \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
 Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window.
@@
 
-\paragraph{Analysis}
+\paragraph*{Analysis}
 

### 2017-04-02 Docs/Papers/Technical/old/main.tex
sub_v2

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,A4]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{ragged2e}

\usepackage{color,xcolor}

%\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{
%\includegraphics[width=2.0in]{PLOS-submission-eps-converted-to.pdf}
}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf Bergeaud, Potiron and Raimbault, 2016 }

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%%%%%%%%%%%%%%%%%%%%%%
%% User-defined commands
%%%%%%%%%%%%%%%%%%%%%%

%Yoann's commands
\newcommand{\reels}{\mathbb{R}}
\newcommand{\naturels}{\mathbb{N}}
\newcommand{\relatifs}{\mathbb{Z}}
\newcommand{\rat}{\mathbb{Q}}
\newcommand{\complex}{\mathbb{C}}
\newcommand{\esp}{\mathbb{E}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\var}{\operatorname{Var}}
\newcommand{\cov}{\operatorname{Cov}}
\newcommand{\Tau}{\mathrm{T}}

% writing utilities

% comments and responses
\usepackage{xparse}
\DeclareDocumentCommand{\comment}{m o o}  
{%
    \textcolor{red}{#1}\IfValueT{#2}{\textcolor{blue}{#2}}\IfValueT{#3}{\textcolor{green}{#3}}
}

% todo
\newcommand{\todo}[1]{\textcolor{red!50!blue}{\textbf{\textit{#1}}}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.

\begin{flushleft}
{\Large
\textbf\newline{
%An Hypernetwork Approach to Measure Technological Innovation
Unveiling Endogenous Patterns of Technological Innovation
% TODO find a good title expressing both the multi-layer character and the novelty looking at semantic data
}
}
\newline
\\
Antonin Bergeaud\textsuperscript{1},
Yoann Potiron\textsuperscript{2},
Juste Raimbault\textsuperscript{3,*}
\\
\bigskip
\bf{1} Department of Economics, London School of Economics, London, UK
\\
\bf{2} Faculty of Business and Commerce, Keio University, Tokyo, Japan
\\
\bf{3} UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* juste.raimbault@polytechnique.edu

\end{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the abstract below 300 words
\begin{abstract}
\justify
The understanding of technological innovation's patterns is crucial for both economical growth theories and practical applications. In this paper, we examine the relevance of a classification resulting from a large-scale data-mining and network approach on patent data. We construct an open consolidated database from raw data taken from the US patent office from 1976 onward yielding a database of around $4\cdot 10^6$ patents. We show that the patents' text content encompasses information which is not well captured by the existing technological classification and the citation network. The network-modularity-and-size multi-objective optimization is realized under the constraint that the distribution of the community and the techonological size have the same shape. In addition, it is performed on network construction parameters (filtering thresholds) through high performance computing. We obtain for each year a multi-layer network, containing semantic community, technological class and citation relations between patents. The mining of network layers yields interesting results, such as an increase of patent semantic originality over time combined with a counter-intuitive loss of class-level interdisciplinarity, which confirms the stylized facts of both invention refinement and specialization in time.\textcolor{red}{derinere phrase pas tres claire. En plus, on a pas que la patent semantic originality is increasing d'apres les graphes.}

\end{abstract}

\linenumbers

\justify

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Innovation and technological change have been described by many scholars as the main driver of economic growth as in~\cite{aghionhowitt1992} and~\cite{romer1990}. ~\cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation. Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data~\cite{hall2001} \comment{Le papier cite traite des deux trucs avant a la fois?} have opened the way to a very wide range of analysis. Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review. Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields~\cite{Youn:2015fk}. With methods such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-authorship networks analysis~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters. Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.

Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies. But it is also crucial for firms that face a ever changing demand structure and need to anticipate future technological trends and convergence~\cite{curran2011patent} to adapt to the resulting increase in competition~\cite{Katz1996remarks} and to maintain market share. Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network''~\cite{AAKnetwork2016}. In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it. In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent. Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} We claim that combining the regular classification with a new classification based on text-mining of abstract enables to better detect and follow the birth of technological clusters by finding semantic links between seemingly unrelated patents. These semantic links are clues of one technology taking inspiration from another and are good predictors of future technology convergence~\cite{preschitschek2013}. One can for instance consider the case of the word \textit{optic}. Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic. This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.

\comment{On peut laisser le paragraphe suivant ou bien le bouger en partie 2.4, vous en pensez quoi ? Moi je la trouve bien ici}[Yo: je le trouve bien ici!][(Juste) idem]

Previous research has already proposed to use semantic networks \comment{des abstracts ?} to study technological domains and detect novelty. ~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain. The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in ~\cite{park2014semantic} and ~\cite{yoon2011detecting}. More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation. Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}). Building on such previous research, we make several contributions. To the best of our knowledge, this is the first attempt to build a complete classification of all patents based on automatic semantic analysis and to make it freely accessible. Second, we show that this new classification combined with the classic one enables to better detect breakthrough technologies using the dispersion of keywords.

\comment{La Bergeasse: Il est très important que l'on définisse exactement ce que l'on ressort comme résultat car pour l'instant l'intro ne le dit pas. La fin de l'intro est fausse car on ne montre pas que combiner les deux classifications est bien, enfin on le fait mais ce n'est pas mis en avant... brainstorming needed}[Yo: Je suis d'accord, peut-etre qu'il faut simplement parler des differences de graphes et statistiques au lieu de s'aventurer dans le reste. C'est deja largement "assez" pour un papier, et ca a le merite d'etre clair et solide. Le reste n'a pas besoin d'etre mentione dans l'intro, il viendra en bonus au fur-et-a-mesure du papier, et aussi dans les parties Further developments et conclusion. D'autant plus que l'on ne soumet pas a une revue economique! Je ne vois pas un reviewer nous dire "quel est l'interet de telle methode?" etant donne que Plos One n'est pas cense juge sur cet aspect.][(Juste) on montre pas la complémentarité en effet mais nos résultats la suggèrent vu les différences qualitatives qu'on obtient dans certains cas. le mieux comme dit Yo serait de parler de la dynamique des différentes mesures (notamment les changements de régime) et de la performance au regard du réseau de citation.]

The rest of the paper is organized as follows. Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process. Section \ref{keywords} explains the construction of the semantic classes. Section \ref{result} tests their relevance by providing exploratory results. Finally, section \ref{discussion} discusses potential further developments and applications.

%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background \label{data}}
%%%%%%%%%%%%%%%%%%%%%%%%

In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013. A clearer definition of utility patent is given in supporting information. Additional information on how to correctly exploit patent data can be found in~\cite{hall2001} and ~\cite{lerner2015use}.

%%%%%%%%%%%%%%%%%%%%%
\subsection{An existing classification: the USPC system}

Each USPTO patent is associated with a non-empty set of technological classes and subclasses. There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system. While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention. A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass. At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes. When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A bibliographical network between patents: citations \label{sub:citation}}

As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art. They therefore indicate the past knowledge which relates to the patented invention. Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent. One can consult~\cite{oecdpatentmanual} for more details about this. Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}). Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves. 
From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations). We can thus build a complete network of citations that we will use later on in the analysis.

Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years. This distribution is highly skewed, the $95^{th}$ percentile is 21 years. We also report 164,000 citations with a negative time lag. This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others. Fig. \ref{fig1} reports the time lag empirical distribution.

In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years. We impose this restriction for two reasons. First as seen in Fig. \ref{fig1} the number of citations received peaks at 4-5 years. Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones, regardless of their respective qualities.

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}

Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although the core text is structured in a specific way which could be useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included in a semantic analysis which includes more than 4 million patents. Furthermore, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study~\cite{Adams2010text}, indeed the USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8). For this reason, we choose to restrict attention to the content of the abstracts and will not consider the core text. Abstracts have an average length of 120.8 words (with a standard deviation of $62.4$) a size that is already challenging in terms of computational burden and data size.

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}. The latest dump of the database in \texttt{Mongodb} format is available at \url{http://37.187.242.99/files/public/USPTOredbook.gz}.
%\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are not well documented and change frequently.

We count 4,666,365 utility patents granted between 1976 to 2013 with an abstract.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn, we do not consider them in this analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013. When distributed by the year of application, the picture is slightly different: the number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007. Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents. These patents cite 38,756,292 other patents with the empirical lag distribution presented in Fig. \ref{fig1}. Conditionally on being cited at least once, a patent receives on average 13.5 citations within a five-year window. 270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations. A within class citation is defined as a citation between two patents sharing at least one common technological class. Following this definition, 84\% of the citations are within class citations. 14\% of the citations are between two patents that share the exact same set of technological classes.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Towards a Complementary Classification}

Potentialities of text-mining techniques as an alternative way to analyze and classify patents are namely documented in~\cite{tseng2007text}. Their main argument in support of an automatic classification tool for patent is to reduce the considerable amount of human efforts needed to classify all the applications. Most of the work conducted in the field of using natural language processing or text analysis has been mostly developed in order to improve search performance in patent databases, to build technology map or to investigate the potential infringement risks before developing a new technologies (see~\cite{abbas2014literature} for a review). Text-mining of patent documents is also widely used as a tool to build networks that carry additional information than the too simple bibliographic connections as argued in~\cite{yoon2004text}. The use of text-mining as a way to build a global classification of patents remains however largely unexplored. One notable exception is~\cite{preschitschek2013} where semantic based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples. Semantic analysis therefore reveals more flexible and more quickly adaptable to the apparition of new clusters of technologies. Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies starts to clearly converge, one should expect similar words to be used in the respective patents.

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network component that is more developed that in the USPC case. As it will be explained in next section, each patent is associated with a vector of probability for belonging to each of the semantic classes. Using co-occurrence of keywords, it is possible to construct a network of patents and to study the influence of some key topological features.

%%%%%%%%%%%%%%%%%%%%%
\section{Semantic Classification Construction \label{keywords}}

We describe in this section methods and empirical analyses leading to the construction of semantic network and classes.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords extraction}

Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from the abstract ${\mathcal{A}}(p)$.
They are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
\begin{enumerate}
\item Text parsing and Tokenization: we transform raw abstracts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).
%normalized on typographical variations (e.g. caps). \comment{Je ne comprends pas l'exemple (e.g. caps), il faudrait expliquer un peu mieux en 3 mots.} j'ai viré ça, car en gros c'est passer tout en minuscules, c'est évident pas besoin de le préciser
\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.
\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens. Abstract text as this point is reduced to a set of stems and their grammatical functions.
\item Multi-stems construction: these are the basic semantic units used in further analysis; they are constructed as groups of successive stems in a sentence verifying a simple grammatical function rule: length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives.
%\comment{Y a pas un typo là ? c'est $n_0-n_1\leq 2$ ? Dans tous les cas ce n'est pas très clair cette expression, c'est quoi n0 et n1? Et puis c'est quoi la différence entre NN et NNP et NNS? peut être qu'ici les maths sont en trop non?} $\displaystyle s = (s_i)_{n_0 \leq i \leq n_1}$ with $0\leq n_0 - n_1 \leq 2$ and $f(s_i) \in \{NN,NNP,NNS,VBG,JJ,JJR\}$ (NN, NNP, NNS: nouns; VBG: attributive verb; JJ, JJR: adjectives). \comment{yes les maths étaient de trop je pense aussi}
We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
\end{enumerate}

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/AnonymousAuthor1/PatentsMining} % TODO - Anonymous user created ; need to transfer-anonymize-hide actual before submission - Après c'est pas comme si on était connu, c'est presque déjà de l'anonymat :p - lol en effet ^^ ; non mais c'est pour la revue, c'est possible d'être refusé sans même review parce que c'est pas totalement blind !
}.

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\paragraph{Relevance definition}

Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The total number of keywords to be extracted is a fixed parameter $K_w$ (that we take as $K_w = 1\cdot 10^5$ in the following; smaller values yield similar network structures but with less information whereas very large values tend to include non-relevant keywords \comment{Do we show that? (not a criticism here but a referee might ask, I would go for saying nothing or to show this properly)}[we actually do not show it rigorously, c'est au doigt mouillé, en gros c'est à peu près l'ordre de grandeur (rescalé du coup) auquel les mots poubelles commencaient à sortir sur les one-year window ; après peut être que 200000 serait très bien aussi, qu'on pourrait optimiser avec un $K_W$ variable sur chaque fenetre etc. mais à des moments je pense qu'il faut rester simple et faire certains choix arbitraires s'ils paraissent raisonnables, sinon on s'en sort plus ; qu'en pensez vous ?]). A first filtration of $k\cdot K_w$ (with $k=4$) is done on the \emph{unithood} $u_i$, defined as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$. The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is thus defined as

\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\]

\paragraph{Moving window estimation}
These scores are estimated on a fixed length-time window following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is constructed at year $t$ using patents which appeared on the time window $\left[ t - T_0 ; t \right]$. Note that the causal property of the window is crucial as the future can't play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network. We take in the following $T_0 = 5$ years consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for a different $T_0$ can be found in Appendix~\ref{app:sensitivity}. \comment{A faire donc avec T=3, mais quel résultat présenter?}[je mettrai certains des main graphs correspondants, ça suffira bien (fig 1,3,5 par example)]

%%%%%%%%%%%%%%%%%%%%
\subsection{Construction of the semantic network}

We keep the $K_W$ most relevant keywords and obtain the co-occurrence matrix that can be directly interpreted as a weighted adjacency matrix of the semantic network \comment{Is it clear that there is a semantic network at this stage?}[it is exactly where it appears : a square matrix is equivalent to a network. maybe then reformulate that way ?]. The topology of raw networks does not allow the extraction of clear communities. This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g. \texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant. We introduce here an additional exogenous measure to correct the network topology, that is the concentration of keywords across technological classes, defined as $c_{tech}(s) = \displaystyle \sum_j \left(\frac{k_j(s)}{\sum_i k_i(s)}\right)^2$,  where $k_j(s)$ is the number of occurrences of $s$ in class $j$. The higher $c_{tech}$, the more specific to a technological class the node is \comment{give an example here: semiconductor? For example, the terms ``semiconductor'' is widely used in electronics and does not contain any significant information in this field.}. We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$. In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$ \comment{Un exemple pour l'intuition? J'ai du mal à voir ce qu'un edge peut être}. To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus. Communities are then extracted using a standard modularity maximization procedure as in~\cite{clauset2004finding}. As shown in Fig.~\ref{fig:networksensitivity}, we choose parameter values that maximize modularity under the constraint that the community number and the size distribution is of same magnitude as the ones of technological classes \comment{Yo: Ne pensez-vous pas qu'il faudrait detailler ce point? Car la je ne vois pas vraiment ce qu'est ta contrainte}[c'est une loose constraint ; je vais reformuler ainsi que la figure]\comment{Yo: ok cool!}. This multi-objective optimization does not have a unique solution as objectives are contradictory and a choice of a point on the Pareto front is made. In the specific example of Fig.~\ref{fig:networksensitivity}, we take $\theta_d = 0.06$ and $\theta_w^{(0)} = 4.5\cdot 10^{-5}$.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace{-2.5cm}
\includegraphics[width=0.55\textwidth,height=0.25\textheight]{figures/comsizes_refined_EDITED}
\includegraphics[width=0.55\textwidth,height=0.25\textheight]{figures/pareto_comnum-vcount_color-mod_EDITED}
% TODO redo figures
\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters} We show plot for one example year (2000-2004), all years having the same qualitative behavior (see Supp. Material \ref{XX}) \textit{(Left)} Number of communities as a function of $\theta_w$ for different $\theta_c$ values. The maximum is roughly stable across $\theta_c$ (dashed red line) and years when normalized by patent number, yielding the choice of $\theta_w^{(0)} = 4.5\cdot 10^{-5}$. \textit{(Right)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (green overline) on the Pareto front (red dashed line; grey level gives modularity) gives $\theta_c = 0.06$.\comment{Comment pour la Figure 1: Yo: $\theta_w$ et $\theta_c$ devrait etre ecrit comme dans latex, et dans le meme format que le reste des axes/legende je pense. communities est un nombre positif, donc il faut enlever la partie jusqua -50 sur la figure de droite. Pareil pour vcount. min com size correspond a quoi ? De meme, vcount n'a pas ete defini pour le moment. Quand tu dis "communities" tu sous-entends "number of communites" ? Aussi, le titre des deux graph est le meme, i.e. year: 2004 ; min com size. Je pense qu'il faut soit le diferencier, soit ne pas le mettre du tout. Finalement, la legende doit etre ultra precise, mais au pire des cas je changerai ca a la fin quand tu auras repondu a toutes ces questions :) a-t-on vraiment besoin de preciser que les autres annees sont similaires dans la legende de la Figure? Le reviewer se doute bien que tu ne vas pas plotter les 30 annees. Je pense que c'est mieux de mettre ca dans le corps du texte. Desole pour tous ces retours techniques, mais je me suis fait tellement deboite dans mes DM en PhD :p}}
\label{fig:networksensitivity}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-7cm}
\includegraphics[width=0.75\textwidth]{figures/graph-filtered_2000-2004_kwLimit100000_dispth0_06_ethunit4_5e-05_LOWRES}
\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$. The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available as Supplementary Material.}
\label{fig:rawnetwork}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characteristics of Semantic Classes}

% content, number of classes in time
% description

% find an example of a patent which was really innovative and for which semantic classes give an insight

Both technological and semantic classes exhibit a hierarchical structure in the sense of a power-law type of distribution of class sizes, as shown in Fig.~\ref{fig:class-sizes}.

\textit{Describe structure of classes (cf graphs hierarchy) ; examples ; Anto case study here ?}

[TBD: ANTO (ETA: 2 days)]

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-2.5cm}
\includegraphics[width=1.2\textwidth]{figures/all_raw_counts}
\caption{Yearly from 1960 to 2012, we plot the log-sizes when restricting to patents which appeared during the corresponding year of semantic classes (left-side) and technological classes (right-side) as a function of their log-rank from the biggest to the smallest. Sizes are computed as the sum over patents of probabilities to belong to the class. Each color corresponds to one specific year. Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications. This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}. Over time, curves are translated and levels of hierarchy stays roughly constant. \comment{(Juste) du coup pour cette figure j'ai laissé les échelles telle quelles pour comparabilité entre les deux ; j'ai précisé que size = sum(probas) ; peut être qu'il faudrait bouger la def des probas pour à la fois sémantic et techno en section 3.4. Sinon pour titres/légendes/axes ça vous va ?}
}
\label{fig:class-sizes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\section{Results \label{result}}
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}

% this section describes semantic communities reconstruction and their temporal dynamics

A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics. Communities are constructed yearly and thus one can define proximity between two successive communities $S_i(t)$ and $S_j(t+1)$ using a set similarity index between both sets of keywords, defined as the normalized intersection $j(A,B)=2\cdot \frac{\left|A\cap B\right|}{\left|A\right|+\left|B\right|}$, where $\left|X\right|$ corresponds to the cardinal of $X$. It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields. We show in figure~\ref{fig:semanticflows} a sample of these flows for the largest classes.
\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}

\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time. Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
% full flow graph or a snapshot depending on readability on all years and all classes

%  Sankey network of Citation flows ? -> not relevant to my mind

\hspace*{-2.5cm}
% placeholder figure for now
%\includegraphics[width=\textwidth]{figures/example_semanticFlows_1998-2010}
\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes. \comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}[Question sur les noms, on est obligé de mettre les stem ce que je comprends mais du coup c'est pas toujours évident de comprendre... On peut faire un link stem $\rightarrow$ most used kw ?]\comment{arf chaud là comme ça, je l'ai pas memorisé lors de l'extraction des stem parce que je voulais pas prendre trop de memoire, il faudrait coder ça et refaire tourner.. (j'ai toujours pas accès au serveur :/ )}}
\label{fig:semanticflows}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Patent Level Diversity}

Given a classification system (technological or semantic classes), given by probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ \comment{Yo: C'est la premiere fois qu'on definit $p_{ij}$, je pense qu'il est necessaire d'etre un peu plus clair sur ce que c'est. L'explication qu'on donne dans le paragraphe d'apres est encore plus floue en premiere lecture. Je comprends le truc car je suis coauteur, mais je ne pense pas qu'un reviewer comprendrait en premiere lecture. (Anto) Oui je suis d'accord, il faudrait expliquer que conceptuellement c'est différent des classes techno car on a des proba d'appartenance, et même dans les classes techno, ce n'est pas trivial que la proba d'appartenir à chaque classe est égal à 1/N, c'est une hypothèse que l'on fait}[(Juste) est ce que ça vous semblerait pertinent de bouger la def des probas à la fois pour sémantique et techno en 3.4, parce qu'on les utilise déjà pour les tailles en fait, et plus tôt c'est le mieux car le concept est central par la suite], one can define a patent-level diversity measure as one minus the herfindhal index \comment{c'est classique le herfindhal ?} on $p_{ij}$ by:

\[
D_i = 1 - \sum_j {p_{ij}^2}.
\]

For the semantic classification, these probabilities are computed over classified keywords of a patent: taking all potential keywords yield very small probabilities (as a lot of keywords are not nodes of the semantic network) and may include bias due e.g. to the variation of abstract length in time. For technological class, there is no probability directly associated with each class. We considered for this reason that each class received a probability equal to 1 over the total number of patent $i$'s technological classes, generalizing the technological classification in a way comparable to the semantic classification. \comment{Yo: C'est pas mal quand meme l'explication, mais il faut vraiment qu'on betonne ca en reformulant quelques trucs :) Par exemple, le biais est plus embrouillant qu'autre chose en premiere lecture. Il devrait venir apres les definitions claires des objets.}

\comment{Yo: IMPORTANT: C'est quoi la definition de $p_{ij}$ pour les classes technologiques (je ne comprends pas la derniere phrase en fait)}[c'est écrit au dessus ``For technological class,... comparable to the semantic classification'' ; il faudrait peut etre le reformuler. les probas technos des patents, c'est 0 s'il apprtient pas à la classe, 1/son nombre de classes s'il y appartient]\comment{ok, j'avais loupe quelque chose, c'est de ma faute. Je vais essayer de re-ecrire un poil cette partie!}

\comment{Je pense qu'il faut dire un mot sur la définition usuelle de l'originality ou de la generality en classe techno: c'est la même efinition mais en definissant $p_{ij}$ comme la part dans la classe $j$ des brevets citants ou étant cités par le brevet $i$ dans les 5 ans. Je vais le calculer pour les classes semantiques.}[très bonne idée, du coup on peut splitter cette partie en diversity et originality/generality ; ça donne un équivalent de 4.4 et 4.5 mais au niveau du patent]
We show in Figure~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series. This is carried with two different settings, namely including/not including patents with zero diversity (single class patents). We call other patents ``complicated patents'' in the following. First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes. More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification system, can be interpreted as an increase in invention specialization. This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}. Furthermore, a qualitative regime shift on semantic classification occurs around 1996. This can be seen whether or not we include patents with zero diversity. The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease. This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity. It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents. This effect does not seem to be spurious neither with patent count nor with network size. \textcolor{red}{do we add the corresponding figures as supplementary to justify this ?}\textcolor{blue}{Yo: soit on l'ajoute as supplementary material en referencant, soit on enleve la phrase}

%\textit{Row 2 of the corresponding figure Fig.\ref{fig:patent-level-orig} will be kept ; we evoke row 1 saying that keywords are more difficult to classify in time (increase of diversity $\iff$ smaller probas $\iff$ ``biais'' due to longer abtrsacts, more complicated inventions etc.  )} % TODO plot length of abstracts in time. Rq : we could have taken a total number of kws linked to mean abstact length.. but a level of complication more..
%\textit{thus we work with probas computed on \textbf{classified keywords}. Try to interpret the peak in semantic; it is not a direct bias due to patent count, as begins to decrease in 96; when removing zero-originality patents (third row), clear decreasing trend for semantic as for techno : interpretation : apparent increase of diversity was due to a decrease of single class patent ; but considering only multi-class patents semantic follows techno. Can it have an economic interpretation ?}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}

%First row : semantic with all keywords ; 
%\includegraphics[width=0.24\textwidth,height=0.15\textheight]{figures/patentlevel-origs-techno}
%\includegraphics[width=0.24\textwidth,height=0.15\textheight]{figures/patentlevel_semorigs_high_logscale}
%\includegraphics[width=0.45\textwidth]{figures/patentlevel-origs-mean-ts}
%\\
%First row : semantic with relevant keywords only - all patents 
\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_all_semcounts}
\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_all_ts_semcounts}\\
%Second row : patents with diversity $> 0$ (more than one class)}
\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_positive_semcounts}
\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_positive_ts_semcounts}
\caption{
\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column). First row includes all classified patents, whereas second row includes only patents with more than one class (i.e. patent with diversity greater than 0). \comment{(Juste) Même question pour les axes/labels, ça vous va ?}
}
\label{fig:patent-level-orig}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classes overlaps}

% comparison of techno classes / semantic communities - citation done with modularity and stat method further

A proximity measure between two classes can be defined by their overlap in terms of patents. In a generalized form with class belonging probability matrix $\left(p_{ki}\right)$ (giving for patent $k$ probabilities to belong to each class $i$) it writes $O_{ij} = \frac{1}{N_P}\cdot \sum_{k} p_{ki} p_{kj}$. The overlap is normalized by patent count to remove effect size. The corresponding relative overlap (set similarity defined in section~\ref{subsec:semantic-flows}) is computed the same way.

\paragraph{Intra-classification overlaps}

The study of distributions of overlaps inside each classification, i.e. between technological classes and between semantic classes separately, reveals the structural difference between the two classifications methods, suggesting their complementary nature. Their evolution in time can furthermore give insights into trends of specialization. We show in figure~\ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications. Technological classification globally always follow a decreasing trend (years after 2007 being not significant as stationary regime is not yet reached), what corresponds to more and more isolated classes, i.e. specialized inventions, confirming the stylized fact obtained in previous subsection. For semantic classes, the dynamic is somehow more intriguing and supports the story of a qualitative regime shift suggested before. Although globally decreasing as technological overlap, normalized (resp. relative) mean overlap exhibit a peak (clearer for normalized overlap) culminating in 1996 (resp. 1999). Looking at normalized overlaps, classification structure was somewhat stable until 1990, then strongly increased to peak in 1996 to then decrease at a similar pace until today. Technologies began to share more and more until a breakpoint when increasing isolation became the rule again. An evolutionary perspective on technological innovation~\cite{ziman2003technological} could shed light on possible interpretations of this regime shift: as species evolve, the fitness landscape first would have been locally favorable to cross-insemination, until each fitness reaches a threshold above which auto-specialization becomes the optimal path. It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation. This interpretation is consistent with the dynamics of semantic flows presented in Fig.~\ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.

\todo{it may be interesting to find the most overlapping semantic classes in 1996 ; and look the closest classes in 1980 and in 2004, to try to have a concrete insight on what happened. Anto could you do that ? Also for this part the most important is to try to interpret the dynamics accurately from an economic point of view, i'm not sure my bla-bla is very relevant economically ; and maybe too long, do not hesitate to shorten !}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
%\includegraphics[width=0.49\textwidth]{figures/real_all_density}
%\includegraphics[width=0.49\textwidth]{figures/real_all_ts} 
%\\
%\includegraphics[width=0.49\textwidth]{figures/patentnorm_all_density_logscale}
%\includegraphics[width=0.49\textwidth]{figures/patentnorm_all_ts} \\

%\includegraphics[width=0.49\textwidth]{figures/real_all_density_semcounts}
%\includegraphics[width=0.49\textwidth]{figures/real_all_ts_semcounts} \\

\includegraphics[width=0.49\textwidth]{figures/patentnorm_all_density_semcounts}
\includegraphics[width=0.49\textwidth]{figures/patentnorm_all_ts_semcounts} \\
\includegraphics[width=0.49\textwidth]{figures/relative_all_density_semcounts}
\includegraphics[width=0.49\textwidth]{figures/relative_all_ts_semcounts}

\caption{
\textbf{Intra-classification overlaps.}
\textit{(Left column)} Distribution of overlaps ($O_{ij}$ for all $i\neq j$; zero are removed because of the log-scale). \textit{(Right column)} Corresponding mean time-series. \textit{(First row)} Normalized overlaps. \textit{(Second row)} Relative overlaps.}
%\comment{(Juste) I put results for different definitions of overlap, which having its sense ; do we choose the most interesting ? (!! selection bias) - First row : non-normalized overlaps, biased by patent count, nothing to say ; Second row : overlaps normalized by patent count - I think there is signal here ; Third-Fourth raw : same plots with semantic probas computed with the number of relevant keywords and not all (removes a "patent-size" effect) ; Fifth row : relative overlaps (jaccard similarity), also with count probas; Note : for log-scale plots, zeros are removed}
\label{fig:intra-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Inter-classification overlaps}

\comment{Yo: pourrais-tu donner la definition ?}[en fait la def des overlap en debut de section vaut pour le intra et inter, c'est pas clair ?]\comment{Yo:Non, c'est pas clair pour moi le lien.} Overlaps \emph{between} classifications describe their relative correspondence and are a good indicator to spot relative changes, as shown in Fig.~\ref{fig:inter-classif-overlap}. Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease. Although difficult to interpret directly, this stylized fact clearly unveils a change in the \emph{nature} of inventions, or at least in the relation between content of inventions and technological classification (as we observe a relative shift, it may have only been the way to classify by the bureau that changed). The tipping point being at the same time as the ones observed in the previous sections, it is probably not a coincidence and all of these would be markers of a hidden underlying structural changes in processes. The economic interpretation is for now left for further theoretical, modeling and empirical work.

%\textbf{we observe here the same ``shock'' in 1996 ; the story is a bit different ; here the plot can be understood as the adequacy between the two classifications (its variation imply a variation in adequacy) ; so if there is really a hidden phenomenon, here it caused a constant decrease in inter-overlap.}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
% figure : interlayer overlap
%\includegraphics[width=0.49\textwidth]{figures/interov_patentnorm_all_density}
%\includegraphics[width=0.49\textwidth]{figures/interov_patentnorm_all_ts}\\

\includegraphics[width=0.49\textwidth]{figures/interov_relative_all_density}
\includegraphics[width=0.49\textwidth]{figures/interov_relative_all_ts}

\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series. The decreasing trend starting around 1996 confirms a qualitative regime shift in that period. Effective normalized overlaps (available in Supplementary Material) provide the same qualitative insight.}
\label{fig:inter-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Citation Modularity}

%  distribution of second order interdisciplinarity
%   -> in supplementary material ? or is it really necessary ?

%\textbf{I think the heatmaps are not a good idea ; we do not see anything ; I will do the second-order diversity distributions plots but it will be boring to have analog plots as previous sections ; maybe put them in supplementary material ; a good compromise would be the evolution of overlapping communities citation modularity in time, for semantic and techno ; to be linked with Yo's part ; need to code it \cite{nicosia2009extending} and do the plots ; ETA:JR:0.5d}

An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}. The correspondance between citation links and class belonging should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily \comment{def?}[ce n'est pas une mesure particulière, mais une façon de dire que tu cites tes semblables] is expected to be quite high (see, e.g, ~\cite{AAKnetwork2016}). This section studies empirically modularities of the citation network regarding the different classifications, whereas the same aspect will be investigated more rigorously by modeling from a statistical point of view in the next section. Modularity is a simple measure of how communities in a network are well clustered (see \cite{clauset2004finding} for the precise definition). Although initially designed for single-class classifications, this measure can be extended to overlapping classes (when nodes can belong to several classes at the same time, in our case with different probabilities) as introduced by~\cite{nicosia2009extending}. \textcolor{blue}{Super solide ta def Juste, je me suis permis de la solidifier encore pluset je laisse mes commentaires}
\comment{The Simple directed modularity is given in our case by $Q_d = \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j)$, with $A_{ij}$ the citation adjacency matrix (i.e. $A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not --c'est bien la def que tu avais en tete Juste???), $k_i^{in}$ (resp. $k_i^{out}$) in-degree (resp. out-degree) of patents (i.e. the number of citations from the $i$th patent and the number of citations made to the $i$th patent --- c'est bien ca???) and $c_i$ is defined as the main patent class, which is taken as the primary class for technological classification and the class with the biggest probability for semantic classification. Multi-class modularity is given by $Q_{ov} = \frac{1}{N_P} \sum_{c\in C} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,j,c}^{out}k_i^{out}\beta_{i,j,c}^{in}k_j^{in}}{N_P}\right]$ where $\beta_{i,j,c}^{out} = \frac{\sum_j F(p_{ic},p_{jc})}{N_P}$ and $\beta_{i,j,c}^{in} = \frac{\sum_i F(p_{ic},p_{jc})}{N_P}$. We take $F(p_{ic},p_{jc}) = p_{ic}\cdot p_{jc}$ as it is suggested in \cite{nicosia2009extending}.}
We show in Fig.~\ref{fig:modularities} both simple and multi-class modularities in time. For simple modularity, technological classification is low and stable whereas semantic is slightly greater and increasing (expect perturbations in latest years that should be due to the non-stationarity of citation processes). These values are however low and suggest that single classes are not enough to capture citation homophily. Multi-class modularities tell a totally different story. First of all, both classification modularities have a clear increasing trend, meaning that they are in time more and more adequate with citation network. This effect could have been expected regarding the specializations unveiled in previous subsections. Secondly, semantic modularity dominates technological modularity by an order of magnitude (e.g. 0.012 against 0.082 in 2010) at each time. Quantitatively not interpretable, this discrepancy has a strong qualitative significance: our semantic classification is much more adequate to the citation network when using multiple class. This underlines one of the advantages of our classification approach, that is the ability to take fully into account the heterogeneous nature of invention through this multi-class aspect. \comment{la derniere phrase est pas claire, et de plus on n'a plus au vu des plots l'originalite semantic ne monte pas, si?}[je vais reformuler, ce que je voulais dire c'est l'exemple de la figure ci-dessous]

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\textwidth]{figures/simplemodularity}
\includegraphics[width=0.49\textwidth]{figures/overlappingmodularity}
\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability). (Right) Multi-class modularity, computed following~\cite{nicosia2009extending} \comment{Yo: pourquoi les derniers points sont variables comme ca a gauche? c'est quoi la difference entre les deux def ?}[la variabilité je me disais que ça devait être du au fait que le regime de citation est pas encore stationaire pour les dernieres années, du coup elles apparaissent plus comme random ; mais pourquoi ça arrive moins sur techno (un peu comparé à la faible variabilité dans le temps), et pas avec la multi-class, difficile à savoir - ça doit vouloir dire que la destabilisation due aux citations manquantes se reporte sur des classes voisines (en terme d'overlap) ce qui ne modifie pas la multi-class modularity. La diff entre les deux, la première suppose une unique classe par patent, la deuxième prend en compte les probabilités des patent d'appartenir aux classes : si un patent 55\% x et 45\% y cite 50\% de x et 50\% de y, avec la modularité simple le lien y-y assez fort ici est ignoré, avec la deuxième il est pris en compte]}\comment{ok t'as l'air cale dessus, pas forcement besoin de commenter, mais on peut peut etre retirer les dernieres annees en disant qu'elles sont bruitees!}
\label{fig:modularities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical Model}
\label{statisticalmodel}
\textcolor{red}{Je pense que le premier paragraphe peut etre mis avant la methode de Juste, car fondamentalement c'est le meme genre de trucs qui est fait (si je ne m'abuse pas!)}  
In this section, we develop a statistical model aimed at quantifying performance of both technological and semantic classification systems.
\textcolor{green}{The inclusion of 'perform' in the previous sentence is perhaps a little rash. It is not the point to show that one approach dominates the other, but rather than our new approach enjoy good statistical properties.} \textcolor{red}{je trouve cette formulation un peu malvenue pour un papier scientifique ; est-ce qu'on pourrait remplacer par un truc comme (bien reformulé du coup) ``\ldots classification systems, in the sense that an external validation of classifications and a statistical comparison, with the inclusion of the citation network.''}

To compare the technological and semantic classes, we choose to look at within class citations proportion (for both technological and semantic approaches). We provide two obvious reasons why we choose this. First, the citations are commonly used \textcolor{red}{shall we make some citations here, or refer to the introduction?} as a proxy for performance. Second, this choice is "statistically fair" in the sense that both approaches have focused on various goals and not on maximizing directly the within class proportion. 
Nonetheless, the within class proportion is too sensitive to the distribution of the shape of classes. For example, a dataset where patents for each class account for 10\% of the total number of patents will mechanically have a better within class proportion than if each class accounts for 1\%. Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed.

We introduce a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g. \cite{decelle2011asymptotic}, \cite{valles2016multilayer}), and compute the corresponding maximum likelihood estimator (MLE). In view of~\cite{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.

To compare both approaches, a formal definition of the problem is needed. In addition, models for both approaches are required. We need to introduce some notations to answer those two questions. We consider a specific window of observations (typically 5 years long), and we define $Z$ the number of patents which appeared during that time window. We let $t_1, \cdots, t_Z$ their corresponding appearance date by chronological order. For each patent $i=1, \cdots, Z$ we consider $C_i$ the number of distinctive couples \{cited patent , cited patent's class\} made by the $i$th patent (for instance if there is only one citation and that the cited patent is associated with three classes, then $C_i = 3$). Let $z \in \{tec, sem\}$, which stands respectively for "technological class" and "semantic class". We define $N_{k,i}^{(z)}$  the number of patents associated to the $k$th technological or semantic class at the time of the $i$th patent's submission. Correspondingly, we define as
$$S_i^{(z)} = \sum_{k \geq 1} N_{k,i}^{(z)}$$
the sum of patents' number of classes at time $t_i$. For $l = 1, \cdots, C_i$ we consider the Bernoulli variables $B_{l,i}$, which equal $1$ if the cited patent's class is also common to the $i$th patent. We assume that $B_{l,i}$ are independent of each other and follow 
$$B \Big( \min \Big\{ 1, \frac{\sum_{k \in K_{i}} N_i^{(z)}}{S_i^{(z)}} + \theta^{(z)} \Big\} \Big),$$ 
where $K_i$ corresponds to the ith patent classes. The parameter $0 < \theta^{(z)} < 1$ indicates the propensity for any patent to cite patents of its own technological or semantic class. When $\theta^{(z)} = 0$, the probability of citing patents from its own class is simply $\frac{\sum_{k \in K_{i}} N_i^{(z)}}{S_i^{(z)}}$ , which is what we would have if classes were assigned randomly and independently from patents' contents. Conversely, there are 100\% of within class citations when $\theta^{(z)} = 1$. Finally, we assume that the number of couples $C_i$ are a sequence of independent and identically distributed random variables following the discrete distribution $C$, and also independent from the other quantities.

The problem can now be expressed as the statistical test $\theta^{(sem)} > \theta^{(tec)}$. To do that, we first estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding MLE $\hat{\theta}^{(z)}$. The likelihood function, along with derivations of the standard deviation expression and details about the test, can be found in Supplementary Material \textcolor{red}{C'est bien comme ca qu'on appelle l'Appendix?}. The fitted values, standard errors, statistic values and p-values on non-overlapping blocks from the period 81-2010 are reported on Table bla bla. We use different values of thresholds for semantic classes. For a given class and threshold, we only keep the patents with a semantic value \textcolor{red}{Comment t'appelles ca Juste?}\textcolor{blue}{tu peux mettre ``semantic probability'', c'est exactement la proba empirique du patent d'appartenir à la classe} above the threshold. Bla bla ba to continue on interpretation

%%%%%%%%%%%%%%%%%%%%%
\section{Discussion \label{discussion}}
%%%%%%%%%%%%%%%%%%%%%

% Rationale for now : extract information that is quite independent from technological classification ; potential of this method demonstrated through simple examples (descriptive stats, basic measures, simple model)

% develop here the possible developments we talked about (trajectories of firms, etc ?)

%%%%%%%%%%%%%%%%
\subsection{Further Developments}

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Supervised and unsupervised Data Mining}

% learn patterns, what makes a patent innovative ; detect breakthrough innovation, etc.

We tested simple potential predictors of patent innovative character and/or success, i.e. supervised data-mining. \comment{Anto put here your regressions, to demonstrate the potentialities of our approach as predictors ?}

Insights from unsupervised data-mining techniques on features linked to both classifications, patents characteristics and the citation network, will surely be a broad and fertile research direction to investigate. As this kind of approach generally requires a fine-tuning of features (at least with ``classical'', non-deep, techniques) that could be the subject of a full paper, we let this for further work.

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Multi-modeling semantic classification}

The semantic classification method could be reinforced by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method~\cite{blei2003latent}, already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a  field rather than distant technological recombination. Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation), and secondly, depending on the level of orthogonality with our classification, potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Hyper-network analysis}

% how different info layers : citations ; techno ; semantic forms a multiplex (nodes = patents, with different types of connexions)

% we can then use multi-layer network analysis, such as generalized centrality de la miss Elisa \cite{de2015ranking}

%\textbf{how bipartite/multilayer approaches can push us further ; ex multilayer centrality that is trendy and hot now~\cite{de2015ranking} %(as the miss working on it ---> https://twitter.com/elisa_omodei ;) - totally unscientific sorry, it's to see if you read the comments ^^)

% note : redefine more precisely layers of the nw and clarify if dealing with multilayer nw or hypernw. if nodes are patents only, that can be linked by different type of relations (citation, belonging to same techno class, belonging to same semantic class) then it is an hypernetwork.

%\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network. We apply a similar methodology to compare technological and semantic layers.

Our use of network analysis stayed somehow limited here, and newly developed techniques could be applied. Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sens of multiple layers with different classification links and citation links. \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network, what could be applied as a refinement of the overlap, modularity and statistical modeling done here. Furthermore, is has been recently shown that measures on projections of multilayer networks induced a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, what confirms the potentiality of such a development.

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Towards a more exhaustive database}

%\textit{how we will parse full texts ; do OCR (we won't, we will parse Google as it would take at least a postdoc to manage a very bad OCR, whereas gogole is an easy target with very good data ; the difficult point will be to explain how we actually got the data...)}

\comment{Attention, un peu contradictoire avec la partie "toward a complementary classification}
Our semantic analysis was limited to the text of abstracts and a legitimate question is what information the use of full texts would allow to capture: it may contain more information but with more noise, making the filtration process more tricky; it may also be less structured than abstracts and thus have a smaller information-to-length ratio (compression rate) than using abstracts. These questions can not be answered from scratch, as the level of compression and information loss of the abstract writing process is not known. USPTO redbook raw data provides full texts up to 1976: their collection will be a first step into the reinforcement of our database. \comment{Je préfère séparer bien les choses, ici on parle de récupérer les full texts, plus loin on parle de remonter plus loin dans le temps. Donc je déplacerai la phrase suivante}. Furthermore, going back in time, patents are available in image format. Then the use of Optical Character Recognition techniques is a way to retrieve plain text and extend our analysis in time, with both abstracts and full texts.

\comment{Les gars là-dessus j'ai trouvé la pirouette pour qu'on s'en sorte : on va crawler google, faire l'extended database, et la poster sur dataverse de manière anonyme (compte anonyme, faux nom et independent researcher, tout ça derrière ip anonyme), on aura plus qu'à la recup et la citer pour l'utiliser ! :) }[Pour une prochaine application alors ?]

%%%%%%%%%%%%%%%%%%%%%
\subsection{Potential Applications}

% I put random ideas ; plan not fixed at all !

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Trajectories of firms}

\comment{En chantier}[][]

The existence of a classification for technology enables researchers to build a technology space in which each USPC class is an axis. This approach has been popularized by~\cite{Jaffe1986distance} and is namely used in~\cite{Bloom2005distance} to consider firms' technological proximity. This approach has also been used to study the existence of clusters of technology or knowledge spillover. In our framework, we add an additional classification whose construction does not directly rely on the USPC system. It is therefore possible to use the current firm's patents portfolio and its content in terms of semantic class to study its movement in a technological space.~\cite{omodei2014social} studies trajectories of authors in a semantic space.

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Towards concrete measures of endogenous growth theories}

\textit{recall the very beginning of the project ; Aghion et al. ; is it a good idea Anto ?}

%%%%%%%%%%%%%%%%%%%%%
\paragraph{Looking backward into the history of innovation}

USPTO patent data have been digitized from the first patent in July 1790. However, not all of them contain a text that is directly exploitable. We consider that the quality of patent's images is good enough to rely on Optical Character Recognition techniques to retrieve plain text from at least 1920. With such data, we would be able to extend our analysis further back in time and to study how technological progress occur and combine in time. ~\cite{akcigit2013mechanics} conduct a similar .

%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%
\section*{Supporting Information \label{sectionSI}}
% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.

\subsection*{S1 Text : Definition of utility patent}

\textbf{Describes with more details the definition of patents and  context.}

\subsection*{S2 Text : Data collection procedure}

\textbf{Detailed description of data collection}

\subsection*{S3 File : Semantic Network Visualization}

\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})}

%%%%%%%%%%%%%%%%%%%%%
%\section*{Acknowledgments}

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%

\bibliographystyle{plos2015}
\bibliography{patents}

%%%%%%%%%%%%%%%%%%%%
%% Supplementary Information
%%%%%%%%%%%%%%%%%%%%

\newpage

\section*{Supporting Information \label{sectionSI}}

\subsection*{Definition of utility patent}

A utility patent at the USPTO is a document providing intellectual property and protection of an invention. It excludes others to making, using, or selling the invention the same invention in the United States in exchange for a disclosure of the patent content. The protection is granted for 20 years since 1995 (it was 17 years before that from 1860) starting from the year the patent application was filled, but can be interrupted before if its owner fails to pay the maintenance fees due after 3.5, 7.5 and 11.5 years. Utility patents are by far the most numerous, with more than 90\% of the total universe of USPTO patents.\footnote{Other categories are Plant patents, Design patents and Reissue patents.} According to the Title 35 of the United States Codes (35 USC) section 101: \textit{``Whoever invents or discovers any new and useful process, machine, manufacture, or composition of matter, or any new and useful improvement thereof, may obtain a patent therefor, subject to the conditions and requirements of this title.''}\footnote{%
Patent laws can be found in http://www.uspto.gov/web/offices/pac/mpep/mpep-9015-appx-l.html\#d0e302376} In practice however, other types of invention including algorithms can also be patented.\footnote{A notable example is the patent \textit{US6285999} protecting the Page Rank algorithm invented by Larry Page in 1998 which was the genesis of Google.} The two following sections of the 35 USC defined the condition an invention must meet to be protected by the USPTO: (i) novelty: the claimed invention cannot be already patented or described in a previous publication (35 USC section 102); (ii) obviousness: \textit{``differences between the claimed invention and the prior art must not be such that the claimed invention as a whole would have been obvious before the effective filing date of the claimed invention to a person having ordinary skill in the art to which the claimed invention pertains''}. (35 USC section 103). After review from the USPTO experts, an application satisfying these requirements will be accepted and a patent granted. The average time lag for such a review is on average a little more than 2 years since 1976, with some patents being granted after much more than two years.\footnote{This time lag, sometimes called the grant lag, is highly heterogeneous across technological fields. In addition, it cannot be considered as totally random. For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\cite{regibeau2010}.}

\paragraph{Sample restriction}
As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013. For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below). We restrict attention to patents applied for before 2007. The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO. However, in order to date them as closely as possible to the date of invention, we use the application date as a reference. As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013. Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
 %\vspace{1cm}
\centering
\frame{
\includegraphics[scale=0.8]{figures/cit_lag.png}
}
 \caption{Number of citations per lag in year}
 \label{fig1}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\subsection*{Data collection procedure}

\label{supp:data}

Raw version of USPTO redbook with abstracts are available for years 1976-2014 starting from bulk download page at \url{https://bulkdata.uspto.gov/}. A script automatically downloads and proceeds files, with the following filters transforming different format and xml schemes into a uniform dictionary data structure :

\begin{itemize}
\item \texttt{dat} files (1976-2000) : handmade parser
\item \texttt{xml}
\end{itemize}

Everything is then stored into a MongoDB database, which latest dump is available at \url{http://dx.doi.org/10.7910/DVN/BW3ACK} % TODO find a way to anonymize the db for submission

%%%%%%%%%%%%%%%%%%%%
\subsection*{Network Sensitivity Analysis \label{app:sensitivity}}

% indicators etc

% sensitivity on time window length ?

\subsubsection*{Network Optimization for all years}

% plots for all years

% TODO plots for all years and pointer here to subfolder on repo ?

The example of Fig.~\ref{fig:networksensitivity} for a given year yielded the same qualitative behavior for all years. All corresponding plots are available on the repository at \texttt{}.

\subsubsection*{An alternative filtering method}

Other heuristic for network construction were tested. We describe one in the following. We assume the highest degree terms do not carry specific information on particular classes and can be thus filtered given a maximal degree threshold $k{max}$. Similarly, edge with small weight must not carry significant information and are filtered according to a minimal edge weight threshold $w_{min}$. Keywords are preliminary filtered by a document frequency window $\left[ f_{min},f_{max} \right]$ which is slightly different from network filtering and complementary. A sensitivity analysis of resulting network topology to these parameters is shown in Fig. .

%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
% values of some topological measures in 2D parameter space
\includegraphics[width=\textwidth]{figures/graph_sens_2010_msesizes}
\caption{Variation of semantic network indicators across a 4-dimensional parameter space (figure-level axis : $(k_{max},w_{min})$; meta axis: $(f_{min},f_{max})$), for year 2010, where indicators are modularity (louvain method), number of connected components, proximity of class size distribution to technological classes size distribution, communities number, network size, community size balance. A good optimization compromise is given here by $()$.}
% TODO change with proportion parameters in new figure
% TODO detail which obj to be minimized etc in supplementary material
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\subsection*{Semantic Network Characteristics}

% network degree distrib, connected components, etc.
% -> basic descriptive stats of the nw

\textcolor{red}{not sure this additional work is very useful}

%%%%%%%%%%%%%%%%%%%%
\subsection*{Time-window size sensitivity}

% put some graphs for 3-years time window : same qualitative properties but a bit more noisy

% TODO which graphs ?

%%%%%%%%%%%%%%%%%%%%
\subsection*{Statistical derivations}
\subsubsection*{Likelihood expression}
This will facilitate the likelihood analysis in the following. We have
\begin{eqnarray*}
\log \mathcal{L} \big( C_N, C_N^{(z)} , \cdots , C_1, C_1^{(z)} \big) & = & \sum_{i=2}^N \log \mathcal{L} \big( C_i, C_i^{(z)} | C_{i-1}, C_{i-1}^{(z)} \cdots , C_1, C_1^{(z)} \big) + \log \mathcal{L} \big( C_1, C_1^{(z)} \big).
\end{eqnarray*}
Note that in view of our assumptions we have
\begin{eqnarray*}
\log \mathcal{L} \big( C_i, C_i^{(z)} | C_{i-1}, C_{i-1}^{(z)} \cdots , C_1, C_1^{(z)} \big) & = & \log \mathcal{L} \big( C_i, C_i^{(z)} | N_{i}^{(z)} \big)\\
& = & \log \mathcal{L} \big(C_i^{(z)} | C_i , N_{i}^{(z)} \big) +
\log \mathcal{L} \big( C_i | N_{i}^{(z)} \big)\\
& = & \log \mathcal{L} \big(C_i^{(z)} | C_i , N_{i}^{(z)} \big) +
\log \mathcal{L} \big( C_i \big)
\end{eqnarray*}
Thus, the log likelihood is equal to
\begin{eqnarray}
\label{lik} \log \mathcal{L} \big( C_N, C_N^{(z)} , \cdots , C_1, C_1^{(z)} \big) & = &\sum_{i=1}^N  \log \mathcal{L} \big(C_i^{(z)} | C_i , N_{i}^{(z)} \big) +
\log \mathcal{L} \big( C_i \big).
\end{eqnarray}
Note that on the right-hand side in (\ref{lik}), the left term depends on the parameter $\theta^{(z)}$ whereas the right term doesn't depend on $\theta^{(z)}$. Thus we can remove it for the maximization procedure.

\subsubsection*{Standard error}

\subsubsection*{Test statistic}

%%%%%%%%%%%%%%%%%%%%
\subsection*{Additional plots}

% plots that have some info but not included in paper

%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
% figure : interlayer overlap
\includegraphics[width=0.49\textwidth]{figures/interov_patentnorm_all_density}
\includegraphics[width=0.49\textwidth]{figures/interov_patentnorm_all_ts}\\
\caption{Inter-classification effective overlaps (normalized by patent count)}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
%% Junk
%%%%%%%%%%%%%%%%%%%%%%

%Data-mining and network analysis~\cite{newman2010networks} can bring different insights.  As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g. in the recent analysis on 20\textsuperscript{th} century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation necessarily involves complex patterns which understanding must have positive feedback on the economy.\par

%%%%%%%%%%%%%%%%%%%%
%%  Templates
%%%%%%%%%%%%%%%%%%%%

% For figure citations, please use "Fig." instead of "Figure".
%\begin{figure}[h]
%\caption{{\bf Figure Title first bold sentence}
%Figure Caption}
%\label{fig1}
%\end{figure}

%
%
%
%\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
%\caption{
%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
%\begin{tabular}{|l|l|l|l|l|l|l|l|}
%\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
%\end{tabular}
%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
%\end{flushleft}
%\label{table1}
%\end{adjustwidth}
%\end{table}
%
%

%
%\subsection*{S1 Video}
%\label{S1_Video}
%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Text}
%\label{S1_Text}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Fig}
%\label{S1_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S2 Fig}
%\label{S2_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
%\subsection*{S1 Table}
%\label{S1_Table}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%

%\begin{thebibliography}{10}
%\bibitem{bib1}
%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005

%\bibitem{bib2}
%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.

%\end{thebibliography}

\end{document}

### 2017-04-02 Models/Japan/network.R

@@ -1,0 +1,44 @@
+
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/Japan'))
+
+filepath = paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Data/Japan/jp.csv')
+
+library(dplyr)
+library(igraph)
+
+raw <- as.tbl(read.csv(file=filepath,sep=',',stringsAsFactors = FALSE))
+
+firms = as.character(unique(raw$fno))
+classes = unique(raw$IPC)
+
+probas = matrix(0,length(firms),length(classes))
+rownames(probas) = firms
+colnames(probas) = classes
+
+# compute count matrix
+for(i in 1:nrow(raw)){probas[as.character(raw$fno[i]),raw$IPC[i]]=probas[as.character(raw$fno[i]),raw$IPC[i]]+1}
+
+# normalize to have probas by firm
+probas <- t(apply(probas,1,function(r){r/sum(r)}))
+
+# proximity matrix between firms
+firmproximity = probas%*%t(probas)
+
+# hist(c(firmproximity[firmproximity>0]),breaks=10000)
+# -> seem to have a nice distribution
+
+# optional threshold parameters, set > 0 to have smaller graphs
+link_threshold = 0.05
+firmproximity[firmproximity<link_threshold]=0
+
+g = graph_from_adjacency_matrix(firmproximity,mode="undirected",weighted = TRUE,diag = FALSE)
+
+# check modularity
+#cl = cluster_louvain(g)
+
+dir.create('test')
+outfile = 'test/graph_theta0.05.gml'
+write_graph(graph = g,file = outfile,format = 'gml')
+
+

### 2017-04-02 Models/Semantic/semanalysis.R

@@ -91,14 +91,17 @@ for(year in wyears){
   #ranks=append(ranks,1:length(semsizes));sortedsizes=append(sortedsizes,sort(semsizes,decreasing = TRUE));sortednsizes=append(sortednsizes,sort(semsizes/nrow(semprobas),decreasing = TRUE))
 }
 
+#save(sizes,years,type,ranks,file='figdata/fig4.RData')
+#load('figdata/fig4.RData')
 
 ## rank size plot 
 
 g=ggplot(data.frame(size=sizes,year=as.character(years),rank=ranks,type=type))
 g+geom_line(aes(x=rank,y=size,colour=year,group=year))+
   scale_x_log10()+scale_y_log10()+facet_wrap(~type,scales="fixed")+ylab("size") + theme(axis.title = element_text(size = 22), 
-    axis.text.x = element_text(size = 15), 
-    axis.text.y = element_text(size = 15))
+    axis.text.x = element_text(size = 15),axis.text.y = element_text(size = 15),
+    strip.text = element_text(size=15),
+    legend.text=element_text(size=15), legend.title=element_text(size=15))
 ggsave(file=paste0(Sys.getenv("CS_HOME"),'/PatentsMining/Results/Semantic/Analysis/window5/sizes/all_raw_counts.pdf'),width=10,height=5)
 
 
@@ -213,7 +216,9 @@ plotsIntraOverlap <-function(measure,xlabel){
   g=ggplot(df[df$measure==measure&df$type!="inter-classifications",],aes(x=overlap,colour=year))
   g+geom_density(alpha=0.25)+xlab(xlabel)+ylab("density")+
     scale_x_log10()+facet_wrap(~type,scales="free_y")+
-    theme(axis.title = element_text(size = 22), axis.text.x = element_text(size = 15),  axis.text.y = element_text(size = 15))
+    theme(axis.title = element_text(size = 22), axis.text.x = element_text(size = 15),  axis.text.y = element_text(size = 15),
+          strip.text = element_text(size=15),
+          legend.text=element_text(size=15), legend.title=element_text(size=15))
   ggsave(file=paste0(Sys.getenv("CS_HOME"),'/PatentsMining/Results/Semantic/Analysis/window5/overlap/',measure,'_all_density_semcounts.pdf'),width=10,height=5)
 
   rm(g);gc()
@@ -224,7 +229,7 @@ plotsIntraOverlap <-function(measure,xlabel){
   gsum+geom_point()+geom_line()+
[…]

### 2018-11-10 Docs/Papers/Technical/overleafv2/Response_to_Reviewers.tex
slides_seminar

%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\usepackage[document]{ragged2e}
% pour justifier

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\rmdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{xparse}
\DeclareDocumentCommand{\comment}{m o o o o}
{%
    \textcolor{red}{#1}
    \IfValueT{#2}{\textcolor{blue}{#2}}
    \IfValueT{#3}{\textcolor{ForestGreen}{#3}}
    \IfValueT{#4}{\textcolor{red!50!blue}{#4}}
    \IfValueT{#5}{\textcolor{Aquamarine}{#5}}
}

% personal data
%\name{Yoann}{Potiron}
%\title{Keio University}                               % optional, remove / comment the line if not wanted
%\address{Assistant Professor Faculty Business and Commerce}{2-15-45 Mita, Minato-ku, Tokyo, 108-8345}{Japan}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{+1~(234)~567~890}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+81~(0)3~5418~6571}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
%\email{potiron@fbc.keio.ac.jp}  
%\extrainfo{yoann.potiron@gmail.com}
% optional, remove / comment the line if not wanted
%\homepage{http://www.fbc.keio.ac.jp/\char`\~ potiron}                         % optional, remove / comment the line if not wanted
%\extrainfo{yoann.potiron@gmail.com}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
%-----       letter       ---------------------------------------------------------

% must contain :
%Summarize the study’s contribution to the scientific literature
%Relate the study to previously published work
%Specify the type of article (for example, research article, systematic review, meta-analysis, clinical trial)
%Describe any prior interactions with PLOS regarding the submitted manuscript
%Suggest appropriate Academic Editors to handle your manuscript (see the full list of Academic Editors)
%List any opposed reviewers
\firstname{}
\lastname{}
\begin{document}

% recipient data
\recipient{Editor PLOS ONE}{}
\date{\today}
\opening{Dear Editor,}
\closing{Yours faithfully,\\
Juste Raimbault\\
Université Paris 7 - UMR CNRS 8504 Géographie-cités
}
         % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

\justify
\justify
Thank you for considering our manuscript ``Classifying Patents Based
on their Semantic Content'' for possible publication in PLOS ONE. We are also very grateful to your suggestions and comments. This will undoubtedly be of great value to the paper.

We have read carefully your suggestions and comments, and have updated the paper accordingly. We provide you now the point-by-point response to the Editor and referees' reports.

We deal first with the Editor's comments. 
\begin{enumerate}
    \item We made adjustments to fully meet PLOS ONE requirements. All figures were converted and assessed using the PACE tool.
    \item "Authors used co-occurrence of keywords to construct a patent network. Is this a new way? Or at least a discussion of the advantages should be provided." \\
    $\rightarrow$ The use of co-occurrences to construct a semantic network has already been used, and is the best way to extract the endogenous semantic structure. We added a discussion on this point.
    \item "Authors introduced a measure to correct the network topology. But how to properly determine the threshold? Why choose the value 0.06 ?"\\
    $\rightarrow$ Thank you for pointing out this issue. We have been more specific about it now, adding three sentences. Indeed, the explanation at the end of Section 3.3 was sloppy.

    \item "The research background include complex network analysis, community detection and data analysis, some recent progress in these areas should be reviewed" \\
    $\rightarrow$ We included some of the references suggested in Section 3.5, as time series complex network analysis is indeed an interesting potential development.
    \item "All the parameters should be clearly explained."\\
    $\rightarrow$ Thank you for also pointing this out. We have been clearer on the definition of $K_w$, $k$ and $t_i$ (Section 3.2), $\theta_c$, $\theta_w$ and $\theta_w^{(0)}$ (Section 3.3).
\end{enumerate}

\bigskip

We also provide you responses to Reviewer \#3. Reviewers \#1 and \#2 did not ask anything specific but their comments were taken into account in the adjustments we made.
\begin{enumerate}
\item "Maybe a minor typo in Page 24 - "availability of these data" --> "this data" or "these datasets"".\\
$\rightarrow$ We corrected accordingly.
\item "I also did not see a caption for the figures and it is quite hard to read the text in the figures due to their current small size. New readers are attracted to tables and figures, and thus it is useful to have descriptive captions - the current caption for Table 1 does not describe the variables being used (I know the text does it) - a brief description of theta being the likelihood estimates (or similar) would be useful."\\
$\rightarrow$ We have made the according changes. All captions inside figures were magnified as large as possible to ensure readability.
\item "I like the authors' approach overall, but would also recommend adding some discussion on how a semantic approach enables information integration and reuse - possibly with how their dataset / ontology can be linked to others already existing in Linked Open Data. If such linking already exists, it should be shown - otherwise, this is a strong direction for future work."\\
$\rightarrow$ This is indeed a very good suggestion and we add ideas of interesting potential developments by joining our database with existing open databases. We added accordingly a part to the discussion.
\end{enumerate}
\justify

%%
%Antonin Bergeaud received no specific grant from any funding agency in the public, commercial, or not-for-profit sectors for this research.

%[(Juste) comme je disais dans le mail, je pense vraiment pas utile de citer des trucs qui ont pas grand chose à voir sachant qu'on cite la litérature la plus précise possible sur les techniques qu'on utilise. Je vous laisse juger de ce qu'il propose, je trouve ça scandaleux ce ne sont que de ses papiers qui n'ont quasiment aucun rapport.. si la publi rapide de notre papier n'en dépendait pas, je signalerais l'éditeur pour manquement d'éthique académique, mais bon on va faire des compromis..%
%    \begin{itemize}
%    \item Europhysics Letters, 2016, 116: 50001; Gao, Z. K., Small, M., \& Kurths, J. (2017). Complex network analysis of time series. EPL (Europhysics Letters), 116(5), 50001. papier de l'éditeur, sur le lien entre systèmes dynamiques et Complex networks. pas trop de rapport.. gao2017complex
%    \item Scientific Reports, 2016, 6: 20052 : Gao, Z. K., Yang, Y. X., Zhai, L. S., Dang, W. D., Yu, J. L., \& Jin, N. D. (2016). Multivariate multiscale complex network analysis of vertical upward oil-water two-phase flow in a small diameter pipe. Scientific reports, 6. $\rightarrow$ c'est un papier de l'éditeur, absolument rien à voir avec ce qu'on utilise, si ce n'est le nom de Complex Networks.. gao2016multivariate
%    \item Europhysics Letters, 2015, 109: 30005; Gao, Z. K., Yang, Y. X., Fang, P. C., Zou, Y., Xia, C. Y., \& Du, M. (2015). Multiscale complex network for analyzing experimental multivariate time series. EPL (Europhysics Letters), 109(3), 30005. ENCORE un papier de l'éditeur gao2015multiscale
%    \item Scientific Reports, 2015, 5: 8222. Gao, Z. K., Yang, Y. X., Fang, P. C., Jin, N. D., Xia, C. Y., \& Hu, L. D. (2015). Multi-frequency complex network from time series for uncovering oil-water flow structure. Scientific reports, 5, 8222. idem.. gao2015multi
%    \end{itemize}]

%%
% potential editors

%César A Hidalgo
%Massachusetts Institute of Technology
%UNITED STATES 
%Subject Areas: Science policy and economics, Social sciences, Sociology, Communications, Social systems, Computational sociology, Economics, Economic models, Structural economic models, Industrial organization, Economics of technical change, Microeconomics, Urban economics, International trade, Development economics, Economic development, Spatial economic analysis, Computer and information sciences, Computing methods, Computer graphics, Infographics, Data mining, Social networks, Complex systems, Economic geography, Human geography, Engineering and technology, Mathematics, Applied mathematics, Physics, Research monitoring, Publication practices

%Tobias Preis
%University of Warwick
%UNITED KINGDOM 
%Subject Areas: Social sciences, Communications, Media studies, Economics, Economic models, Structure of markets, Information economics, Microeconomics, Spatial economic analysis, Linguistics, Semantics, Computational linguistics, Lexicography, Computer and information sciences, Computing methods, Mathematical computing, Computer applications, Web-based applications, Information technology, Information architecture, Information storage and retrieval, Natural language processing, Text mining, Information theory, Operations research, Complex systems, Computer modeling, Computerized simulations, Economic geography, Decision analysis, Mathematics, Mathematical economics, Numerical analysis, Applied mathematics, Algorithms, Decision theory, Physics, Interdisciplinary physics, Statistical mechanics

%Wolfgang Glanzel
%Katholieke Universiteit Leuven
%BELGIUM 
%Subject Areas: Science policy, Economics, Information economics, Computer and information sciences, Algorithms, Research assessment, Bibliometrics, Publication practices

%Joshua L Rosenbloom
%Iowa State University
%UNITED STATES 
%Subject Areas: Science policy, Research funding, Science and technology workforce, Science policy and economics, Social sciences, Economics, Human capital, Labor economics, Microeconomics, Commerce, Economic analysis, Economic history, Economic geography

\makeletterclosing

\end{document}

%% end of file `template.tex'.

### 2018-11-10 Docs/Papers/Technical/overleafv2/S1_Text.tex
slides_seminar

--- 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
@@
-\documentclass[12pt,twoside,a4paper]{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{eurosym}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage[section]{placeins}
-\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
-\usepackage{setspace}
-\usepackage{rotating}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{etoolbox}
-\usepackage{amsmath,amssymb}
-\usepackage{float}
-\usepackage{xcolor}
-\usepackage{hyperref}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{enumitem}
-\usepackage{caption}
-\usepackage{nameref}
-\usepackage{lscape}
-\usepackage{fancyhdr}
+\input{si.tex}
 
-\setcounter{MaxMatrixCols}{10}
-\hypersetup{
-    colorlinks, linkcolor={dark-red},
-    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
-}
-\geometry{hmargin=4cm,vmargin=4cm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{assumption}{Assumption}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-\setcounter{secnumdepth}{5}
-\textwidth 6.0in
-\textheight 8.84in 
-\setlength{\topmargin}{-0.3in}
-\setlength{\oddsidemargin}{0.0in}
-\setlength{\evensidemargin}{0.0in}
-\setlength{\abovecaptionskip}{0pt}
-\setlength{\belowcaptionskip}{5pt}
-\setlength{\textfloatsep}{25pt}  
-\setlength{\intextsep}{5pt}   
-\fancyhf{}
-\pagestyle{fancy}
-\renewcommand{\headrulewidth}{1pt}
-\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
-\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
-\fancyfoot[C]{\thepage}
-
-\begin{document}
-
-\title{Classifying Patents Based on their Semantic Content\thanks{%
-Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
-Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
-\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
- \ \ \ \ \ Juste Raimbault \bigskip}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% Please keep the abstract below 300 words
-\begin{abstract}
-In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach.
-This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward.
-To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly.
-We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes.
-Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model.
-This suggests that our method is a useful tool to extract endogenous information.
-\end{abstract}
-
-\pagebreak
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}.
-\cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation.
-Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis.
-Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review.
-Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}.
-With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters.
-Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.
-
-Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies.
-But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share.
-Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g.
-~\cite{AAKnetwork2016}).
-
-In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it.
-In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract.
-Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach.
-The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence).
-One can for instance consider the case of the word \textit{optic}.
-Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic.
-This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.
-
-Previous research has already proposed to use semantic networks to study technological domains and detect novelty.
-~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain.
-The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}.
-More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation.
-Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).
-
-Building on such previous research, we make several contributions by fulfilling some shortcomings of existing studies, such as for example the use of frequency-selected single keywords.
-First of all, we develop and implement a novel fully-automatized methodology to classify patents according to their semantic abstract content, which is to the best of our knowledge the first of its type.
-This includes the following refinements for which details can be found in Section \ref{keywords}: (i) use of multi-stems as potential keywords; (ii) filtering of keywords based on a second-order (co-occurrences) relevance measure and on an external independent measure (technological dispersion); (iii) multi-objective optimization of semantic network modularity and size.
-The use of all this techniques in the context of semantic classification is new and essential from a practical perspective.
-
-Furthermore, most of the existing studies rely on a subsample of patent data, whereas we implement it on the full US Patent database from 1976 to 2013.
-This way, a general structure of technological innovation can be studied.
-We draw from this application promising qualitative stylized facts, such as a qualitative regime shift around the end of the 1990s, and a significant improvement of citation modularity for the semantic classification when comparing to the technological classification.
-These thematic conclusions validate our method as a useful tool to extract endogenous information, in a complementary way to the technological classification.
-
-Finally, the statistical model introduced in Section \ref{statisticalmodel} seems to indicate that patents tend to cite more similar patents in the semantic network  when fitted to data.
-In particular, this propensity is shown to be significantly bigger than the corresponding propensity for technological classes, and this seems to be consistent over time.
-On the account of this information, we believe that patent officers could benefit very much from looking at the semantic network when considering potential citation candidates of a patent in review.
-
-The paper is organized as follows.
-Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process.
-Section \ref{keywords} explains the construction of the semantic classes.
-Section \ref{result} tests their relevance by providing exploratory results.
-Finally, section \ref{discussion} discusses potential further developments and conclude.
-More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background \label{data}}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013.
-A clearer definition of utility patent is given in~\nameref{sectionSI}.
-Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{An existing classification: the USPC system}
-
-Each USPTO patent is associated with a non-empty set of technological classes and subclasses.
-There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system.
-While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention.
-A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass.
-At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes.
-When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A bibliographical network between patents: citations \label{sub:citation}}
-
-As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art.
-They therefore indicate the past knowledge which relates to the patented invention.
-Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent.
-One can consult~\cite{oecdpatentmanual} for more details about this.
-Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}).
-Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves.
-From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations).
-We can thus build a complete network of citations that we will use later on in the analysis.
-
-Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years.
-This distribution is highly skewed, the $95^{th}$ percentile is 21 years.
-We also report 164,000 citations with a negative time lag.
-This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others.
-
-In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years.
-We impose this restriction for two reasons.
-First, the number of citations received peaks 4-5 years after application.
-Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones.
-As we are restricting to citations received no later than 5 years after the application date, this effect will only affect patents with an application date after 2007.
-
-%%%%%%%%%%%%%%%%%%
-\subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
-Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
-In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}).
-The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).
-
-We construct from raw data a unified database.
-Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976.
-Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}.
-The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
-Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
-
-We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013.
-When distributed by the year of application, the picture is slightly different.
-The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007.
-Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents.
-These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}.
-Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window.
-270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations.
-A within class citation is defined as a citation between two patents sharing at least one common technological class.
-Following this definition, 84\% of the citations are within class citations.
-14\% of the citations are between two patents that share the exact same set of technological classes.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Towards a Complementary Classification}
-
-Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}.
-The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications.
-The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review).
-Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}.
-As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored.
-One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples.
-Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies.
-Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.
-
-Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}).
-Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Semantic Classification Construction \label{keywords}}
-
-In this section, we describe methods and empirical analysis leading to the construction of semantic network and the corresponding classification.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords extraction}
-\label{keywordsextraction}
-
-Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
-$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
-\begin{enumerate}
-\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).
-
-\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.
-
-\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens.
-At this point the abstract text is reduced to a set of stems and their grammatical functions.
-\item Multi-stems construction: these are the basic semantic units used in further analysis.
-They are constructed as groups of successive stems in a sentence which satisfies a simple grammatical function rule.
-The length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives.
-We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
-\end{enumerate}
-
-Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations.
-This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining}
-}
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords relevance estimation}
-\label{keywords_est}
-\paragraph{Relevance definition}
-
-Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
-We choose to set this parameter to $K_w = 100,000$.
-We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$.
-The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
-Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
-More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together.
-The \emph{termhood} score $t_i$ is defined as
-
-\[
-t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
-\]
-
-\paragraph{Moving window estimation}
-The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past.
-Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$.
-Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents.
-This way, we will obtain semantic classes which are exploitable on a $T_0$ time span.
-For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}.
-In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}.
-Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Construction of the semantic network}
-\label{construction}
-
-We keep the set of most relevant keywords $\mathcal{K}_W$ and obtain their co-occurrence matrix as defined in Section \ref{keywords_est}.
-This matrix can be directly interpreted as the weighted adjacency matrix of the semantic network.
-At this stage, the topology of raw networks does not allow the extraction of clear communities.
-This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g.
-\texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant.
-We therefore introduce an additional measure to correct the network topology: the concentration of keywords across technological classes, defined as:
-
-$$c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2},$$
-
-where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes.
-The higher $c_{tech}$, the more specific to a technological class the node is.
-For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$.
-In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
-To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
-Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
-At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward.
-Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities.
-We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-%\hspace{-2.5cm}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
-%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
-\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values.
-The maximum is roughly stable across $\theta_c$ (dashed red line).
-\textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
-\label{fig:networksensitivity}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{striking}
-%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
-\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
-The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
-\label{fig:rawnetwork}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Characteristics of Semantic Classes}
-\label{characteristics}
-For each year $t$, we define as $N^{(sem)}_t$ the number of semantic classes which have been computed by clustering keywords from patents appeared during the period $\big[ t-T_0, t \big]$ (we recall that we have chosen $T_0=4$).
-Each semantic class $k =  1, \cdots, N^{(sem)}_t$ is characterized by a set of keywords $K(k,t)$ which is a subset of $\mathcal{K}_W$ selected as described in Section \ref{keywordsextraction} to Section \ref{construction}.
-The cardinal of $K(k, t)$ distribution across each semantic class $k$ is highly skewed with a few semantic classes containing over $1,000$ keywords, most of them with roughly the same number of keywords.
-In contrast, there are also many semantic classes with only two keywords.
-There are around 30 keywords by semantic class on average and the median is 2 for any $t$.
-Fig.~\ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{meancomsize}
-%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
-\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
-\label{fig:mean_K}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph*{Title of semantic classes}
-USPC technological classes are defined by a title and a highly accurate definition which help retrieve patents easily.
-The title can be a single word (e.g.: class 101: ``Printing'') or more complex (e.g.: class 218: ``High-voltage switches with arc preventing or extinguishing devices'').
-As our goal is to release a comprehensive database in which each patent is associated with a set of semantic classes, it is necessary to give an insight on what these classes represent by associating a short description or a title as in~\cite{tseng2007text}.
-In our case, such description is taken as a subset of keywords taken from $K(k,t)$.
-For the vast majority of semantic classes that have less than 5 keywords, we decide to keep all of theses keywords as a description.
-For the remaining classes which feature around 50 keywords on average, we rely on the topological properties of the semantic network.~\cite{yang2000improving} suggest to retain only the most frequently used terms in $K(k,t)$.
-Another possibility is to select 5 keywords based on their network centrality with the idea that very central keywords are the best candidates to describe the overall idea captured by a community.
-For example, the largest semantic class in 2003-2007 is characterized by the keywords: \texttt{Support Packet; Tree Network; Network Wide; Voic Stream; Code Symbol Reader}.
-
-\paragraph*{Size of technological and semantic classes} 
-We consider a specific window of observations (for example 2000-2004), and we define $Z$ the number of patents which appeared during that time window.
-For each patent $i=1, \cdots, Z$ we associate a vector of probability where each component $p_{ij}^{(sem)} \in \big[ 0,1 \big]$, with  $j = 1, \cdots, N{(sem)}$ and where\footnote{When there is no room for confusion, we drop the subscript $t$ in $N_t^{(sem)}$.}
-$$\displaystyle \sum_{j=1}^{N^{(sem)}} p_{ij}^{(sem)} = 1.$$ On average across all time windows, a patent is associated to 1.8 semantic classes with a positive probability.
-Next we define the size of a semantic class as $$S_j^{(sem)} = \displaystyle \sum_{i=1}^Z p_{ij}^{(sem)}.$$
-Correspondingly, we aim to provide a consistent definition for technological classes.
-For that purpose, we follow the so-called ``fractional count'' method, which was introduced by the USPTO and consists in dividing equally the patents between all the classes they belong to.
-Formally, we define the number of technological classes as
-$N^{(tec)}$  (which is not time dependent contrary to the semantic case) and for $j = 1, \cdots, N^{(tec)}$ the corresponding matrix of probability is defined as
-\[
- p_{ij}^{(tec)} = \frac{B_{ij}}{\displaystyle \sum_{k=1}^{N^{(tec)}}{B_{ik}}},
-\]
-where  $B_{ij}$ equals $1$ if the $i$th patent belongs to the $j$th technological class and $0$ if not.
-When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix.
-Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Fig.~\ref{fig:class-sizes}.
-This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
-\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$,
-from the biggest to the smallest.
-The formal definition of size can be found in Section \ref{characteristics}.
-Each color corresponds to one specific year.
-Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications.
-This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}.
-Over time, curves are translated and levels of hierarchy stays roughly constant.}
-\label{fig:class-sizes}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Potential Refinements of the Method}
-
-Our semantic classification method could be refined by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method (e.g.~\cite{blei2003latent}), already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a field rather than distant technological recombination.
-Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation).
-Also, depending on the level of orthogonality with our classification, it can potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.
-
-Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis.
-Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
-Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Results \label{result}}
-%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present some key features of our resulting semantic classification showing both complementary and differences with the technological classification.
-We first present several measures derived from this semantic classification at the patent level: Diversity, Originality, Generality (Section \ref{subsec:orig-gene}) and Overlapping (Section \ref{subsec:overlaps}).
-We then show that the two classifications show highly
-different topological measures and strong statistical evidence that they feature a different model (Sections \ref{citationmodularity} and \ref{statisticalmodel}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Patent Level Measures}  \label{subsec:orig-gene}
-
-Given a classification system (technological or semantic classes), and the associated probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ (that were defined in Section \ref{characteristics}), one can define a patent-level diversity measure as one minus the Herfindhal concentration index on $p_{ij}$  by
-
-\[
-D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}.
-\]
-
-We show in Fig.~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series.
-This is carried with two different settings, namely including/not including patents with zero diversity (i.e.
-single class patents).
-We call other patents ``complicated patents'' in the following.
-First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes.
-More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization.
-This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}.
-Furthermore, a qualitative regime shift on semantic classification occurs around 1996.
-This can be seen whether or not we include patents with zero diversity.
-The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease.
-This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity.
-It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents.
-
-More commonly used in the literature are the measures of originality and generality.
-These measures follow the same idea than the above-defined diversity in quantifying the diversity of classes (whether technological or semantic) associated with a patent.
-But instead of looking at the patent's classes, they consider the classes of the patents that are cited or citing.
-Formally, the originality $O_i$ and the generality $G_i$ of a patent $i$ are defined as
-\[
-O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2} \text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2},
-\]
-where $z \in \{tec, sem\}$, $I_i$ denotes the set of patents that are cited by the $i$th patent within a five year window (i.e.
-if the $i$th patent appears at year $t$, then we consider patents on $[t-T_0, t]$) when considering the originality and $\tilde{I}_i$ the set of patents that cite patent $i$ after less than five years (i.e.
-we consider patents on $[t ,t + T_0]$) in the case of generality.
-Note that the measure of generality is forward looking in the sense that $G_i^{(z)}$ used information that will only be available 5 years after patent applications.
-Both measures are lower on average based on semantic classification than on technological classification.
-Fig.
-\ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-%First row : semantic with relevant keywords only - all patents 
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
-%Second row : patents with diversity $> 0$ (more than one class)}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
-%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
-\caption{
-\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$).
-The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e.
-patents with diversity greater than 0).
-}
-\label{fig:patent-level-orig}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\includegraphics[width=0.49\textwidth]{originality.png}
-\includegraphics[width=0.49\textwidth]{generality.png}\\
-%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
-\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
-}
-\label{fig:orig-gene}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classes overlaps} \label{subsec:overlaps}
-
-A proximity measure between two classes can be defined by their overlap in terms of patents. 
-Such measures could for example be used to construct a metrics between semantic classes.
-Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{Bloom2005distance}.
-Formally, recalling the definition of $\left(p_{ij}\right)$ as the probability for the $i$th patent to belong to the $j$th class and $N_P$ as the number of patents it writes
-\begin{eqnarray}
-\label{overlap}
-Overlap_{jk} = \frac{1}{N_P}\cdot \sum_{i=1}^{N_P} p_{ij} p_{ik}. 
-\end{eqnarray}
-
-The overlap is normalized by patent count to account for the effect of corpus size: by convention, we assume the overlap to be maximal when there is only one class in the corpus.
-A corresponding relative overlap is computed as a set similarity measure in the number of patents common to two classes A and B, given by $o(A,B)=2\cdot \frac{\left|A\cap B\right|}{\left|A\right| + \left|B\right|}$.
-
-\paragraph{Intra-classification overlaps}
-
-The study of distributions of overlaps inside each classification, i.e.
-between technological classes and between semantic classes separately, reveals the structural difference between the two classification methods, suggesting their complementary nature.
-Their evolution in time can furthermore give insights into trends of specialization.
-We show in Fig.~\ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications.
-The technological classification globally always follow a decreasing trend, corresponding to more and more isolated classes, i.e.
-specialized inventions, confirming the stylized fact obtained in previous subsection.
-For semantic classes, the dynamic is somehow more intriguing and supports the story of a qualitative regime shift suggested before.
-Although globally decreasing as technological overlap, normalized (resp.
-relative) mean overlap exhibits a peak (clearer for normalized overlap) culminating in 1996 (resp.
-1999).
-Looking at normalized overlaps, classification structure was somewhat stable until 1990, then strongly increased to peak in 1996 and then decrease at a similar pace up to now.
-Technologies began to share more and more until a breakpoint when increasing isolation became the rule again.
-An evolutionary perspective on technological innovation~\cite{ziman2003technological} could shed light on possible interpretations of this regime shift: as species evolve, the fitness landscape first would have been locally favorable to cross-insemination, until each fitness reaches a threshold above which auto-specialization becomes the optimal path.
-It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation.
-%This interpretation is consistent with the dynamics of semantic flows presented in Fig.~\ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
-\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
-\caption{
-\textbf{Intra-classification overlaps.}
-\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
-\textit{(Right column)} Corresponding mean time-series.
-\textit{(First row)} Normalized overlaps.
-\textit{(Second row)} Relative overlaps.}
-\label{fig:intra-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Inter-classification overlaps}
-
-Overlaps \emph{between} classifications are defined as in (\ref{overlap}), but with $j$ standing for the $j$th technological class and $k$ for the $k$th semantic class: $p_{ij}$ are technological probabilities and $p_{ik}$ semantic probabilities.
-They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Fig.~\ref{fig:inter-classif-overlap}.
-Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease.
-Although difficult to interpret directly, this stylized fact clearly unveils a change in the \emph{nature} of inventions, or at least in the relation between content of inventions and technological classification.
-As the tipping point is at the same time as the ones observed in the previous section and since the two statistics are different, it is unlikely that this is a mere coincidence.
-Thus, these observations could be markers of a hidden underlying structural changes in processes.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
-\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series.
-The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
-\label{fig:inter-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Citation Modularity}
-\label{citationmodularity}
-
-An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}.
-The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\cite{AAKnetwork2016}).
-This section studies empirically modularities of the citation network regarding the different classifications.
-To corroborate the obtained results, we propose to look at a more rigorous framework in Section \ref{statisticalmodel}.
-Modularity is a simple measure of how communities in a network are well clustered (see \cite{clauset2004finding} for the accurate definition).
-Although initially designed for single-class classifications, this measure can be extended to the case where nodes can belong to several classes at the same time, in our case with different probabilities as introduced in \cite{nicosia2009extending}.
-The simple directed modularity is given in our case by
-\[
-Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
-\]
-with $A_{ij}$ the citation adjacency matrix (i.e.
-$A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not), $k_i^{in}=\left| I_i\right|$ (resp.
-$k_i^{out}= \left|\tilde{I}_i \right|$) in-degree (resp.
-out-degree) of patents (i.e.
-the number of citations made by the $i$th patent to others and the number of citations received by the $i$th patent).
-$Q_d$ can be defined for each of the two classification systems: $z \in \{tec, sem\}$.
-If $z=tec$, $c_i$ is defined as the main patent class, which is taken as the first class whereas if $z=sem$, $c_i$ is the class with the largest probability.
-
-Multi-class modularity in turns is given by
-
-\[
-\displaystyle Q_{ov}^{(z)} = \frac{1}{N_P} \sum_{c = 1}^{N^{(z)}} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,c}^{out}k_i^{out}\beta_{j,c}^{in}k_j^{in}}{N_P}\right],
-\]
-where
-\[
- \beta_{i,c}^{out} =   \frac{1}{N_P} \displaystyle \sum_j F(p_{ic},p_{jc}) \text{ and } \beta_{j,c}^{in} =  \frac{1}{N_P} \displaystyle \sum_i F(p_{ic},p_{jc}).
-\]
-We take $F(p_{ic},p_{jc}) = p_{ic}\cdot p_{jc}$ as suggested in \cite{nicosia2009extending}.
-Modularity is an aggregated measure of how the network deviates from a null model where links would be randomly made according to node degree.
-In other words it captures the propensity for links to be inside the classes.
-Overlapping modularity naturally extends simple modularity by taking into account the fact that nodes can belong simultaneously to many classes.
-We document in Fig.~\ref{fig:modularities} both simple and multi-class modularities over time.
-For simple modularity, $Q_d^{(tec)}$ is low and stable across the years whereas $Q_d^{(sem)}$ is slightly greater and increasing.
-These values are however low and suggest that single classes are not sufficient to capture citation homophily.
-Multi-class modularities tell a different story.
-First of all, both classification modularities have a clear increasing trend, meaning that they become more and more adequate with citation network.
-The specializations revealed by both patent level diversities and classes overlap is a candidate explanation for this growing modularities.
-Secondly, semantic modularity dominates technological modularity by an order of magnitude (e.g.
-0.0094 for technological against 0.0853 for semantic in 2007) at each time.
-This discrepancy has a strong qualitative significance.
-Our semantic classification fits better the citation network when using multiple classes.
-As technologies can be seen as a combination of different components as shown by~\cite{Youn:2015fk}, this heterogeneous nature is most likely better taken into account by our multi-class semantic classification.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.49\textwidth]{simplemodularity}
-\includegraphics[width=0.49\textwidth]{overlappingmodularity}
-%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
-\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability).
-(Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
-\label{fig:modularities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistical Model}
-\label{statisticalmodel}
-In this section, we develop a statistical model aimed at quantifying performance of both technological and semantic classification systems.
-In particular, we aim at corroborating findings obtained in Section \ref{citationmodularity}.
-The mere difference between this approach and the citation modularity approach lies in the choice of the underlying model, and the according quantities of interest.
-In addition for the semantic approach, we want to see if when restricting to patents with higher probabilities to belong to a class, we obtain better results.
-To do that, we choose to look at within class citations proportion (for both technological and semantic approaches).
-We provide two obvious reasons why we choose this.
-First, the citations are commonly used as a proxy for performance as mentioned in Section \ref{citationmodularity}.
-Second, this choice is ``statistically fair'' in the sense that both approaches have focused on various goals and not on maximizing directly the within class proportion.
-Nonetheless, the within class proportion is too sensitive to the distribution of the shape of classes.
-For example, a dataset where patents for each class account for 10\% of the total number of patents will mechanically have a better within class proportion than if each class accounts for only 1\%.
-Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed.
-This effort ressembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth.
-Furthermore, the parameters fitted here can have a direct interpretation as a citation probability.
-
-We need to introduce and recall some notations.
-We consider a specific window of observations $\big[t- T_0, t \big]$, and we define $Z$ the number of patents which appeared during that time window.
-We let $t_1, \cdots, t_Z$ their corresponding appearance date by chronological order, which for simplicity are assumed to be such that $t_1 < \cdots < t_Z$.
-For each patent $i=1, \cdots, Z$ we consider $C_i$ the number of distinctive couples \{cited patent, cited patent's class\} made by the $i$th patent (for instance if the $i$th patent has only made one citation and that the cited patent is associated with three classes, then $C_i = 3$).
-Let $z \in \{tec, sem\}$, we define $N_{i}^{(z)}$  the number of patents associated to at least one of the $i$th classes at time $t_{i-1}$.
-For $l = 1, \cdots, C_i$ we consider the variables $B_{l,i}$, which equal $1$ if the cited patent's class is also common to the $i$th patent.
-We assume that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-where the parameter $0 \leq \theta^{(z)} \leq 1$ indicates the propensity for any patent to cite patents of its own technological or semantic class.
-When $\theta^{(z)} = 0$, the probability of citing patents from its own class is simply $N_{i}^{(z)}(i-1)^{-1}$, which corresponds to the observed proportion of patents which belong to at least one of the $i$th patent's classes.
-Thus this corresponds to the estimated probability of citing one patent if we assume that the probability of citing any patent $k=1, \cdots, i-1$ is uniformly distributed, which could be a reasonable assumption if classes were assigned randomly and independently from patent abstract contents.
-Conversely if $\theta^{(z)} = 1$, we are in the case of a model where there are 100\% of within class citations.
-A reasonable choice of $\theta^{(z)}$ lies between those two extreme values.
-Finally, we assume that the number of distinctive couples $C_i$ are a sequence of independent and identically distributed random variables following the discrete distribution $C$, and also independent from the other quantities.
-
-We estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding maximum likelihood estimator (MLE) $\hat{\theta}^{(z)}$.
-The likelihood function, along with the standard deviation expression and details about the test, can be found in~\nameref{sectionSI}.
-The fitted values, standard errors and p-values corresponding to the statistical test $\theta^{(sem)} = \theta^{(tec)}$ (with corresponding alternative hypothesis $\theta^{(sem)} > \theta^{(tec)}$) on non-overlapping blocks from the period 1980-2007\footnote{Note that the estimation included patents up until 2010 in the period 2006-2007 and not the patents from 1980 in the period 1980-1985 for homogeneity in size with other periods.
-This doesn't affect the significativity of the results.} are reported on Table \ref{summary}.
-Semantic values are reported for four different chosen thresholds $p^{-}=.04, .06, .08, .1$.
-It means that we restricted to the couples ($i$th patent, $j$th class) such that $p_{ij} \geq p^{-}$.
-
-The choice of considering non-overlapping blocks (instead of overlapping blocks) is merely statistical.
-Ultimately, our interest is in the significance of the test over the whole period 1980-2007.
-Thus, we want to compute a global p-value.
-This can be done considering the local p-values (by local, we mean for instance computed on the period 2001-2005) assuming independence between them.
-This assumption is reasonable only if the blocks are non-overlapping.
-All of this can be found in~\nameref{sectionSI}.
-Finally, note that from a statistical perspective, including overlapping blocks wouldn't yield more information.
-
-The values reported in Table \ref{summary} are overwhelmingly against the null hypothesis.
-The global estimates of $\theta^{(sem)}$ are significantly bigger than the estimate of $\theta^{(tec)}$ for all the considered thresholds.
-Although the corresponding p-values (which are also very close to 0) are not reported, it is also quite clear that the bigger the threshold, the higher the corresponding $\theta^{(sem)}$ is estimated.
-This is consistently seen for any period, and significant for the global period.
-This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propension to cite patents from its own class $\theta^{(sem)}$ is increasing.
-We believe that this might provide extra information to patent officers when making their choice of citations.
-Indeed, they could look first to patents which belong to the same semantic class, especially when patents have high probability semantic values.
-
-Note that the introduced model can be seen as a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g.
-\cite{decelle2011asymptotic}, \cite{valles2016multilayer}).
-The parameters are estimated computing the corresponding MLE.
-In view of~\cite{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.
-
-\begin{table}[!ht]
-\centering
-\caption{\label{summary} Estimated values of $\theta^{(tec)}$ and $\theta^{(sem)}$ and corresponding standard errors obtained from a Maximum Likelihood estimator as presented in section \ref{statisticalmodel}.}
-\label{stdQMLE}
-\begin{tabular}{@{}rccccccccc@{}}
-\toprule
-\toprule
-\multicolumn{1}{l}{Approach} & \multicolumn{1}{l}{Estimated Value} & \multicolumn{1}{l}{st. er.} & \multicolumn{1}{l}{p-value} \\ \toprule
-\multicolumn{4}{l}{1980-1985 period} \\
-technological & .664 &.008&\\
-semantic $p^{-} = .04$ & .741 &.047 & .053\\
-semantic $p^{-} = .06$ & .799 &.081 & .049\\
-semantic $p^{-} = .08$ & .828 &.126 & .097\\
-semantic $p^{-} = .10$ & .834 &.166 & .153\\
-\multicolumn{4}{l}{1986-1990 period} \\
-technological & .634 &.007&\\
-semantic $p^{-} = .04$ & .703 &.022 & .001\\
-semantic $p^{-} = .06$ & .768 &.040 & .0004\\
-semantic $p^{-} = .08$ & .804 &.069 & .007\\
-semantic $p^{-} = .10$ & .832 &.114 & .041\\
-\multicolumn{4}{l}{1991-1995 period} \\
-technological & .619 &.006&\\
-semantic $p^{-} = .04$ & .655 &.009 & .0004\\
-semantic $p^{-} = .06$ & .713 &.017 & 9e-08\\
-semantic $p^{-} = .08$ & .731 &.025 & 7e-06\\
-semantic $p^{-} = .10$ & .750 &.037 & 9e-06\\
-\multicolumn{4}{l}{1996-2000 period} \\
-technological & .551 &.003&\\
-semantic $p^{-} = .04$ & .585 &.002 & $\approx 0$\\
-semantic $p^{-} = .06$ & .638 &.004 & $\approx 0$\\
-semantic $p^{-} = .08$ & .660 &.006 & $\approx 0$\\
-semantic $p^{-} = .10$ & .686 &.008 & $\approx 0$\\
-\multicolumn{4}{l}{2001-2005 period} \\
-technological & .567 &.003&\\
-semantic $p^{-} = .04$ & .621 &.004 & $\approx 0$\\
-semantic $p^{-} = .06$ & .676 &.007 & $\approx 0$\\
-semantic $p^{-} = .08$ & .701 &.010 & $\approx 0$\\
-semantic $p^{-} = .10$ & .710 &.013 & $\approx 0$\\
-\multicolumn{4}{l}{2006-2007 period} \\
-technological & .600 &.007&\\
-semantic $p^{-} = .04$ & .683 &.016 & 1e-06\\
-semantic $p^{-} = .06$ & .732 &.025 & 2e-07\\
-semantic $p^{-} = .08$ & .760 &.036 & 6e-06\\
-semantic $p^{-} = .10$ & .782 &.048 &9e-05\\
-\multicolumn{4}{l}{1980-2007 global period} \\
-technological & .606 &.002&\\
-semantic $p^{-} = .04$ & .665 &.009 & 8e-11\\
-semantic $p^{-} = .06$ & .721 &.017 & 9e-12\\
-semantic $p^{-} = .08$ & .747 &.025 & 9e-09\\
-semantic $p^{-} = .10$ & .782 &.035 & 3e-07\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion \label{discussion}}
-%%%%%%%%%%%%%%%%%%%%%
-
-The main contribution of this study was twofold.
-First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts.
-We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...).
-The availability of these data suggests new avenues for further research.
-
-A first potential application is to use the patents' topological measures inherited from their relevant keywords.
-The fact that these measures are backward-looking and immediately available after the publication of the patent information is an important asset.
-It would for example be very interesting to test their predicting power to assess the quality of an innovation, using the number of forward citations received by a patent, and subsequently the future effect on the firm's market value.
-
-Regarding firm innovative strategy, a second extension could be to study trajectories of firms in the two networks: technological and semantic.
-Merging these information with data on the market value of firms can give a lot of insight about the more efficient innovative strategies, about the importance of technology convergence or about acquisition of small innovative firms.
-It will also allow to observe innovation pattern over a firm life cycle and how this differ across technology field.
-
-A third extension would be to use dig further into the history of innovation.
-USPTO patent data have been digitized from the first patent in July 1790.
-However, not all of them contain a text that is directly exploitable.
-We consider that the quality of patent's images is good enough to rely on Optical Character Recognition techniques to retrieve plain text from at least 1920.
-With such data, we would be able to extend our analysis further back in time and to study how technological progress occurs and combines in time.
-\cite{akcigit2013mechanics} conduct a similar work by looking at recombination and apparition of technological subclasses.
-Using the fact that communities are constructed yearly, one can construct a measure of proximity between two successive classes.
-This could give clear view on how technologies converged over the year and when others became obsolete and replaced by new methods.
-
-%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supporting Information \label{sectionSI}}
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-
-\subsection*{S1 Text : Definition of utility patent}
-
-\textbf{Describes with more details the definition of patents and  context.}
-
-\subsection*{S2 Text : Data collection procedure}
-
-\textbf{Detailed description of data collection}
-
-\subsection*{S3 File : Semantic Network Visualization}
-
-\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}
-
-\subsection*{S4 Text : Network Sensitivity Analysis\label{app:sensitivity}}
-
-\textbf{Extended figures for Network Sensitivity Analysis}
-
-\subsection*{S5 Text : Statistical definitions and derivations}
-
-\textbf{Extended definitions and derivations for the statistical model}
-
-%%%%%%%%%%%%%%%%%%%%%
-%\section*{Acknowledgments}
-
-%\nolinenumbers
-
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-%\bibliographystyle{plos2015}
-%\bibliography{patents}
-
-\begin{thebibliography}{10}
-
-\bibitem{aghionhowitt1992}
-Aghion P, Howitt P.
-\newblock {A Model of Growth through Creative Destruction}.
-\newblock Econometrica. 1992 March;60(2):323--51.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v60y1992i2p323-51.html}.
-
-\bibitem{romer1990}
-Romer PM.
-\newblock {Endogenous Technological Change}.
-\newblock Journal of Political Economy. 1990 October;98(5):S71--102.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ucp/jpolec/v98y1990i5ps71-102.html}.
-
-\bibitem{RePEc:nbr:nberwo:3301}
-Griliches Z.
-\newblock {Patent Statistics as Economic Indicators: A Survey}.
-\newblock National Bureau of Economic Research, Inc; 1990. 3301.
-\newblock Available from: \url{https://ideas.repec.org/p/nbr/nberwo/3301.html}.
-
-\bibitem{Hall2001}
-Hall BH, Jaffe AB, Trajtenberg M.
-\newblock {The NBER Patent Citations Data File: Lessons, Insights and
-  Methodological Tools}.
-\newblock C.E.P.R. Discussion Papers; 2001. 3094.
-\newblock Available from: \url{https://ideas.repec.org/p/cpr/ceprdp/3094.html}.
-
-\bibitem{Youn:2015fk}
-Youn H, Strumsky D, Bettencourt LMA, Lobo J.
-\newblock Invention as a combinatorial process: evidence from US patents.
-\newblock Journal of The Royal Society Interface. 2015;12(106).
-
-\bibitem{2013arXiv1310.8220N}
-{Newman} MEJ.
-\newblock {Prediction of highly cited papers}.
-\newblock ArXiv e-prints. 2013 Oct;.
-
-\bibitem{2014arXiv1402.7268S}
-{Sarig{\"o}l} E, {Pfitzner} R, {Scholtes} I, {Garas} A, {Schweitzer} F.
-\newblock {Predicting Scientific Success Based on Coauthorship Networks}.
-\newblock ArXiv e-prints. 2014 Feb;.
-
-\bibitem{sorenson2006complexity}
-Sorenson O, Rivkin JW, Fleming L.
-\newblock Complexity, networks and knowledge flow.
-\newblock Research policy. 2006;35(7):994--1017.
-
-\bibitem{kay2014patent}
-Kay L, Newman N, Youtie J, Porter AL, Rafols I.
-\newblock Patent overlay mapping: Visualizing technological distance.
-\newblock Journal of the Association for Information Science and Technology.
-  2014;65(12):2432--2443.
-
-\bibitem{bruck2016recognition}
-Bruck P, R{\'e}thy I, Szente J, Tobochnik J, {\'E}rdi P.
-\newblock Recognition of emerging technology trends: class-selective study of
-  citations in the US Patent Citation Network.
-\newblock Scientometrics. 2016;107(3):1465--1475.
-
-\bibitem{curran2011patent}
-Curran CS, Leker J.
-\newblock Patent indicators for monitoring convergence--examples from NFF and
-  ICT.
-\newblock Technological Forecasting and Social Change. 2011;78(2):256--273.
-
-\bibitem{Katz1996remarks}
-Katz ML.
-\newblock Remarks on the economic implications of convergence.
-\newblock Industrial and Corporate Change. 1996;5(4):1079--1095.
-
-\bibitem{Furman2011shoulders}
-Furman JL, Stern S.
-\newblock Climbing atop the Shoulders of Giants: The Impact of Institutions on
-  Cumulative Research.
-\newblock American Economic Review. 2011 August;101(5):1933--63.
-\newblock Available from:
-  \url{http://www.aeaweb.org/articles?id=10.1257/aer.101.5.1933}.
-
-\bibitem{AAKnetwork2016}
-Acemoglu AU Daron, Kerr W.
-\newblock {Innovation Network}.
-\newblock Proceedings of the National Academy of Sciences (forthcoming). 2016;.
-
-\bibitem{preschitschek2013}
-Preschitschek N, Niemann H, Leker J, Moehrle MG.
-\newblock Anticipating industry convergence: Semantic analyses vs IPC
-  co-classification analyses of patents.
-\newblock Foresight. 2013 11;15(6):446--464.
-
-\bibitem{yoon2004text}
-Yoon B, Park Y.
-\newblock A text-mining-based patent network: Analytical tool for
-  high-technology trend.
-\newblock The Journal of High Technology Management Research.
-  2004;15(1):37--50.
-
-\bibitem{park2014semantic}
-Park I, Yoon B.
-\newblock A semantic analysis approach for identifying patent infringement
-  based on a product--patent map.
-\newblock Technology Analysis \& Strategic Management. 2014;26(8):855--874.
-
-\bibitem{yoon2011detecting}
-Yoon J, Kim K.
-\newblock Detecting signals of new technological opportunities using semantic
-  patent analysis and outlier detection.
-\newblock Scientometrics. 2011;90(2):445--461.
-
-\bibitem{gerken2012new}
-Gerken JM, Moehrle MG.
-\newblock A new instrument for technology monitoring: novelty in patents
-  measured by semantic patent analysis.
-\newblock Scientometrics. 2012;91(3):645--670.
-
-\bibitem{choi2014patent}
-Choi J, Hwang YS.
-\newblock Patent keyword network analysis for improving technology development
-  efficiency.
-\newblock Technological Forecasting and Social Change. 2014;83:170--182.
-
-\bibitem{fattori2003text}
-Fattori M, Pedrazzi G, Turra R.
-\newblock Text mining applied to patent mapping: a practical business case.
-\newblock World Patent Information. 2003;25(4):335--342.
-
-\bibitem{2015arXiv151003797G}
-{Gurciullo} S, {Smallegan} M, {Pereda} M, {Battiston} F, {Patania} A, {Poledna}
-  S, et~al.
-\newblock {Complex Politics: A Quantitative Semantic and Topological Analysis
-  of UK House of Commons Debates}.
-\newblock ArXiv e-prints. 2015 Oct;.
-
-\bibitem{lerner2015use}
-Lerner J, Seru A.
-\newblock The use and misuse of patent data: Issues for corporate finance and
-  beyond.
-\newblock Booth/Harvard Business School Working Paper. 2015;.
-
-\bibitem{oecdpatentmanual}
-OECD.
-\newblock OECD Patent Statistics Manual. 2009;Available from:
-  \url{/content/book/9789264056442-en}.
-
-\bibitem{martin2015}
-Dechezlepretre A, Martin R, Mohnen M.
-\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
-\newblock Centre for Economic Performance, LSE; 2014. dp1300.
-\newblock Available from:
-  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.
-
-\bibitem{tseng2007text}
-Tseng YH, Lin CJ, Lin YI.
-\newblock Text mining techniques for patent analysis.
-\newblock Information Processing \& Management. 2007;43(5):1216--1247.
-
-\bibitem{Adams2010text}
-Adams S.
-\newblock {The text, the full text and nothing but the text: Part 1 - Standards
-  for creating textual information in patent documents and general search
-  implications}.
-\newblock World Patent Information. 2010 March;32(1):22--29.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/eee/worpat/v32y2010i1p22-29.html}.
-
-\bibitem{abbas2014literature}
-Abbas A, Zhang L, Khan SU.
-\newblock A literature review on the state-of-the-art in patent analysis.
-\newblock World Patent Information. 2014;37:3--13.
-
-\bibitem{chavalarias2013phylomemetic}
-Chavalarias D, Cointet JP.
-\newblock Phylomemetic patterns in science evolution---the rise and fall of
-  scientific fields.
-\newblock Plos One. 2013;8(2):e54847.
-
-\bibitem{nltk}
-NLTK. Natural Language Toolkit, Stanford University; 2015.
-
-\bibitem{clauset2004finding}
-Clauset A, Newman ME, Moore C.
-\newblock Finding community structure in very large networks.
-\newblock Physical review E. 2004;70(6):066111.
-
-\bibitem{yang2000improving}
-Yang Y, Ault T, Pierce T, Lattimer CW.
-\newblock Improving text categorization methods for event tracking.
-\newblock In: Proceedings of the 23rd annual international ACM SIGIR conference
-  on Research and development in information retrieval. ACM; 2000. p. 65--72.
-
-\bibitem{blei2003latent}
-Blei DM, Ng AY, Jordan MI.
-\newblock Latent dirichlet allocation.
-\newblock Journal of machine Learning research. 2003;3(Jan):993--1022.
-
-\bibitem{kaplan2015double}
-Kaplan S, Vakili K.
-\newblock The double-edged sword of recombination in breakthrough innovation.
-\newblock Strategic Management Journal. 2015;36(10):1435--1457.
-
-\bibitem{iacovacci2015mesoscopic}
-Iacovacci J, Wu Z, Bianconi G.
-\newblock Mesoscopic Structures Reveal the Network Between the Layers of
-  Multiplex Datasets.
-\newblock arXiv preprint arXiv:150503824. 2015;.
-
-\bibitem{de2015ranking}
-De~Domenico M, Sol{\'e}-Ribalta A, Omodei E, G{\'o}mez S, Arenas A.
-\newblock Ranking in interconnected multilayer networks reveals versatile
-  nodes.
-\newblock Nature communications. 2015;6.
-
-\bibitem{ARCHIBUGI199279}
-Archibugi D, Pianta M.
-\newblock Specialization and size of technological activities in industrial
-  countries: The analysis of patent data.
-\newblock Research Policy. 1992;21(1):79 -- 93.
-\newblock Available from:
-  \url{http://www.sciencedirect.com/science/article/pii/0048733392900283}.
-
-\bibitem{Bloom2005distance}
-Bloom N, Schankerman M, Reenen JV.
-\newblock {Identifying Technology Spillovers and Product Market Rivalry}.
-\newblock Econometrica. 2013 07;81(4):1347--1393.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v81y2013i4p1347-1393.html}.
-
-\bibitem{ziman2003technological}
-Ziman J.
-\newblock Technological innovation as an evolutionary process.
-\newblock Cambridge University Press; 2003.
-
-\bibitem{holland2012signals}
-Holland JH.
-\newblock Signals and boundaries: Building blocks for complex adaptive systems.
-\newblock Mit Press; 2012.
-
-\bibitem{nicosia2009extending}
-Nicosia V, Mangioni G, Carchiolo V, Malgeri M.
-\newblock Extending the definition of modularity to directed graphs with
-  overlapping communities.
-\newblock Journal of Statistical Mechanics: Theory and Experiment.
-  2009;2009(03):P03024.
-
-\bibitem{decelle2011asymptotic}
-Decelle A, Krzakala F, Moore C, Zdeborov{\'a} L.
-\newblock Asymptotic analysis of the stochastic block model for modular
-  networks and its algorithmic applications.
-\newblock Physical Review E. 2011;84(6):066106.
-
-\bibitem{valles2016multilayer}
-Valles-Catala T, Massucci FA, Guimera R, Sales-Pardo M.
-\newblock Multilayer stochastic block models reveal the multilayer structure of
-  complex networks.
-\newblock Physical Review X. 2016;6(1):011036.
-
-\bibitem{2016arXiv160602319N}
-{Newman} MEJ.
-\newblock {Community detection in networks: Modularity optimization and maximum
-  likelihood are equivalent}.
-\newblock ArXiv e-prints. 2016 Jun;.
-
-\bibitem{akcigit2013mechanics}
-Akcigit U, Kerr WR, Nicholas T.
-\newblock The Mechanics of Endogenous Innovation and Growth: Evidence from
-  Historical US Patents.
-\newblock Citeseer; 2013.
-
-\bibitem{regibeau2010}
-R{\'e}gibeau P, Rockett K.
-\newblock Innovation cycles and learning at the patent office: does the early
-  patent get the delay?
-\newblock Journal of Industrial Economics. 2010;58(2):222--246.
-\newblock Available from:
-  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
-
-\end{thebibliography}
-
-\newpage
+%\section*{Supporting Information \label{sectionSI}}
 
@@
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}
+ %\vspace{1cm}
+%\centering
+%\frame{
+%\includegraphics[scale=0.8]{figures/cit_lag.png}
+%}
+%\caption{Number of citations per lag in year}
+% \label{fig1}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section*{S2 Text : Data collection and Workflow}
+\begin{thebibliography}{10}
 
-\label{supp:data}
+\bibitem{regibeau2010}
+R{\'e}gibeau P, Rockett K.
+\newblock Innovation cycles and learning at the patent office: does the early
+  patent get the delay?
+\newblock Journal of Industrial Economics. 2010;58(2):222--246.
+\newblock Available from:
+  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
 
-\subsubsection*{Data Collection Procedure}
-
-Raw version of USPTO redbook with abstracts are available for years 1976-2014 starting from bulk download page at \url{https://bulkdata.uspto.gov/}.
-A script first automatically downloads files.
-Before being automatically processed, a few error in files (corresponding to missing end of records probably due to line dropping during the concatenation of weekly files) had to be corrected manually.
-Files are then processed with the following filters transforming different format and xml schemes into a uniform dictionary data structure :
-
-\begin{itemize}
-\item \texttt{dat} files (1976-2000): handmade parser
-\item \texttt{xml} files (2001-2012): xml parser, used with different schemas definitions.
-\end{itemize}
-
-Everything is stored into a MongoDB database, which latest dump is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % anonymize the db for submission
-
-\subsubsection*{Processing Workflow}
-
-The source code for the full workflow is available at \url{https://github.com/JusteRaimbault/PatentsMining}.
-A simplified shell wrapper is at \texttt{Models/fullpipe.sh}.
-Note that keywords co-occurrence estimation requires a memory amount in $O(N^2)$ (although optimized using dictionaries) and the operation on the full database requires a consequent infrastructure.
-Launch specifications are the following :
-
-\paragraph{Setup}
-
-Install the database and required packages.
-
-\begin{itemize}
-\item Having a running local mongod instance
-\item mongo host, port, user and password to be configured in \texttt{conf/parameters.csv}
-\item raw data import from gz file : use mongorestore -d redbook -c raw --gzip {\$}FILE
-\item specific python packages required : pymongo, python-igraph, nltk (with resources punkt, averaged{\_}perceptron{\_}tagger,porter{\_}test)
-\end{itemize}
-
-\paragraph{Running}
-
-The utility fullpipe.sh launches the successive stages of the processing pipe.
-
-\paragraph{Options}
-
-\textit{this configuration options can be changed in }\texttt{conf/parameters.csv}
-
-\begin{itemize}
-\item window size in years
-\item beginning of first window
-\item beginning of last window
-\item number of parallel runs
-\item \texttt{kwLimit} : total number of keywords $K_W$
-\item \texttt{edge{\_}th} : $\theta_w$ pre-filtering for memory storage purposes
-\item \texttt{dispth} : $\theta_c$
-\item \texttt{ethunit} : $\theta_w^{(0)}$
-\end{itemize}
-
-\paragraph{Tasks}
-
-The tasks to be done in order : keywords extraction, relevance estimation, network construction, semantic probas construction, are launched with the following options :
-%!! keywords and kw-consolidation tested with python3 ; rest with python2 (igraph compatibility issues)
-
-\begin{enumerate}
-\item \texttt{keywords} : extracts keywords
-\item \texttt{kw-consolidation} : consolidate keywords database (techno disp measure)
-\item \texttt{raw-network} : estimates relevance, constructs raw network and perform sensitivity analysis
-\item \texttt{classification} : classify and compute patent probability, keyword measures and patent measures ; here parameters $(\theta_w,\theta_c)$ can be changed in configuration file.
-\end{enumerate}
-
-\paragraph{Classification Data}
-
-The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
-Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window.
-The format are the following :
-
-\begin{itemize}
-\item Keywords files : keyword ; community ; termhood times inverse document frequency ; technological concentration ; document frequency ; termhood ; degree ; weighted degree ; betweenness centrality ; closeness centrality ; eigenvector centrality
-\item Patents measures : patent id ; total number of potential keywords ; number of classified keywords ; same topological measures as for keywords
-\item Patent probabilities : patent id ; total number of potential keywords ; id of the semantic class ; number of keywords in this class.
-Probabilities have to be reconstructed by extracting all the lines corresponding to a patent and dividing each count by the total number of classified keywords.
-\end{itemize}
-
-\paragraph{Analysis}
-
-The results of classification has to be processed for analysis (construction of sparse matrices for efficiency e.g.), following the steps:
-\begin{itemize}
-\item from classification files to R variables with \texttt{Semantic/semanalfun.R}
-\item from csv technological classes to R-formatted sparse Matrix with \texttt{Techno/prepareData.R} 
-\item from csv citation file to citation network in R-formatted graph and adjacency sparse matrix with \texttt{Citation/constructNW.R}
-\end{itemize}
-
-Analyses are done in \texttt{Semantic/semanalysis.R}.
-
-\newpage
-
-\section*{S4 Text : Network Sensitivity Analysis \label{app:sensitivity}}
-
-\subsubsection*{Network Sensitivity}
-
-The example of Fig.1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Fig.~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.
-We also show an other point of view over the Pareto optimization, that is the third plot giving the values of normalized objectives as a function of $\theta_c$.
-
-% Figures :
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
-\caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
-\label{fig:ext-sensitivity-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
-\caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
-\label{fig:ext-sensitivity-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
-\caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
-\label{fig:ext-sensitivity-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Time-window size sensitivity}
-
-% put some graphs for 3-years time window : same qualitative properties but a bit more noisy
-
-We show in Fig.~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$.
-The same qualitative behavior is observed (with different quantitative values, as typically $\theta_w^{(0)}$ is for example expected to vary with document number and semantic regime, thus with window size), what confirms that the method is valid across different time windows.
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
-\caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
-\label{fig:sensitivity-window3-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
-\caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
-\label{fig:sensitivity-window3-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
-\caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
-\label{fig:sensitivity-window3-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-\section*{S5 Text : Statistical definitions and derivations}
-\subsubsection*{Likelihood expression}
-We define $\mathcal{F}_i$ the filtration which corresponds to the time $t_i$.
-With this notation $\mathcal{L}( X | \mathcal{F}_{i-1})$ simply means the likelihood of $X$ conditioned on the past.
-We consider $\widehat{\theta}^{(z)}$ the MLE\footnote{Apparently, this MLE is a partial MLE, but we will not refer to partial for simplicity.} of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
-\begin{eqnarray*}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} \log \mathcal{L} \big( B_{l,i} | \mathcal{F}_{i-1} \big).
-\end{eqnarray*}
-Recalling that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables 
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-the log-likelihood of the model can be expressed as 
-\begin{eqnarray}
-\label{loglik}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} B_{l,i} \log \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big) +(1 - B_{l,i}) \log \Big(1 - \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big).
-\end{eqnarray}
-In practice, the user can easily implement the formula (\ref{loglik}) for any $0 \leq \theta^{(z)} \leq 1$, and maximize it over a predefined grid to obtain $\widehat{\theta}^{(z)}$.
-
-\subsubsection*{Standard errors of the estimated values}
-Under some assumptions, it is possible to show the asymptotic normality of $\widehat{\theta}^{(z)}$ and to compute the asymptotic variance.
-For simplicity of exposition, we assume that we restrict to $\theta^{(z)}$ such that we have $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} < 1$ for any $i=2, \cdots, Z$.
-The central limit theorem can be expressed as
-\begin{eqnarray}
-\label{variance}
-\sqrt{Z \mathbb{E} [ C ]} (\widehat{\theta}^{(z)} - \theta^{(z)}) \overset{\mathcal{L}}{\rightarrow} MN \Big( 0, \int (p + \theta^{(z)})(1 - (p + \theta^{(z)})) d\pi^{(z)} (p) \Big),
-\end{eqnarray}
-where MN stands for a multinormal distribution and $\pi^{(z)}$ for the asymptotic limit distribution of the quantity $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)}$.
-Note that the variance term in (\ref{variance}) is equal to an aggregate version of the Fisher information matrix.
-The proof of such statement is beyond the scope of this paper.
-On the basis of (\ref{variance}), we provide a variance estimator as
-$$v^{(z)} = \frac{1}{C_k-1}\sum_{i=2}^{C_k}  \frac{N_{i_k}^{(z)}}{i-1} + \widehat{\theta}^{(z)},$$ 
-where $i_k$ is such that the $i_k$th patent corresponds to the $k$th couple. This estimator was used to compute the standard deviation in Table \ref{summary}.
-\subsubsection*{Test statistic}
-The test statistic used is a mean difference test statistic between $\widehat{\theta}^{(tec)}$ and  $\widehat{\theta}^{(sem)}$, where the formal expression can be found in (\ref{teststat}).
-We assume independence between both quantities and thus under the null hypothesis, we have that
-$$\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)} {\rightarrow} MN(0,V),$$
-where $V= \int (p + \theta^{(tec)})(1 - (p + \theta^{(tec)})) d\pi^{(tec)} (p) + \int (p + \theta^{(sem)})(1 - (p + \theta^{(sem)})) d\pi^{(sem)} (p)$ can be estimated by $\widehat{V} = v^{(sem)} + v^{(tec)}$.
-Then, we obtain that
-\begin{eqnarray}
-\label{teststat}
-A = \frac{\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)}}{\widehat{V}} \approx \mathcal{N} (0,1),
-\end{eqnarray}
-where $A$ is the mean difference test static.
-
-%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Information
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S1 Text : Definition of utility patent}
-
-%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%\section*{S2 Text : Data collection and Workflow}
-
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S4 Text : Network Sensitivity Analysis}
-
-%%%%%%%%%%%%%%%%%%%%
-%\bigskip
-%\bigskip
-%\newpage
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\subsection*{Additional plots}
-%
-%% plots that have some info but not included in paper
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!ht]
-%% figure : interlayer overlap
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_density_semcounts.png}
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_ts_semcounts.png}\\
-%\caption{Inter-classification effective overlaps (normalized by patent count)}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-
-%%%%%%%%%%%%%%%%%%%%%%
-%% Junk
-%%%%%%%%%%%%%%%%%%%%%%
-
-%Data-mining and network analysis~\cite{newman2010networks} can bring different insights.
-As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
-in the recent analysis on 20\textsuperscript{th} century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation necessarily involves complex patterns which understanding must have positive feedback on the economy.\par
-
-%%%%%%%%%%%%%%%%%%%%
-%%  Templates
-%%%%%%%%%%%%%%%%%%%%
-
-% For figure citations, please use "Fig." instead of "Figure".
-%\begin{figure}[h]
-%\caption{{\bf Figure Title first bold sentence}
-%Figure Caption}
-%\label{fig1}
-%\end{figure}
-
-%
-%
-%
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-%
-%
-
-%
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-
-%\begin{thebibliography}{10}
-%\bibitem{bib1}
-%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS.
-Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes.
-Mol Immunol.
-2014 Nov 22.
-pii: S0161-5890(14)00313-7.
-doi: 10.1016/j.molimm.2014.11.005
-
-%\bibitem{bib2}
-%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
-
-%\end{thebibliography}
+\end{thebibliography}
 
 \end{document}
-
-\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
-
-A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics.
-Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
-\[
-\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
-\]
-It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields.
-We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
-\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}
-
-% eventually do stats on merging/splitting : distribution of kws overlaps in time ?
-
-\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time.
-Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
-\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes.
-\comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
-\label{fig:semanticflows}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-10 Docs/Papers/Technical/overleafv2/S4_Text.tex
slides_seminar

--- 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
@@
-\documentclass[12pt,twoside,a4paper]{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{eurosym}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage[section]{placeins}
-\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
-\usepackage{setspace}
-\usepackage{rotating}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{etoolbox}
-\usepackage{amsmath,amssymb}
-\usepackage{float}
-\usepackage{xcolor}
-\usepackage{hyperref}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{enumitem}
-\usepackage{caption}
-\usepackage{nameref}
-\usepackage{lscape}
-\usepackage{fancyhdr}
-
-\setcounter{MaxMatrixCols}{10}
-\hypersetup{
-    colorlinks, linkcolor={dark-red},
-    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
-}
-\geometry{hmargin=4cm,vmargin=4cm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{assumption}{Assumption}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-\setcounter{secnumdepth}{5}
-\textwidth 6.0in
-\textheight 8.84in 
-\setlength{\topmargin}{-0.3in}
-\setlength{\oddsidemargin}{0.0in}
-\setlength{\evensidemargin}{0.0in}
-\setlength{\abovecaptionskip}{0pt}
-\setlength{\belowcaptionskip}{5pt}
-\setlength{\textfloatsep}{25pt}  
-\setlength{\intextsep}{5pt}   
-\fancyhf{}
-\pagestyle{fancy}
-\renewcommand{\headrulewidth}{1pt}
-\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
-\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
-\fancyfoot[C]{\thepage}
-
-\begin{document}
-
-\title{Classifying Patents Based on their Semantic Content\thanks{%
-Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
-Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
-\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
- \ \ \ \ \ Juste Raimbault \bigskip}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% Please keep the abstract below 300 words
-\begin{abstract}
-In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach.
-This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward.
-To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly.
-We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes.
-Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model.
-This suggests that our method is a useful tool to extract endogenous information.
-\end{abstract}
-
-\pagebreak
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}.
-\cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation.
-Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis.
-Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review.
-Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}.
-With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters.
-Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.
-
-Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies.
-But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share.
-Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g.
-~\cite{AAKnetwork2016}).
-
-In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it.
-In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract.
-Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach.
-The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence).
-One can for instance consider the case of the word \textit{optic}.
-Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic.
-This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.
-
-Previous research has already proposed to use semantic networks to study technological domains and detect novelty.
-~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain.
-The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}.
-More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation.
-Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).
-
-Building on such previous research, we make several contributions by fulfilling some shortcomings of existing studies, such as for example the use of frequency-selected single keywords.
-First of all, we develop and implement a novel fully-automatized methodology to classify patents according to their semantic abstract content, which is to the best of our knowledge the first of its type.
-This includes the following refinements for which details can be found in Section \ref{keywords}: (i) use of multi-stems as potential keywords; (ii) filtering of keywords based on a second-order (co-occurrences) relevance measure and on an external independent measure (technological dispersion); (iii) multi-objective optimization of semantic network modularity and size.
-The use of all this techniques in the context of semantic classification is new and essential from a practical perspective.
-
-Furthermore, most of the existing studies rely on a subsample of patent data, whereas we implement it on the full US Patent database from 1976 to 2013.
-This way, a general structure of technological innovation can be studied.
-We draw from this application promising qualitative stylized facts, such as a qualitative regime shift around the end of the 1990s, and a significant improvement of citation modularity for the semantic classification when comparing to the technological classification.
-These thematic conclusions validate our method as a useful tool to extract endogenous information, in a complementary way to the technological classification.
-
-Finally, the statistical model introduced in Section \ref{statisticalmodel} seems to indicate that patents tend to cite more similar patents in the semantic network  when fitted to data.
-In particular, this propensity is shown to be significantly bigger than the corresponding propensity for technological classes, and this seems to be consistent over time.
-On the account of this information, we believe that patent officers could benefit very much from looking at the semantic network when considering potential citation candidates of a patent in review.
-
-The paper is organized as follows.
-Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process.
-Section \ref{keywords} explains the construction of the semantic classes.
-Section \ref{result} tests their relevance by providing exploratory results.
-Finally, section \ref{discussion} discusses potential further developments and conclude.
-More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background \label{data}}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013.
-A clearer definition of utility patent is given in~\nameref{sectionSI}.
-Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{An existing classification: the USPC system}
-
-Each USPTO patent is associated with a non-empty set of technological classes and subclasses.
-There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system.
-While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention.
-A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass.
-At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes.
-When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A bibliographical network between patents: citations \label{sub:citation}}
-
-As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art.
-They therefore indicate the past knowledge which relates to the patented invention.
-Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent.
-One can consult~\cite{oecdpatentmanual} for more details about this.
-Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}).
-Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves.
-From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations).
-We can thus build a complete network of citations that we will use later on in the analysis.
-
-Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years.
-This distribution is highly skewed, the $95^{th}$ percentile is 21 years.
-We also report 164,000 citations with a negative time lag.
-This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others.
-
-In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years.
-We impose this restriction for two reasons.
-First, the number of citations received peaks 4-5 years after application.
-Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones.
-As we are restricting to citations received no later than 5 years after the application date, this effect will only affect patents with an application date after 2007.
-
-%%%%%%%%%%%%%%%%%%
-\subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
-Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
-In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}).
-The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).
-
-We construct from raw data a unified database.
-Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976.
-Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}.
-The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
-Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
-
-We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013.
-When distributed by the year of application, the picture is slightly different.
-The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007.
-Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents.
-These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}.
-Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window.
-270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations.
-A within class citation is defined as a citation between two patents sharing at least one common technological class.
-Following this definition, 84\% of the citations are within class citations.
-14\% of the citations are between two patents that share the exact same set of technological classes.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Towards a Complementary Classification}
-
-Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}.
-The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications.
-The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review).
-Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}.
-As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored.
-One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples.
-Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies.
-Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.
-
-Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}).
-Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Semantic Classification Construction \label{keywords}}
-
-In this section, we describe methods and empirical analysis leading to the construction of semantic network and the corresponding classification.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords extraction}
-\label{keywordsextraction}
-
-Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
-$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
-\begin{enumerate}
-\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).
-
-\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.
-
-\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens.
-At this point the abstract text is reduced to a set of stems and their grammatical functions.
-\item Multi-stems construction: these are the basic semantic units used in further analysis.
-They are constructed as groups of successive stems in a sentence which satisfies a simple grammatical function rule.
-The length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives.
-We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
-\end{enumerate}
-
-Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations.
-This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining}
-}
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords relevance estimation}
-\label{keywords_est}
-\paragraph{Relevance definition}
-
-Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
-We choose to set this parameter to $K_w = 100,000$.
-We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$.
-The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
-Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
-More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together.
-The \emph{termhood} score $t_i$ is defined as
-
-\[
-t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
-\]
-
-\paragraph{Moving window estimation}
-The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past.
-Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$.
-Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents.
-This way, we will obtain semantic classes which are exploitable on a $T_0$ time span.
-For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}.
-In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}.
-Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Construction of the semantic network}
-\label{construction}
-
-We keep the set of most relevant keywords $\mathcal{K}_W$ and obtain their co-occurrence matrix as defined in Section \ref{keywords_est}.
-This matrix can be directly interpreted as the weighted adjacency matrix of the semantic network.
-At this stage, the topology of raw networks does not allow the extraction of clear communities.
-This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g.
-\texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant.
-We therefore introduce an additional measure to correct the network topology: the concentration of keywords across technological classes, defined as:
-
-$$c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2},$$
-
-where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes.
-The higher $c_{tech}$, the more specific to a technological class the node is.
-For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$.
-In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
-To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
-Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
-At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward.
-Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities.
-We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-%\hspace{-2.5cm}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
-%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
-\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values.
-The maximum is roughly stable across $\theta_c$ (dashed red line).
-\textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
-\label{fig:networksensitivity}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{striking}
-%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
-\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
-The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
-\label{fig:rawnetwork}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Characteristics of Semantic Classes}
-\label{characteristics}
-For each year $t$, we define as $N^{(sem)}_t$ the number of semantic classes which have been computed by clustering keywords from patents appeared during the period $\big[ t-T_0, t \big]$ (we recall that we have chosen $T_0=4$).
-Each semantic class $k =  1, \cdots, N^{(sem)}_t$ is characterized by a set of keywords $K(k,t)$ which is a subset of $\mathcal{K}_W$ selected as described in Section \ref{keywordsextraction} to Section \ref{construction}.
-The cardinal of $K(k, t)$ distribution across each semantic class $k$ is highly skewed with a few semantic classes containing over $1,000$ keywords, most of them with roughly the same number of keywords.
-In contrast, there are also many semantic classes with only two keywords.
-There are around 30 keywords by semantic class on average and the median is 2 for any $t$.
-Fig.~\ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{meancomsize}
-%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
-\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
-\label{fig:mean_K}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph*{Title of semantic classes}
-USPC technological classes are defined by a title and a highly accurate definition which help retrieve patents easily.
-The title can be a single word (e.g.: class 101: ``Printing'') or more complex (e.g.: class 218: ``High-voltage switches with arc preventing or extinguishing devices'').
-As our goal is to release a comprehensive database in which each patent is associated with a set of semantic classes, it is necessary to give an insight on what these classes represent by associating a short description or a title as in~\cite{tseng2007text}.
-In our case, such description is taken as a subset of keywords taken from $K(k,t)$.
-For the vast majority of semantic classes that have less than 5 keywords, we decide to keep all of theses keywords as a description.
-For the remaining classes which feature around 50 keywords on average, we rely on the topological properties of the semantic network.~\cite{yang2000improving} suggest to retain only the most frequently used terms in $K(k,t)$.
-Another possibility is to select 5 keywords based on their network centrality with the idea that very central keywords are the best candidates to describe the overall idea captured by a community.
-For example, the largest semantic class in 2003-2007 is characterized by the keywords: \texttt{Support Packet; Tree Network; Network Wide; Voic Stream; Code Symbol Reader}.
-
-\paragraph*{Size of technological and semantic classes} 
-We consider a specific window of observations (for example 2000-2004), and we define $Z$ the number of patents which appeared during that time window.
-For each patent $i=1, \cdots, Z$ we associate a vector of probability where each component $p_{ij}^{(sem)} \in \big[ 0,1 \big]$, with  $j = 1, \cdots, N{(sem)}$ and where\footnote{When there is no room for confusion, we drop the subscript $t$ in $N_t^{(sem)}$.}
-$$\displaystyle \sum_{j=1}^{N^{(sem)}} p_{ij}^{(sem)} = 1.$$ On average across all time windows, a patent is associated to 1.8 semantic classes with a positive probability.
-Next we define the size of a semantic class as $$S_j^{(sem)} = \displaystyle \sum_{i=1}^Z p_{ij}^{(sem)}.$$
-Correspondingly, we aim to provide a consistent definition for technological classes.
-For that purpose, we follow the so-called ``fractional count'' method, which was introduced by the USPTO and consists in dividing equally the patents between all the classes they belong to.
-Formally, we define the number of technological classes as
-$N^{(tec)}$  (which is not time dependent contrary to the semantic case) and for $j = 1, \cdots, N^{(tec)}$ the corresponding matrix of probability is defined as
-\[
- p_{ij}^{(tec)} = \frac{B_{ij}}{\displaystyle \sum_{k=1}^{N^{(tec)}}{B_{ik}}},
-\]
-where  $B_{ij}$ equals $1$ if the $i$th patent belongs to the $j$th technological class and $0$ if not.
-When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix.
-Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Fig.~\ref{fig:class-sizes}.
-This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
-\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$,
-from the biggest to the smallest.
-The formal definition of size can be found in Section \ref{characteristics}.
-Each color corresponds to one specific year.
-Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications.
-This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}.
-Over time, curves are translated and levels of hierarchy stays roughly constant.}
-\label{fig:class-sizes}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Potential Refinements of the Method}
-
-Our semantic classification method could be refined by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method (e.g.~\cite{blei2003latent}), already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a field rather than distant technological recombination.
-Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation).
-Also, depending on the level of orthogonality with our classification, it can potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.
-
-Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis.
-Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
-Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Results \label{result}}
-%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present some key features of our resulting semantic classification showing both complementary and differences with the technological classification.
-We first present several measures derived from this semantic classification at the patent level: Diversity, Originality, Generality (Section \ref{subsec:orig-gene}) and Overlapping (Section \ref{subsec:overlaps}).
-We then show that the two classifications show highly
-different topological measures and strong statistical evidence that they feature a different model (Sections \ref{citationmodularity} and \ref{statisticalmodel}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Patent Level Measures}  \label{subsec:orig-gene}
-
-Given a classification system (technological or semantic classes), and the associated probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ (that were defined in Section \ref{characteristics}), one can define a patent-level diversity measure as one minus the Herfindhal concentration index on $p_{ij}$  by
-
-\[
-D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}.
-\]
-
-We show in Fig.~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series.
-This is carried with two different settings, namely including/not including patents with zero diversity (i.e.
-single class patents).
-We call other patents ``complicated patents'' in the following.
-First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes.
-More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization.
-This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}.
-Furthermore, a qualitative regime shift on semantic classification occurs around 1996.
-This can be seen whether or not we include patents with zero diversity.
-The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease.
-This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity.
-It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents.
-
-More commonly used in the literature are the measures of originality and generality.
-These measures follow the same idea than the above-defined diversity in quantifying the diversity of classes (whether technological or semantic) associated with a patent.
-But instead of looking at the patent's classes, they consider the classes of the patents that are cited or citing.
-Formally, the originality $O_i$ and the generality $G_i$ of a patent $i$ are defined as
-\[
-O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2} \text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2},
-\]
-where $z \in \{tec, sem\}$, $I_i$ denotes the set of patents that are cited by the $i$th patent within a five year window (i.e.
-if the $i$th patent appears at year $t$, then we consider patents on $[t-T_0, t]$) when considering the originality and $\tilde{I}_i$ the set of patents that cite patent $i$ after less than five years (i.e.
-we consider patents on $[t ,t + T_0]$) in the case of generality.
-Note that the measure of generality is forward looking in the sense that $G_i^{(z)}$ used information that will only be available 5 years after patent applications.
-Both measures are lower on average based on semantic classification than on technological classification.
-Fig.
-\ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-%First row : semantic with relevant keywords only - all patents 
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
-%Second row : patents with diversity $> 0$ (more than one class)}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
-%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
-\caption{
-\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$).
-The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e.
-patents with diversity greater than 0).
-}
-\label{fig:patent-level-orig}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\includegraphics[width=0.49\textwidth]{originality.png}
-\includegraphics[width=0.49\textwidth]{generality.png}\\
-%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
-\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
-}
-\label{fig:orig-gene}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classes overlaps} \label{subsec:overlaps}
-
-A proximity measure between two classes can be defined by their overlap in terms of patents. 
-Such measures could for example be used to construct a metrics between semantic classes.
-Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{Bloom2005distance}.
-Formally, recalling the definition of $\left(p_{ij}\right)$ as the probability for the $i$th patent to belong to the $j$th class and $N_P$ as the number of patents it writes
-\begin{eqnarray}
-\label{overlap}
-Overlap_{jk} = \frac{1}{N_P}\cdot \sum_{i=1}^{N_P} p_{ij} p_{ik}. 
-\end{eqnarray}
-
-The overlap is normalized by patent count to account for the effect of corpus size: by convention, we assume the overlap to be maximal when there is only one class in the corpus.
-A corresponding relative overlap is computed as a set similarity measure in the number of patents common to two classes A and B, given by $o(A,B)=2\cdot \frac{\left|A\cap B\right|}{\left|A\right| + \left|B\right|}$.
-
-\paragraph{Intra-classification overlaps}
-
-The study of distributions of overlaps inside each classification, i.e.
-between technological classes and between semantic classes separately, reveals the structural difference between the two classification methods, suggesting their complementary nature.
-Their evolution in time can furthermore give insights into trends of specialization.
-We show in Fig.~\ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications.
-The technological classification globally always follow a decreasing trend, corresponding to more and more isolated classes, i.e.
-specialized inventions, confirming the stylized fact obtained in previous subsection.
-For semantic classes, the dynamic is somehow more intriguing and supports the story of a qualitative regime shift suggested before.
-Although globally decreasing as technological overlap, normalized (resp.
-relative) mean overlap exhibits a peak (clearer for normalized overlap) culminating in 1996 (resp.
-1999).
-Looking at normalized overlaps, classification structure was somewhat stable until 1990, then strongly increased to peak in 1996 and then decrease at a similar pace up to now.
-Technologies began to share more and more until a breakpoint when increasing isolation became the rule again.
-An evolutionary perspective on technological innovation~\cite{ziman2003technological} could shed light on possible interpretations of this regime shift: as species evolve, the fitness landscape first would have been locally favorable to cross-insemination, until each fitness reaches a threshold above which auto-specialization becomes the optimal path.
-It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation.
-%This interpretation is consistent with the dynamics of semantic flows presented in Fig.~\ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
-\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
-\caption{
-\textbf{Intra-classification overlaps.}
-\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
-\textit{(Right column)} Corresponding mean time-series.
-\textit{(First row)} Normalized overlaps.
-\textit{(Second row)} Relative overlaps.}
-\label{fig:intra-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Inter-classification overlaps}
-
-Overlaps \emph{between} classifications are defined as in (\ref{overlap}), but with $j$ standing for the $j$th technological class and $k$ for the $k$th semantic class: $p_{ij}$ are technological probabilities and $p_{ik}$ semantic probabilities.
-They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Fig.~\ref{fig:inter-classif-overlap}.
-Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease.
-Although difficult to interpret directly, this stylized fact clearly unveils a change in the \emph{nature} of inventions, or at least in the relation between content of inventions and technological classification.
-As the tipping point is at the same time as the ones observed in the previous section and since the two statistics are different, it is unlikely that this is a mere coincidence.
-Thus, these observations could be markers of a hidden underlying structural changes in processes.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
-\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series.
-The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
-\label{fig:inter-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Citation Modularity}
-\label{citationmodularity}
-
-An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}.
-The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\cite{AAKnetwork2016}).
-This section studies empirically modularities of the citation network regarding the different classifications.
-To corroborate the obtained results, we propose to look at a more rigorous framework in Section \ref{statisticalmodel}.
-Modularity is a simple measure of how communities in a network are well clustered (see \cite{clauset2004finding} for the accurate definition).
-Although initially designed for single-class classifications, this measure can be extended to the case where nodes can belong to several classes at the same time, in our case with different probabilities as introduced in \cite{nicosia2009extending}.
-The simple directed modularity is given in our case by
-\[
-Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
-\]
-with $A_{ij}$ the citation adjacency matrix (i.e.
-$A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not), $k_i^{in}=\left| I_i\right|$ (resp.
-$k_i^{out}= \left|\tilde{I}_i \right|$) in-degree (resp.
-out-degree) of patents (i.e.
-the number of citations made by the $i$th patent to others and the number of citations received by the $i$th patent).
-$Q_d$ can be defined for each of the two classification systems: $z \in \{tec, sem\}$.
-If $z=tec$, $c_i$ is defined as the main patent class, which is taken as the first class whereas if $z=sem$, $c_i$ is the class with the largest probability.
-
-Multi-class modularity in turns is given by
-
-\[
-\displaystyle Q_{ov}^{(z)} = \frac{1}{N_P} \sum_{c = 1}^{N^{(z)}} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,c}^{out}k_i^{out}\beta_{j,c}^{in}k_j^{in}}{N_P}\right],
-\]
-where
-\[
- \beta_{i,c}^{out} =   \frac{1}{N_P} \displaystyle \sum_j F(p_{ic},p_{jc}) \text{ and } \beta_{j,c}^{in} =  \frac{1}{N_P} \displaystyle \sum_i F(p_{ic},p_{jc}).
-\]
-We take $F(p_{ic},p_{jc}) = p_{ic}\cdot p_{jc}$ as suggested in \cite{nicosia2009extending}.
-Modularity is an aggregated measure of how the network deviates from a null model where links would be randomly made according to node degree.
-In other words it captures the propensity for links to be inside the classes.
-Overlapping modularity naturally extends simple modularity by taking into account the fact that nodes can belong simultaneously to many classes.
-We document in Fig.~\ref{fig:modularities} both simple and multi-class modularities over time.
-For simple modularity, $Q_d^{(tec)}$ is low and stable across the years whereas $Q_d^{(sem)}$ is slightly greater and increasing.
-These values are however low and suggest that single classes are not sufficient to capture citation homophily.
-Multi-class modularities tell a different story.
-First of all, both classification modularities have a clear increasing trend, meaning that they become more and more adequate with citation network.
-The specializations revealed by both patent level diversities and classes overlap is a candidate explanation for this growing modularities.
-Secondly, semantic modularity dominates technological modularity by an order of magnitude (e.g.
-0.0094 for technological against 0.0853 for semantic in 2007) at each time.
-This discrepancy has a strong qualitative significance.
-Our semantic classification fits better the citation network when using multiple classes.
-As technologies can be seen as a combination of different components as shown by~\cite{Youn:2015fk}, this heterogeneous nature is most likely better taken into account by our multi-class semantic classification.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.49\textwidth]{simplemodularity}
-\includegraphics[width=0.49\textwidth]{overlappingmodularity}
-%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
-\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability).
-(Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
-\label{fig:modularities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistical Model}
-\label{statisticalmodel}
-In this section, we develop a statistical model aimed at quantifying performance of both technological and semantic classification systems.
-In particular, we aim at corroborating findings obtained in Section \ref{citationmodularity}.
-The mere difference between this approach and the citation modularity approach lies in the choice of the underlying model, and the according quantities of interest.
-In addition for the semantic approach, we want to see if when restricting to patents with higher probabilities to belong to a class, we obtain better results.
-To do that, we choose to look at within class citations proportion (for both technological and semantic approaches).
-We provide two obvious reasons why we choose this.
-First, the citations are commonly used as a proxy for performance as mentioned in Section \ref{citationmodularity}.
-Second, this choice is ``statistically fair'' in the sense that both approaches have focused on various goals and not on maximizing directly the within class proportion.
-Nonetheless, the within class proportion is too sensitive to the distribution of the shape of classes.
-For example, a dataset where patents for each class account for 10\% of the total number of patents will mechanically have a better within class proportion than if each class accounts for only 1\%.
-Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed.
-This effort ressembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth.
-Furthermore, the parameters fitted here can have a direct interpretation as a citation probability.
-
-We need to introduce and recall some notations.
-We consider a specific window of observations $\big[t- T_0, t \big]$, and we define $Z$ the number of patents which appeared during that time window.
-We let $t_1, \cdots, t_Z$ their corresponding appearance date by chronological order, which for simplicity are assumed to be such that $t_1 < \cdots < t_Z$.
-For each patent $i=1, \cdots, Z$ we consider $C_i$ the number of distinctive couples \{cited patent, cited patent's class\} made by the $i$th patent (for instance if the $i$th patent has only made one citation and that the cited patent is associated with three classes, then $C_i = 3$).
-Let $z \in \{tec, sem\}$, we define $N_{i}^{(z)}$  the number of patents associated to at least one of the $i$th classes at time $t_{i-1}$.
-For $l = 1, \cdots, C_i$ we consider the variables $B_{l,i}$, which equal $1$ if the cited patent's class is also common to the $i$th patent.
-We assume that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-where the parameter $0 \leq \theta^{(z)} \leq 1$ indicates the propensity for any patent to cite patents of its own technological or semantic class.
-When $\theta^{(z)} = 0$, the probability of citing patents from its own class is simply $N_{i}^{(z)}(i-1)^{-1}$, which corresponds to the observed proportion of patents which belong to at least one of the $i$th patent's classes.
-Thus this corresponds to the estimated probability of citing one patent if we assume that the probability of citing any patent $k=1, \cdots, i-1$ is uniformly distributed, which could be a reasonable assumption if classes were assigned randomly and independently from patent abstract contents.
-Conversely if $\theta^{(z)} = 1$, we are in the case of a model where there are 100\% of within class citations.
-A reasonable choice of $\theta^{(z)}$ lies between those two extreme values.
-Finally, we assume that the number of distinctive couples $C_i$ are a sequence of independent and identically distributed random variables following the discrete distribution $C$, and also independent from the other quantities.
-
-We estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding maximum likelihood estimator (MLE) $\hat{\theta}^{(z)}$.
-The likelihood function, along with the standard deviation expression and details about the test, can be found in~\nameref{sectionSI}.
-The fitted values, standard errors and p-values corresponding to the statistical test $\theta^{(sem)} = \theta^{(tec)}$ (with corresponding alternative hypothesis $\theta^{(sem)} > \theta^{(tec)}$) on non-overlapping blocks from the period 1980-2007\footnote{Note that the estimation included patents up until 2010 in the period 2006-2007 and not the patents from 1980 in the period 1980-1985 for homogeneity in size with other periods.
-This doesn't affect the significativity of the results.} are reported on Table \ref{summary}.
-Semantic values are reported for four different chosen thresholds $p^{-}=.04, .06, .08, .1$.
-It means that we restricted to the couples ($i$th patent, $j$th class) such that $p_{ij} \geq p^{-}$.
-
-The choice of considering non-overlapping blocks (instead of overlapping blocks) is merely statistical.
-Ultimately, our interest is in the significance of the test over the whole period 1980-2007.
-Thus, we want to compute a global p-value.
-This can be done considering the local p-values (by local, we mean for instance computed on the period 2001-2005) assuming independence between them.
-This assumption is reasonable only if the blocks are non-overlapping.
-All of this can be found in~\nameref{sectionSI}.
-Finally, note that from a statistical perspective, including overlapping blocks wouldn't yield more information.
-
-The values reported in Table \ref{summary} are overwhelmingly against the null hypothesis.
-The global estimates of $\theta^{(sem)}$ are significantly bigger than the estimate of $\theta^{(tec)}$ for all the considered thresholds.
-Although the corresponding p-values (which are also very close to 0) are not reported, it is also quite clear that the bigger the threshold, the higher the corresponding $\theta^{(sem)}$ is estimated.
-This is consistently seen for any period, and significant for the global period.
-This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propension to cite patents from its own class $\theta^{(sem)}$ is increasing.
-We believe that this might provide extra information to patent officers when making their choice of citations.
-Indeed, they could look first to patents which belong to the same semantic class, especially when patents have high probability semantic values.
-
-Note that the introduced model can be seen as a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g.
-\cite{decelle2011asymptotic}, \cite{valles2016multilayer}).
-The parameters are estimated computing the corresponding MLE.
-In view of~\cite{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.
-
-\begin{table}[!ht]
-\centering
-\caption{\label{summary} Estimated values of $\theta^{(tec)}$ and $\theta^{(sem)}$ and corresponding standard errors obtained from a Maximum Likelihood estimator as presented in section \ref{statisticalmodel}.}
-\label{stdQMLE}
-\begin{tabular}{@{}rccccccccc@{}}
-\toprule
-\toprule
-\multicolumn{1}{l}{Approach} & \multicolumn{1}{l}{Estimated Value} & \multicolumn{1}{l}{st. er.} & \multicolumn{1}{l}{p-value} \\ \toprule
-\multicolumn{4}{l}{1980-1985 period} \\
-technological & .664 &.008&\\
-semantic $p^{-} = .04$ & .741 &.047 & .053\\
-semantic $p^{-} = .06$ & .799 &.081 & .049\\
-semantic $p^{-} = .08$ & .828 &.126 & .097\\
-semantic $p^{-} = .10$ & .834 &.166 & .153\\
-\multicolumn{4}{l}{1986-1990 period} \\
-technological & .634 &.007&\\
-semantic $p^{-} = .04$ & .703 &.022 & .001\\
-semantic $p^{-} = .06$ & .768 &.040 & .0004\\
-semantic $p^{-} = .08$ & .804 &.069 & .007\\
-semantic $p^{-} = .10$ & .832 &.114 & .041\\
-\multicolumn{4}{l}{1991-1995 period} \\
-technological & .619 &.006&\\
-semantic $p^{-} = .04$ & .655 &.009 & .0004\\
-semantic $p^{-} = .06$ & .713 &.017 & 9e-08\\
-semantic $p^{-} = .08$ & .731 &.025 & 7e-06\\
-semantic $p^{-} = .10$ & .750 &.037 & 9e-06\\
-\multicolumn{4}{l}{1996-2000 period} \\
-technological & .551 &.003&\\
-semantic $p^{-} = .04$ & .585 &.002 & $\approx 0$\\
-semantic $p^{-} = .06$ & .638 &.004 & $\approx 0$\\
-semantic $p^{-} = .08$ & .660 &.006 & $\approx 0$\\
-semantic $p^{-} = .10$ & .686 &.008 & $\approx 0$\\
-\multicolumn{4}{l}{2001-2005 period} \\
-technological & .567 &.003&\\
-semantic $p^{-} = .04$ & .621 &.004 & $\approx 0$\\
-semantic $p^{-} = .06$ & .676 &.007 & $\approx 0$\\
-semantic $p^{-} = .08$ & .701 &.010 & $\approx 0$\\
-semantic $p^{-} = .10$ & .710 &.013 & $\approx 0$\\
-\multicolumn{4}{l}{2006-2007 period} \\
-technological & .600 &.007&\\
-semantic $p^{-} = .04$ & .683 &.016 & 1e-06\\
-semantic $p^{-} = .06$ & .732 &.025 & 2e-07\\
-semantic $p^{-} = .08$ & .760 &.036 & 6e-06\\
-semantic $p^{-} = .10$ & .782 &.048 &9e-05\\
-\multicolumn{4}{l}{1980-2007 global period} \\
-technological & .606 &.002&\\
-semantic $p^{-} = .04$ & .665 &.009 & 8e-11\\
-semantic $p^{-} = .06$ & .721 &.017 & 9e-12\\
-semantic $p^{-} = .08$ & .747 &.025 & 9e-09\\
-semantic $p^{-} = .10$ & .782 &.035 & 3e-07\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion \label{discussion}}
-%%%%%%%%%%%%%%%%%%%%%
-
-The main contribution of this study was twofold.
-First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts.
-We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...).
-The availability of these data suggests new avenues for further research.
-
-A first potential application is to use the patents' topological measures inherited from their relevant keywords.
-The fact that these measures are backward-looking and immediately available after the publication of the patent information is an important asset.
-It would for example be very interesting to test their predicting power to assess the quality of an innovation, using the number of forward citations received by a patent, and subsequently the future effect on the firm's market value.
-
-Regarding firm innovative strategy, a second extension could be to study trajectories of firms in the two networks: technological and semantic.
-Merging these information with data on the market value of firms can give a lot of insight about the more efficient innovative strategies, about the importance of technology convergence or about acquisition of small innovative firms.
-It will also allow to observe innovation pattern over a firm life cycle and how this differ across technology field.
-
-A third extension would be to use dig further into the history of innovation.
-USPTO patent data have been digitized from the first patent in July 1790.
-However, not all of them contain a text that is directly exploitable.
-We consider that the quality of patent's images is good enough to rely on Optical Character Recognition techniques to retrieve plain text from at least 1920.
-With such data, we would be able to extend our analysis further back in time and to study how technological progress occurs and combines in time.
-\cite{akcigit2013mechanics} conduct a similar work by looking at recombination and apparition of technological subclasses.
-Using the fact that communities are constructed yearly, one can construct a measure of proximity between two successive classes.
-This could give clear view on how technologies converged over the year and when others became obsolete and replaced by new methods.
-
-%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supporting Information \label{sectionSI}}
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-
-\subsection*{S1 Text : Definition of utility patent}
-
-\textbf{Describes with more details the definition of patents and  context.}
-
-\subsection*{S2 Text : Data collection procedure}
-
-\textbf{Detailed description of data collection}
-
-\subsection*{S3 File : Semantic Network Visualization}
-
-\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}
-
-\subsection*{S4 Text : Network Sensitivity Analysis\label{app:sensitivity}}
-
-\textbf{Extended figures for Network Sensitivity Analysis}
-
-\subsection*{S5 Text : Statistical definitions and derivations}
-
-\textbf{Extended definitions and derivations for the statistical model}
-
-%%%%%%%%%%%%%%%%%%%%%
-%\section*{Acknowledgments}
-
-%\nolinenumbers
-
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-%\bibliographystyle{plos2015}
-%\bibliography{patents}
-
-\begin{thebibliography}{10}
-
-\bibitem{aghionhowitt1992}
-Aghion P, Howitt P.
-\newblock {A Model of Growth through Creative Destruction}.
-\newblock Econometrica. 1992 March;60(2):323--51.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v60y1992i2p323-51.html}.
-
-\bibitem{romer1990}
-Romer PM.
-\newblock {Endogenous Technological Change}.
-\newblock Journal of Political Economy. 1990 October;98(5):S71--102.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ucp/jpolec/v98y1990i5ps71-102.html}.
-
-\bibitem{RePEc:nbr:nberwo:3301}
-Griliches Z.
-\newblock {Patent Statistics as Economic Indicators: A Survey}.
-\newblock National Bureau of Economic Research, Inc; 1990. 3301.
-\newblock Available from: \url{https://ideas.repec.org/p/nbr/nberwo/3301.html}.
-
-\bibitem{Hall2001}
-Hall BH, Jaffe AB, Trajtenberg M.
-\newblock {The NBER Patent Citations Data File: Lessons, Insights and
-  Methodological Tools}.
-\newblock C.E.P.R. Discussion Papers; 2001. 3094.
-\newblock Available from: \url{https://ideas.repec.org/p/cpr/ceprdp/3094.html}.
-
-\bibitem{Youn:2015fk}
-Youn H, Strumsky D, Bettencourt LMA, Lobo J.
-\newblock Invention as a combinatorial process: evidence from US patents.
-\newblock Journal of The Royal Society Interface. 2015;12(106).
-
-\bibitem{2013arXiv1310.8220N}
-{Newman} MEJ.
-\newblock {Prediction of highly cited papers}.
-\newblock ArXiv e-prints. 2013 Oct;.
-
-\bibitem{2014arXiv1402.7268S}
-{Sarig{\"o}l} E, {Pfitzner} R, {Scholtes} I, {Garas} A, {Schweitzer} F.
-\newblock {Predicting Scientific Success Based on Coauthorship Networks}.
-\newblock ArXiv e-prints. 2014 Feb;.
-
-\bibitem{sorenson2006complexity}
-Sorenson O, Rivkin JW, Fleming L.
-\newblock Complexity, networks and knowledge flow.
-\newblock Research policy. 2006;35(7):994--1017.
-
-\bibitem{kay2014patent}
-Kay L, Newman N, Youtie J, Porter AL, Rafols I.
-\newblock Patent overlay mapping: Visualizing technological distance.
-\newblock Journal of the Association for Information Science and Technology.
-  2014;65(12):2432--2443.
-
-\bibitem{bruck2016recognition}
-Bruck P, R{\'e}thy I, Szente J, Tobochnik J, {\'E}rdi P.
-\newblock Recognition of emerging technology trends: class-selective study of
-  citations in the US Patent Citation Network.
-\newblock Scientometrics. 2016;107(3):1465--1475.
-
-\bibitem{curran2011patent}
-Curran CS, Leker J.
-\newblock Patent indicators for monitoring convergence--examples from NFF and
-  ICT.
-\newblock Technological Forecasting and Social Change. 2011;78(2):256--273.
-
-\bibitem{Katz1996remarks}
-Katz ML.
-\newblock Remarks on the economic implications of convergence.
-\newblock Industrial and Corporate Change. 1996;5(4):1079--1095.
-
-\bibitem{Furman2011shoulders}
-Furman JL, Stern S.
-\newblock Climbing atop the Shoulders of Giants: The Impact of Institutions on
-  Cumulative Research.
-\newblock American Economic Review. 2011 August;101(5):1933--63.
-\newblock Available from:
-  \url{http://www.aeaweb.org/articles?id=10.1257/aer.101.5.1933}.
-
-\bibitem{AAKnetwork2016}
-Acemoglu AU Daron, Kerr W.
-\newblock {Innovation Network}.
-\newblock Proceedings of the National Academy of Sciences (forthcoming). 2016;.
-
-\bibitem{preschitschek2013}
-Preschitschek N, Niemann H, Leker J, Moehrle MG.
-\newblock Anticipating industry convergence: Semantic analyses vs IPC
-  co-classification analyses of patents.
-\newblock Foresight. 2013 11;15(6):446--464.
-
-\bibitem{yoon2004text}
-Yoon B, Park Y.
-\newblock A text-mining-based patent network: Analytical tool for
-  high-technology trend.
-\newblock The Journal of High Technology Management Research.
-  2004;15(1):37--50.
-
-\bibitem{park2014semantic}
-Park I, Yoon B.
-\newblock A semantic analysis approach for identifying patent infringement
-  based on a product--patent map.
-\newblock Technology Analysis \& Strategic Management. 2014;26(8):855--874.
-
-\bibitem{yoon2011detecting}
-Yoon J, Kim K.
-\newblock Detecting signals of new technological opportunities using semantic
-  patent analysis and outlier detection.
-\newblock Scientometrics. 2011;90(2):445--461.
-
-\bibitem{gerken2012new}
-Gerken JM, Moehrle MG.
-\newblock A new instrument for technology monitoring: novelty in patents
-  measured by semantic patent analysis.
-\newblock Scientometrics. 2012;91(3):645--670.
-
-\bibitem{choi2014patent}
-Choi J, Hwang YS.
-\newblock Patent keyword network analysis for improving technology development
-  efficiency.
-\newblock Technological Forecasting and Social Change. 2014;83:170--182.
-
-\bibitem{fattori2003text}
-Fattori M, Pedrazzi G, Turra R.
-\newblock Text mining applied to patent mapping: a practical business case.
-\newblock World Patent Information. 2003;25(4):335--342.
-
-\bibitem{2015arXiv151003797G}
-{Gurciullo} S, {Smallegan} M, {Pereda} M, {Battiston} F, {Patania} A, {Poledna}
-  S, et~al.
-\newblock {Complex Politics: A Quantitative Semantic and Topological Analysis
-  of UK House of Commons Debates}.
-\newblock ArXiv e-prints. 2015 Oct;.
-
-\bibitem{lerner2015use}
-Lerner J, Seru A.
-\newblock The use and misuse of patent data: Issues for corporate finance and
-  beyond.
-\newblock Booth/Harvard Business School Working Paper. 2015;.
-
-\bibitem{oecdpatentmanual}
-OECD.
-\newblock OECD Patent Statistics Manual. 2009;Available from:
-  \url{/content/book/9789264056442-en}.
-
-\bibitem{martin2015}
-Dechezlepretre A, Martin R, Mohnen M.
-\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
-\newblock Centre for Economic Performance, LSE; 2014. dp1300.
-\newblock Available from:
-  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.
-
-\bibitem{tseng2007text}
-Tseng YH, Lin CJ, Lin YI.
-\newblock Text mining techniques for patent analysis.
-\newblock Information Processing \& Management. 2007;43(5):1216--1247.
-
-\bibitem{Adams2010text}
-Adams S.
-\newblock {The text, the full text and nothing but the text: Part 1 - Standards
-  for creating textual information in patent documents and general search
-  implications}.
-\newblock World Patent Information. 2010 March;32(1):22--29.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/eee/worpat/v32y2010i1p22-29.html}.
-
-\bibitem{abbas2014literature}
-Abbas A, Zhang L, Khan SU.
-\newblock A literature review on the state-of-the-art in patent analysis.
-\newblock World Patent Information. 2014;37:3--13.
-
-\bibitem{chavalarias2013phylomemetic}
-Chavalarias D, Cointet JP.
-\newblock Phylomemetic patterns in science evolution---the rise and fall of
-  scientific fields.
-\newblock Plos One. 2013;8(2):e54847.
-
-\bibitem{nltk}
-NLTK. Natural Language Toolkit, Stanford University; 2015.
-
-\bibitem{clauset2004finding}
-Clauset A, Newman ME, Moore C.
-\newblock Finding community structure in very large networks.
-\newblock Physical review E. 2004;70(6):066111.
-
-\bibitem{yang2000improving}
-Yang Y, Ault T, Pierce T, Lattimer CW.
-\newblock Improving text categorization methods for event tracking.
-\newblock In: Proceedings of the 23rd annual international ACM SIGIR conference
-  on Research and development in information retrieval. ACM; 2000. p. 65--72.
-
-\bibitem{blei2003latent}
-Blei DM, Ng AY, Jordan MI.
-\newblock Latent dirichlet allocation.
-\newblock Journal of machine Learning research. 2003;3(Jan):993--1022.
-
-\bibitem{kaplan2015double}
-Kaplan S, Vakili K.
-\newblock The double-edged sword of recombination in breakthrough innovation.
-\newblock Strategic Management Journal. 2015;36(10):1435--1457.
-
-\bibitem{iacovacci2015mesoscopic}
-Iacovacci J, Wu Z, Bianconi G.
-\newblock Mesoscopic Structures Reveal the Network Between the Layers of
-  Multiplex Datasets.
-\newblock arXiv preprint arXiv:150503824. 2015;.
-
-\bibitem{de2015ranking}
-De~Domenico M, Sol{\'e}-Ribalta A, Omodei E, G{\'o}mez S, Arenas A.
-\newblock Ranking in interconnected multilayer networks reveals versatile
-  nodes.
-\newblock Nature communications. 2015;6.
-
-\bibitem{ARCHIBUGI199279}
-Archibugi D, Pianta M.
-\newblock Specialization and size of technological activities in industrial
-  countries: The analysis of patent data.
-\newblock Research Policy. 1992;21(1):79 -- 93.
-\newblock Available from:
-  \url{http://www.sciencedirect.com/science/article/pii/0048733392900283}.
-
-\bibitem{Bloom2005distance}
-Bloom N, Schankerman M, Reenen JV.
-\newblock {Identifying Technology Spillovers and Product Market Rivalry}.
-\newblock Econometrica. 2013 07;81(4):1347--1393.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v81y2013i4p1347-1393.html}.
-
-\bibitem{ziman2003technological}
-Ziman J.
-\newblock Technological innovation as an evolutionary process.
-\newblock Cambridge University Press; 2003.
-
-\bibitem{holland2012signals}
-Holland JH.
-\newblock Signals and boundaries: Building blocks for complex adaptive systems.
-\newblock Mit Press; 2012.
-
-\bibitem{nicosia2009extending}
-Nicosia V, Mangioni G, Carchiolo V, Malgeri M.
-\newblock Extending the definition of modularity to directed graphs with
-  overlapping communities.
-\newblock Journal of Statistical Mechanics: Theory and Experiment.
-  2009;2009(03):P03024.
-
-\bibitem{decelle2011asymptotic}
-Decelle A, Krzakala F, Moore C, Zdeborov{\'a} L.
-\newblock Asymptotic analysis of the stochastic block model for modular
-  networks and its algorithmic applications.
-\newblock Physical Review E. 2011;84(6):066106.
-
-\bibitem{valles2016multilayer}
-Valles-Catala T, Massucci FA, Guimera R, Sales-Pardo M.
-\newblock Multilayer stochastic block models reveal the multilayer structure of
-  complex networks.
-\newblock Physical Review X. 2016;6(1):011036.
-
-\bibitem{2016arXiv160602319N}
-{Newman} MEJ.
-\newblock {Community detection in networks: Modularity optimization and maximum
-  likelihood are equivalent}.
-\newblock ArXiv e-prints. 2016 Jun;.
-
-\bibitem{akcigit2013mechanics}
-Akcigit U, Kerr WR, Nicholas T.
-\newblock The Mechanics of Endogenous Innovation and Growth: Evidence from
-  Historical US Patents.
-\newblock Citeseer; 2013.
-
-\bibitem{regibeau2010}
-R{\'e}gibeau P, Rockett K.
-\newblock Innovation cycles and learning at the patent office: does the early
-  patent get the delay?
-\newblock Journal of Industrial Economics. 2010;58(2):222--246.
-\newblock Available from:
-  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
-
-\end{thebibliography}
-
-\newpage
-
-\section*{S1 Text : Definition of utility patent}
-
-A utility patent at the USPTO is a document providing intellectual property and protection of an invention.
-It excludes others to making, using, or selling the invention the same invention in the United States in exchange for a disclosure of the patent content.
-The protection is granted for 20 years since 1995 (it was 17 years before that from 1860) starting from the year the patent application was filled, but can be interrupted before if its owner fails to pay the maintenance fees due after 3.5, 7.5 and 11.5 years.
-Utility patents are by far the most numerous, with more than 90\% of the total universe of USPTO patents.\footnote{Other categories are Plant patents, Design patents and Reissue patents.} According to the Title 35 of the United States Codes (35 USC) section 101: \textit{``Whoever invents or discovers any new and useful process, machine, manufacture, or composition of matter, or any new and useful improvement thereof, may obtain a patent therefor, subject to the conditions and requirements of this title.''}\footnote{%
-Patent laws can be found in http://www.uspto.gov/web/offices/pac/mpep/mpep-9015-appx-l.html\#d0e302376} In practice however, other types of invention including algorithms can also be patented.\footnote{A notable example is the patent \textit{US6285999} protecting the Page Rank algorithm invented by Larry Page in 1998 which was the genesis of Google.} The two following sections of the 35 USC defined the condition an invention must meet to be protected by the USPTO: (i) novelty: the claimed invention cannot be already patented or described in a previous publication (35 USC section 102); (ii) obviousness: \textit{``differences between the claimed invention and the prior art must not be such that the claimed invention as a whole would have been obvious before the effective filing date of the claimed invention to a person having ordinary skill in the art to which the claimed invention pertains''}.
-(35 USC section 103).
-After review from the USPTO experts, an application satisfying these requirements will be accepted and a patent granted.
-The average time lag for such a review is on average a little more than 2 years since 1976, with some patents being granted after much more than two years.\footnote{This time lag, sometimes called the grant lag, is highly heterogeneous across technological fields.
-In addition, it cannot be considered as totally random.
-For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\cite{regibeau2010}.}
-
-\paragraph{Sample restriction}
-As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013.
-For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below).
-We restrict attention to patents applied for before 2007.
-The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO.
-However, in order to date them as closely as possible to the date of invention, we use the application date as a reference.
-As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013.
-Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.
-
-\newpage
-
-\section*{S2 Text : Data collection and Workflow}
-
-\label{supp:data}
-
-\subsubsection*{Data Collection Procedure}
-
-Raw version of USPTO redbook with abstracts are available for years 1976-2014 starting from bulk download page at \url{https://bulkdata.uspto.gov/}.
-A script first automatically downloads files.
-Before being automatically processed, a few error in files (corresponding to missing end of records probably due to line dropping during the concatenation of weekly files) had to be corrected manually.
-Files are then processed with the following filters transforming different format and xml schemes into a uniform dictionary data structure :
-
-\begin{itemize}
-\item \texttt{dat} files (1976-2000): handmade parser
-\item \texttt{xml} files (2001-2012): xml parser, used with different schemas definitions.
-\end{itemize}
-
-Everything is stored into a MongoDB database, which latest dump is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % anonymize the db for submission
-
-\subsubsection*{Processing Workflow}
-
-The source code for the full workflow is available at \url{https://github.com/JusteRaimbault/PatentsMining}.
-A simplified shell wrapper is at \texttt{Models/fullpipe.sh}.
-Note that keywords co-occurrence estimation requires a memory amount in $O(N^2)$ (although optimized using dictionaries) and the operation on the full database requires a consequent infrastructure.
-Launch specifications are the following :
-
-\paragraph{Setup}
-
-Install the database and required packages.
-
-\begin{itemize}
-\item Having a running local mongod instance
-\item mongo host, port, user and password to be configured in \texttt{conf/parameters.csv}
-\item raw data import from gz file : use mongorestore -d redbook -c raw --gzip {\$}FILE
-\item specific python packages required : pymongo, python-igraph, nltk (with resources punkt, averaged{\_}perceptron{\_}tagger,porter{\_}test)
-\end{itemize}
-
-\paragraph{Running}
-
-The utility fullpipe.sh launches the successive stages of the processing pipe.
-
-\paragraph{Options}
-
-\textit{this configuration options can be changed in }\texttt{conf/parameters.csv}
-
-\begin{itemize}
-\item window size in years
-\item beginning of first window
-\item beginning of last window
-\item number of parallel runs
-\item \texttt{kwLimit} : total number of keywords $K_W$
-\item \texttt{edge{\_}th} : $\theta_w$ pre-filtering for memory storage purposes
-\item \texttt{dispth} : $\theta_c$
-\item \texttt{ethunit} : $\theta_w^{(0)}$
-\end{itemize}
-
-\paragraph{Tasks}
-
-The tasks to be done in order : keywords extraction, relevance estimation, network construction, semantic probas construction, are launched with the following options :
-%!! keywords and kw-consolidation tested with python3 ; rest with python2 (igraph compatibility issues)
-
-\begin{enumerate}
-\item \texttt{keywords} : extracts keywords
-\item \texttt{kw-consolidation} : consolidate keywords database (techno disp measure)
-\item \texttt{raw-network} : estimates relevance, constructs raw network and perform sensitivity analysis
-\item \texttt{classification} : classify and compute patent probability, keyword measures and patent measures ; here parameters $(\theta_w,\theta_c)$ can be changed in configuration file.
-\end{enumerate}
-
-\paragraph{Classification Data}
-
-The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
-Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window.
-The format are the following :
-
-\begin{itemize}
-\item Keywords files : keyword ; community ; termhood times inverse document frequency ; technological concentration ; document frequency ; termhood ; degree ; weighted degree ; betweenness centrality ; closeness centrality ; eigenvector centrality
-\item Patents measures : patent id ; total number of potential keywords ; number of classified keywords ; same topological measures as for keywords
-\item Patent probabilities : patent id ; total number of potential keywords ; id of the semantic class ; number of keywords in this class.
-Probabilities have to be reconstructed by extracting all the lines corresponding to a patent and dividing each count by the total number of classified keywords.
-\end{itemize}
-
-\paragraph{Analysis}
-
-The results of classification has to be processed for analysis (construction of sparse matrices for efficiency e.g.), following the steps:
-\begin{itemize}
-\item from classification files to R variables with \texttt{Semantic/semanalfun.R}
-\item from csv technological classes to R-formatted sparse Matrix with \texttt{Techno/prepareData.R} 
-\item from csv citation file to citation network in R-formatted graph and adjacency sparse matrix with \texttt{Citation/constructNW.R}
-\end{itemize}
-
-Analyses are done in \texttt{Semantic/semanalysis.R}.
-
-\newpage
+\input{si.tex}
 
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{figures/commnum_thetaw_byyears.png}
 \caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{figures/vcount_comnum_pareto.png}
 \caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{figures/normalizedObjs-dispth_eth4_1e-5.png}
 \caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{figures/commnum_thetaw_byyears_window3.png}
 \caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{figures/vcount_comnum_pareto_window3.png}
 \caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
@@
 \centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
+\includegraphics[width=\textheight,height=\textwidth,angle=90]{figures/normalizedObjs-dispth_window3_eth4_1e-5.png}
 \caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
@@
 
-\newpage
+%\subsubsection*{An alternative filtering method}
 
-\section*{S5 Text : Statistical definitions and derivations}
-\subsubsection*{Likelihood expression}
-We define $\mathcal{F}_i$ the filtration which corresponds to the time $t_i$.
-With this notation $\mathcal{L}( X | \mathcal{F}_{i-1})$ simply means the likelihood of $X$ conditioned on the past.
-We consider $\widehat{\theta}^{(z)}$ the MLE\footnote{Apparently, this MLE is a partial MLE, but we will not refer to partial for simplicity.} of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
-\begin{eqnarray*}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} \log \mathcal{L} \big( B_{l,i} | \mathcal{F}_{i-1} \big).
-\end{eqnarray*}
-Recalling that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables 
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-the log-likelihood of the model can be expressed as 
-\begin{eqnarray}
-\label{loglik}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} B_{l,i} \log \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big) +(1 - B_{l,i}) \log \Big(1 - \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big).
-\end{eqnarray}
-In practice, the user can easily implement the formula (\ref{loglik}) for any $0 \leq \theta^{(z)} \leq 1$, and maximize it over a predefined grid to obtain $\widehat{\theta}^{(z)}$.
+%Other heuristic for network construction were tested.
+We describe one in the following.
+We assume the highest degree terms do not carry specific information on particular classes and can be thus filtered given a maximal degree threshold $k{max}$.
+Similarly, edge with small weight must not carry significant information and are filtered according to a minimal edge weight threshold $w_{min}$.
+Keywords are preliminary filtered by a document frequency window $\left[ f_{min},f_{max} \right]$ which is slightly different from network filtering and complementary.
+A sensitivity analysis of resulting network topology to these parameters is shown in Fig.
+.
 
-\subsubsection*{Standard errors of the estimated values}
-Under some assumptions, it is possible to show the asymptotic normality of $\widehat{\theta}^{(z)}$ and to compute the asymptotic variance.
-For simplicity of exposition, we assume that we restrict to $\theta^{(z)}$ such that we have $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} < 1$ for any $i=2, \cdots, Z$.
-The central limit theorem can be expressed as
-\begin{eqnarray}
-\label{variance}
-\sqrt{Z \mathbb{E} [ C ]} (\widehat{\theta}^{(z)} - \theta^{(z)}) \overset{\mathcal{L}}{\rightarrow} MN \Big( 0, \int (p + \theta^{(z)})(1 - (p + \theta^{(z)})) d\pi^{(z)} (p) \Big),
-\end{eqnarray}
-where MN stands for a multinormal distribution and $\pi^{(z)}$ for the asymptotic limit distribution of the quantity $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)}$.
-Note that the variance term in (\ref{variance}) is equal to an aggregate version of the Fisher information matrix.
-The proof of such statement is beyond the scope of this paper.
-On the basis of (\ref{variance}), we provide a variance estimator as
-$$v^{(z)} = \frac{1}{C_k-1}\sum_{i=2}^{C_k}  \frac{N_{i_k}^{(z)}}{i-1} + \widehat{\theta}^{(z)},$$ 
-where $i_k$ is such that the $i_k$th patent corresponds to the $k$th couple. This estimator was used to compute the standard deviation in Table \ref{summary}.
-\subsubsection*{Test statistic}
-The test statistic used is a mean difference test statistic between $\widehat{\theta}^{(tec)}$ and  $\widehat{\theta}^{(sem)}$, where the formal expression can be found in (\ref{teststat}).
-We assume independence between both quantities and thus under the null hypothesis, we have that
-$$\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)} {\rightarrow} MN(0,V),$$
-where $V= \int (p + \theta^{(tec)})(1 - (p + \theta^{(tec)})) d\pi^{(tec)} (p) + \int (p + \theta^{(sem)})(1 - (p + \theta^{(sem)})) d\pi^{(sem)} (p)$ can be estimated by $\widehat{V} = v^{(sem)} + v^{(tec)}$.
-Then, we obtain that
-\begin{eqnarray}
-\label{teststat}
-A = \frac{\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)}}{\widehat{V}} \approx \mathcal{N} (0,1),
-\end{eqnarray}
-where $A$ is the mean difference test static.
-
-%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Information
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S1 Text : Definition of utility patent}
-
-%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%\section*{S2 Text : Data collection and Workflow}
-
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S4 Text : Network Sensitivity Analysis}
-
-%%%%%%%%%%%%%%%%%%%%
-%\bigskip
-%\bigskip
-%\newpage
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\subsection*{Additional plots}
-%
-%% plots that have some info but not included in paper
-%
 %
@@
 %\begin{figure}[!ht]
-%% figure : interlayer overlap
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_density_semcounts.png}
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_ts_semcounts.png}\\
-%\caption{Inter-classification effective overlaps (normalized by patent count)}
+%% values of some topological measures in 2D parameter space
+%\includegraphics[width=\textwidth]{figures/graph_sens_2010_msesizes}
+%\caption{Variation of semantic network indicators across a 4-dimensional parameter space (figure-level axis : $(k_{max},w_{min})$; meta axis: $(f_{min},f_{max})$), for year 2010, where indicators are modularity (louvain method), number of connected components, proximity of class size distribution to technological classes size distribution, communities number, network size, community size balance.
+A good optimization compromise is given here by $()$.}
+%% TODO change with proportion parameters in new figure
+%% TODO detail which obj to be minimized etc in supplementary material
 %\end{figure}
@@
 %
-%
-%
-
-%%%%%%%%%%%%%%%%%%%%%%
-%% Junk
-%%%%%%%%%%%%%%%%%%%%%%
-
-%Data-mining and network analysis~\cite{newman2010networks} can bring different insights.
-As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
-in the recent analysis on 20\textsuperscript{th} century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation necessarily involves complex patterns which understanding must have positive feedback on the economy.\par
-
-%%%%%%%%%%%%%%%%%%%%
-%%  Templates
-%%%%%%%%%%%%%%%%%%%%
-
-% For figure citations, please use "Fig." instead of "Figure".
-%\begin{figure}[h]
-%\caption{{\bf Figure Title first bold sentence}
-%Figure Caption}
-%\label{fig1}
-%\end{figure}
-
-%
-%
-%
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-%
-%
-
-%
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-
-%\begin{thebibliography}{10}
-%\bibitem{bib1}
-%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS.
-Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes.
-Mol Immunol.
-2014 Nov 22.
-pii: S0161-5890(14)00313-7.
-doi: 10.1016/j.molimm.2014.11.005
-
-%\bibitem{bib2}
-%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
-
-%\end{thebibliography}
 
 \end{document}
-
-\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
-
-A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics.
-Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
-\[
-\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
-\]
-It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields.
-We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
-\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}
-
-% eventually do stats on merging/splitting : distribution of kws overlaps in time ?
-
-\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time.
-Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
-\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes.
-\comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
-\label{fig:semanticflows}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-10 Docs/Papers/Technical/overleafv2/Slides.tex
slides_seminar

\documentclass{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{Boadilla}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[scale=2]{ccicons}

%\AtBeginSection[]
%{
%  \begin{frame}<beamer>
%    \frametitle{Plan}
%    \tableofcontents[currentsection]
%  \end{frame}
%}
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>
%    \frametitle{Plan}
%    \tableofcontents[currentsection, currentsubsection]
%  \end{frame}
%}

\title[Patent Mining]{Classifying Patent Based on their Semantic Content \\ An empirical exploration into patents text mining}
\author[Bergeaud, Potiron, Raimbault]{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
\institute[]{Banque de France, Keio University and ISC-PIF}
\date{November 2018}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\section{Introduction}
\begin{frame}{Motivation}
    %Patenting is increasing, big data blablabla

    \textit{Patenting as a footprint of technology and its coevolution with science and culture~\cite{bais2010praise}}

\bigskip
\centering

\includegraphics[width=0.35\textwidth,angle=90]{figures/USX1}
\includegraphics[width=0.45\textwidth]{figures/pageRank}

\end{frame}

\begin{frame}{Why study patents ?}
\justify

$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge ; propagation of knowledge

$\rightarrow$ Economics~\cite{griliches1998patent} : dynamics of innovation ; R{\&}D returns ; innovation at the core of endogenous growth theories~\cite{aghionhowitt1992}

\bigskip

\textbf{Examples :}

\begin{itemize}
\item \cite{Youn:2015fk} interaction between technological fields ; combinatorial nature of inventions
\item \cite{2016arXiv160207928B} citation network analysis to detect emerging research front
\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis
\end{itemize}

\end{frame}

%\begin{frame}{What we do}
%\end{frame}
\begin{frame}{A large scale semantic insight into USPTO database}

    % integrer le ``what we do'' ici ?

    \textbf{Proposed approach}

    \textit{Complement existing patent office classifications using patent semantic content}

    \bigskip

    \textbf{Takeaway results}

    $\rightarrow$ \textit{An endogenous semantic classification is constructed for the full USPTO abstracts and titles, 1976-2012}

    \bigskip

    $\rightarrow$ \textit{Information carried is complementary to the technological classification}

\end{frame}
\section{Background}

\begin{frame}{Patent data}

\end{frame}
\begin{frame}{Descriptive statistics}
    % summary of our database ?
\end{frame}

\begin{frame}{Database construction}

Construction of a Database from US Patent and Trademark Office redbook 1976-2012 (full patent description), which provide raw data but on separate files and different formats

\bigskip

\textbf{Data Collection Procedure}

\begin{itemize}
\item Automatic download of raw data file
\item Parsing depending on format : \texttt{dat} or \texttt{xml} (varying schema)
\item Uniformisation and storing in MongoDB
\end{itemize}

\bigskip

$\rightarrow$ 4391272 patents with text data ; dated by application date (current state of knowledge)

\end{frame}
\section{Methods}
\begin{frame}{Extracting relevant n-grams}

    % Situate regarding other classical approaches : LDA etc

    \textit{Text-mining in python with \texttt{nltk}~\cite{bird2006nltk}}, method adapted from
\cite{chavalarias2013phylomemetic}. Advantage over LDA: scalability and flexibility

\bigskip

\begin{itemize}
\item Parsing and tokenizing / pos-tagging (word functions) / stemming  with \texttt{nltk}
\item Selection of potential \textit{n-grams} (with $1 \leq n \leq 3$) with the rule $\bigcap \{NN \cup VBG \cup JJ \}$
\item Database insertion for instantaneous use (several days $\rightarrow$ 1min)
\item Estimation of \textit{n-grams} relevance, following co-occurrences statistical distribution (\textit{termhood} score as chi-2 score)
\end{itemize}
\end{frame}

\begin{frame}{Estimation of n-gram relevance}

    \begin{itemize}
        \item Termhood-based selection of a fixed number of keywords
        \item Estimation on temporal moving windows
        \item Filtering of network edge, with an additional exogenous control by technological class keyword concentration to filter nodes
    \end{itemize}

\end{frame}

\section{Results}
\begin{frame}{Optimizing network structure}

    \centering
    \includegraphics[width=\textwidth]{figures/Fig1.png}

    \medskip

    \textit{Pareto optimization on cutoff parameters for modularity, size and number of communities}

\end{frame}

\begin{frame}{Semantic network visualization}
   \centering
    \includegraphics[height=\textheight]{figures/Fig2.png}

\end{frame}

\begin{frame}{Classes Examples (2000-2004)}

\justify

\begin{itemize}
\item Memory devices : \texttt{semiconductor memori devic; memori cell plural; memori cell transistor; layer ferroelectr}
\item Chemical analysis : \texttt{time-of-flight mass spectromet; chromatograph column; ion trap mass}
\item Particular steel : \texttt{martensit; austenit stainless steel}
\item Laser : \texttt{emit laser beam; vertic caviti surfac; vcsel}
\item Sewing : \texttt{circular knit machin; stitch; sew machin; embroideri}
\item Lithography : \texttt{lithograph mask; project beam radiat; heat-sensit; planograph print plate}
\item Tobacco : \texttt{cigarett filter; cigarett pack; tobacco; tobacco rod}
\end{itemize}
\end{frame}

\begin{frame}{Size of classes}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig3.png}

    \medskip

    \textit{A peak in average class size around 1998}

\end{frame}

\begin{frame}{Hierarchical class structure}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig4.png}

    \medskip

    \textit{Fat-tail distribution of class size for both classification, closer to a power-law for semantic classes}

\end{frame}

\begin{frame}{Evolution of patent diversities}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig5.png}

    \medskip

    \textit{General increase in average invention specialization seen both for semantic and technological; semantic regime shift in 1996} 
    % "change in the regime of specialization, the new regime being caused by more single-class patents"

\end{frame}

\begin{frame}{Originality and generality measures}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig6.png}

    \medskip

    \textit{Systematically lower originality and generality (citation-based measures) for the semantic classification (consistent with the higher modularity shown therafter)}

\end{frame}

\begin{frame}{Interaction between classes: intra-classification overlaps}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig7.png}

    \medskip

    % techno : increasing specializatino trend
    % semantic : consistent with 1996 breakpoint in the structure of technologies - rq : how to control specifically that it is not an artifact of the method / or biased by sizes ?

    \textit{Increased technological specialization; qualitative regime shift confirmed in 1996 for the semantic classification}

\end{frame}

\begin{frame}{Inter-classification overlaps}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig8.png}

    \medskip

    \textit{Confirms the change in nature of inventions around 1996}

\end{frame}

\begin{frame}{Modularity of classifications}
   \centering
    \includegraphics[width=\textwidth]{figures/Fig9.png}

    \medskip

    \textit{Semantic classification is more significant regarding the structure of the citation network, both for single-class and multi-class modularities.}

\end{frame}

%\begin{frame}{Stochastic Block Modeling to evaluate consistency of classifications}

    % tableau trop long, impossible a inserer

%\end{frame}

\section{Conclusion}

\begin{frame}{Discussion}
    \justify

    \textbf{Implications}

     \smallskip

    $\rightarrow$ Possible application to detection of emerging research fronts

    \smallskip

    $\rightarrow$ An interactive exploration of semantic content ?

    \textbf{Developments (ongoing)}

      \smallskip

     $\rightarrow$ Application on the European patent database

     \smallskip

     $\rightarrow$ Quantifying the diffusion of innovation in urban systems, and its co-evolution with the socio-economic structure

     \smallskip

     \textbf{Possible developments}

      \smallskip

     $\rightarrow$ Agent-based modeling of interactions between technologies

     \smallskip

     $\rightarrow$ Full-text mining and history of technology

\end{frame}

\begin{frame}{Conclusion}

\bigskip

\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\smallskip
\textbf{Raw database} at \texttt{http://dx.doi.org/10.7910/DVN/BW3ACK} and \textbf{Semantic classification database} at  \texttt{http:// dx.doi.org/10.7910/DVN/ZULMOY}\\\smallskip
\textbf{Acknowledgments}: thanks to ISC-PIF for access to the computation infrastructure.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[allowframebreaks]
\frametitle{References}
\bibliographystyle{apalike}
\bibliography{patents}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2018-11-10 Docs/Papers/Technical/overleafv2/bdf_wp.tex
slides_seminar

--- 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
@@
-\documentclass[12pt,twoside,a4paper]{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[article]{article}%
 \usepackage{eurosym}
+\usepackage{amssymb}
 \usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{graphicx}
+\usepackage{graphics}
+\usepackage{natbib}
+\usepackage[export]{adjustbox}%
+\setcounter{MaxMatrixCols}{30}
 \usepackage{multirow}
@@
 \usepackage[section]{placeins}
-\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
+\usepackage{geometry}
 \usepackage{setspace}
-\usepackage{rotating}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{etoolbox}
-\usepackage{amsmath,amssymb}
-\usepackage{float}
-\usepackage{xcolor}
+\usepackage{lscape}
 \usepackage{hyperref}
-\usepackage{booktabs,caption,fixltx2e}
+\usepackage{booktabs,caption}
 \usepackage[flushleft]{threeparttable}
 \usepackage{tabularx}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{enumitem}
-\usepackage{caption}
-\usepackage{nameref}
-\usepackage{lscape}
-\usepackage{fancyhdr}
-
-\setcounter{MaxMatrixCols}{10}
+\usepackage[FIGTOPCAP, hang]{subfigure}
+\usepackage{floatrow}
+\floatsetup[table]{capposition=top}
+\floatsetup[figure]{capposition=top}
+
+\def\tablename{TABLE}
+\def\figurename{FIGURE}
+
+\newcommand{\fignote}[2]{\begin{center}\parbox[c]{#1}{\footnotesize #2} \end{center}}
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
+
 \hypersetup{
@@
 }
-\geometry{hmargin=4cm,vmargin=4cm}
+\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
 \newtheorem{theorem}{Theorem}
@@
 \newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{assumption}{Assumption}
 \newtheorem{axiom}[theorem]{Axiom}
@@
 \newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}{Proposition}
+\newtheorem{proposition}[theorem]{Proposition}
 \newtheorem{remark}[theorem]{Remark}
@@
 \newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-\setcounter{secnumdepth}{5}
-\textwidth 6.0in
-\textheight 8.84in 
-\setlength{\topmargin}{-0.3in}
-\setlength{\oddsidemargin}{0.0in}
-\setlength{\evensidemargin}{0.0in}
-\setlength{\abovecaptionskip}{0pt}
-\setlength{\belowcaptionskip}{5pt}
-\setlength{\textfloatsep}{25pt}  
-\setlength{\intextsep}{5pt}   
-\fancyhf{}
-\pagestyle{fancy}
-\renewcommand{\headrulewidth}{1pt}
-\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
-\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
-\fancyfoot[C]{\thepage}
+
+%Yoann's commands
+\newcommand{\reels}{\mathbb{R}}
+\newcommand{\naturels}{\mathbb{N}}
+\newcommand{\relatifs}{\mathbb{Z}}
+\newcommand{\rat}{\mathbb{Q}}
+\newcommand{\complex}{\mathbb{C}}
+\newcommand{\esp}{\mathbb{E}}
+\newcommand{\proba}{\mathbb{P}}
+\newcommand{\var}{\operatorname{Var}}
+\newcommand{\cov}{\operatorname{Cov}}
+\newcommand{\Tau}{\mathrm{T}}
 
@@
 
-\title{Classifying Patents Based on their Semantic Content\thanks{%
-Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
-Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
-\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
- \ \ \ \ \ Juste Raimbault \bigskip}
+\title{Classifying Patents Based on their Semantic Content\thanks{Addresses: Bergeaud: Banque de France (antonin.bergeaud@banque-france.fr), Potiron: Keio University, Raimbault: ISC-PIF }}
+\vskip.5em 
+\author{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
+\smallskip
+\date{June 2018}
 \maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% Please keep the abstract below 300 words
 \begin{abstract}
@@
 
-\pagebreak
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
 \section{Introduction}
-Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}.
-\cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation.
-Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis.
+
+Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \citet{aghionhowitt1992} and \citet{romer1990}.
+\citet{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation.
+Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\citealt{Hall2001}) have opened the way to a very wide range of analysis (see among many recent examples \citealt{bloom2013}, \citealt{aghion2018a} or \citealt{aghion2018b}).
 Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review.
-Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}.
-With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters.
-Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.
+Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \citet{Youn:2015fk}.
+With methods such as citation dynamics modeling discussed in~\citet{2013arXiv1310.8220N} or co-authorship networks analysis in~\citet{2014arXiv1402.7268S}, a large body of the literature such as~\citet{sorenson2006complexity} or~\citet{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters.
+Finally, \citet{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.
 
 Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies.
-But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share.
-Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g.
-~\cite{AAKnetwork2016}).
+But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \citealt{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share.
+Curiously, and in spite of the large number of studies that analyze interactions across technologies~\citet{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g.
+~\citealt{AAKnetwork2016}).
 
@@
 Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach.
-The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence).
+The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\citealt{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence).
 One can for instance consider the case of the word \textit{optic}.
-Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic.
+Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of transistor design and electro-optic.
 This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.
@@
 Previous research has already proposed to use semantic networks to study technological domains and detect novelty.
-~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain.
-The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}.
-More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation.
-Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).
+~\citet{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain.
+The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \citet{park2014semantic} and \citet{yoon2011detecting}.
+More closely related to our methodology,~\citet{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation.
+Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\citealt{choi2014patent} and~\citealt{fattori2003text}) and in political science (e.g.~\citealt{2015arXiv151003797G}).
 
@@
 Finally, section \ref{discussion} discusses potential further developments and conclude.
-More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.
+More details, including robustness checking, figures and technical derivations can be found in the Appendix.
 
@@
 In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013.
-A clearer definition of utility patent is given in~\nameref{sectionSI}.
-Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.
+A clearer definition of utility patent is given in Appendix \ref{app:utility}.
+Also, additional information on how to correctly exploit patent data can be found in \citet{Hall2001} and \citet{lerner2015use}.
 
@@
 Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent.
-One can consult~\cite{oecdpatentmanual} for more details about this.
-Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}).
+One can consult~\citet{oecdpatentmanual} for more details about this.
+Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\citealt{martin2015}).
 Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves.
@@
 \subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
+Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ format at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
 Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
-In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}).
+In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\citealt{Adams2010text}).
 The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).
@@
 Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976.
-Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}.
-The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
+Detailed procedure of data collection, parsing and consolidation are available in Appendix \ref{app:datacollection}.
+The latest dump of the database in \texttt{Mongodb} format is available at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}.
 Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
@@
 Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents.
-These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}.
+These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\citet{Hall2001}.
 Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window.
@@
 
-Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}.
+Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\citet{tseng2007text}.
 The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications.
-The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review).
+The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\citealt{abbas2014literature} for a review).
 Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}.
@@
 Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies.
-Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.
+Indeed, as argued in~\citet{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.
 
@@
 Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
+As reviewed previously, the use of co-occurrences is the usual way to construct a semantic network.
+Other hybrid technique such as bipartite semantic/authors networks, do not have the nice feature of relying solely on endogenous semantic information contained in data.
 
@@
 Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
-$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
+$K(p)$ are extracted through a similar procedure as the one detailed in~\citet{chavalarias2013phylomemetic}: 
 \begin{enumerate}
@@
 
-Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations.
+Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library for most of above operations.
 This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining}
@@
 
-Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
+Following the heuristic in~\citet{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
+The choice of the total number of keywords to be extracted, which we shall denote $K_w$, is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
 We choose to set this parameter to $K_w = 100,000$.
 We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$.
-The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
+This step has only very marginal effects on the nature of the final keywords but is necessary for computational purposes.
+The filtration is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
+A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$, where the formal definition can be found in (\ref{termhood}).
+It is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
 Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
@@
 
-\[
+\begin{eqnarray}
+\label{termhood}
 t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
-\]
+\end{eqnarray}
 
@@
 Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
+Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
 
@@
 For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$.
-In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
+We use a threshold parameter, defined as $\theta_c$, and keep nodes with $c_{tech}(s) > \theta_c$.
+Likewise, edges with low weights correspond to rare co-occurrences and are considered to be noise.
+To account for this we define the threshold parameter for edges $\theta_w$, and we filter edges with a weight below $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
 To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
+$\theta_w^{(0)}$ is thus a varying parameter interpreted as a noise threshold \emph{per patent}.
 Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
@@
 We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-%\hspace{-2.5cm}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
-%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
-\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values.
+Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size.
+There is a priori no reason to choose any specific point among the different optimums.
+Consequently, we have tried the analysis with all the candidate values for $\theta_c$ and found that the results are the most reasonable when taking $\theta_c = 0.06$ (see Figure {\ref{fig:networksensitivity}}).
+
+%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\caption{Sensitivity analysis of network community structure to filtering parameters.}
+\includegraphics[width=\textwidth]{figures/Fig1.png}
+\floatfoot{\textbf{Note:} This figure considers a specific window 2000-2004 and the obtained plots are typical.
+\textit{(Left panel)} plots the number of communities as a function of the edge threshold parameter $\theta_w$ for different values of the node threshold parameter $\theta_c$.
 The maximum is roughly stable across $\theta_c$ (dashed red line).
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{striking}
-%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
-\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
-The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/Fig2}
+\caption{An example of semantic network visualization.}
+\floatfoot{\textbf{Note:}  This figure shows the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
+The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available as Supplementary Material.}
 \label{fig:rawnetwork}
@@
 There are around 30 keywords by semantic class on average and the median is 2 for any $t$.
-Fig.~\ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{meancomsize}
-%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
-\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
+Figure \ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.
+
+%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/Fig3}
+\caption{Keywords by semantic class}
+\floatfoot{\textbf{Note:}  This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$ from $t=1980$ to $t=2007$.}
 \label{fig:mean_K}
@@
 When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix.
-Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Fig.~\ref{fig:class-sizes}.
+Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Figure \ref{fig:class-sizes}.
 This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.
@@
 \hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
-\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$,
-from the biggest to the smallest.
+\includegraphics[width=\textwidth]{figures/Fig4}
+\caption{Sizes of classes.} 
+\floatfoot{\textbf{Note:}  This figure plots for each year $t = 1980$ to $t =2007$, the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$, from the biggest to the smallest.
 The formal definition of size can be found in Section \ref{characteristics}.
@@
 Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
+The combination of citation network modeling by Stochastic Block Modeling with topic modeling was studied for scientific papers by \cite{zhu2013scalable}, outperforming previous link prediction algorithms.
+\citet{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
 Furthermore, is has recently been shown that measures of multilayer network projections induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
+
+An other potential research development would be to further exploit the temporal structure of our dataset.
+Indeed, large progress have recently been made in complex network analysis of time-series data (see~\citealt{gao2017complex} for a review).
+For example, \cite{gao2015multiscale} develops a method to construct multiscale network from time series, which could in our case be a solution to identify structures in patents trajectories at different levels, and be an alternative to the single scale modularity analysis we use.
 
@@
 
-We show in Fig.~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series.
+We show in Figure \ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series.
 This is carried with two different settings, namely including/not including patents with zero diversity (i.e.
@@
 More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization.
-This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}.
+This is a well-known stylized fact as documented in~\citet{ARCHIBUGI199279}.
 Furthermore, a qualitative regime shift on semantic classification occurs around 1996.
@@
 \]
+
 where $z \in \{tec, sem\}$, $I_i$ denotes the set of patents that are cited by the $i$th patent within a five year window (i.e.
@@
 Both measures are lower on average based on semantic classification than on technological classification.
-Fig.
-\ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-%First row : semantic with relevant keywords only - all patents 
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
-%Second row : patents with diversity $> 0$ (more than one class)}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
-%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
-\caption{
-\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$).
+Figure \ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.
+
+%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\includegraphics[width=\textwidth]{figures/Fig5}
+\caption{Patent level diversities.} 
+\floatfoot{\textbf{Note:}  Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$).
 The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e.
-patents with diversity greater than 0).
-}
+patents with diversity greater than 0).}
 \label{fig:patent-level-orig}
@@
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{originality.png}
-\includegraphics[width=0.49\textwidth]{generality.png}\\
-%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
-\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
+\includegraphics[width=\textwidth]{figures/Fig6}
+\caption{Patent level originality and generality} 
+\floatfoot{\textbf{Note:}  Originality (left hand side) and generality (right hand side) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
 }
@@
 Such measures could for example be used to construct a metrics between semantic classes.
-Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{Bloom2005distance}.
+Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{bloom2013}.
 Formally, recalling the definition of $\left(p_{ij}\right)$ as the probability for the $i$th patent to belong to the $j$th class and $N_P$ as the number of patents it writes
+
 \begin{eqnarray}
@@
 Their evolution in time can furthermore give insights into trends of specialization.
-We show in Fig.~\ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications.
+We show in Figure \ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications.
 The technological classification globally always follow a decreasing trend, corresponding to more and more isolated classes, i.e.
@@
 It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation.
-%This interpretation is consistent with the dynamics of semantic flows presented in Fig.~\ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.
+%This interpretation is consistent with the dynamics of semantic flows presented in Figure \ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.
 
@@
 \centering
-\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
-\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
-\caption{
-\textbf{Intra-classification overlaps.}
-\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
-\textit{(Right column)} Corresponding mean time-series.
-\textit{(First row)} Normalized overlaps.
-\textit{(Second row)} Relative overlaps.}
+\includegraphics[width=\textwidth]{figures/Fig7}
+\caption{Intra-Classification overlaps}
+\floatfoot{\textbf{Note:}  Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale) and corresponding mean time-series.
+(First row) Normalized overlaps.
+(Second row) Relative overlaps.}
 \label{fig:intra-classif-overlap}
@@
 Overlaps \emph{between} classifications are defined as in (\ref{overlap}), but with $j$ standing for the $j$th technological class and $k$ for the $k$th semantic class: $p_{ij}$ are technological probabilities and $p_{ik}$ semantic probabilities.
-They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Fig.~\ref{fig:inter-classif-overlap}.
+They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Figure \ref{fig:inter-classif-overlap}.
 Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease.
@@
 \begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
-\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series.
-The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
+\includegraphics[width=\textwidth]{figures/Fig8}
+\caption{Distribution of relative overlaps between classifications.} 
+\floatfoot{\textbf{Note:}  Distribution of overlaps at all time steps and corresponding mean time-series. The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
 \label{fig:inter-classif-overlap}
@@
 An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}.
-The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\cite{AAKnetwork2016}).
+The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\citealt{AAKnetwork2016}).
 This section studies empirically modularities of the citation network regarding the different classifications.
@@
 Overlapping modularity naturally extends simple modularity by taking into account the fact that nodes can belong simultaneously to many classes.
-We document in Fig.~\ref{fig:modularities} both simple and multi-class modularities over time.
+We document in Figure \ref{fig:modularities} both simple and multi-class modularities over time.
 For simple modularity, $Q_d^{(tec)}$ is low and stable across the years whereas $Q_d^{(sem)}$ is slightly greater and increasing.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{simplemodularity}
-\includegraphics[width=0.49\textwidth]{overlappingmodularity}
-%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
-\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability).
-(Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
+\includegraphics[width=\textwidth]{figures/Fig9}
+\caption{Temporal evolution of semantic and technological modularities of the citation network.} 
+\floatfoot{\textbf{Note:}  Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability) and Multi-class modularity, computed following~\citet{nicosia2009extending} }
 \label{fig:modularities}
@@
 Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed.
-This effort ressembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth.
+This effort resembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth.
 Furthermore, the parameters fitted here can have a direct interpretation as a citation probability.
@@
 We estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding maximum likelihood estimator (MLE) $\hat{\theta}^{(z)}$.
-The likelihood function, along with the standard deviation expression and details about the test, can be found in~\nameref{sectionSI}.
+The likelihood function, along with the standard deviation expression and details about the test, can be found in \ref{app:stat}.
 The fitted values, standard errors and p-values corresponding to the statistical test $\theta^{(sem)} = \theta^{(tec)}$ (with corresponding alternative hypothesis $\theta^{(sem)} > \theta^{(tec)}$) on non-overlapping blocks from the period 1980-2007\footnote{Note that the estimation included patents up until 2010 in the period 2006-2007 and not the patents from 1980 in the period 1980-1985 for homogeneity in size with other periods.
@@
 This assumption is reasonable only if the blocks are non-overlapping.
-All of this can be found in~\nameref{sectionSI}.
+All of this can be found in \ref{app:stat}.
 Finally, note that from a statistical perspective, including overlapping blocks wouldn't yield more information.
@@
 This is consistently seen for any period, and significant for the global period.
-This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propension to cite patents from its own class $\theta^{(sem)}$ is increasing.
+This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propensity to cite patents from its own class $\theta^{(sem)}$ is increasing.
 We believe that this might provide extra information to patent officers when making their choice of citations.
@@
 Note that the introduced model can be seen as a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g.
-\cite{decelle2011asymptotic}, \cite{valles2016multilayer}).
+\citealt{decelle2011asymptotic}, \citealt{valles2016multilayer}).
 The parameters are estimated computing the corresponding MLE.
-In view of~\cite{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.
+In view of~\citet{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.
 
@@
 We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...).
-The availability of these data suggests new avenues for further research.
+Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree, etc.).
+The availability of this data suggests new avenues for further research.
+Linking our dataset with existing open ones can lead to various powerful developments.
+For example, using it together with the disambiguated inventor database provided by~\cite{li2014disambiguation} could be a way to study semantic profiles of inventors, or of cities as inventor addresses are provided.
+The investigation of spatial diffusion of innovation between cities, which is a key component of Pumain's Evolutive Urban Theory~\cite{pumain2010theorie}, would be made possible.
 
@@
 It would for example be very interesting to test their predicting power to assess the quality of an innovation, using the number of forward citations received by a patent, and subsequently the future effect on the firm's market value.
-
 Regarding firm innovative strategy, a second extension could be to study trajectories of firms in the two networks: technological and semantic.
@@
 It will also allow to observe innovation pattern over a firm life cycle and how this differ across technology field.
-
 A third extension would be to use dig further into the history of innovation.
@@
 
-%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supporting Information \label{sectionSI}}
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-
-\subsection*{S1 Text : Definition of utility patent}
-
-\textbf{Describes with more details the definition of patents and  context.}
-
-\subsection*{S2 Text : Data collection procedure}
-
-\textbf{Detailed description of data collection}
-
-\subsection*{S3 File : Semantic Network Visualization}
-
-\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}
-
-\subsection*{S4 Text : Network Sensitivity Analysis\label{app:sensitivity}}
-
-\textbf{Extended figures for Network Sensitivity Analysis}
-
-\subsection*{S5 Text : Statistical definitions and derivations}
-
-\textbf{Extended definitions and derivations for the statistical model}
-
-%%%%%%%%%%%%%%%%%%%%%
-%\section*{Acknowledgments}
-
-%\nolinenumbers
-
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-%\bibliographystyle{plos2015}
-%\bibliography{patents}
-
-\begin{thebibliography}{10}
-
-\bibitem{aghionhowitt1992}
-Aghion P, Howitt P.
-\newblock {A Model of Growth through Creative Destruction}.
-\newblock Econometrica. 1992 March;60(2):323--51.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v60y1992i2p323-51.html}.
-
-\bibitem{romer1990}
-Romer PM.
-\newblock {Endogenous Technological Change}.
-\newblock Journal of Political Economy. 1990 October;98(5):S71--102.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ucp/jpolec/v98y1990i5ps71-102.html}.
-
-\bibitem{RePEc:nbr:nberwo:3301}
-Griliches Z.
-\newblock {Patent Statistics as Economic Indicators: A Survey}.
-\newblock National Bureau of Economic Research, Inc; 1990. 3301.
-\newblock Available from: \url{https://ideas.repec.org/p/nbr/nberwo/3301.html}.
-
-\bibitem{Hall2001}
-Hall BH, Jaffe AB, Trajtenberg M.
-\newblock {The NBER Patent Citations Data File: Lessons, Insights and
-  Methodological Tools}.
-\newblock C.E.P.R. Discussion Papers; 2001. 3094.
-\newblock Available from: \url{https://ideas.repec.org/p/cpr/ceprdp/3094.html}.
-
-\bibitem{Youn:2015fk}
-Youn H, Strumsky D, Bettencourt LMA, Lobo J.
-\newblock Invention as a combinatorial process: evidence from US patents.
-\newblock Journal of The Royal Society Interface. 2015;12(106).
-
-\bibitem{2013arXiv1310.8220N}
-{Newman} MEJ.
-\newblock {Prediction of highly cited papers}.
-\newblock ArXiv e-prints. 2013 Oct;.
-
-\bibitem{2014arXiv1402.7268S}
-{Sarig{\"o}l} E, {Pfitzner} R, {Scholtes} I, {Garas} A, {Schweitzer} F.
-\newblock {Predicting Scientific Success Based on Coauthorship Networks}.
-\newblock ArXiv e-prints. 2014 Feb;.
-
-\bibitem{sorenson2006complexity}
-Sorenson O, Rivkin JW, Fleming L.
-\newblock Complexity, networks and knowledge flow.
-\newblock Research policy. 2006;35(7):994--1017.
-
-\bibitem{kay2014patent}
-Kay L, Newman N, Youtie J, Porter AL, Rafols I.
-\newblock Patent overlay mapping: Visualizing technological distance.
-\newblock Journal of the Association for Information Science and Technology.
-  2014;65(12):2432--2443.
-
-\bibitem{bruck2016recognition}
-Bruck P, R{\'e}thy I, Szente J, Tobochnik J, {\'E}rdi P.
-\newblock Recognition of emerging technology trends: class-selective study of
-  citations in the US Patent Citation Network.
-\newblock Scientometrics. 2016;107(3):1465--1475.
-
-\bibitem{curran2011patent}
-Curran CS, Leker J.
-\newblock Patent indicators for monitoring convergence--examples from NFF and
-  ICT.
-\newblock Technological Forecasting and Social Change. 2011;78(2):256--273.
-
-\bibitem{Katz1996remarks}
-Katz ML.
-\newblock Remarks on the economic implications of convergence.
-\newblock Industrial and Corporate Change. 1996;5(4):1079--1095.
-
-\bibitem{Furman2011shoulders}
-Furman JL, Stern S.
-\newblock Climbing atop the Shoulders of Giants: The Impact of Institutions on
-  Cumulative Research.
-\newblock American Economic Review. 2011 August;101(5):1933--63.
-\newblock Available from:
-  \url{http://www.aeaweb.org/articles?id=10.1257/aer.101.5.1933}.
-
-\bibitem{AAKnetwork2016}
-Acemoglu AU Daron, Kerr W.
-\newblock {Innovation Network}.
-\newblock Proceedings of the National Academy of Sciences (forthcoming). 2016;.
-
-\bibitem{preschitschek2013}
-Preschitschek N, Niemann H, Leker J, Moehrle MG.
-\newblock Anticipating industry convergence: Semantic analyses vs IPC
-  co-classification analyses of patents.
-\newblock Foresight. 2013 11;15(6):446--464.
-
-\bibitem{yoon2004text}
-Yoon B, Park Y.
-\newblock A text-mining-based patent network: Analytical tool for
-  high-technology trend.
-\newblock The Journal of High Technology Management Research.
-  2004;15(1):37--50.
-
-\bibitem{park2014semantic}
-Park I, Yoon B.
-\newblock A semantic analysis approach for identifying patent infringement
-  based on a product--patent map.
-\newblock Technology Analysis \& Strategic Management. 2014;26(8):855--874.
-
-\bibitem{yoon2011detecting}
-Yoon J, Kim K.
-\newblock Detecting signals of new technological opportunities using semantic
-  patent analysis and outlier detection.
-\newblock Scientometrics. 2011;90(2):445--461.
-
-\bibitem{gerken2012new}
-Gerken JM, Moehrle MG.
-\newblock A new instrument for technology monitoring: novelty in patents
-  measured by semantic patent analysis.
-\newblock Scientometrics. 2012;91(3):645--670.
-
-\bibitem{choi2014patent}
-Choi J, Hwang YS.
-\newblock Patent keyword network analysis for improving technology development
-  efficiency.
-\newblock Technological Forecasting and Social Change. 2014;83:170--182.
-
-\bibitem{fattori2003text}
-Fattori M, Pedrazzi G, Turra R.
-\newblock Text mining applied to patent mapping: a practical business case.
-\newblock World Patent Information. 2003;25(4):335--342.
-
-\bibitem{2015arXiv151003797G}
-{Gurciullo} S, {Smallegan} M, {Pereda} M, {Battiston} F, {Patania} A, {Poledna}
-  S, et~al.
-\newblock {Complex Politics: A Quantitative Semantic and Topological Analysis
-  of UK House of Commons Debates}.
-\newblock ArXiv e-prints. 2015 Oct;.
-
-\bibitem{lerner2015use}
-Lerner J, Seru A.
-\newblock The use and misuse of patent data: Issues for corporate finance and
-  beyond.
-\newblock Booth/Harvard Business School Working Paper. 2015;.
-
-\bibitem{oecdpatentmanual}
-OECD.
-\newblock OECD Patent Statistics Manual. 2009;Available from:
-  \url{/content/book/9789264056442-en}.
-
-\bibitem{martin2015}
-Dechezlepretre A, Martin R, Mohnen M.
-\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
-\newblock Centre for Economic Performance, LSE; 2014. dp1300.
-\newblock Available from:
-  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.
-
-\bibitem{tseng2007text}
-Tseng YH, Lin CJ, Lin YI.
-\newblock Text mining techniques for patent analysis.
-\newblock Information Processing \& Management. 2007;43(5):1216--1247.
-
-\bibitem{Adams2010text}
-Adams S.
-\newblock {The text, the full text and nothing but the text: Part 1 - Standards
-  for creating textual information in patent documents and general search
-  implications}.
-\newblock World Patent Information. 2010 March;32(1):22--29.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/eee/worpat/v32y2010i1p22-29.html}.
-
-\bibitem{abbas2014literature}
-Abbas A, Zhang L, Khan SU.
-\newblock A literature review on the state-of-the-art in patent analysis.
-\newblock World Patent Information. 2014;37:3--13.
-
-\bibitem{chavalarias2013phylomemetic}
-Chavalarias D, Cointet JP.
-\newblock Phylomemetic patterns in science evolution---the rise and fall of
-  scientific fields.
-\newblock Plos One. 2013;8(2):e54847.
-
-\bibitem{nltk}
-NLTK. Natural Language Toolkit, Stanford University; 2015.
-
-\bibitem{clauset2004finding}
-Clauset A, Newman ME, Moore C.
-\newblock Finding community structure in very large networks.
-\newblock Physical review E. 2004;70(6):066111.
-
-\bibitem{yang2000improving}
-Yang Y, Ault T, Pierce T, Lattimer CW.
-\newblock Improving text categorization methods for event tracking.
-\newblock In: Proceedings of the 23rd annual international ACM SIGIR conference
-  on Research and development in information retrieval. ACM; 2000. p. 65--72.
-
-\bibitem{blei2003latent}
-Blei DM, Ng AY, Jordan MI.
-\newblock Latent dirichlet allocation.
-\newblock Journal of machine Learning research. 2003;3(Jan):993--1022.
-
-\bibitem{kaplan2015double}
-Kaplan S, Vakili K.
-\newblock The double-edged sword of recombination in breakthrough innovation.
-\newblock Strategic Management Journal. 2015;36(10):1435--1457.
-
-\bibitem{iacovacci2015mesoscopic}
-Iacovacci J, Wu Z, Bianconi G.
-\newblock Mesoscopic Structures Reveal the Network Between the Layers of
-  Multiplex Datasets.
-\newblock arXiv preprint arXiv:150503824. 2015;.
-
-\bibitem{de2015ranking}
-De~Domenico M, Sol{\'e}-Ribalta A, Omodei E, G{\'o}mez S, Arenas A.
-\newblock Ranking in interconnected multilayer networks reveals versatile
-  nodes.
-\newblock Nature communications. 2015;6.
-
-\bibitem{ARCHIBUGI199279}
-Archibugi D, Pianta M.
-\newblock Specialization and size of technological activities in industrial
-  countries: The analysis of patent data.
-\newblock Research Policy. 1992;21(1):79 -- 93.
-\newblock Available from:
-  \url{http://www.sciencedirect.com/science/article/pii/0048733392900283}.
-
-\bibitem{Bloom2005distance}
-Bloom N, Schankerman M, Reenen JV.
-\newblock {Identifying Technology Spillovers and Product Market Rivalry}.
-\newblock Econometrica. 2013 07;81(4):1347--1393.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v81y2013i4p1347-1393.html}.
-
-\bibitem{ziman2003technological}
-Ziman J.
-\newblock Technological innovation as an evolutionary process.
-\newblock Cambridge University Press; 2003.
-
-\bibitem{holland2012signals}
-Holland JH.
-\newblock Signals and boundaries: Building blocks for complex adaptive systems.
-\newblock Mit Press; 2012.
-
-\bibitem{nicosia2009extending}
-Nicosia V, Mangioni G, Carchiolo V, Malgeri M.
-\newblock Extending the definition of modularity to directed graphs with
-  overlapping communities.
-\newblock Journal of Statistical Mechanics: Theory and Experiment.
-  2009;2009(03):P03024.
-
-\bibitem{decelle2011asymptotic}
-Decelle A, Krzakala F, Moore C, Zdeborov{\'a} L.
-\newblock Asymptotic analysis of the stochastic block model for modular
-  networks and its algorithmic applications.
-\newblock Physical Review E. 2011;84(6):066106.
-
-\bibitem{valles2016multilayer}
-Valles-Catala T, Massucci FA, Guimera R, Sales-Pardo M.
-\newblock Multilayer stochastic block models reveal the multilayer structure of
-  complex networks.
-\newblock Physical Review X. 2016;6(1):011036.
-
-\bibitem{2016arXiv160602319N}
-{Newman} MEJ.
-\newblock {Community detection in networks: Modularity optimization and maximum
-  likelihood are equivalent}.
-\newblock ArXiv e-prints. 2016 Jun;.
-
-\bibitem{akcigit2013mechanics}
-Akcigit U, Kerr WR, Nicholas T.
-\newblock The Mechanics of Endogenous Innovation and Growth: Evidence from
-  Historical US Patents.
-\newblock Citeseer; 2013.
-
-\bibitem{regibeau2010}
-R{\'e}gibeau P, Rockett K.
-\newblock Innovation cycles and learning at the patent office: does the early
-  patent get the delay?
-\newblock Journal of Industrial Economics. 2010;58(2):222--246.
-\newblock Available from:
-  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
-
-\end{thebibliography}
-
 \newpage
-
-\section*{S1 Text : Definition of utility patent}
+\appendix
+
+\section{Definition of utility patent}  \label{app:utility}
 
@@
 In addition, it cannot be considered as totally random.
-For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\cite{regibeau2010}.}
+For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\citet{regibeau2010}.}
 
@@
 
-\newpage
-
-\section*{S2 Text : Data collection and Workflow}
-
-\label{supp:data}
+\section{Data collection procedure}\label{app:datacollection}
 
@@
 
-Everything is stored into a MongoDB database, which latest dump is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % anonymize the db for submission
+Everything is stored into a MongoDB database, which latest dump is available at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}
 
@@
 
-The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
+The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://dx.doi.org/10.7910/DVN/ZULMOY}.
 Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window.
@@
 
-\newpage
-
-\section*{S4 Text : Network Sensitivity Analysis \label{app:sensitivity}}
-
-\subsubsection*{Network Sensitivity}
-
-The example of Fig.1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Fig.~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.
+\section{Network Sensitivity Analysis \label{app:sensitivity}}
+
+\subsection{Network Sensitivity}
+
+The example of Figure 1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Figures ~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.
 We also show an other point of view over the Pareto optimization, that is the third plot giving the values of normalized objectives as a function of $\theta_c$.
@@
 	\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
+	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/commnum_thetaw_byyears.png}
 	\caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
@@
 	\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
+	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/vcount_comnum_pareto.png}
 	\caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
@@
 	\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
+	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/normalizedObjs-dispth_eth4_1e-5.png}
 	\caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
@@
 %%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Time-window size sensitivity}
+\subsection{Time-window size sensitivity}
 
@@
 
-We show in Fig.~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$.
+We show in Figures ~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$.
 The same qualitative behavior is observed (with different quantitative values, as typically $\theta_w^{(0)}$ is for example expected to vary with document number and semantic regime, thus with window size), what confirms that the method is valid across different time windows.
@@
 	\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
+	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/commnum_thetaw_byyears_window3.png}
 	\caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
@@
 	\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
+	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/vcount_comnum_pareto_window3.png}
 	\caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
@@
 	\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
+	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/normalizedObjs-dispth_window3_eth4_1e-5.png}
 	\caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-\section*{S5 Text : Statistical definitions and derivations}
-\subsubsection*{Likelihood expression}
+
+\section{Statistical definitions and derivations} \label{app:stat}
+\subsection{Likelihood expression}
 We define $\mathcal{F}_i$ the filtration which corresponds to the time $t_i$.
 With this notation $\mathcal{L}( X | \mathcal{F}_{i-1})$ simply means the likelihood of $X$ conditioned on the past.
-We consider $\widehat{\theta}^{(z)}$ the MLE\footnote{Apparently, this MLE is a partial MLE, but we will not refer to partial for simplicity.} of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
+We consider $\widehat{\theta}^{(z)}$ the MLE of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
 \begin{eqnarray*}
@@
 
-\subsubsection*{Standard errors of the estimated values}
+\subsection{Standard errors of the estimated values}
 Under some assumptions, it is possible to show the asymptotic normality of $\widehat{\theta}^{(z)}$ and to compute the asymptotic variance.
@@
 
-%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Information
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S1 Text : Definition of utility patent}
-
-%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%\section*{S2 Text : Data collection and Workflow}
-
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S4 Text : Network Sensitivity Analysis}
-
-%%%%%%%%%%%%%%%%%%%%
-%\bigskip
-%\bigskip
-%\newpage
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\subsection*{Additional plots}
-%
-%% plots that have some info but not included in paper
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!ht]
-%% figure : interlayer overlap
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_density_semcounts.png}
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_ts_semcounts.png}\\
-%\caption{Inter-classification effective overlaps (normalized by patent count)}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-
-%%%%%%%%%%%%%%%%%%%%%%
-%% Junk
-%%%%%%%%%%%%%%%%%%%%%%
-
-%Data-mining and network analysis~\cite{newman2010networks} can bring different insights.
-As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
-in the recent analysis on 20\textsuperscript{th} century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation necessarily involves complex patterns which understanding must have positive feedback on the economy.\par
-
-%%%%%%%%%%%%%%%%%%%%
-%%  Templates
-%%%%%%%%%%%%%%%%%%%%
-
-% For figure citations, please use "Fig." instead of "Figure".
-%\begin{figure}[h]
-%\caption{{\bf Figure Title first bold sentence}
-%Figure Caption}
-%\label{fig1}
-%\end{figure}
-
-%
-%
-%
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-%
-%
-
-%
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-
-%\begin{thebibliography}{10}
-%\bibitem{bib1}
-%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS.
-Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes.
-Mol Immunol.
-2014 Nov 22.
-pii: S0161-5890(14)00313-7.
-doi: 10.1016/j.molimm.2014.11.005
-
-%\bibitem{bib2}
-%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
-
-%\end{thebibliography}
+\newpage
+\bibliographystyle{ecta}
+\bibliography{patents}
 
 \end{document}
-
-\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
-
-A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics.
-Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
-\[
-\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
-\]
-It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields.
-We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
-\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}
-
-% eventually do stats on merging/splitting : distribution of kws overlaps in time ?
-
-\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time.
-Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
-\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes.
-\comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
-\label{fig:semanticflows}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-10 Docs/Papers/Technical/overleafv2/main.tex
slides_seminar

--- 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
@@
-\documentclass[12pt,twoside,a4paper]{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{eurosym}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage[section]{placeins}
-\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
-\usepackage{setspace}
-\usepackage{rotating}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{etoolbox}
-\usepackage{amsmath,amssymb}
-\usepackage{float}
-\usepackage{xcolor}
-\usepackage{hyperref}
+% Template for PLoS
+% Version 3.1 February 2015
+%
+% To compile to pdf, run:
+% latex plos.template
+% bibtex plos.template
+% latex plos.template
+% latex plos.template
+% dvipdf plos.template
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
+% the final text of your manuscript.
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig." instead of "Figure".
+% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - tabs/spacing/line breaks within cells to alter layout or alignment
+% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
+% - colors, shading, or graphic objects
+% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
+%
+% Please be sure to include all portions of an equation in the math environment.
+%
+% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,A4]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8]{inputenc}
 \usepackage{booktabs,caption,fixltx2e}
@@
 \usepackage{tabularx}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{enumitem}
-\usepackage{caption}
-\usepackage{nameref}
-\usepackage{lscape}
-\usepackage{fancyhdr}
-
-\setcounter{MaxMatrixCols}{10}
-\hypersetup{
-    colorlinks, linkcolor={dark-red},
-    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% fixltx2e package for \textsubscript
+\usepackage{fixltx2e}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+%\DisableLigatures[f]{encoding = *, family = * }
+
+% rotating package for sideways tables
+\usepackage{rotating}
+
+% Remove comment for double spacing
+\usepackage{setspace} 
+\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Leave date blank
+\date{}
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{ragged2e}
+
+\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
+
+%\usepackage{epstopdf}
+\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{
+\includegraphics[width=2.0in]{PLOS-submission-eps-converted-to.pdf}
 }
-\geometry{hmargin=4cm,vmargin=4cm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{assumption}{Assumption}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-\setcounter{secnumdepth}{5}
-\textwidth 6.0in
-\textheight 8.84in 
-\setlength{\topmargin}{-0.3in}
-\setlength{\oddsidemargin}{0.0in}
-\setlength{\evensidemargin}{0.0in}
-\setlength{\abovecaptionskip}{0pt}
-\setlength{\belowcaptionskip}{5pt}
-\setlength{\textfloatsep}{25pt}  
-\setlength{\intextsep}{5pt}   
-\fancyhf{}
-\pagestyle{fancy}
-\renewcommand{\headrulewidth}{1pt}
-\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
-\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
-\fancyfoot[C]{\thepage}
+\rhead{Classifying Patents Based on their Semantic Content\vspace{2mm}}
+\rfoot{\thepage}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\sf Bergeaud, Potiron and Raimbault, 2017}
+%\lfoot{}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%%%%%%%%%%%%%%%%%%%%%%
+%% User-defined commands
+%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage[normalem]{ulem} % use normalem to protect \emph
+\newcommand\hl{\bgroup\markoverwith
+  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}
+
+%Yoann's commands
+\newcommand{\reels}{\mathbb{R}}
+\newcommand{\naturels}{\mathbb{N}}
+\newcommand{\relatifs}{\mathbb{Z}}
+\newcommand{\rat}{\mathbb{Q}}
+\newcommand{\complex}{\mathbb{C}}
+\newcommand{\esp}{\mathbb{E}}
+\newcommand{\proba}{\mathbb{P}}
+\newcommand{\var}{\operatorname{Var}}
+\newcommand{\cov}{\operatorname{Cov}}
+\newcommand{\Tau}{\mathrm{T}}
+
+% writing utilities
+%%%%%
+% variable to include comments or not in the compilation ; set to 1 to include
+%\def \draft {1}
+\def \draft {0}
+
+\def \trackdiff {1}
+%\def \trackdiff {0}
+
+% comments and responses
+\usepackage{xparse}
+\usepackage{ifthen}
+\DeclareDocumentCommand{\comment}{m o o o o}
+{\ifthenelse{\draft=1}{
+    \textcolor{red}{\textbf{C : }#1}
+    \IfValueT{#2}{\textcolor{blue}{\textbf{A1 : }#2}}
+    \IfValueT{#3}{\textcolor{ForestGreen}{\textbf{A2 : }#3}}
+    \IfValueT{#4}{\textcolor{red!50!blue}{\textbf{A3 : }#4}}
+    \IfValueT{#5}{\textcolor{Aquamarine}{\textbf{A4 : }#5}}
+ }{}
+}
+
+% todo
+\newcommand{\todo}[1]{
+\ifthenelse{\draft=1}{\textcolor{red!50!blue}{\textbf{TODO : \textit{#1}}}}{}
+}
+
+% track changes
+\newcommand{\change}[1]{
+\ifthenelse{\trackdiff=1}{\hl{#1}}{#1}
+}
+
+%% END MACROS SECTION
 
 \begin{document}
-
-\title{Classifying Patents Based on their Semantic Content\thanks{%
-Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
-Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
-\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
- \ \ \ \ \ Juste Raimbault \bigskip}
-\maketitle
+\vspace*{0.35in}
+
+% Title must be 250 characters or less.
+% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
+
+\begin{flushleft}
+{\Large
+\textbf\newline{
+Classifying Patents Based on their Semantic Content
+}
+}
+\newline
+\\
+Antonin Bergeaud\textsuperscript{1,\Yinyang},
+Yoann Potiron\textsuperscript{2,\Yinyang},
+Juste Raimbault\textsuperscript{3,4,\Yinyang,*}
+\\
+\bigskip
+\bf{1} Paris School of Economics - EHESS and Bank of France, Paris, France
+\\
+\bf{2} Faculty of Business and Commerce, Keio University, Tokyo, Japan
+\\
+\bf{3} UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France
+\\
+\bf{4} UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France
+\\
+\bigskip
+
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+\Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+%\ddag These authors also contributed equally to this work.
+
+% Current address notes
+%\textcurrency a Insert current address of first author with an address update
+% \textcurrency b Insert current address of second author with an address update
+% \textcurrency c Insert current address of third author with an address update
+
+% Deceased author note
+%\dag Deceased
+
+% Group/Consortium Author Note
+%\textpilcrow Membership list can be found in the Acknowledgments section.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+
+* Corresponding Author
+
+Email : juste.raimbault@polytechnique.edu
+
+\end{flushleft}
+
+\bigskip
+%\newpage
 
@@
 \begin{abstract}
+\justify
 In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach.
@@
 
-\pagebreak
-%\linenumbers
+\linenumbers
+
+\justify
 
@@
 \subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
+Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ format at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
 Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
@@
 Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}.
-The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
-Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
+The latest dump of the database in \texttt{Mongodb} format is available \change{at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}.} Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
 
@@
 Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
+\change{As reviewed previously, the use of co-occurrences is the usual way to construct a semantic network.
+Other hybrid technique such as bipartite semantic/authors networks, do not have the nice feature of relying solely on endogenous semantic information contained in data.}
 
@@
 Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
+The choice of the total number of keywords to be extracted, \change{which we shall denote $K_w$}, is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
 We choose to set this parameter to $K_w = 100,000$.
 We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$.
-The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
+\change{This step has only very marginal effects on the nature of the final keywords but is necessary for computational purposes.} The filtration is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
+A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$, \change{where the formal definition can be found in (\ref{termhood})}.
+It is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
 Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
@@
 For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$.
-In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
+We use a threshold parameter, \change{defined as $\theta_c$, and keep nodes with $c_{tech}(s) > \theta_c$.
+Likewise, edges with low weights correspond to rare co-occurrences and are considered to be noise.
+To account for this we define the threshold parameter for edges $\theta_w$, and we filter edges with a weight below $\theta_w$}, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
 To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
-Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
+\change{$\theta_w^{(0)}$ is thus a varying parameter interpreted as a noise threshold \emph{per patent}.} Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
 At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward.
@@
 We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).
+Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size.
+\change{There is a priori no reason to choose any specific point among the different optimums.
+Consequently, we have tried the analysis with all the candidate values for $\theta_c$ and found that the results are the most reasonable when taking $\theta_c = 0.06$ (see Fig.~{\ref{fig:networksensitivity}}).}
 
@@
 \centering
-%\hspace{-2.5cm}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
-%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
+%\includegraphics[width=\textwidth]{figures/Fig1}
 \caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values.
+\textit{(Left panel)} We plot the number of communities as a function of the edge threshold parameter $\theta_w$ for different values of the node threshold parameter $\theta_c$.
 The maximum is roughly stable across $\theta_c$ (dashed red line).
@@
 \centering
-\includegraphics[width=\textwidth]{striking}
-%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
+%\includegraphics[width=\textwidth]{figures/Fig2}
 \caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
-The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
+The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available as Supplementary Material.}
 \label{fig:rawnetwork}
@@
 \centering
-\includegraphics[width=0.9\textwidth]{meancomsize}
-%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
+%\includegraphics[width=\textwidth]{figures/Fig3}
 \caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
@@
 \hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
+%\includegraphics[width=\textwidth]{figures/Fig4}
 \caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$,
@@
 Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
+\change{The combination of citation network modeling by Stochastic Block Modeling with topic modeling was studied for scientific papers by }\cite{zhu2013scalable}\change{, outperforming previous link prediction algorithms.} \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
 Furthermore, is has recently been shown that measures of multilayer network projections induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
+
+\change{An other potential research development would be to further exploit the temporal structure of our dataset.
+Indeed, large progress have recently been made in complex network analysis of time-series data (see}~\cite{gao2017complex}\change{ for a review).
+For example, }\cite{gao2015multiscale}\change{develops a method to construct multiscale network from time series, which could in our case be a solution to identify structures in patents trajectories at different levels, and be an alternative to the single scale modularity analysis we use.}
 
@@
 \begin{figure}
-%First row : semantic with relevant keywords only - all patents 
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
-%Second row : patents with diversity $> 0$ (more than one class)}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
-%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
+%\includegraphics[width=\textwidth]{figures/Fig5}
 \caption{
@@
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{originality.png}
-\includegraphics[width=0.49\textwidth]{generality.png}\\
-%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
+%\includegraphics[width=\textwidth]{figures/Fig6}
 \caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
-\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
+%\includegraphics[width=\textwidth]{figures/Fig7}
 \caption{
-\textbf{Intra-classification overlaps.}
-\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
-\textit{(Right column)} Corresponding mean time-series.
-\textit{(First row)} Normalized overlaps.
-\textit{(Second row)} Relative overlaps.}
+\textbf{Intra-Classification overlaps.}
+(Left column) Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
+Right column) Corresponding mean time-series.
+(First row) Normalized overlaps.
+(Second row) Relative overlaps.}
 \label{fig:intra-classif-overlap}
@@
 \begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
+%\includegraphics[width=\textwidth]{figures/Fig8}
 \caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{simplemodularity}
-\includegraphics[width=0.49\textwidth]{overlappingmodularity}
-%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
+%\includegraphics[width=\textwidth]{figures/Fig9}
 \caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability).
@@
 We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...).
-The availability of these data suggests new avenues for further research.
+Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree, etc.).
+The availability of \change{this} data suggests new avenues for further research.
+\change{Linking our dataset with existing open ones can lead to various powerful developments.
+For example, using it together with the disambiguated inventor database provided by}~\cite{li2014disambiguation}\change{ could be a way to study semantic profiles of inventors, or of cities as inventor addresses are provided.
+The investigation of spatial diffusion of innovation between cities, which is a key component of Pumain's Evolutive Urban Theory}~\cite{pumain2010theorie}\change{, would be made possible.}
 
@@
 
-\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}
+\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})}
 
@@
 
-%\nolinenumbers
+\nolinenumbers
 
@@
 \bibitem{martin2015}
-Dechezlepretre A, Martin R, Mohnen M.
+Dechezlepr{\~A}ªtre A, Martin R, Mohnen M.
 \newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
@@
 \bibitem{nltk}
-NLTK. Natural Language Toolkit, Stanford University; 2015.
+NLTK. Natural Language Toolkit, Stanford Univeristy; 2015.
 
@@
 
+\bibitem{zhu2013scalable}
+Zhu Y, Yan X, Getoor L, Moore C.
+\newblock Scalable text and link analysis with mixed-topic link models.
+\newblock In: Proceedings of the 19th ACM SIGKDD international conference on
+  Knowledge discovery and data mining. ACM; 2013. p. 473--481.
+
 \bibitem{iacovacci2015mesoscopic}
@@
 \newblock Nature communications. 2015;6.
+
+\bibitem{gao2017complex}
+Gao ZK, Small M, Kurths J.
+\newblock Complex network analysis of time series.
+\newblock EPL (Europhysics Letters). 2017;116(5):50001.
+
+\bibitem{gao2015multiscale}
+Gao ZK, Yang YX, Fang PC, Zou Y, Xia CY, Du M.
+\newblock Multiscale complex network for analyzing experimental multivariate
+  time series.
+\newblock EPL (Europhysics Letters). 2015;109(3):30005.
 
@@
 
+\bibitem{li2014disambiguation}
+Li GC, Lai R, D’Amour A, Doolin DM, Sun Y, Torvik VI, et~al.
+\newblock Disambiguation and co-authorship networks of the US patent inventor
+  database (1975--2010).
+\newblock Research Policy. 2014;43(6):941--955.
+
+\bibitem{pumain2010theorie}
+Pumain D.
+\newblock Une th{\'e}orie g{\'e}ographique des villes.
+\newblock Bulletin de la Soci{\'e}t{\'e} g{\'e}ographie de Li{\`e}ge.
+  2010;(55):5--15.
+
 \bibitem{akcigit2013mechanics}
@@
 
-\bibitem{regibeau2010}
-R{\'e}gibeau P, Rockett K.
-\newblock Innovation cycles and learning at the patent office: does the early
-  patent get the delay?
-\newblock Journal of Industrial Economics. 2010;58(2):222--246.
-\newblock Available from:
-  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
-
 \end{thebibliography}
-
-\newpage
-
-\section*{S1 Text : Definition of utility patent}
-
-A utility patent at the USPTO is a document providing intellectual property and protection of an invention.
-It excludes others to making, using, or selling the invention the same invention in the United States in exchange for a disclosure of the patent content.
-The protection is granted for 20 years since 1995 (it was 17 years before that from 1860) starting from the year the patent application was filled, but can be interrupted before if its owner fails to pay the maintenance fees due after 3.5, 7.5 and 11.5 years.
-Utility patents are by far the most numerous, with more than 90\% of the total universe of USPTO patents.\footnote{Other categories are Plant patents, Design patents and Reissue patents.} According to the Title 35 of the United States Codes (35 USC) section 101: \textit{``Whoever invents or discovers any new and useful process, machine, manufacture, or composition of matter, or any new and useful improvement thereof, may obtain a patent therefor, subject to the conditions and requirements of this title.''}\footnote{%
-Patent laws can be found in http://www.uspto.gov/web/offices/pac/mpep/mpep-9015-appx-l.html\#d0e302376} In practice however, other types of invention including algorithms can also be patented.\footnote{A notable example is the patent \textit{US6285999} protecting the Page Rank algorithm invented by Larry Page in 1998 which was the genesis of Google.} The two following sections of the 35 USC defined the condition an invention must meet to be protected by the USPTO: (i) novelty: the claimed invention cannot be already patented or described in a previous publication (35 USC section 102); (ii) obviousness: \textit{``differences between the claimed invention and the prior art must not be such that the claimed invention as a whole would have been obvious before the effective filing date of the claimed invention to a person having ordinary skill in the art to which the claimed invention pertains''}.
-(35 USC section 103).
-After review from the USPTO experts, an application satisfying these requirements will be accepted and a patent granted.
-The average time lag for such a review is on average a little more than 2 years since 1976, with some patents being granted after much more than two years.\footnote{This time lag, sometimes called the grant lag, is highly heterogeneous across technological fields.
-In addition, it cannot be considered as totally random.
-For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\cite{regibeau2010}.}
-
-\paragraph{Sample restriction}
-As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013.
-For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below).
-We restrict attention to patents applied for before 2007.
-The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO.
-However, in order to date them as closely as possible to the date of invention, we use the application date as a reference.
-As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013.
-Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.
-
-\newpage
-
-\section*{S2 Text : Data collection and Workflow}
-
-\label{supp:data}
-
-\subsubsection*{Data Collection Procedure}
-
-Raw version of USPTO redbook with abstracts are available for years 1976-2014 starting from bulk download page at \url{https://bulkdata.uspto.gov/}.
-A script first automatically downloads files.
-Before being automatically processed, a few error in files (corresponding to missing end of records probably due to line dropping during the concatenation of weekly files) had to be corrected manually.
-Files are then processed with the following filters transforming different format and xml schemes into a uniform dictionary data structure :
-
-\begin{itemize}
-\item \texttt{dat} files (1976-2000): handmade parser
-\item \texttt{xml} files (2001-2012): xml parser, used with different schemas definitions.
-\end{itemize}
-
-Everything is stored into a MongoDB database, which latest dump is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % anonymize the db for submission
-
-\subsubsection*{Processing Workflow}
-
-The source code for the full workflow is available at \url{https://github.com/JusteRaimbault/PatentsMining}.
-A simplified shell wrapper is at \texttt{Models/fullpipe.sh}.
-Note that keywords co-occurrence estimation requires a memory amount in $O(N^2)$ (although optimized using dictionaries) and the operation on the full database requires a consequent infrastructure.
-Launch specifications are the following :
-
-\paragraph{Setup}
-
-Install the database and required packages.
-
-\begin{itemize}
-\item Having a running local mongod instance
-\item mongo host, port, user and password to be configured in \texttt{conf/parameters.csv}
-\item raw data import from gz file : use mongorestore -d redbook -c raw --gzip {\$}FILE
-\item specific python packages required : pymongo, python-igraph, nltk (with resources punkt, averaged{\_}perceptron{\_}tagger,porter{\_}test)
-\end{itemize}
-
-\paragraph{Running}
-
-The utility fullpipe.sh launches the successive stages of the processing pipe.
-
-\paragraph{Options}
-
-\textit{this configuration options can be changed in }\texttt{conf/parameters.csv}
-
-\begin{itemize}
-\item window size in years
-\item beginning of first window
-\item beginning of last window
-\item number of parallel runs
-\item \texttt{kwLimit} : total number of keywords $K_W$
-\item \texttt{edge{\_}th} : $\theta_w$ pre-filtering for memory storage purposes
-\item \texttt{dispth} : $\theta_c$
-\item \texttt{ethunit} : $\theta_w^{(0)}$
-\end{itemize}
-
-\paragraph{Tasks}
-
-The tasks to be done in order : keywords extraction, relevance estimation, network construction, semantic probas construction, are launched with the following options :
-%!! keywords and kw-consolidation tested with python3 ; rest with python2 (igraph compatibility issues)
-
-\begin{enumerate}
-\item \texttt{keywords} : extracts keywords
-\item \texttt{kw-consolidation} : consolidate keywords database (techno disp measure)
-\item \texttt{raw-network} : estimates relevance, constructs raw network and perform sensitivity analysis
-\item \texttt{classification} : classify and compute patent probability, keyword measures and patent measures ; here parameters $(\theta_w,\theta_c)$ can be changed in configuration file.
-\end{enumerate}
-
-\paragraph{Classification Data}
-
-The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
-Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window.
-The format are the following :
-
-\begin{itemize}
-\item Keywords files : keyword ; community ; termhood times inverse document frequency ; technological concentration ; document frequency ; termhood ; degree ; weighted degree ; betweenness centrality ; closeness centrality ; eigenvector centrality
-\item Patents measures : patent id ; total number of potential keywords ; number of classified keywords ; same topological measures as for keywords
-\item Patent probabilities : patent id ; total number of potential keywords ; id of the semantic class ; number of keywords in this class.
-Probabilities have to be reconstructed by extracting all the lines corresponding to a patent and dividing each count by the total number of classified keywords.
-\end{itemize}
-
-\paragraph{Analysis}
-
-The results of classification has to be processed for analysis (construction of sparse matrices for efficiency e.g.), following the steps:
-\begin{itemize}
-\item from classification files to R variables with \texttt{Semantic/semanalfun.R}
-\item from csv technological classes to R-formatted sparse Matrix with \texttt{Techno/prepareData.R} 
-\item from csv citation file to citation network in R-formatted graph and adjacency sparse matrix with \texttt{Citation/constructNW.R}
-\end{itemize}
-
-Analyses are done in \texttt{Semantic/semanalysis.R}.
-
-\newpage
-
-\section*{S4 Text : Network Sensitivity Analysis \label{app:sensitivity}}
-
-\subsubsection*{Network Sensitivity}
-
-The example of Fig.1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Fig.~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.
-We also show an other point of view over the Pareto optimization, that is the third plot giving the values of normalized objectives as a function of $\theta_c$.
-
-% Figures :
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
-\caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
-\label{fig:ext-sensitivity-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
-\caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
-\label{fig:ext-sensitivity-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
-\caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
-\label{fig:ext-sensitivity-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Time-window size sensitivity}
-
-% put some graphs for 3-years time window : same qualitative properties but a bit more noisy
-
-We show in Fig.~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$.
-The same qualitative behavior is observed (with different quantitative values, as typically $\theta_w^{(0)}$ is for example expected to vary with document number and semantic regime, thus with window size), what confirms that the method is valid across different time windows.
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
-\caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
-\label{fig:sensitivity-window3-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
-\caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
-\label{fig:sensitivity-window3-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
-\caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
-\label{fig:sensitivity-window3-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-\section*{S5 Text : Statistical definitions and derivations}
-\subsubsection*{Likelihood expression}
-We define $\mathcal{F}_i$ the filtration which corresponds to the time $t_i$.
-With this notation $\mathcal{L}( X | \mathcal{F}_{i-1})$ simply means the likelihood of $X$ conditioned on the past.
-We consider $\widehat{\theta}^{(z)}$ the MLE\footnote{Apparently, this MLE is a partial MLE, but we will not refer to partial for simplicity.} of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
-\begin{eqnarray*}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} \log \mathcal{L} \big( B_{l,i} | \mathcal{F}_{i-1} \big).
-\end{eqnarray*}
-Recalling that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables 
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-the log-likelihood of the model can be expressed as 
-\begin{eqnarray}
-\label{loglik}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} B_{l,i} \log \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big) +(1 - B_{l,i}) \log \Big(1 - \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big).
-\end{eqnarray}
-In practice, the user can easily implement the formula (\ref{loglik}) for any $0 \leq \theta^{(z)} \leq 1$, and maximize it over a predefined grid to obtain $\widehat{\theta}^{(z)}$.
-
-\subsubsection*{Standard errors of the estimated values}
-Under some assumptions, it is possible to show the asymptotic normality of $\widehat{\theta}^{(z)}$ and to compute the asymptotic variance.
-For simplicity of exposition, we assume that we restrict to $\theta^{(z)}$ such that we have $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} < 1$ for any $i=2, \cdots, Z$.
-The central limit theorem can be expressed as
-\begin{eqnarray}
-\label{variance}
-\sqrt{Z \mathbb{E} [ C ]} (\widehat{\theta}^{(z)} - \theta^{(z)}) \overset{\mathcal{L}}{\rightarrow} MN \Big( 0, \int (p + \theta^{(z)})(1 - (p + \theta^{(z)})) d\pi^{(z)} (p) \Big),
-\end{eqnarray}
-where MN stands for a multinormal distribution and $\pi^{(z)}$ for the asymptotic limit distribution of the quantity $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)}$.
-Note that the variance term in (\ref{variance}) is equal to an aggregate version of the Fisher information matrix.
-The proof of such statement is beyond the scope of this paper.
-On the basis of (\ref{variance}), we provide a variance estimator as
-$$v^{(z)} = \frac{1}{C_k-1}\sum_{i=2}^{C_k}  \frac{N_{i_k}^{(z)}}{i-1} + \widehat{\theta}^{(z)},$$ 
-where $i_k$ is such that the $i_k$th patent corresponds to the $k$th couple. This estimator was used to compute the standard deviation in Table \ref{summary}.
-\subsubsection*{Test statistic}
-The test statistic used is a mean difference test statistic between $\widehat{\theta}^{(tec)}$ and  $\widehat{\theta}^{(sem)}$, where the formal expression can be found in (\ref{teststat}).
-We assume independence between both quantities and thus under the null hypothesis, we have that
-$$\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)} {\rightarrow} MN(0,V),$$
-where $V= \int (p + \theta^{(tec)})(1 - (p + \theta^{(tec)})) d\pi^{(tec)} (p) + \int (p + \theta^{(sem)})(1 - (p + \theta^{(sem)})) d\pi^{(sem)} (p)$ can be estimated by $\widehat{V} = v^{(sem)} + v^{(tec)}$.
-Then, we obtain that
-\begin{eqnarray}
-\label{teststat}
-A = \frac{\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)}}{\widehat{V}} \approx \mathcal{N} (0,1),
-\end{eqnarray}
-where $A$ is the mean difference test static.
 
@@
 
-\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
-
-A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics.
-Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
-\[
-\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
-\]
-It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields.
-We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
-\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}
-
-% eventually do stats on merging/splitting : distribution of kws overlaps in time ?
-
-\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time.
-Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
-\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes.
-\comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
-\label{fig:semanticflows}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-10 Docs/Papers/Technical/overleafv2/main_v1.tex
slides_seminar

--- 2018-11-10 Docs/Papers/Technical/overleafv2/main.tex
@@
 
-\documentclass[10pt,A4]{article}
+\documentclass[10pt,A4,draft]{article}
 \usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
@@
 \lhead{
-\includegraphics[width=2.0in]{PLOS-submission-eps-converted-to.pdf}
+%\includegraphics[width=2.0in]{PLOS-submission-eps-converted-to.pdf}
 }
-\rhead{Classifying Patents Based on their Semantic Content\vspace{2mm}}
 \rfoot{\thepage}
@@
 \fancyfootoffset[L]{2.25in}
-\lfoot{\sf Bergeaud, Potiron and Raimbault, 2017}
-%\lfoot{}
+%\lfoot{\sf Bergeaud, Potiron and Raimbault, 2016 }
+\lfoot{}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[normalem]{ulem} % use normalem to protect \emph
-\newcommand\hl{\bgroup\markoverwith
-  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}
 
@@
 % writing utilities
-%%%%%
-% variable to include comments or not in the compilation ; set to 1 to include
-%\def \draft {1}
-\def \draft {0}
-
-\def \trackdiff {1}
-%\def \trackdiff {0}
 
@@
 \usepackage{xparse}
-\usepackage{ifthen}
 \DeclareDocumentCommand{\comment}{m o o o o}
-{\ifthenelse{\draft=1}{
-    \textcolor{red}{\textbf{C : }#1}
-    \IfValueT{#2}{\textcolor{blue}{\textbf{A1 : }#2}}
-    \IfValueT{#3}{\textcolor{ForestGreen}{\textbf{A2 : }#3}}
-    \IfValueT{#4}{\textcolor{red!50!blue}{\textbf{A3 : }#4}}
-    \IfValueT{#5}{\textcolor{Aquamarine}{\textbf{A4 : }#5}}
- }{}
+{%
+    \textcolor{red}{#1}
+    \IfValueT{#2}{\textcolor{blue}{#2}}
+    \IfValueT{#3}{\textcolor{ForestGreen}{#3}}
+    \IfValueT{#4}{\textcolor{red!50!blue}{#4}}
+    \IfValueT{#5}{\textcolor{Aquamarine}{#5}}
 }
@@
 % todo
-\newcommand{\todo}[1]{
-\ifthenelse{\draft=1}{\textcolor{red!50!blue}{\textbf{TODO : \textit{#1}}}}{}
-}
-
-% track changes
-\newcommand{\change}[1]{
-\ifthenelse{\trackdiff=1}{\hl{#1}}{#1}
-}
+\newcommand{\todo}[1]{\textcolor{red!50!blue}{\textbf{\textit{#1}}}}
 
@@
 \textbf\newline{
+%An Hypernetwork Approach to Measure Technological Innovation
+%Unveiling Endogenous Patterns of Technological Innovation
+%Extracting Endogenous Information from Patent Semantic Data
+%Patents Are Words: Extracting the Endogenous Information of Technological Innovation
+%Classifying patents based on patent semantic content
+%The Knowledge of Meaning Unveils the Meaning of Knowledge: Classifying Patents Based on their Semantic Content
 Classifying Patents Based on their Semantic Content
+% find a good title expressing both the multi-layer character and the novelty looking at semantic data
 }
@@
 \bigskip
-\bf{1} Paris School of Economics - EHESS and Bank of France, Paris, France
+\bf{1} Department of Economics, London School of Economics, London, UK
 \\
@@
 
-\bigskip
-%\newpage
+\newpage
 
@@
 \subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ format at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
+Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
 Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
@@
 Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}.
-The latest dump of the database in \texttt{Mongodb} format is available \change{at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}.} Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
+The latest dump of the database in \texttt{Mongodb} format is available at \url{http://37.187.242.99/files/public/USPTOredbook.gz}.
+%\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
+Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
 
@@
 Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
-\change{As reviewed previously, the use of co-occurrences is the usual way to construct a semantic network.
-Other hybrid technique such as bipartite semantic/authors networks, do not have the nice feature of relying solely on endogenous semantic information contained in data.}
 
@@
 Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations.
-This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining}
+This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/AnonymousAuthor1/PatentsMining}
 }
@@
 Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted, \change{which we shall denote $K_w$}, is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
+The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
 We choose to set this parameter to $K_w = 100,000$.
 We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-\change{This step has only very marginal effects on the nature of the final keywords but is necessary for computational purposes.} The filtration is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$, \change{where the formal definition can be found in (\ref{termhood})}.
-It is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
+This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
+A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$.
+The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
 Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
@@
 
-\begin{eqnarray}
-\label{termhood}
+\[
 t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
-\end{eqnarray}
+\]
 
@@
 For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter, \change{defined as $\theta_c$, and keep nodes with $c_{tech}(s) > \theta_c$.
-Likewise, edges with low weights correspond to rare co-occurrences and are considered to be noise.
-To account for this we define the threshold parameter for edges $\theta_w$, and we filter edges with a weight below $\theta_w$}, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
+We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$.
+In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
 To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
-\change{$\theta_w^{(0)}$ is thus a varying parameter interpreted as a noise threshold \emph{per patent}.} Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
+Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
 At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward.
@@
 We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size.
-\change{There is a priori no reason to choose any specific point among the different optimums.
-Consequently, we have tried the analysis with all the candidate values for $\theta_c$ and found that the results are the most reasonable when taking $\theta_c = 0.06$ (see Fig.~{\ref{fig:networksensitivity}}).}
+Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).
 
@@
 \centering
-%\includegraphics[width=\textwidth]{figures/Fig1}
+%\hspace{-2.5cm}
+%\includegraphics[width=0.45\textwidth,height=0.25\textheight]{figures/comnum_thetaw_2004.png}
+%\includegraphics[width=0.45\textwidth,height=0.25\textheight]{figures/comnum_vcount_pareto_2004.png}
+%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
 \caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} We plot the number of communities as a function of the edge threshold parameter $\theta_w$ for different values of the node threshold parameter $\theta_c$.
+\textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values.
 The maximum is roughly stable across $\theta_c$ (dashed red line).
@@
 \centering
-%\includegraphics[width=\textwidth]{figures/Fig2}
+%\includegraphics[width=0.75\textwidth]{figures/graph-filtered_2000-2004_kwLimit100000_dispth0_06_ethunit4_5e-05_LOWRES}
+%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
 \caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
@@
 \centering
-%\includegraphics[width=\textwidth]{figures/Fig3}
+%\includegraphics[width=0.9\textwidth]{figures/meancomsize}
+%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
 \caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
@@
 \hspace*{-2.5cm}
-%\includegraphics[width=\textwidth]{figures/Fig4}
+%\includegraphics[width=1.2\textwidth]{figures/all_raw_counts.png}
+%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
 \caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$,
@@
 Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-\change{The combination of citation network modeling by Stochastic Block Modeling with topic modeling was studied for scientific papers by }\cite{zhu2013scalable}\change{, outperforming previous link prediction algorithms.} \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
+\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
 Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
-
-\change{An other potential research development would be to further exploit the temporal structure of our dataset.
-Indeed, large progress have recently been made in complex network analysis of time-series data (see}~\cite{gao2017complex}\change{ for a review).
-For example, }\cite{gao2015multiscale}\change{develops a method to construct multiscale network from time series, which could in our case be a solution to identify structures in patents trajectories at different levels, and be an alternative to the single scale modularity analysis we use.}
 
@@
 \begin{figure}
-%\includegraphics[width=\textwidth]{figures/Fig5}
+%First row : semantic with relevant keywords only - all patents 
+%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_all_semcounts}
+%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_all_ts_semcounts}\\
+%Second row : patents with diversity $> 0$ (more than one class)}
+%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_positive_semcounts}
+%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_positive_ts_semcounts}
+%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
 \caption{
@@
 \begin{figure}
-%\includegraphics[width=\textwidth]{figures/Fig6}
+%\includegraphics[width=0.49\textwidth]{figures/originality.png}
+%\includegraphics[width=0.49\textwidth]{figures/generality.png}\\
+%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
 \caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
@@
 \centering
-%\includegraphics[width=\textwidth]{figures/Fig7}
+%\includegraphics[width=0.49\textwidth]{figures/norm-patents_all_density_semcounts.png}
+%\includegraphics[width=0.49\textwidth]{figures/norm-patents_all_ts_semcounts.png} \\
+%\includegraphics[width=0.49\textwidth]{figures/relative_all_density_semcounts.png}
+%\includegraphics[width=0.49\textwidth]{figures/relative_all_ts_semcounts.png} 
+%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
 \caption{
-\textbf{Intra-Classification overlaps.}
-(Left column) Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
-Right column) Corresponding mean time-series.
-(First row) Normalized overlaps.
-(Second row) Relative overlaps.}
+\textbf{Intra-classification overlaps.}
+\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
+\textit{(Right column)} Corresponding mean time-series.
+\textit{(First row)} Normalized overlaps.
+\textit{(Second row)} Relative overlaps.}
 \label{fig:intra-classif-overlap}
@@
 \begin{figure}[!ht]
-%\includegraphics[width=\textwidth]{figures/Fig8}
+%\includegraphics[width=0.49\textwidth]{figures/relative_interclassif_all_density_semcounts.png}
+%\includegraphics[width=0.49\textwidth]{figures/relative_interclassif_all_ts_semcounts.png}
+%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
 \caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series.
@@
 \centering
-%\includegraphics[width=\textwidth]{figures/Fig9}
+%\includegraphics[width=0.49\textwidth]{figures/simplemodularity}
+%\includegraphics[width=0.49\textwidth]{figures/overlappingmodularity}
+%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
 \caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability).
@@
 We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree, etc.).
-The availability of \change{this} data suggests new avenues for further research.
-\change{Linking our dataset with existing open ones can lead to various powerful developments.
-For example, using it together with the disambiguated inventor database provided by}~\cite{li2014disambiguation}\change{ could be a way to study semantic profiles of inventors, or of cities as inventor addresses are provided.
-The investigation of spatial diffusion of innovation between cities, which is a key component of Pumain's Evolutive Urban Theory}~\cite{pumain2010theorie}\change{, would be made possible.}
+Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...).
+The availability of these data suggests new avenues for further research.
 
@@
 \bibitem{martin2015}
-Dechezlepr{\~A}ªtre A, Martin R, Mohnen M.
+Dechezlepretre A, Martin R, Mohnen M.
 \newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
@@
 \bibitem{nltk}
-NLTK. Natural Language Toolkit, Stanford Univeristy; 2015.
+NLTK. Natural Language Toolkit, Stanford University; 2015.
 
@@
 
-\bibitem{zhu2013scalable}
-Zhu Y, Yan X, Getoor L, Moore C.
-\newblock Scalable text and link analysis with mixed-topic link models.
-\newblock In: Proceedings of the 19th ACM SIGKDD international conference on
-  Knowledge discovery and data mining. ACM; 2013. p. 473--481.
-
 \bibitem{iacovacci2015mesoscopic}
@@
 \newblock Nature communications. 2015;6.
-
-\bibitem{gao2017complex}
-Gao ZK, Small M, Kurths J.
-\newblock Complex network analysis of time series.
-\newblock EPL (Europhysics Letters). 2017;116(5):50001.
-
-\bibitem{gao2015multiscale}
-Gao ZK, Yang YX, Fang PC, Zou Y, Xia CY, Du M.
-\newblock Multiscale complex network for analyzing experimental multivariate
-  time series.
-\newblock EPL (Europhysics Letters). 2015;109(3):30005.
 
@@
 
-\bibitem{li2014disambiguation}
-Li GC, Lai R, D’Amour A, Doolin DM, Sun Y, Torvik VI, et~al.
-\newblock Disambiguation and co-authorship networks of the US patent inventor
-  database (1975--2010).
-\newblock Research Policy. 2014;43(6):941--955.
-
-\bibitem{pumain2010theorie}
-Pumain D.
-\newblock Une th{\'e}orie g{\'e}ographique des villes.
-\newblock Bulletin de la Soci{\'e}t{\'e} g{\'e}ographie de Li{\`e}ge.
-  2010;(55):5--15.
-
 \bibitem{akcigit2013mechanics}
@@
 \newblock Citeseer; 2013.
+
+\bibitem{regibeau2010}
+R{\'e}gibeau P, Rockett K.
+\newblock Innovation cycles and learning at the patent office: does the early
+  patent get the delay?
+\newblock Journal of Industrial Economics. 2010;58(2):222--246.
+\newblock Available from:
+  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
+
+A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics.
+Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
+\[
+\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
+\]
+It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields.
+We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
+\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}
+
+% eventually do stats on merging/splitting : distribution of kws overlaps in time ?
+
+\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time.
+Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}
+
+%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\hspace*{-2.5cm}
+\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
+\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes.
+\comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
+\label{fig:semanticflows}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-10 Docs/Papers/Technical/overleafv2/old.tex
slides_seminar

--- 2016-04-20 Docs/Papers/Technical/local/paper.tex
@@
-% Template for PLoS
-% Version 3.1 February 2015
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig." instead of "Figure".
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout or alignment
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% fixltx2e package for \textsubscript
-\usepackage{fixltx2e}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-\usepackage{rotating}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
-\begin{document}
-\vspace*{0.35in}
-
-% Title must be 250 characters or less.
-% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
-\begin{flushleft}
-{\Large
-\textbf\newline{An Hypernetwork Approach to Measure Technological Innovation - Submission to PLOS Journals}
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Antonin Bergeaud\textsuperscript{1,\Yinyang},
-Yoann Potiron\textsuperscript{2,\Yinyang},
-Juste Raimbault\textsuperscript{3,\Yinyang}
-\\
-\bigskip
-\bf{1} Department of Economics, London School of Economics, London, UK
-\\
-\bf{2} Department of Statistics, University of Chicago, Chicago, US
-\\
-\bf{3} UMR 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency a Insert current address of first author with an address update
-% \textcurrency b Insert current address of second author with an address update
-% \textcurrency c Insert current address of third author with an address update
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* le.corresponding@polytechnique.edu
-
-\end{flushleft}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% Please keep the abstract below 300 words
-\section*{Abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%\section*{Author Summary}
-
-\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Introduction}
-
-The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including data-mining and network analysis~\cite{newman2010networks} has shed a new light on the approach.
-With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation.
-As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
-in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.
-
-A consequent amount of research already proposed to use semantic networks to study technological domains.
-One of the first works to enhance the approach was~\cite{yoon2004text}, where the idea of visualizing keywords network was introduced and illustrated on a small technological domain.
-Semantic analysis has already proved its efficiency in various fields, such as~\cite{choi2014patent,fattori2003text} for technology studies, or~\cite{2015arXiv151003797G} in political science for example.
-We will also be interested in measures based on technological classification, as in~\cite{Youn:2015fk} where the study of the distribution of classes within patents leads to confirm the combinatory nature of the innovation process.
-Advanced citation-based measures have been proposed in order to gain an order of information extracted from the citation network~\cite{2015arXiv150907285A}, but we will stay to rather simple indicators concerning this network as we will cross it with other type of data.
-Concerning dynamic analysis, models of citation processes have been proposed and fit to data such as in~\cite{valverde2007topology}, and depending on temporal patterns we observe on features, we may propose to use dynamic models for network evolution.
-
-%%%%%%%%%%%%%%%%%%%%%
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Materials and Methods}
-
-\subsection*{Raw Data}
-
-% cite and describe datasets
-
-\subsection*{Semantic Network Construction}
-
-We first assign to a patent $p\in \mathcal{P}$ a set of significant keywords $K(p)\in \bigcup_{n\in \mathbb{N}} {\mathcal{A}^{\ast}}^n$, that are precisely extracted following a similar procedure to the one detailed in~\cite{chavalarias2013phylomemetic} :
-\begin{itemize}
-\item Text parsing and tokenizing.
-\item Part-of-speech tagging, normalization.
-\item Stem extraction and multi-stems constructions.
-\item Relevant multi-stems filtering.
-\end{itemize}
-
-The semantic network is then constructed by co-occurrences analysis : nodes are keywords, i.e.
-$V=\bigcup_{p\in\mathcal{P}}K(p)$, and edges represent co-occurrences : $E = \{(k,k') | \exists p \textrm{ s.t.
-} k, k' \in K(p)\}$.
-This specification aims to capture semantic communities that do necessarily have a thematic meaning and that should correspond to a specific domain, field, technology or technique.
-
-Text processing operations will be implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{nltk} which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations.
-Source code is openly available on the repository of the project\footnote{at \texttt{url}}.
-Steps one to three are directly done using built-in functions of the library.
-Step four needs a particular treatment that we propose as an extension of the original method for large corpuses, which is detailed in the following.
-
-\paragraph{Bootstrap on random sub-corpuses for relevance estimation}
-
-Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words.
-Let $K_w$ the maximal number of relevant keywords per patent.
-If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $k\cdot N$ keywords on the whole corpus (and take a fixed value $k=4)$, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of cooccurrences of the stem, compared to an uniform distribution within the whole corpus.
-More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as
-
-\[
-t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
-\]
-
-One issue arising when working with large corpuses is the square complexity for determining cooccurrences, that can be simplified at best to the sum of squared sizes of pre-relevant keywords for each patent.
-
-%% Convergence of bootstrap estimator / parameter values for estimation -> sensitivity analysis in supplementary information.
-
-%% construction of semantic nw from cooccurrences
-%  -> sensitivity analysis in supplementary info also
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semantic Communities Dynamics}
-
-% this section describes semantic communities reconstruction and their temporal dynamics
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Layer Structure Comparison}
-
-% comparison of techno classes / semantic communities / citation communities
-
-\cite{iacovacci2015mesoscopic}
-
-\subsection*{Unsupervised Data Mining}
+% old text from project that does not have much sense in the current version of the paper
 
@@
 \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-
-%\section*{Supporting Information}
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-
-%\section*{Acknowledgments}
-
-\nolinenumbers
-
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-\bibliographystyle{plos2015}
-\bibliography{../../../Biblio/patents}
-
-%%%%%%%%%%%%%%%%%%%%
-%%  Templates
-%%%%%%%%%%%%%%%%%%%%
-
-% For figure citations, please use "Fig." instead of "Figure".
-%\begin{figure}[h]
-%\caption{{\bf Figure Title first bold sentence}
-%Figure Caption}
-%\label{fig1}
-%\end{figure}
-
-%
-%
-%
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-%
-%
-
-%
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-
-%\begin{thebibliography}{10}
-%\bibitem{bib1}
-%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS.
-Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes.
-Mol Immunol.
-2014 Nov 22.
-pii: S0161-5890(14)00313-7.
-doi: 10.1016/j.molimm.2014.11.005
-
-%\bibitem{bib2}
-%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
-
-%\end{thebibliography}
-
-\end{document}

### 2018-11-10 Docs/Papers/Technical/overleafv2/figures.sh

@@ -1,0 +1,31 @@
+
+# fig 1
+montage figuresraw/comnum_thetaw_2004.png figuresraw/comnum_vcount_pareto_2004.png -tile 2x1 -geometry +5+0 figures/Fig1.png
+
+# fig 2
+#cp figuresraw/graph-filtered_2000-2004_kwLimit100000_dispth0_06_ethunit4_5e-05_LOWRES.png figures/Fig2.png
+
+# fig 3
+cp figuresraw/meancomsize.png figures/Fig3.png
+
+# fig 4
+cp figuresraw/all_raw_counts.png figures/Fig4.png
+
+# fig 5
+montage figuresraw/patentlevelorigs_all_semcounts.png figuresraw/patentlevelorigs_all_ts_semcounts.png figuresraw/patentlevelorigs_positive_semcounts.png figuresraw/patentlevelorigs_positive_ts_semcounts.png -tile 2x2 -geometry +5+50 figures/Fig5.png
+
+# fig 6
+#montage figuresraw/originality.png figuresraw/generality.png -tile 2x1 -geometry +5+0 figures/Fig6.png
+montage figuresraw/originality.png figuresraw/generality.png -tile 2x1 -geometry 1500x900 figures/Fig6.png
+
+# fig 7
+montage figuresraw/norm-patents_all_density_semcounts.png figuresraw/norm-patents_all_ts_semcounts.png figuresraw/relative_all_density_semcounts.png figuresraw/relative_all_ts_semcounts.png -tile 2x2 -geometry +5+50 figures/Fig7.png
+
+# fig 8
+#montage figuresraw/relative_interclassif_all_density_semcounts.png figuresraw/relative_interclassif_all_ts_semcounts.png -tile 2x1 -geometry +5+0 figures/Fig8.png
+montage figuresraw/relative_interclassif_all_density_semcounts.png figuresraw/relative_interclassif_all_ts_semcounts.png -tile 2x1 -geometry 1500x900 figures/Fig8.png
+
+# fig 9
+#montage figuresraw/simplemodularity.png figuresraw/overlappingmodularity.png -tile 2x1 -geometry +5+0 figures/Fig9.png
+montage figuresraw/simplemodularity.png figuresraw/overlappingmodularity.png -tile 2x1 -geometry 1500x900 figures/Fig9.png
+

### 2018-11-19 Docs/Papers/Technical/overleafv2/Slides.tex
slides

@@
 
-%\AtBeginSection[]
-%{
-%  \begin{frame}<beamer>
-%    \frametitle{Plan}
-%    \tableofcontents[currentsection]
-%  \end{frame}
-%}
+\AtBeginSection[]
+{
+  \begin{frame}<beamer>
+    \frametitle{Plan}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 %\AtBeginSubsection[]
@@
 
-\title[Patent Mining]{Classifying Patent Based on their Semantic Content \\ An empirical exploration into patents text mining}
+\title[Patent Mining]{Classifying Patent Based on their Semantic Content \\ An empirical exploration into patent text mining}
 \author[Bergeaud, Potiron, Raimbault]{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
@@
 \end{frame}
+\begin{frame}{Motivation}
+    \begin{figure}
+        \includegraphics[width=0.8\linewidth]{figures/patent_usa.png}
+        \caption{Log number of patent applications per capita at the USPTO. Source : USPTO}
+    \end{figure}
+\end{frame}
+\begin{frame}{Motivation}
+What are patents?
+\begin{itemize}
+    \item Property rights to an invention (novelty, non-obviousness and industrial applicability). Set the state of the art of a technology.
+    \item Classification system in technology fields (or classes).
+    \item Concept of ``Person having ordinary skill in the art'': an invention must be sufficiently disclosed in the description of the patent.
+    \item Different realities between countries/IP offices (USPTO, EPO, JPO, CNIPA...).
+\end{itemize}
 
+In practice, patent data are available in the form of a relational database.
+\end{frame}
+\begin{frame}{Motivation}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\linewidth]{figures/patent_abstract_ex.png}
+        \caption{Example of patent front page. Source : USPTO}
+    \end{figure}
+\end{frame}
+\begin{frame}{Patents and text-mining}
+    \begin{itemize}
+        \item Main usage: matching between patents and firms/inventors
+        \item Used in the search of prior-art/litigation
+        \item Technology mapping
+    \end{itemize}
+\end{frame}
 \begin{frame}{Why study patents ?}
-\justify
+%\justify
 
-$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge ; propagation of knowledge
-
-$\rightarrow$ Economics~\cite{griliches1998patent} : dynamics of innovation ; R{\&}D returns ; innovation at the core of endogenous growth theories~\cite{aghionhowitt1992}
-
+$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
+$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.
 \bigskip
@@
 \begin{itemize}
+\item \cite{griliches1998patent}: patent as an economic indicator
 \item \cite{Youn:2015fk} interaction between technological fields ; combinatorial nature of inventions
 \item \cite{2016arXiv160207928B} citation network analysis to detect emerging research front
-\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis
+\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis (remains limited to specific fields and time windows)
 \end{itemize}
@@
 
-%\begin{frame}{What we do}
-%\end{frame}
 \begin{frame}{A large scale semantic insight into USPTO database}
@@
 
-    \textit{Complement existing patent office classifications using patent semantic content}
+    \medskip
+
+    \textit{Complement existing patent office classifications using patent semantic content} \\
+    \textbf{Why?}: more endogenous, flexible and informative (?). And comparison with \emph{technological} classification to detect outliers.
 
@@
 
+    \medskip
+
     $\rightarrow$ \textit{An endogenous semantic classification is constructed for the full USPTO abstracts and titles, 1976-2012}
@@
 
-    $\rightarrow$ \textit{Information carried is complementary to the technological classification}
+    $\rightarrow$ \textit{Information carried in the semantic classification is complementary to the technological classification}
 
@@
 
-\begin{frame}{Patent data}
+%\begin{frame}{Patent data}
 
-\end{frame}
+%\end{frame}
 \begin{frame}{Descriptive statistics}
     % summary of our database ?
+
+    % We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.
+A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.
+The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013.
+When distributed by the year of application, the picture is slightly different.
+The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007.
+Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents.
+These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in [4].
+Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window.
+270,877 patents receive no citation during the next five years following application, 10% of patents receive only one citation and 1% of them receive more than 100 citations.
+A within class citation is defined as a citation between two patents sharing at least one common technological class.
+Following this definition, 84% of the citations are within class citations.
+14% of the citations are between two patents that share the exact same set of technological classes.
+
+    \textit{Summary statistics for the USPTO database between 1976 and 2013}
+
+    \begin{itemize}
+        \item 4,666,365 utility patents from 1976 to 2013
+        \item 70,000 in 1976 to 278,000 in 2013
+        \item 38,756,292 citation links (84\% of within-class citations)
+        \item 270,877 patents with no citations 5 years next to publication
+    \end{itemize}
+
+    Does this mean that innovation is 4 time larger en 2013 than in 1976... \alert{Not necessary}. Although definitely more specialized.
+\end{frame}
+\begin{frame}{Number of inventors}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\linewidth]{figures/inventors.png}
+        \caption{Evolution of number of researchers and productivity of R\&D. Source: Bloom et al. (2017)}
+    \end{figure}
+\end{frame}
+\begin{frame}{Inventors per patent}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\linewidth]{figures/inv_per_patent.png}
+        \caption{Average number of inventors per patent. Source: USPTO.}
+    \end{figure}
+
+    (It was 1.2 in 1900). Ideas are getting harder to find?
 \end{frame}
@@
 
-$\rightarrow$ 4391272 patents with text data ; dated by application date (current state of knowledge)
+$\rightarrow$ 4,666,365 patents with text data (abstract); dated by application date (current state of knowledge, differs from the granted date which implies review processes and an exogenous intervention)
 
@@
     \begin{itemize}
-        \item Termhood-based selection of a fixed number of keywords
-        \item Estimation on temporal moving windows
-        \item Filtering of network edge, with an additional exogenous control by technological class keyword concentration to filter nodes
+        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general})
+        % bias to keep fixed size of vocabulary ?
+        %  if variable = f(patents) -> arbitrary fixes a number of kws "per patent"; should them optimize regarding an exogenous criteria, which one ?
+        %  if fixed, this number varies, so the resolution of classes varies, thus larger classes more recently ?
+peak in sizes contradicts that, so should not capture this bias significantly (or structure is more important).
+        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 5y$ after sensitivity analysis)
+        \item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
+        % potential bias here -> would capture the exogenous classification system ? idem our results suggest that bias does not dominate results
+        \item Low sensibility to the size of the time windows for the network structure % in comparable lengths of course
     \end{itemize}
@@
 
-    \textit{Pareto optimization on cutoff parameters for modularity, size and number of communities}
+    \textit{Pareto optimization on cutoff parameters with the objectives of modularity, size and number of communities}
 
@@
 
-\begin{frame}{Semantic network visualization}
+\begin{frame}{Semantic network visualization (example for 2000-2004)}
+% TODO check date and parameters
    \centering
-    \includegraphics[height=\textheight]{figures/Fig2.png}
+    \includegraphics[height=0.85\textheight]{figures/Fig2.png}
 
@@
 \justify
+
+% discuss on naming class here
 
@@
     \textit{Fat-tail distribution of class size for both classification, closer to a power-law for semantic classes}
+    % different distribution shapes but comparable in order of magnitudes for both extremities -> important for the statistical analysis (?)
 
@@
     \textit{General increase in average invention specialization seen both for semantic and technological; semantic regime shift in 1996} 
-    % "change in the regime of specialization, the new regime being caused by more single-class patents"
+    % "change in the regime of specialization, the new regime being caused by more single-class patents" => confirms the idea of a new type of more specialized inventions
 
@@
 
-    \textit{Systematically lower originality and generality (citation-based measures) for the semantic classification (consistent with the higher modularity shown therafter)}
+    \textit{Systematically lower originality and generality (citation-based measures) for the semantic classification (consistent with the higher modularity shown thereafter).}
 
@@
 
+    % discussion on the fact that techno has been done a posteriori ? (for one part at least)
+
 \end{frame}
@@
 
-    \textit{Confirms the change in nature of inventions around 1996}
+    \textit{Constant then decreasing average overlap between technological and semantic classes; confirms the change in nature of inventions around 1996.}
+
+    \smallskip
+
+    $\rightarrow$ an impact of new information technologies ? (regarding knowledge production: from expert and contextualized to automatized search in references e.g.)
 
@@
 
-\begin{frame}{Modularity of classifications}
+\begin{frame}{Modularity of classifications} \label{slide:modularity}
+\hyperlink{slide:modularity_def}{\beamerbutton{Definition}}
+
    \centering
@@
 
-    \textit{Semantic classification is more significant regarding the structure of the citation network, both for single-class and multi-class modularities.}
+    \textit{Semantic classification is more significant regarding the structure of the citation network, both for single-class and multi-class modularities (confirmed statistically using a simple Stochastic Block Model).}
 
@@
 
-%\begin{frame}{Stochastic Block Modeling to evaluate consistency of classifications}
+\begin{frame}{Stochastic Block Modeling to evaluate consistency of classifications}
+\begin{itemize}
+    \item   We complete the analysis by developing a statistical model aiming at quantifying performance of both technological and semantic classification systems
+    \item Intuitively, we look at within class citations proportion (for both technological and semantic approaches)
+    \item Question: is the semantic classification better at predicting future within class citations? \\
+    $\longrightarrow$ short answer is \alert{yes}.
+\end{itemize} 
+\end{frame}
 
-    % tableau trop long, impossible a inserer
+\begin{frame}{Summary of outcomes}
+    \begin{itemize}
+        \item A clean redbook
+        \item Semantic and technological classification for each patent
+        \item Network based measure of centrality for each patent
+    \end{itemize}
 
-%\end{frame}
+    Most importance insight: semantic classification does carry some information beyond what the technological classification provides.
+\end{frame}
 
 \section{Conclusion}
-
-\begin{frame}{Discussion}
+\begin{frame}{Possible developments}
+\textbf{Direct}
+    \begin{itemize}
+        \item Look at the correlation between patent quality indicators and centrality indices.
+        \item Use patent-firm matching to study a \emph{firm-level} semantic network.
+        \item Extending the analysis to other patent offices (EPO/JPO).
+    \end{itemize}
+    \pause
+\textbf{Economic}
+    \begin{itemize}
+        \item Linking semantic measures to values of firms
+        \item Can semantic proximity helps understand M\&A?
+        \item Firms trajectories in relation to their life-cycle
+    \end{itemize}
+    \pause
+\textbf{Technology}
+\begin{itemize}
+    \item Measure of complementarity between technology?
+    \item Possible application to detection of emerging research fronts
+    \item An interactive exploration of semantic content?
+\end{itemize}
+\end{frame}
+\begin{frame}{Other projects}
     \justify
 
-    \textbf{Implications}
-
-     \smallskip
-
-    $\rightarrow$ Possible application to detection of emerging research fronts
-
-    \smallskip
-
-    $\rightarrow$ An interactive exploration of semantic content ?
-
-    \textbf{Developments (ongoing)}
-
-      \smallskip
-
-     $\rightarrow$ Application on the European patent database
+     \textbf{At the interface of geography and economics}
 
@@
 
-     \textbf{Possible developments}
+     \bigskip
+
+     \textbf{Possible developments in other disciplines}
 
@@
 
-     $\rightarrow$ Full-text mining and history of technology
+     $\rightarrow$ Full-text mining and history of technology \\
 
@@
 
+$\rightarrow$ A quantitative epistemology insight into the evolution of technology
+
+\medskip
+
+$\rightarrow$ Towards reflexive approaches in science and technology to ease technological transfer / foster the co-evolution between the two ?
+
+\bigskip
 \bigskip
 
-\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\smallskip
-\textbf{Raw database} at \texttt{http://dx.doi.org/10.7910/DVN/BW3ACK} and \textbf{Semantic classification database} at  \texttt{http:// dx.doi.org/10.7910/DVN/ZULMOY}\\\smallskip
+\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\medskip
+\textbf{Raw database} at \texttt{http://dx.doi.org/10.7910/DVN/BW3ACK}\\\medskip 
+\textbf{Semantic classification database} at  \texttt{http:// dx.doi.org/10.7910/DVN/ZULMOY}\\\medskip
 \textbf{Acknowledgments}: thanks to ISC-PIF for access to the computation infrastructure.
+
+\end{frame}
+
+\begin{frame}{Reserve slides}
+
+    \centering
+    \Huge
+    \textbf{Reserve slides}
+
+\end{frame}
+
+\begin{frame}{Definition of termhood}
+
+\end{frame}
+
+\begin{frame}{Patent measures}
+
+\end{frame}
+
+\begin{frame}{Definition of modularities} \label{slide:modularity_def}
+\hyperlink{slide:modularity}{\beamerbutton{Back}}
+
+    Directed simple modularity:
+    \[
+Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
+\]
+
+%with $A_{ij}$ the citation adjacency matrix (i.e.
+$A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not), $k_i^{in}=\left| I_i\right|$ (resp.
+$k_i^{out}= \left|\tilde{I}_i \right|$) in-degree (resp.
+out-degree) of patents (i.e.
+the number of citations made by the $i$th patent to others and the number of citations received by the $i$th patent).
+$Q_d$ can be defined for each of the two classification systems: $z \in \{tec, sem\}$.
+If $z=tec$, $c_i$ is defined as the main patent class, which is taken as the first class whereas if $z=sem$, $c_i$ is the class with the largest probability.
+
+\bigskip
+
+Multi-class modularity:
+
+\[
+\displaystyle Q_{ov}^{(z)} = \frac{1}{N_P} \sum_{c = 1}^{N^{(z)}} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,c}^{out}k_i^{out}\beta_{j,c}^{in}k_j^{in}}{N_P}\right],
+\]
+where
+\[
+ \beta_{i,c}^{out} =   \frac{1}{N_P} \displaystyle \sum_j F(p_{ic},p_{jc}) \text{ and } \beta_{j,c}^{in} =  \frac{1}{N_P} \displaystyle \sum_i F(p_{ic},p_{jc}).
+\]
 

### 2018-11-27 Models/Database/simpleexport.sh
.

@@ -1,0 +1,16 @@
+
+# auth params
+USER=`cat user`
+PWD=`cat psswd`
+AUTHDB=`cat authdb`
+PORT=`cat port`
+
+DB='redbook'
+COLLECTION='raw'
+
+QUERYFILE=$1
+#FIELDS='{"abstract":1,"title":1,"id":1,"year":1,"grant_date":1}'
+FIELDS="abstract,title,id,year"
+
+mongoexport -u $USER -p $PWD --authenticationDatabase $AUTHDB --port $PORT --db $DB --collection $COLLECTION -f $FIELDS --queryFile $QUERYFILE --limit 2 
+

### 2018-11-27 Docs/Papers/Technical/overleafv2/S2_Text.tex

--- 2018-11-10 Docs/Papers/Technical/overleafv2/bdf_wp.tex
@@
-\documentclass[article]{article}%
-\usepackage{eurosym}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{graphicx}
-\usepackage{graphics}
-\usepackage{natbib}
-\usepackage[export]{adjustbox}%
-\setcounter{MaxMatrixCols}{30}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage[section]{placeins}
-\usepackage{geometry}
-\usepackage{setspace}
-\usepackage{lscape}
-\usepackage{hyperref}
-\usepackage{booktabs,caption}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage[FIGTOPCAP, hang]{subfigure}
-\usepackage{floatrow}
-\floatsetup[table]{capposition=top}
-\floatsetup[figure]{capposition=top}
+\input{si.tex}
 
-\def\tablename{TABLE}
-\def\figurename{FIGURE}
+\section*{S2 Text : Data collection and Workflow}
 
-\newcommand{\fignote}[2]{\begin{center}\parbox[c]{#1}{\footnotesize #2} \end{center}}
-\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
-
-\hypersetup{
-    colorlinks, linkcolor={dark-red},
-    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
-}
-\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
-\newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-
-%Yoann's commands
-\newcommand{\reels}{\mathbb{R}}
-\newcommand{\naturels}{\mathbb{N}}
-\newcommand{\relatifs}{\mathbb{Z}}
-\newcommand{\rat}{\mathbb{Q}}
-\newcommand{\complex}{\mathbb{C}}
-\newcommand{\esp}{\mathbb{E}}
-\newcommand{\proba}{\mathbb{P}}
-\newcommand{\var}{\operatorname{Var}}
-\newcommand{\cov}{\operatorname{Cov}}
-\newcommand{\Tau}{\mathrm{T}}
-
-\begin{document}
-
-\title{Classifying Patents Based on their Semantic Content\thanks{Addresses: Bergeaud: Banque de France (antonin.bergeaud@banque-france.fr), Potiron: Keio University, Raimbault: ISC-PIF }}
-\vskip.5em 
-\author{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
-\smallskip
-\date{June 2018}
-\maketitle
-
-\begin{abstract}
-In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach.
-This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward.
-To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly.
-We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes.
-Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model.
-This suggests that our method is a useful tool to extract endogenous information.
-\end{abstract}
-
-\newpage
-
-\section{Introduction}
-
-Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \citet{aghionhowitt1992} and \citet{romer1990}.
-\citet{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation.
-Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\citealt{Hall2001}) have opened the way to a very wide range of analysis (see among many recent examples \citealt{bloom2013}, \citealt{aghion2018a} or \citealt{aghion2018b}).
-Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review.
-Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \citet{Youn:2015fk}.
-With methods such as citation dynamics modeling discussed in~\citet{2013arXiv1310.8220N} or co-authorship networks analysis in~\citet{2014arXiv1402.7268S}, a large body of the literature such as~\citet{sorenson2006complexity} or~\citet{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters.
-Finally, \citet{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.
-
-Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies.
-But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \citealt{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share.
-Curiously, and in spite of the large number of studies that analyze interactions across technologies~\citet{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g.
-~\citealt{AAKnetwork2016}).
-
-In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it.
-In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract.
-Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach.
-The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\citealt{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence).
-One can for instance consider the case of the word \textit{optic}.
-Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of transistor design and electro-optic.
-This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.
-
-Previous research has already proposed to use semantic networks to study technological domains and detect novelty.
-~\citet{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain.
-The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \citet{park2014semantic} and \citet{yoon2011detecting}.
-More closely related to our methodology,~\citet{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation.
-Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\citealt{choi2014patent} and~\citealt{fattori2003text}) and in political science (e.g.~\citealt{2015arXiv151003797G}).
-
-Building on such previous research, we make several contributions by fulfilling some shortcomings of existing studies, such as for example the use of frequency-selected single keywords.
-First of all, we develop and implement a novel fully-automatized methodology to classify patents according to their semantic abstract content, which is to the best of our knowledge the first of its type.
-This includes the following refinements for which details can be found in Section \ref{keywords}: (i) use of multi-stems as potential keywords; (ii) filtering of keywords based on a second-order (co-occurrences) relevance measure and on an external independent measure (technological dispersion); (iii) multi-objective optimization of semantic network modularity and size.
-The use of all this techniques in the context of semantic classification is new and essential from a practical perspective.
-
-Furthermore, most of the existing studies rely on a subsample of patent data, whereas we implement it on the full US Patent database from 1976 to 2013.
-This way, a general structure of technological innovation can be studied.
-We draw from this application promising qualitative stylized facts, such as a qualitative regime shift around the end of the 1990s, and a significant improvement of citation modularity for the semantic classification when comparing to the technological classification.
-These thematic conclusions validate our method as a useful tool to extract endogenous information, in a complementary way to the technological classification.
-
-Finally, the statistical model introduced in Section \ref{statisticalmodel} seems to indicate that patents tend to cite more similar patents in the semantic network  when fitted to data.
-In particular, this propensity is shown to be significantly bigger than the corresponding propensity for technological classes, and this seems to be consistent over time.
-On the account of this information, we believe that patent officers could benefit very much from looking at the semantic network when considering potential citation candidates of a patent in review.
-
-The paper is organized as follows.
-Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process.
-Section \ref{keywords} explains the construction of the semantic classes.
-Section \ref{result} tests their relevance by providing exploratory results.
-Finally, section \ref{discussion} discusses potential further developments and conclude.
-More details, including robustness checking, figures and technical derivations can be found in the Appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background \label{data}}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013.
-A clearer definition of utility patent is given in Appendix \ref{app:utility}.
-Also, additional information on how to correctly exploit patent data can be found in \citet{Hall2001} and \citet{lerner2015use}.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{An existing classification: the USPC system}
-
-Each USPTO patent is associated with a non-empty set of technological classes and subclasses.
-There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system.
-While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention.
-A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass.
-At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes.
-When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A bibliographical network between patents: citations \label{sub:citation}}
-
-As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art.
-They therefore indicate the past knowledge which relates to the patented invention.
-Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent.
-One can consult~\citet{oecdpatentmanual} for more details about this.
-Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\citealt{martin2015}).
-Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves.
-From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations).
-We can thus build a complete network of citations that we will use later on in the analysis.
-
-Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years.
-This distribution is highly skewed, the $95^{th}$ percentile is 21 years.
-We also report 164,000 citations with a negative time lag.
-This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others.
-
-In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years.
-We impose this restriction for two reasons.
-First, the number of citations received peaks 4-5 years after application.
-Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones.
-As we are restricting to citations received no later than 5 years after the application date, this effect will only affect patents with an application date after 2007.
-
-%%%%%%%%%%%%%%%%%%
-\subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ format at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
-Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
-In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\citealt{Adams2010text}).
-The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).
-
-We construct from raw data a unified database.
-Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976.
-Detailed procedure of data collection, parsing and consolidation are available in Appendix \ref{app:datacollection}.
-The latest dump of the database in \texttt{Mongodb} format is available at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}.
-Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
-
-We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013.
-When distributed by the year of application, the picture is slightly different.
-The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007.
-Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents.
-These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\citet{Hall2001}.
-Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window.
-270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations.
-A within class citation is defined as a citation between two patents sharing at least one common technological class.
-Following this definition, 84\% of the citations are within class citations.
-14\% of the citations are between two patents that share the exact same set of technological classes.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Towards a Complementary Classification}
-
-Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\citet{tseng2007text}.
-The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications.
-The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\citealt{abbas2014literature} for a review).
-Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}.
-As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored.
-One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples.
-Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies.
-Indeed, as argued in~\citet{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.
-
-Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}).
-Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
-As reviewed previously, the use of co-occurrences is the usual way to construct a semantic network.
-Other hybrid technique such as bipartite semantic/authors networks, do not have the nice feature of relying solely on endogenous semantic information contained in data.
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Semantic Classification Construction \label{keywords}}
-
-In this section, we describe methods and empirical analysis leading to the construction of semantic network and the corresponding classification.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords extraction}
-\label{keywordsextraction}
-
-Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
-$K(p)$ are extracted through a similar procedure as the one detailed in~\citet{chavalarias2013phylomemetic}: 
-\begin{enumerate}
-\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).
-
-\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.
-
-\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens.
-At this point the abstract text is reduced to a set of stems and their grammatical functions.
-\item Multi-stems construction: these are the basic semantic units used in further analysis.
-They are constructed as groups of successive stems in a sentence which satisfies a simple grammatical function rule.
-The length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives.
-We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
-\end{enumerate}
-
-Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library for most of above operations.
-This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining}
-}
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords relevance estimation}
-\label{keywords_est}
-\paragraph{Relevance definition}
-
-Following the heuristic in~\citet{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted, which we shall denote $K_w$, is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
-We choose to set this parameter to $K_w = 100,000$.
-We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-This step has only very marginal effects on the nature of the final keywords but is necessary for computational purposes.
-The filtration is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$, where the formal definition can be found in (\ref{termhood}).
-It is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
-Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
-More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together.
-The \emph{termhood} score $t_i$ is defined as
-
-\begin{eqnarray}
-\label{termhood}
-t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
-\end{eqnarray}
-
-\paragraph{Moving window estimation}
-The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past.
-Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$.
-Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents.
-This way, we will obtain semantic classes which are exploitable on a $T_0$ time span.
-For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}.
-In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}.
-Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
-Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Construction of the semantic network}
-\label{construction}
-
-We keep the set of most relevant keywords $\mathcal{K}_W$ and obtain their co-occurrence matrix as defined in Section \ref{keywords_est}.
-This matrix can be directly interpreted as the weighted adjacency matrix of the semantic network.
-At this stage, the topology of raw networks does not allow the extraction of clear communities.
-This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g.
-\texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant.
-We therefore introduce an additional measure to correct the network topology: the concentration of keywords across technological classes, defined as:
-
-$$c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2},$$
-
-where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes.
-The higher $c_{tech}$, the more specific to a technological class the node is.
-For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter, defined as $\theta_c$, and keep nodes with $c_{tech}(s) > \theta_c$.
-Likewise, edges with low weights correspond to rare co-occurrences and are considered to be noise.
-To account for this we define the threshold parameter for edges $\theta_w$, and we filter edges with a weight below $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
-To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
-$\theta_w^{(0)}$ is thus a varying parameter interpreted as a noise threshold \emph{per patent}.
-Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
-At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward.
-Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities.
-We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size.
-There is a priori no reason to choose any specific point among the different optimums.
-Consequently, we have tried the analysis with all the candidate values for $\theta_c$ and found that the results are the most reasonable when taking $\theta_c = 0.06$ (see Figure {\ref{fig:networksensitivity}}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\caption{Sensitivity analysis of network community structure to filtering parameters.}
-\includegraphics[width=\textwidth]{figures/Fig1.png}
-\floatfoot{\textbf{Note:} This figure considers a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} plots the number of communities as a function of the edge threshold parameter $\theta_w$ for different values of the node threshold parameter $\theta_c$.
-The maximum is roughly stable across $\theta_c$ (dashed red line).
-\textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
-\label{fig:networksensitivity}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/Fig2}
-\caption{An example of semantic network visualization.}
-\floatfoot{\textbf{Note:}  This figure shows the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
-The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available as Supplementary Material.}
-\label{fig:rawnetwork}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Characteristics of Semantic Classes}
-\label{characteristics}
-For each year $t$, we define as $N^{(sem)}_t$ the number of semantic classes which have been computed by clustering keywords from patents appeared during the period $\big[ t-T_0, t \big]$ (we recall that we have chosen $T_0=4$).
-Each semantic class $k =  1, \cdots, N^{(sem)}_t$ is characterized by a set of keywords $K(k,t)$ which is a subset of $\mathcal{K}_W$ selected as described in Section \ref{keywordsextraction} to Section \ref{construction}.
-The cardinal of $K(k, t)$ distribution across each semantic class $k$ is highly skewed with a few semantic classes containing over $1,000$ keywords, most of them with roughly the same number of keywords.
-In contrast, there are also many semantic classes with only two keywords.
-There are around 30 keywords by semantic class on average and the median is 2 for any $t$.
-Figure \ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/Fig3}
-\caption{Keywords by semantic class}
-\floatfoot{\textbf{Note:}  This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$ from $t=1980$ to $t=2007$.}
-\label{fig:mean_K}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph*{Title of semantic classes}
-USPC technological classes are defined by a title and a highly accurate definition which help retrieve patents easily.
-The title can be a single word (e.g.: class 101: ``Printing'') or more complex (e.g.: class 218: ``High-voltage switches with arc preventing or extinguishing devices'').
-As our goal is to release a comprehensive database in which each patent is associated with a set of semantic classes, it is necessary to give an insight on what these classes represent by associating a short description or a title as in~\cite{tseng2007text}.
-In our case, such description is taken as a subset of keywords taken from $K(k,t)$.
-For the vast majority of semantic classes that have less than 5 keywords, we decide to keep all of theses keywords as a description.
-For the remaining classes which feature around 50 keywords on average, we rely on the topological properties of the semantic network.~\cite{yang2000improving} suggest to retain only the most frequently used terms in $K(k,t)$.
-Another possibility is to select 5 keywords based on their network centrality with the idea that very central keywords are the best candidates to describe the overall idea captured by a community.
-For example, the largest semantic class in 2003-2007 is characterized by the keywords: \texttt{Support Packet; Tree Network; Network Wide; Voic Stream; Code Symbol Reader}.
-
-\paragraph*{Size of technological and semantic classes} 
-We consider a specific window of observations (for example 2000-2004), and we define $Z$ the number of patents which appeared during that time window.
-For each patent $i=1, \cdots, Z$ we associate a vector of probability where each component $p_{ij}^{(sem)} \in \big[ 0,1 \big]$, with  $j = 1, \cdots, N{(sem)}$ and where\footnote{When there is no room for confusion, we drop the subscript $t$ in $N_t^{(sem)}$.}
-$$\displaystyle \sum_{j=1}^{N^{(sem)}} p_{ij}^{(sem)} = 1.$$ On average across all time windows, a patent is associated to 1.8 semantic classes with a positive probability.
-Next we define the size of a semantic class as $$S_j^{(sem)} = \displaystyle \sum_{i=1}^Z p_{ij}^{(sem)}.$$
-Correspondingly, we aim to provide a consistent definition for technological classes.
-For that purpose, we follow the so-called ``fractional count'' method, which was introduced by the USPTO and consists in dividing equally the patents between all the classes they belong to.
-Formally, we define the number of technological classes as
-$N^{(tec)}$  (which is not time dependent contrary to the semantic case) and for $j = 1, \cdots, N^{(tec)}$ the corresponding matrix of probability is defined as
-\[
- p_{ij}^{(tec)} = \frac{B_{ij}}{\displaystyle \sum_{k=1}^{N^{(tec)}}{B_{ik}}},
-\]
-where  $B_{ij}$ equals $1$ if the $i$th patent belongs to the $j$th technological class and $0$ if not.
-When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix.
-Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Figure \ref{fig:class-sizes}.
-This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=\textwidth]{figures/Fig4}
-\caption{Sizes of classes.} 
-\floatfoot{\textbf{Note:}  This figure plots for each year $t = 1980$ to $t =2007$, the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$, from the biggest to the smallest.
-The formal definition of size can be found in Section \ref{characteristics}.
-Each color corresponds to one specific year.
-Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications.
-This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}.
-Over time, curves are translated and levels of hierarchy stays roughly constant.}
-\label{fig:class-sizes}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Potential Refinements of the Method}
-
-Our semantic classification method could be refined by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method (e.g.~\cite{blei2003latent}), already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a field rather than distant technological recombination.
-Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation).
-Also, depending on the level of orthogonality with our classification, it can potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.
-
-Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis.
-Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-The combination of citation network modeling by Stochastic Block Modeling with topic modeling was studied for scientific papers by \cite{zhu2013scalable}, outperforming previous link prediction algorithms.
-\citet{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
-Furthermore, is has recently been shown that measures of multilayer network projections induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
-
-An other potential research development would be to further exploit the temporal structure of our dataset.
-Indeed, large progress have recently been made in complex network analysis of time-series data (see~\citealt{gao2017complex} for a review).
-For example, \cite{gao2015multiscale} develops a method to construct multiscale network from time series, which could in our case be a solution to identify structures in patents trajectories at different levels, and be an alternative to the single scale modularity analysis we use.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Results \label{result}}
-%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present some key features of our resulting semantic classification showing both complementary and differences with the technological classification.
-We first present several measures derived from this semantic classification at the patent level: Diversity, Originality, Generality (Section \ref{subsec:orig-gene}) and Overlapping (Section \ref{subsec:overlaps}).
-We then show that the two classifications show highly
-different topological measures and strong statistical evidence that they feature a different model (Sections \ref{citationmodularity} and \ref{statisticalmodel}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Patent Level Measures}  \label{subsec:orig-gene}
-
-Given a classification system (technological or semantic classes), and the associated probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ (that were defined in Section \ref{characteristics}), one can define a patent-level diversity measure as one minus the Herfindhal concentration index on $p_{ij}$  by
-
-\[
-D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}.
-\]
-
-We show in Figure \ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series.
-This is carried with two different settings, namely including/not including patents with zero diversity (i.e.
-single class patents).
-We call other patents ``complicated patents'' in the following.
-First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes.
-More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization.
-This is a well-known stylized fact as documented in~\citet{ARCHIBUGI199279}.
-Furthermore, a qualitative regime shift on semantic classification occurs around 1996.
-This can be seen whether or not we include patents with zero diversity.
-The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease.
-This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity.
-It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents.
-
-More commonly used in the literature are the measures of originality and generality.
-These measures follow the same idea than the above-defined diversity in quantifying the diversity of classes (whether technological or semantic) associated with a patent.
-But instead of looking at the patent's classes, they consider the classes of the patents that are cited or citing.
-Formally, the originality $O_i$ and the generality $G_i$ of a patent $i$ are defined as
-\[
-O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2} \text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2},
-\]
-
-where $z \in \{tec, sem\}$, $I_i$ denotes the set of patents that are cited by the $i$th patent within a five year window (i.e.
-if the $i$th patent appears at year $t$, then we consider patents on $[t-T_0, t]$) when considering the originality and $\tilde{I}_i$ the set of patents that cite patent $i$ after less than five years (i.e.
-we consider patents on $[t ,t + T_0]$) in the case of generality.
-Note that the measure of generality is forward looking in the sense that $G_i^{(z)}$ used information that will only be available 5 years after patent applications.
-Both measures are lower on average based on semantic classification than on technological classification.
-Figure \ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Fig5}
-\caption{Patent level diversities.} 
-\floatfoot{\textbf{Note:}  Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$).
-The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e.
-patents with diversity greater than 0).}
-\label{fig:patent-level-orig}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Fig6}
-\caption{Patent level originality and generality} 
-\floatfoot{\textbf{Note:}  Originality (left hand side) and generality (right hand side) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
-}
-\label{fig:orig-gene}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classes overlaps} \label{subsec:overlaps}
-
-A proximity measure between two classes can be defined by their overlap in terms of patents. 
-Such measures could for example be used to construct a metrics between semantic classes.
-Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{bloom2013}.
-Formally, recalling the definition of $\left(p_{ij}\right)$ as the probability for the $i$th patent to belong to the $j$th class and $N_P$ as the number of patents it writes
-
-\begin{eqnarray}
-\label{overlap}
-Overlap_{jk} = \frac{1}{N_P}\cdot \sum_{i=1}^{N_P} p_{ij} p_{ik}. 
-\end{eqnarray}
-
-The overlap is normalized by patent count to account for the effect of corpus size: by convention, we assume the overlap to be maximal when there is only one class in the corpus.
-A corresponding relative overlap is computed as a set similarity measure in the number of patents common to two classes A and B, given by $o(A,B)=2\cdot \frac{\left|A\cap B\right|}{\left|A\right| + \left|B\right|}$.
-
-\paragraph{Intra-classification overlaps}
-
-The study of distributions of overlaps inside each classification, i.e.
-between technological classes and between semantic classes separately, reveals the structural difference between the two classification methods, suggesting their complementary nature.
-Their evolution in time can furthermore give insights into trends of specialization.
-We show in Figure \ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications.
-The technological classification globally always follow a decreasing trend, corresponding to more and more isolated classes, i.e.
-specialized inventions, confirming the stylized fact obtained in previous subsection.
-For semantic classes, the dynamic is somehow more intriguing and supports the story of a qualitative regime shift suggested before.
-Although globally decreasing as technological overlap, normalized (resp.
-relative) mean overlap exhibits a peak (clearer for normalized overlap) culminating in 1996 (resp.
-1999).
-Looking at normalized overlaps, classification structure was somewhat stable until 1990, then strongly increased to peak in 1996 and then decrease at a similar pace up to now.
-Technologies began to share more and more until a breakpoint when increasing isolation became the rule again.
-An evolutionary perspective on technological innovation~\cite{ziman2003technological} could shed light on possible interpretations of this regime shift: as species evolve, the fitness landscape first would have been locally favorable to cross-insemination, until each fitness reaches a threshold above which auto-specialization becomes the optimal path.
-It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation.
-%This interpretation is consistent with the dynamics of semantic flows presented in Figure \ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\textwidth]{figures/Fig7}
-\caption{Intra-Classification overlaps}
-\floatfoot{\textbf{Note:}  Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale) and corresponding mean time-series.
-(First row) Normalized overlaps.
-(Second row) Relative overlaps.}
-\label{fig:intra-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Inter-classification overlaps}
-
-Overlaps \emph{between} classifications are defined as in (\ref{overlap}), but with $j$ standing for the $j$th technological class and $k$ for the $k$th semantic class: $p_{ij}$ are technological probabilities and $p_{ik}$ semantic probabilities.
-They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Figure \ref{fig:inter-classif-overlap}.
-Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease.
-Although difficult to interpret directly, this stylized fact clearly unveils a change in the \emph{nature} of inventions, or at least in the relation between content of inventions and technological classification.
-As the tipping point is at the same time as the ones observed in the previous section and since the two statistics are different, it is unlikely that this is a mere coincidence.
-Thus, these observations could be markers of a hidden underlying structural changes in processes.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\includegraphics[width=\textwidth]{figures/Fig8}
-\caption{Distribution of relative overlaps between classifications.} 
-\floatfoot{\textbf{Note:}  Distribution of overlaps at all time steps and corresponding mean time-series. The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
-\label{fig:inter-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Citation Modularity}
-\label{citationmodularity}
-
-An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}.
-The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\citealt{AAKnetwork2016}).
-This section studies empirically modularities of the citation network regarding the different classifications.
-To corroborate the obtained results, we propose to look at a more rigorous framework in Section \ref{statisticalmodel}.
-Modularity is a simple measure of how communities in a network are well clustered (see \cite{clauset2004finding} for the accurate definition).
-Although initially designed for single-class classifications, this measure can be extended to the case where nodes can belong to several classes at the same time, in our case with different probabilities as introduced in \cite{nicosia2009extending}.
-The simple directed modularity is given in our case by
-\[
-Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
-\]
-with $A_{ij}$ the citation adjacency matrix (i.e.
-$A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not), $k_i^{in}=\left| I_i\right|$ (resp.
-$k_i^{out}= \left|\tilde{I}_i \right|$) in-degree (resp.
-out-degree) of patents (i.e.
-the number of citations made by the $i$th patent to others and the number of citations received by the $i$th patent).
-$Q_d$ can be defined for each of the two classification systems: $z \in \{tec, sem\}$.
-If $z=tec$, $c_i$ is defined as the main patent class, which is taken as the first class whereas if $z=sem$, $c_i$ is the class with the largest probability.
-
-Multi-class modularity in turns is given by
-
-\[
-\displaystyle Q_{ov}^{(z)} = \frac{1}{N_P} \sum_{c = 1}^{N^{(z)}} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,c}^{out}k_i^{out}\beta_{j,c}^{in}k_j^{in}}{N_P}\right],
-\]
-where
-\[
- \beta_{i,c}^{out} =   \frac{1}{N_P} \displaystyle \sum_j F(p_{ic},p_{jc}) \text{ and } \beta_{j,c}^{in} =  \frac{1}{N_P} \displaystyle \sum_i F(p_{ic},p_{jc}).
-\]
-We take $F(p_{ic},p_{jc}) = p_{ic}\cdot p_{jc}$ as suggested in \cite{nicosia2009extending}.
-Modularity is an aggregated measure of how the network deviates from a null model where links would be randomly made according to node degree.
-In other words it captures the propensity for links to be inside the classes.
-Overlapping modularity naturally extends simple modularity by taking into account the fact that nodes can belong simultaneously to many classes.
-We document in Figure \ref{fig:modularities} both simple and multi-class modularities over time.
-For simple modularity, $Q_d^{(tec)}$ is low and stable across the years whereas $Q_d^{(sem)}$ is slightly greater and increasing.
-These values are however low and suggest that single classes are not sufficient to capture citation homophily.
-Multi-class modularities tell a different story.
-First of all, both classification modularities have a clear increasing trend, meaning that they become more and more adequate with citation network.
-The specializations revealed by both patent level diversities and classes overlap is a candidate explanation for this growing modularities.
-Secondly, semantic modularity dominates technological modularity by an order of magnitude (e.g.
-0.0094 for technological against 0.0853 for semantic in 2007) at each time.
-This discrepancy has a strong qualitative significance.
-Our semantic classification fits better the citation network when using multiple classes.
-As technologies can be seen as a combination of different components as shown by~\cite{Youn:2015fk}, this heterogeneous nature is most likely better taken into account by our multi-class semantic classification.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\textwidth]{figures/Fig9}
-\caption{Temporal evolution of semantic and technological modularities of the citation network.} 
-\floatfoot{\textbf{Note:}  Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability) and Multi-class modularity, computed following~\citet{nicosia2009extending} }
-\label{fig:modularities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistical Model}
-\label{statisticalmodel}
-In this section, we develop a statistical model aimed at quantifying performance of both technological and semantic classification systems.
-In particular, we aim at corroborating findings obtained in Section \ref{citationmodularity}.
-The mere difference between this approach and the citation modularity approach lies in the choice of the underlying model, and the according quantities of interest.
-In addition for the semantic approach, we want to see if when restricting to patents with higher probabilities to belong to a class, we obtain better results.
-To do that, we choose to look at within class citations proportion (for both technological and semantic approaches).
-We provide two obvious reasons why we choose this.
-First, the citations are commonly used as a proxy for performance as mentioned in Section \ref{citationmodularity}.
-Second, this choice is ``statistically fair'' in the sense that both approaches have focused on various goals and not on maximizing directly the within class proportion.
-Nonetheless, the within class proportion is too sensitive to the distribution of the shape of classes.
-For example, a dataset where patents for each class account for 10\% of the total number of patents will mechanically have a better within class proportion than if each class accounts for only 1\%.
-Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed.
-This effort resembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth.
-Furthermore, the parameters fitted here can have a direct interpretation as a citation probability.
-
-We need to introduce and recall some notations.
-We consider a specific window of observations $\big[t- T_0, t \big]$, and we define $Z$ the number of patents which appeared during that time window.
-We let $t_1, \cdots, t_Z$ their corresponding appearance date by chronological order, which for simplicity are assumed to be such that $t_1 < \cdots < t_Z$.
-For each patent $i=1, \cdots, Z$ we consider $C_i$ the number of distinctive couples \{cited patent, cited patent's class\} made by the $i$th patent (for instance if the $i$th patent has only made one citation and that the cited patent is associated with three classes, then $C_i = 3$).
-Let $z \in \{tec, sem\}$, we define $N_{i}^{(z)}$  the number of patents associated to at least one of the $i$th classes at time $t_{i-1}$.
-For $l = 1, \cdots, C_i$ we consider the variables $B_{l,i}$, which equal $1$ if the cited patent's class is also common to the $i$th patent.
-We assume that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-where the parameter $0 \leq \theta^{(z)} \leq 1$ indicates the propensity for any patent to cite patents of its own technological or semantic class.
-When $\theta^{(z)} = 0$, the probability of citing patents from its own class is simply $N_{i}^{(z)}(i-1)^{-1}$, which corresponds to the observed proportion of patents which belong to at least one of the $i$th patent's classes.
-Thus this corresponds to the estimated probability of citing one patent if we assume that the probability of citing any patent $k=1, \cdots, i-1$ is uniformly distributed, which could be a reasonable assumption if classes were assigned randomly and independently from patent abstract contents.
-Conversely if $\theta^{(z)} = 1$, we are in the case of a model where there are 100\% of within class citations.
-A reasonable choice of $\theta^{(z)}$ lies between those two extreme values.
-Finally, we assume that the number of distinctive couples $C_i$ are a sequence of independent and identically distributed random variables following the discrete distribution $C$, and also independent from the other quantities.
-
-We estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding maximum likelihood estimator (MLE) $\hat{\theta}^{(z)}$.
-The likelihood function, along with the standard deviation expression and details about the test, can be found in \ref{app:stat}.
-The fitted values, standard errors and p-values corresponding to the statistical test $\theta^{(sem)} = \theta^{(tec)}$ (with corresponding alternative hypothesis $\theta^{(sem)} > \theta^{(tec)}$) on non-overlapping blocks from the period 1980-2007\footnote{Note that the estimation included patents up until 2010 in the period 2006-2007 and not the patents from 1980 in the period 1980-1985 for homogeneity in size with other periods.
-This doesn't affect the significativity of the results.} are reported on Table \ref{summary}.
-Semantic values are reported for four different chosen thresholds $p^{-}=.04, .06, .08, .1$.
-It means that we restricted to the couples ($i$th patent, $j$th class) such that $p_{ij} \geq p^{-}$.
-
-The choice of considering non-overlapping blocks (instead of overlapping blocks) is merely statistical.
-Ultimately, our interest is in the significance of the test over the whole period 1980-2007.
-Thus, we want to compute a global p-value.
-This can be done considering the local p-values (by local, we mean for instance computed on the period 2001-2005) assuming independence between them.
-This assumption is reasonable only if the blocks are non-overlapping.
-All of this can be found in \ref{app:stat}.
-Finally, note that from a statistical perspective, including overlapping blocks wouldn't yield more information.
-
-The values reported in Table \ref{summary} are overwhelmingly against the null hypothesis.
-The global estimates of $\theta^{(sem)}$ are significantly bigger than the estimate of $\theta^{(tec)}$ for all the considered thresholds.
-Although the corresponding p-values (which are also very close to 0) are not reported, it is also quite clear that the bigger the threshold, the higher the corresponding $\theta^{(sem)}$ is estimated.
-This is consistently seen for any period, and significant for the global period.
-This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propensity to cite patents from its own class $\theta^{(sem)}$ is increasing.
-We believe that this might provide extra information to patent officers when making their choice of citations.
-Indeed, they could look first to patents which belong to the same semantic class, especially when patents have high probability semantic values.
-
-Note that the introduced model can be seen as a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g.
-\citealt{decelle2011asymptotic}, \citealt{valles2016multilayer}).
-The parameters are estimated computing the corresponding MLE.
-In view of~\citet{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.
-
-\begin{table}[!ht]
-\centering
-\caption{\label{summary} Estimated values of $\theta^{(tec)}$ and $\theta^{(sem)}$ and corresponding standard errors obtained from a Maximum Likelihood estimator as presented in section \ref{statisticalmodel}.}
-\label{stdQMLE}
-\begin{tabular}{@{}rccccccccc@{}}
-\toprule
-\toprule
-\multicolumn{1}{l}{Approach} & \multicolumn{1}{l}{Estimated Value} & \multicolumn{1}{l}{st. er.} & \multicolumn{1}{l}{p-value} \\ \toprule
-\multicolumn{4}{l}{1980-1985 period} \\
-technological & .664 &.008&\\
-semantic $p^{-} = .04$ & .741 &.047 & .053\\
-semantic $p^{-} = .06$ & .799 &.081 & .049\\
-semantic $p^{-} = .08$ & .828 &.126 & .097\\
-semantic $p^{-} = .10$ & .834 &.166 & .153\\
-\multicolumn{4}{l}{1986-1990 period} \\
-technological & .634 &.007&\\
-semantic $p^{-} = .04$ & .703 &.022 & .001\\
-semantic $p^{-} = .06$ & .768 &.040 & .0004\\
-semantic $p^{-} = .08$ & .804 &.069 & .007\\
-semantic $p^{-} = .10$ & .832 &.114 & .041\\
-\multicolumn{4}{l}{1991-1995 period} \\
-technological & .619 &.006&\\
-semantic $p^{-} = .04$ & .655 &.009 & .0004\\
-semantic $p^{-} = .06$ & .713 &.017 & 9e-08\\
-semantic $p^{-} = .08$ & .731 &.025 & 7e-06\\
-semantic $p^{-} = .10$ & .750 &.037 & 9e-06\\
-\multicolumn{4}{l}{1996-2000 period} \\
-technological & .551 &.003&\\
-semantic $p^{-} = .04$ & .585 &.002 & $\approx 0$\\
-semantic $p^{-} = .06$ & .638 &.004 & $\approx 0$\\
-semantic $p^{-} = .08$ & .660 &.006 & $\approx 0$\\
-semantic $p^{-} = .10$ & .686 &.008 & $\approx 0$\\
-\multicolumn{4}{l}{2001-2005 period} \\
-technological & .567 &.003&\\
-semantic $p^{-} = .04$ & .621 &.004 & $\approx 0$\\
-semantic $p^{-} = .06$ & .676 &.007 & $\approx 0$\\
-semantic $p^{-} = .08$ & .701 &.010 & $\approx 0$\\
-semantic $p^{-} = .10$ & .710 &.013 & $\approx 0$\\
-\multicolumn{4}{l}{2006-2007 period} \\
-technological & .600 &.007&\\
-semantic $p^{-} = .04$ & .683 &.016 & 1e-06\\
-semantic $p^{-} = .06$ & .732 &.025 & 2e-07\\
-semantic $p^{-} = .08$ & .760 &.036 & 6e-06\\
-semantic $p^{-} = .10$ & .782 &.048 &9e-05\\
-\multicolumn{4}{l}{1980-2007 global period} \\
-technological & .606 &.002&\\
-semantic $p^{-} = .04$ & .665 &.009 & 8e-11\\
-semantic $p^{-} = .06$ & .721 &.017 & 9e-12\\
-semantic $p^{-} = .08$ & .747 &.025 & 9e-09\\
-semantic $p^{-} = .10$ & .782 &.035 & 3e-07\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion \label{discussion}}
-%%%%%%%%%%%%%%%%%%%%%
-
-The main contribution of this study was twofold.
-First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts.
-We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree, etc.).
-The availability of this data suggests new avenues for further research.
-Linking our dataset with existing open ones can lead to various powerful developments.
-For example, using it together with the disambiguated inventor database provided by~\cite{li2014disambiguation} could be a way to study semantic profiles of inventors, or of cities as inventor addresses are provided.
-The investigation of spatial diffusion of innovation between cities, which is a key component of Pumain's Evolutive Urban Theory~\cite{pumain2010theorie}, would be made possible.
-
-A first potential application is to use the patents' topological measures inherited from their relevant keywords.
-The fact that these measures are backward-looking and immediately available after the publication of the patent information is an important asset.
-It would for example be very interesting to test their predicting power to assess the quality of an innovation, using the number of forward citations received by a patent, and subsequently the future effect on the firm's market value.
-Regarding firm innovative strategy, a second extension could be to study trajectories of firms in the two networks: technological and semantic.
-Merging these information with data on the market value of firms can give a lot of insight about the more efficient innovative strategies, about the importance of technology convergence or about acquisition of small innovative firms.
-It will also allow to observe innovation pattern over a firm life cycle and how this differ across technology field.
-A third extension would be to use dig further into the history of innovation.
-USPTO patent data have been digitized from the first patent in July 1790.
-However, not all of them contain a text that is directly exploitable.
-We consider that the quality of patent's images is good enough to rely on Optical Character Recognition techniques to retrieve plain text from at least 1920.
-With such data, we would be able to extend our analysis further back in time and to study how technological progress occurs and combines in time.
-\cite{akcigit2013mechanics} conduct a similar work by looking at recombination and apparition of technological subclasses.
-Using the fact that communities are constructed yearly, one can construct a measure of proximity between two successive classes.
-This could give clear view on how technologies converged over the year and when others became obsolete and replaced by new methods.
-
-\newpage
-\appendix
-
-\section{Definition of utility patent}  \label{app:utility}
-
-A utility patent at the USPTO is a document providing intellectual property and protection of an invention.
-It excludes others to making, using, or selling the invention the same invention in the United States in exchange for a disclosure of the patent content.
-The protection is granted for 20 years since 1995 (it was 17 years before that from 1860) starting from the year the patent application was filled, but can be interrupted before if its owner fails to pay the maintenance fees due after 3.5, 7.5 and 11.5 years.
-Utility patents are by far the most numerous, with more than 90\% of the total universe of USPTO patents.\footnote{Other categories are Plant patents, Design patents and Reissue patents.} According to the Title 35 of the United States Codes (35 USC) section 101: \textit{``Whoever invents or discovers any new and useful process, machine, manufacture, or composition of matter, or any new and useful improvement thereof, may obtain a patent therefor, subject to the conditions and requirements of this title.''}\footnote{%
-Patent laws can be found in http://www.uspto.gov/web/offices/pac/mpep/mpep-9015-appx-l.html\#d0e302376} In practice however, other types of invention including algorithms can also be patented.\footnote{A notable example is the patent \textit{US6285999} protecting the Page Rank algorithm invented by Larry Page in 1998 which was the genesis of Google.} The two following sections of the 35 USC defined the condition an invention must meet to be protected by the USPTO: (i) novelty: the claimed invention cannot be already patented or described in a previous publication (35 USC section 102); (ii) obviousness: \textit{``differences between the claimed invention and the prior art must not be such that the claimed invention as a whole would have been obvious before the effective filing date of the claimed invention to a person having ordinary skill in the art to which the claimed invention pertains''}.
-(35 USC section 103).
-After review from the USPTO experts, an application satisfying these requirements will be accepted and a patent granted.
-The average time lag for such a review is on average a little more than 2 years since 1976, with some patents being granted after much more than two years.\footnote{This time lag, sometimes called the grant lag, is highly heterogeneous across technological fields.
-In addition, it cannot be considered as totally random.
-For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\citet{regibeau2010}.}
-
-\paragraph{Sample restriction}
-As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013.
-For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below).
-We restrict attention to patents applied for before 2007.
-The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO.
-However, in order to date them as closely as possible to the date of invention, we use the application date as a reference.
-As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013.
-Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.
-
-\section{Data collection procedure}\label{app:datacollection}
+\label{supp:data}
 
@@
 
-\section{Network Sensitivity Analysis \label{app:sensitivity}}
-
-\subsection{Network Sensitivity}
-
-The example of Figure 1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Figures ~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.
-We also show an other point of view over the Pareto optimization, that is the third plot giving the values of normalized objectives as a function of $\theta_c$.
-
-% Figures :
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/commnum_thetaw_byyears.png}
-	\caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
-	\label{fig:ext-sensitivity-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/vcount_comnum_pareto.png}
-	\caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
-	\label{fig:ext-sensitivity-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/normalizedObjs-dispth_eth4_1e-5.png}
-	\caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
-	\label{fig:ext-sensitivity-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Time-window size sensitivity}
-
-% put some graphs for 3-years time window : same qualitative properties but a bit more noisy
-
-We show in Figures ~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$.
-The same qualitative behavior is observed (with different quantitative values, as typically $\theta_w^{(0)}$ is for example expected to vary with document number and semantic regime, thus with window size), what confirms that the method is valid across different time windows.
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/commnum_thetaw_byyears_window3.png}
-	\caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
-	\label{fig:sensitivity-window3-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/vcount_comnum_pareto_window3.png}
-	\caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
-	\label{fig:sensitivity-window3-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\textwidth,height=\textwidth,angle=90]{figures/normalizedObjs-dispth_window3_eth4_1e-5.png}
-	\caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
-	\label{fig:sensitivity-window3-3}
-\end{figure}
-
-\section{Statistical definitions and derivations} \label{app:stat}
-\subsection{Likelihood expression}
-We define $\mathcal{F}_i$ the filtration which corresponds to the time $t_i$.
-With this notation $\mathcal{L}( X | \mathcal{F}_{i-1})$ simply means the likelihood of $X$ conditioned on the past.
-We consider $\widehat{\theta}^{(z)}$ the MLE of $\theta^{(z)}$, where the corresponding log-likelihood of the model can be expressed up to constant terms as
-\begin{eqnarray*}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} \log \mathcal{L} \big( B_{l,i} | \mathcal{F}_{i-1} \big).
-\end{eqnarray*}
-Recalling that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables 
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-the log-likelihood of the model can be expressed as 
-\begin{eqnarray}
-\label{loglik}
-\sum_{i=2}^Z \sum_{l=1}^{C_i} B_{l,i} \log \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big) +(1 - B_{l,i}) \log \Big(1 - \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big).
-\end{eqnarray}
-In practice, the user can easily implement the formula (\ref{loglik}) for any $0 \leq \theta^{(z)} \leq 1$, and maximize it over a predefined grid to obtain $\widehat{\theta}^{(z)}$.
-
-\subsection{Standard errors of the estimated values}
-Under some assumptions, it is possible to show the asymptotic normality of $\widehat{\theta}^{(z)}$ and to compute the asymptotic variance.
-For simplicity of exposition, we assume that we restrict to $\theta^{(z)}$ such that we have $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} < 1$ for any $i=2, \cdots, Z$.
-The central limit theorem can be expressed as
-\begin{eqnarray}
-\label{variance}
-\sqrt{Z \mathbb{E} [ C ]} (\widehat{\theta}^{(z)} - \theta^{(z)}) \overset{\mathcal{L}}{\rightarrow} MN \Big( 0, \int (p + \theta^{(z)})(1 - (p + \theta^{(z)})) d\pi^{(z)} (p) \Big),
-\end{eqnarray}
-where MN stands for a multinormal distribution and $\pi^{(z)}$ for the asymptotic limit distribution of the quantity $\frac{N_{i}^{(z)}}{i-1} + \theta^{(z)}$.
-Note that the variance term in (\ref{variance}) is equal to an aggregate version of the Fisher information matrix.
-The proof of such statement is beyond the scope of this paper.
-On the basis of (\ref{variance}), we provide a variance estimator as
-$$v^{(z)} = \frac{1}{C_k-1}\sum_{i=2}^{C_k}  \frac{N_{i_k}^{(z)}}{i-1} + \widehat{\theta}^{(z)},$$ 
-where $i_k$ is such that the $i_k$th patent corresponds to the $k$th couple. This estimator was used to compute the standard deviation in Table \ref{summary}.
-\subsubsection*{Test statistic}
-The test statistic used is a mean difference test statistic between $\widehat{\theta}^{(tec)}$ and  $\widehat{\theta}^{(sem)}$, where the formal expression can be found in (\ref{teststat}).
-We assume independence between both quantities and thus under the null hypothesis, we have that
-$$\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)} {\rightarrow} MN(0,V),$$
-where $V= \int (p + \theta^{(tec)})(1 - (p + \theta^{(tec)})) d\pi^{(tec)} (p) + \int (p + \theta^{(sem)})(1 - (p + \theta^{(sem)})) d\pi^{(sem)} (p)$ can be estimated by $\widehat{V} = v^{(sem)} + v^{(tec)}$.
-Then, we obtain that
-\begin{eqnarray}
-\label{teststat}
-A = \frac{\widehat{\theta}^{(tec)} - \widehat{\theta}^{(sem)}}{\widehat{V}} \approx \mathcal{N} (0,1),
-\end{eqnarray}
-where $A$ is the mean difference test static.
-
-\newpage
-\bibliographystyle{ecta}
-\bibliography{patents}
-
 \end{document}

### 2018-11-27 Docs/Papers/Technical/overleafv2/S5_Text.tex

--- 2016-12-26 Docs/Papers/Technical/arxiv/v1/main.tex
@@
-\documentclass[12pt,twoside,a4paper]{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{eurosym}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage[section]{placeins}
-\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
-\usepackage{setspace}
-\usepackage{rotating}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{etoolbox}
-\usepackage{amsmath,amssymb}
-\usepackage{float}
-\usepackage{xcolor}
-\usepackage{hyperref}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{booktabs,caption,fixltx2e}
-\usepackage[flushleft]{threeparttable}
-\usepackage{tabularx}
-\usepackage{enumitem}
-\usepackage{caption}
-\usepackage{nameref}
-\usepackage{lscape}
-\usepackage{fancyhdr}
-
-\setcounter{MaxMatrixCols}{10}
-\hypersetup{
-    colorlinks, linkcolor={dark-red},
-    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
-}
-\geometry{hmargin=4cm,vmargin=4cm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{assumption}{Assumption}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
-\setcounter{secnumdepth}{5}
-\textwidth 6.0in
-\textheight 8.84in 
-\setlength{\topmargin}{-0.3in}
-\setlength{\oddsidemargin}{0.0in}
-\setlength{\evensidemargin}{0.0in}
-\setlength{\abovecaptionskip}{0pt}
-\setlength{\belowcaptionskip}{5pt}
-\setlength{\textfloatsep}{25pt}  
-\setlength{\intextsep}{5pt}   
-\fancyhf{}
-\pagestyle{fancy}
-\renewcommand{\headrulewidth}{1pt}
-\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
-\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
-\fancyfoot[C]{\thepage}
-
-\begin{document}
-
-\title{Classifying Patents Based on their Semantic Content\thanks{%
-Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
-Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
-\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
- \ \ \ \ \ Juste Raimbault \bigskip}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% Please keep the abstract below 300 words
-\begin{abstract}
-In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach.
-This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward.
-To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly.
-We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes.
-Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model.
-This suggests that our method is a useful tool to extract endogenous information.
-\end{abstract}
-
-\pagebreak
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}.
-\cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation.
-Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis.
-Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review.
-Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}.
-With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters.
-Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.
-
-Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies.
-But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share.
-Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g.
-~\cite{AAKnetwork2016}).
-
-In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it.
-In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract.
-Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach.
-The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence).
-One can for instance consider the case of the word \textit{optic}.
-Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic.
-This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.
-
-Previous research has already proposed to use semantic networks to study technological domains and detect novelty.
-~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain.
-The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}.
-More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation.
-Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).
-
-Building on such previous research, we make several contributions by fulfilling some shortcomings of existing studies, such as for example the use of frequency-selected single keywords.
-First of all, we develop and implement a novel fully-automatized methodology to classify patents according to their semantic abstract content, which is to the best of our knowledge the first of its type.
-This includes the following refinements for which details can be found in Section \ref{keywords}: (i) use of multi-stems as potential keywords; (ii) filtering of keywords based on a second-order (co-occurrences) relevance measure and on an external independent measure (technological dispersion); (iii) multi-objective optimization of semantic network modularity and size.
-The use of all this techniques in the context of semantic classification is new and essential from a practical perspective.
-
-Furthermore, most of the existing studies rely on a subsample of patent data, whereas we implement it on the full US Patent database from 1976 to 2013.
-This way, a general structure of technological innovation can be studied.
-We draw from this application promising qualitative stylized facts, such as a qualitative regime shift around the end of the 1990s, and a significant improvement of citation modularity for the semantic classification when comparing to the technological classification.
-These thematic conclusions validate our method as a useful tool to extract endogenous information, in a complementary way to the technological classification.
-
-Finally, the statistical model introduced in Section \ref{statisticalmodel} seems to indicate that patents tend to cite more similar patents in the semantic network  when fitted to data.
-In particular, this propensity is shown to be significantly bigger than the corresponding propensity for technological classes, and this seems to be consistent over time.
-On the account of this information, we believe that patent officers could benefit very much from looking at the semantic network when considering potential citation candidates of a patent in review.
-
-The paper is organized as follows.
-Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process.
-Section \ref{keywords} explains the construction of the semantic classes.
-Section \ref{result} tests their relevance by providing exploratory results.
-Finally, section \ref{discussion} discusses potential further developments and conclude.
-More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background \label{data}}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013.
-A clearer definition of utility patent is given in~\nameref{sectionSI}.
-Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{An existing classification: the USPC system}
-
-Each USPTO patent is associated with a non-empty set of technological classes and subclasses.
-There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system.
-While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention.
-A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass.
-At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes.
-When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A bibliographical network between patents: citations \label{sub:citation}}
-
-As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art.
-They therefore indicate the past knowledge which relates to the patented invention.
-Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent.
-One can consult~\cite{oecdpatentmanual} for more details about this.
-Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}).
-Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves.
-From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations).
-We can thus build a complete network of citations that we will use later on in the analysis.
-
-Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years.
-This distribution is highly skewed, the $95^{th}$ percentile is 21 years.
-We also report 164,000 citations with a negative time lag.
-This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others.
-
-In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years.
-We impose this restriction for two reasons.
-First, the number of citations received peaks 4-5 years after application.
-Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones.
-As we are restricting to citations received no later than 5 years after the application date, this effect will only affect patents with an application date after 2007.
-
-%%%%%%%%%%%%%%%%%%
-\subsection{Data collection and basic description}
-Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis.
-Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size.
-In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}).
-The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).
-
-We construct from raw data a unified database.
-Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976.
-Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}.
-The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
-Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.
-
-We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013.
-When distributed by the year of application, the picture is slightly different.
-The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007.
-Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents.
-These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}.
-Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window.
-270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations.
-A within class citation is defined as a citation between two patents sharing at least one common technological class.
-Following this definition, 84\% of the citations are within class citations.
-14\% of the citations are between two patents that share the exact same set of technological classes.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Towards a Complementary Classification}
-
-Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}.
-The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications.
-The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review).
-Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}.
-As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored.
-One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples.
-Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies.
-Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.
-
-Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}).
-Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Semantic Classification Construction \label{keywords}}
-
-In this section, we describe methods and empirical analysis leading to the construction of semantic network and the corresponding classification.
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords extraction}
-\label{keywordsextraction}
-
-Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
-$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
-\begin{enumerate}
-\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).
-
-\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.
-
-\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens.
-At this point the abstract text is reduced to a set of stems and their grammatical functions.
-\item Multi-stems construction: these are the basic semantic units used in further analysis.
-They are constructed as groups of successive stems in a sentence which satisfies a simple grammatical function rule.
-The length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives.
-We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
-\end{enumerate}
-
-Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations.
-This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining}
-}
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Keywords relevance estimation}
-\label{keywords_est}
-\paragraph{Relevance definition}
-
-Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem.
-The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords.
-We choose to set this parameter to $K_w = 100,000$.
-We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed.
-This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words.
-A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$.
-The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus.
-Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification.
-More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together.
-The \emph{termhood} score $t_i$ is defined as
-
-\[
-t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
-\]
-
-\paragraph{Moving window estimation}
-The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past.
-Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$.
-Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents.
-This way, we will obtain semantic classes which are exploitable on a $T_0$ time span.
-For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}.
-In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}.
-Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Construction of the semantic network}
-\label{construction}
-
-We keep the set of most relevant keywords $\mathcal{K}_W$ and obtain their co-occurrence matrix as defined in Section \ref{keywords_est}.
-This matrix can be directly interpreted as the weighted adjacency matrix of the semantic network.
-At this stage, the topology of raw networks does not allow the extraction of clear communities.
-This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g.
-\texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant.
-We therefore introduce an additional measure to correct the network topology: the concentration of keywords across technological classes, defined as:
-
-$$c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2},$$
-
-where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes.
-The higher $c_{tech}$, the more specific to a technological class the node is.
-For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field.
-We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$.
-In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time.
-To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$).
-Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$.
-At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward.
-Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities.
-We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$.
-Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-%\hspace{-2.5cm}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.png}
-\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.png}
-%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
-\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical.
-\textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values.
-The maximum is roughly stable across $\theta_c$ (dashed red line).
-\textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
-\label{fig:networksensitivity}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{striking}
-%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
-\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$.
-The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
-\label{fig:rawnetwork}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Characteristics of Semantic Classes}
-\label{characteristics}
-For each year $t$, we define as $N^{(sem)}_t$ the number of semantic classes which have been computed by clustering keywords from patents appeared during the period $\big[ t-T_0, t \big]$ (we recall that we have chosen $T_0=4$).
-Each semantic class $k =  1, \cdots, N^{(sem)}_t$ is characterized by a set of keywords $K(k,t)$ which is a subset of $\mathcal{K}_W$ selected as described in Section \ref{keywordsextraction} to Section \ref{construction}.
-The cardinal of $K(k, t)$ distribution across each semantic class $k$ is highly skewed with a few semantic classes containing over $1,000$ keywords, most of them with roughly the same number of keywords.
-In contrast, there are also many semantic classes with only two keywords.
-There are around 30 keywords by semantic class on average and the median is 2 for any $t$.
-Fig.~\ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{meancomsize}
-%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
-\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
-\label{fig:mean_K}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph*{Title of semantic classes}
-USPC technological classes are defined by a title and a highly accurate definition which help retrieve patents easily.
-The title can be a single word (e.g.: class 101: ``Printing'') or more complex (e.g.: class 218: ``High-voltage switches with arc preventing or extinguishing devices'').
-As our goal is to release a comprehensive database in which each patent is associated with a set of semantic classes, it is necessary to give an insight on what these classes represent by associating a short description or a title as in~\cite{tseng2007text}.
-In our case, such description is taken as a subset of keywords taken from $K(k,t)$.
-For the vast majority of semantic classes that have less than 5 keywords, we decide to keep all of theses keywords as a description.
-For the remaining classes which feature around 50 keywords on average, we rely on the topological properties of the semantic network.~\cite{yang2000improving} suggest to retain only the most frequently used terms in $K(k,t)$.
-Another possibility is to select 5 keywords based on their network centrality with the idea that very central keywords are the best candidates to describe the overall idea captured by a community.
-For example, the largest semantic class in 2003-2007 is characterized by the keywords: \texttt{Support Packet; Tree Network; Network Wide; Voic Stream; Code Symbol Reader}.
-
-\paragraph*{Size of technological and semantic classes} 
-We consider a specific window of observations (for example 2000-2004), and we define $Z$ the number of patents which appeared during that time window.
-For each patent $i=1, \cdots, Z$ we associate a vector of probability where each component $p_{ij}^{(sem)} \in \big[ 0,1 \big]$, with  $j = 1, \cdots, N{(sem)}$ and where\footnote{When there is no room for confusion, we drop the subscript $t$ in $N_t^{(sem)}$.}
-$$\displaystyle \sum_{j=1}^{N^{(sem)}} p_{ij}^{(sem)} = 1.$$ On average across all time windows, a patent is associated to 1.8 semantic classes with a positive probability.
-Next we define the size of a semantic class as $$S_j^{(sem)} = \displaystyle \sum_{i=1}^Z p_{ij}^{(sem)}.$$
-Correspondingly, we aim to provide a consistent definition for technological classes.
-For that purpose, we follow the so-called ``fractional count'' method, which was introduced by the USPTO and consists in dividing equally the patents between all the classes they belong to.
-Formally, we define the number of technological classes as
-$N^{(tec)}$  (which is not time dependent contrary to the semantic case) and for $j = 1, \cdots, N^{(tec)}$ the corresponding matrix of probability is defined as
-\[
- p_{ij}^{(tec)} = \frac{B_{ij}}{\displaystyle \sum_{k=1}^{N^{(tec)}}{B_{ik}}},
-\]
-where  $B_{ij}$ equals $1$ if the $i$th patent belongs to the $j$th technological class and $0$ if not.
-When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix.
-Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Fig.~\ref{fig:class-sizes}.
-This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth]{all_raw_counts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
-\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$,
-from the biggest to the smallest.
-The formal definition of size can be found in Section \ref{characteristics}.
-Each color corresponds to one specific year.
-Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications.
-This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}.
-Over time, curves are translated and levels of hierarchy stays roughly constant.}
-\label{fig:class-sizes}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Potential Refinements of the Method}
-
-Our semantic classification method could be refined by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method (e.g.~\cite{blei2003latent}), already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a field rather than distant technological recombination.
-Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation).
-Also, depending on the level of orthogonality with our classification, it can potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.
-
-Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis.
-Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links.
-\cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper.
-Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Results \label{result}}
-%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present some key features of our resulting semantic classification showing both complementary and differences with the technological classification.
-We first present several measures derived from this semantic classification at the patent level: Diversity, Originality, Generality (Section \ref{subsec:orig-gene}) and Overlapping (Section \ref{subsec:overlaps}).
-We then show that the two classifications show highly
-different topological measures and strong statistical evidence that they feature a different model (Sections \ref{citationmodularity} and \ref{statisticalmodel}).
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Patent Level Measures}  \label{subsec:orig-gene}
-
-Given a classification system (technological or semantic classes), and the associated probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ (that were defined in Section \ref{characteristics}), one can define a patent-level diversity measure as one minus the Herfindhal concentration index on $p_{ij}$  by
-
-\[
-D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}.
-\]
-
-We show in Fig.~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series.
-This is carried with two different settings, namely including/not including patents with zero diversity (i.e.
-single class patents).
-We call other patents ``complicated patents'' in the following.
-First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes.
-More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization.
-This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}.
-Furthermore, a qualitative regime shift on semantic classification occurs around 1996.
-This can be seen whether or not we include patents with zero diversity.
-The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease.
-This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity.
-It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents.
-
-More commonly used in the literature are the measures of originality and generality.
-These measures follow the same idea than the above-defined diversity in quantifying the diversity of classes (whether technological or semantic) associated with a patent.
-But instead of looking at the patent's classes, they consider the classes of the patents that are cited or citing.
-Formally, the originality $O_i$ and the generality $G_i$ of a patent $i$ are defined as
-\[
-O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2} \text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2},
-\]
-where $z \in \{tec, sem\}$, $I_i$ denotes the set of patents that are cited by the $i$th patent within a five year window (i.e.
-if the $i$th patent appears at year $t$, then we consider patents on $[t-T_0, t]$) when considering the originality and $\tilde{I}_i$ the set of patents that cite patent $i$ after less than five years (i.e.
-we consider patents on $[t ,t + T_0]$) in the case of generality.
-Note that the measure of generality is forward looking in the sense that $G_i^{(z)}$ used information that will only be available 5 years after patent applications.
-Both measures are lower on average based on semantic classification than on technological classification.
-Fig.
-\ref{fig:orig-gene} plots the mean value of $O_i^{(sem)}$, $O_i^{(tec)}$, $G_i^{(sem)}$ and $G_i^{(tec)}$.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-%First row : semantic with relevant keywords only - all patents 
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_all_ts_semcounts}\\
-%Second row : patents with diversity $> 0$ (more than one class)}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_semcounts}
-\includegraphics[width=0.49\textwidth]{patentlevelorigs_positive_ts_semcounts}
-%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
-\caption{
-\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$).
-The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e.
-patents with diversity greater than 0).
-}
-\label{fig:patent-level-orig}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\includegraphics[width=0.49\textwidth]{originality.png}
-\includegraphics[width=0.49\textwidth]{generality.png}\\
-%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
-\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}.
-}
-\label{fig:orig-gene}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classes overlaps} \label{subsec:overlaps}
-
-A proximity measure between two classes can be defined by their overlap in terms of patents. 
-Such measures could for example be used to construct a metrics between semantic classes.
-Intuitively, highly overlapping classes are very close in terms of technological content and one can use them to measure distance between two firms in terms of technology as done in~\cite{Bloom2005distance}.
-Formally, recalling the definition of $\left(p_{ij}\right)$ as the probability for the $i$th patent to belong to the $j$th class and $N_P$ as the number of patents it writes
-\begin{eqnarray}
-\label{overlap}
-Overlap_{jk} = \frac{1}{N_P}\cdot \sum_{i=1}^{N_P} p_{ij} p_{ik}. 
-\end{eqnarray}
-
-The overlap is normalized by patent count to account for the effect of corpus size: by convention, we assume the overlap to be maximal when there is only one class in the corpus.
-A corresponding relative overlap is computed as a set similarity measure in the number of patents common to two classes A and B, given by $o(A,B)=2\cdot \frac{\left|A\cap B\right|}{\left|A\right| + \left|B\right|}$.
-
-\paragraph{Intra-classification overlaps}
-
-The study of distributions of overlaps inside each classification, i.e.
-between technological classes and between semantic classes separately, reveals the structural difference between the two classification methods, suggesting their complementary nature.
-Their evolution in time can furthermore give insights into trends of specialization.
-We show in Fig.~\ref{fig:intra-classif-overlap} distributions and mean time-series of overlaps for the two classifications.
-The technological classification globally always follow a decreasing trend, corresponding to more and more isolated classes, i.e.
-specialized inventions, confirming the stylized fact obtained in previous subsection.
-For semantic classes, the dynamic is somehow more intriguing and supports the story of a qualitative regime shift suggested before.
-Although globally decreasing as technological overlap, normalized (resp.
-relative) mean overlap exhibits a peak (clearer for normalized overlap) culminating in 1996 (resp.
-1999).
-Looking at normalized overlaps, classification structure was somewhat stable until 1990, then strongly increased to peak in 1996 and then decrease at a similar pace up to now.
-Technologies began to share more and more until a breakpoint when increasing isolation became the rule again.
-An evolutionary perspective on technological innovation~\cite{ziman2003technological} could shed light on possible interpretations of this regime shift: as species evolve, the fitness landscape first would have been locally favorable to cross-insemination, until each fitness reaches a threshold above which auto-specialization becomes the optimal path.
-It is very comparable to the establishment of an ecological niche~\cite{holland2012signals}, the strong interdependency originating here during the mutual insemination resulting in a highly path-dependent final situation.
-%This interpretation is consistent with the dynamics of semantic flows presented in Fig.~\ref{fig:semanticflows}, as the increase period roughly corresponds to a sequence where inter-class flows are stronger.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.49\textwidth]{norm-patents_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{norm-patents_all_ts_semcounts.png} \\
-\includegraphics[width=0.49\textwidth]{relative_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
-\caption{
-\textbf{Intra-classification overlaps.}
-\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale).
-\textit{(Right column)} Corresponding mean time-series.
-\textit{(First row)} Normalized overlaps.
-\textit{(Second row)} Relative overlaps.}
-\label{fig:intra-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Inter-classification overlaps}
-
-Overlaps \emph{between} classifications are defined as in (\ref{overlap}), but with $j$ standing for the $j$th technological class and $k$ for the $k$th semantic class: $p_{ij}$ are technological probabilities and $p_{ik}$ semantic probabilities.
-They describe the relative correspondence between the two classifications and are a good indicator to spot relative changes, as shown in Fig.~\ref{fig:inter-classif-overlap}.
-Mean inter-classification overlap clearly exhibits two linear trends, the first one being constant from 1980 to 1996, followed by a constant decrease.
-Although difficult to interpret directly, this stylized fact clearly unveils a change in the \emph{nature} of inventions, or at least in the relation between content of inventions and technological classification.
-As the tipping point is at the same time as the ones observed in the previous section and since the two statistics are different, it is unlikely that this is a mere coincidence.
-Thus, these observations could be markers of a hidden underlying structural changes in processes.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_density_semcounts.png}
-\includegraphics[width=0.49\textwidth]{relative_interclassif_all_ts_semcounts.png}
-%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
-\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series.
-The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
-\label{fig:inter-classif-overlap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Citation Modularity}
-\label{citationmodularity}
-
-An exogenous source of information on relevance of classifications is the citation network described in Section \ref{sub:citation}.
-The correspondence between citation links and classes should provide a measure of accuracy of classifications, in the sense of an external validation since it is well-known that citation homophily  is expected to be quite high (see, e.g, ~\cite{AAKnetwork2016}).
-This section studies empirically modularities of the citation network regarding the different classifications.
-To corroborate the obtained results, we propose to look at a more rigorous framework in Section \ref{statisticalmodel}.
-Modularity is a simple measure of how communities in a network are well clustered (see \cite{clauset2004finding} for the accurate definition).
-Although initially designed for single-class classifications, this measure can be extended to the case where nodes can belong to several classes at the same time, in our case with different probabilities as introduced in \cite{nicosia2009extending}.
-The simple directed modularity is given in our case by
-\[
-Q_d^{(z)} = \displaystyle \frac{1}{N_P}\sum_{1\leq i,j\leq N_P}\left[A_{ij} - \frac{k_{i}^{in}k_{j}^{out}}{N_P}\right]\delta(c_i,c_j),
-\]
-with $A_{ij}$ the citation adjacency matrix (i.e.
-$A_{ij} = 1$ if there is a citation from the $i$th patent to the $j$th patent, and $A_{ij}=0$ if not), $k_i^{in}=\left| I_i\right|$ (resp.
-$k_i^{out}= \left|\tilde{I}_i \right|$) in-degree (resp.
-out-degree) of patents (i.e.
-the number of citations made by the $i$th patent to others and the number of citations received by the $i$th patent).
-$Q_d$ can be defined for each of the two classification systems: $z \in \{tec, sem\}$.
-If $z=tec$, $c_i$ is defined as the main patent class, which is taken as the first class whereas if $z=sem$, $c_i$ is the class with the largest probability.
-
-Multi-class modularity in turns is given by
-
-\[
-\displaystyle Q_{ov}^{(z)} = \frac{1}{N_P} \sum_{c = 1}^{N^{(z)}} \sum_{1\leq i,j \leq N_P}\left[F(p_{ic},p_{jc})A_{ij} - \frac{\beta_{i,c}^{out}k_i^{out}\beta_{j,c}^{in}k_j^{in}}{N_P}\right],
-\]
-where
-\[
- \beta_{i,c}^{out} =   \frac{1}{N_P} \displaystyle \sum_j F(p_{ic},p_{jc}) \text{ and } \beta_{j,c}^{in} =  \frac{1}{N_P} \displaystyle \sum_i F(p_{ic},p_{jc}).
-\]
-We take $F(p_{ic},p_{jc}) = p_{ic}\cdot p_{jc}$ as suggested in \cite{nicosia2009extending}.
-Modularity is an aggregated measure of how the network deviates from a null model where links would be randomly made according to node degree.
-In other words it captures the propensity for links to be inside the classes.
-Overlapping modularity naturally extends simple modularity by taking into account the fact that nodes can belong simultaneously to many classes.
-We document in Fig.~\ref{fig:modularities} both simple and multi-class modularities over time.
-For simple modularity, $Q_d^{(tec)}$ is low and stable across the years whereas $Q_d^{(sem)}$ is slightly greater and increasing.
-These values are however low and suggest that single classes are not sufficient to capture citation homophily.
-Multi-class modularities tell a different story.
-First of all, both classification modularities have a clear increasing trend, meaning that they become more and more adequate with citation network.
-The specializations revealed by both patent level diversities and classes overlap is a candidate explanation for this growing modularities.
-Secondly, semantic modularity dominates technological modularity by an order of magnitude (e.g.
-0.0094 for technological against 0.0853 for semantic in 2007) at each time.
-This discrepancy has a strong qualitative significance.
-Our semantic classification fits better the citation network when using multiple classes.
-As technologies can be seen as a combination of different components as shown by~\cite{Youn:2015fk}, this heterogeneous nature is most likely better taken into account by our multi-class semantic classification.
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.49\textwidth]{simplemodularity}
-\includegraphics[width=0.49\textwidth]{overlappingmodularity}
-%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
-\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability).
-(Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
-\label{fig:modularities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%
-\subsection{Statistical Model}
-\label{statisticalmodel}
-In this section, we develop a statistical model aimed at quantifying performance of both technological and semantic classification systems.
-In particular, we aim at corroborating findings obtained in Section \ref{citationmodularity}.
-The mere difference between this approach and the citation modularity approach lies in the choice of the underlying model, and the according quantities of interest.
-In addition for the semantic approach, we want to see if when restricting to patents with higher probabilities to belong to a class, we obtain better results.
-To do that, we choose to look at within class citations proportion (for both technological and semantic approaches).
-We provide two obvious reasons why we choose this.
-First, the citations are commonly used as a proxy for performance as mentioned in Section \ref{citationmodularity}.
-Second, this choice is ``statistically fair'' in the sense that both approaches have focused on various goals and not on maximizing directly the within class proportion.
-Nonetheless, the within class proportion is too sensitive to the distribution of the shape of classes.
-For example, a dataset where patents for each class account for 10\% of the total number of patents will mechanically have a better within class proportion than if each class accounts for only 1\%.
-Consequently, an adequate statistical model, which treats datasets fairly regardless of their distribution in classes, is needed.
-This effort ressembles to the previous study of citation modularity, but is complementary since the model presented here can be understood as an elementary model of citation network growth.
-Furthermore, the parameters fitted here can have a direct interpretation as a citation probability.
-
-We need to introduce and recall some notations.
-We consider a specific window of observations $\big[t- T_0, t \big]$, and we define $Z$ the number of patents which appeared during that time window.
-We let $t_1, \cdots, t_Z$ their corresponding appearance date by chronological order, which for simplicity are assumed to be such that $t_1 < \cdots < t_Z$.
-For each patent $i=1, \cdots, Z$ we consider $C_i$ the number of distinctive couples \{cited patent, cited patent's class\} made by the $i$th patent (for instance if the $i$th patent has only made one citation and that the cited patent is associated with three classes, then $C_i = 3$).
-Let $z \in \{tec, sem\}$, we define $N_{i}^{(z)}$  the number of patents associated to at least one of the $i$th classes at time $t_{i-1}$.
-For $l = 1, \cdots, C_i$ we consider the variables $B_{l,i}$, which equal $1$ if the cited patent's class is also common to the $i$th patent.
-We assume that $B_{l,i}$ are independent of each other and conditioned on the past follow Bernoulli variables
-$$B \Big( \min \Big\{ 1, \frac{N_{i}^{(z)}}{i-1} + \theta^{(z)} \Big\} \Big),$$ 
-where the parameter $0 \leq \theta^{(z)} \leq 1$ indicates the propensity for any patent to cite patents of its own technological or semantic class.
-When $\theta^{(z)} = 0$, the probability of citing patents from its own class is simply $N_{i}^{(z)}(i-1)^{-1}$, which corresponds to the observed proportion of patents which belong to at least one of the $i$th patent's classes.
-Thus this corresponds to the estimated probability of citing one patent if we assume that the probability of citing any patent $k=1, \cdots, i-1$ is uniformly distributed, which could be a reasonable assumption if classes were assigned randomly and independently from patent abstract contents.
-Conversely if $\theta^{(z)} = 1$, we are in the case of a model where there are 100\% of within class citations.
-A reasonable choice of $\theta^{(z)}$ lies between those two extreme values.
-Finally, we assume that the number of distinctive couples $C_i$ are a sequence of independent and identically distributed random variables following the discrete distribution $C$, and also independent from the other quantities.
-
-We estimate $\theta^{(z)}$ via maximum likelihood, and obtain the corresponding maximum likelihood estimator (MLE) $\hat{\theta}^{(z)}$.
-The likelihood function, along with the standard deviation expression and details about the test, can be found in~\nameref{sectionSI}.
-The fitted values, standard errors and p-values corresponding to the statistical test $\theta^{(sem)} = \theta^{(tec)}$ (with corresponding alternative hypothesis $\theta^{(sem)} > \theta^{(tec)}$) on non-overlapping blocks from the period 1980-2007\footnote{Note that the estimation included patents up until 2010 in the period 2006-2007 and not the patents from 1980 in the period 1980-1985 for homogeneity in size with other periods.
-This doesn't affect the significativity of the results.} are reported on Table \ref{summary}.
-Semantic values are reported for four different chosen thresholds $p^{-}=.04, .06, .08, .1$.
-It means that we restricted to the couples ($i$th patent, $j$th class) such that $p_{ij} \geq p^{-}$.
-
-The choice of considering non-overlapping blocks (instead of overlapping blocks) is merely statistical.
-Ultimately, our interest is in the significance of the test over the whole period 1980-2007.
-Thus, we want to compute a global p-value.
-This can be done considering the local p-values (by local, we mean for instance computed on the period 2001-2005) assuming independence between them.
-This assumption is reasonable only if the blocks are non-overlapping.
-All of this can be found in~\nameref{sectionSI}.
-Finally, note that from a statistical perspective, including overlapping blocks wouldn't yield more information.
-
-The values reported in Table \ref{summary} are overwhelmingly against the null hypothesis.
-The global estimates of $\theta^{(sem)}$ are significantly bigger than the estimate of $\theta^{(tec)}$ for all the considered thresholds.
-Although the corresponding p-values (which are also very close to 0) are not reported, it is also quite clear that the bigger the threshold, the higher the corresponding $\theta^{(sem)}$ is estimated.
-This is consistently seen for any period, and significant for the global period.
-This seems to indicate that when restricting to the couples (patent, class) with high semantic probability, the propension to cite patents from its own class $\theta^{(sem)}$ is increasing.
-We believe that this might provide extra information to patent officers when making their choice of citations.
-Indeed, they could look first to patents which belong to the same semantic class, especially when patents have high probability semantic values.
-
-Note that the introduced model can be seen as a simple model of citations network growth conditional to a classification, which can be expressed as a stochastic block model (e.g.
-\cite{decelle2011asymptotic}, \cite{valles2016multilayer}).
-The parameters are estimated computing the corresponding MLE.
-In view of~\cite{2016arXiv160602319N}, this can be thought as equivalent to maximizing modularity measures.
-
-\begin{table}[!ht]
-\centering
-\caption{\label{summary} Estimated values of $\theta^{(tec)}$ and $\theta^{(sem)}$ and corresponding standard errors obtained from a Maximum Likelihood estimator as presented in section \ref{statisticalmodel}.}
-\label{stdQMLE}
-\begin{tabular}{@{}rccccccccc@{}}
-\toprule
-\toprule
-\multicolumn{1}{l}{Approach} & \multicolumn{1}{l}{Estimated Value} & \multicolumn{1}{l}{st. er.} & \multicolumn{1}{l}{p-value} \\ \toprule
-\multicolumn{4}{l}{1980-1985 period} \\
-technological & .664 &.008&\\
-semantic $p^{-} = .04$ & .741 &.047 & .053\\
-semantic $p^{-} = .06$ & .799 &.081 & .049\\
-semantic $p^{-} = .08$ & .828 &.126 & .097\\
-semantic $p^{-} = .10$ & .834 &.166 & .153\\
-\multicolumn{4}{l}{1986-1990 period} \\
-technological & .634 &.007&\\
-semantic $p^{-} = .04$ & .703 &.022 & .001\\
-semantic $p^{-} = .06$ & .768 &.040 & .0004\\
-semantic $p^{-} = .08$ & .804 &.069 & .007\\
-semantic $p^{-} = .10$ & .832 &.114 & .041\\
-\multicolumn{4}{l}{1991-1995 period} \\
-technological & .619 &.006&\\
-semantic $p^{-} = .04$ & .655 &.009 & .0004\\
-semantic $p^{-} = .06$ & .713 &.017 & 9e-08\\
-semantic $p^{-} = .08$ & .731 &.025 & 7e-06\\
-semantic $p^{-} = .10$ & .750 &.037 & 9e-06\\
-\multicolumn{4}{l}{1996-2000 period} \\
-technological & .551 &.003&\\
-semantic $p^{-} = .04$ & .585 &.002 & $\approx 0$\\
-semantic $p^{-} = .06$ & .638 &.004 & $\approx 0$\\
-semantic $p^{-} = .08$ & .660 &.006 & $\approx 0$\\
-semantic $p^{-} = .10$ & .686 &.008 & $\approx 0$\\
-\multicolumn{4}{l}{2001-2005 period} \\
-technological & .567 &.003&\\
-semantic $p^{-} = .04$ & .621 &.004 & $\approx 0$\\
-semantic $p^{-} = .06$ & .676 &.007 & $\approx 0$\\
-semantic $p^{-} = .08$ & .701 &.010 & $\approx 0$\\
-semantic $p^{-} = .10$ & .710 &.013 & $\approx 0$\\
-\multicolumn{4}{l}{2006-2007 period} \\
-technological & .600 &.007&\\
-semantic $p^{-} = .04$ & .683 &.016 & 1e-06\\
-semantic $p^{-} = .06$ & .732 &.025 & 2e-07\\
-semantic $p^{-} = .08$ & .760 &.036 & 6e-06\\
-semantic $p^{-} = .10$ & .782 &.048 &9e-05\\
-\multicolumn{4}{l}{1980-2007 global period} \\
-technological & .606 &.002&\\
-semantic $p^{-} = .04$ & .665 &.009 & 8e-11\\
-semantic $p^{-} = .06$ & .721 &.017 & 9e-12\\
-semantic $p^{-} = .08$ & .747 &.025 & 9e-09\\
-semantic $p^{-} = .10$ & .782 &.035 & 3e-07\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion \label{discussion}}
-%%%%%%%%%%%%%%%%%%%%%
-
-The main contribution of this study was twofold.
-First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts.
-We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features.
-Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...).
-The availability of these data suggests new avenues for further research.
-
-A first potential application is to use the patents' topological measures inherited from their relevant keywords.
-The fact that these measures are backward-looking and immediately available after the publication of the patent information is an important asset.
-It would for example be very interesting to test their predicting power to assess the quality of an innovation, using the number of forward citations received by a patent, and subsequently the future effect on the firm's market value.
-
-Regarding firm innovative strategy, a second extension could be to study trajectories of firms in the two networks: technological and semantic.
-Merging these information with data on the market value of firms can give a lot of insight about the more efficient innovative strategies, about the importance of technology convergence or about acquisition of small innovative firms.
-It will also allow to observe innovation pattern over a firm life cycle and how this differ across technology field.
-
-A third extension would be to use dig further into the history of innovation.
-USPTO patent data have been digitized from the first patent in July 1790.
-However, not all of them contain a text that is directly exploitable.
-We consider that the quality of patent's images is good enough to rely on Optical Character Recognition techniques to retrieve plain text from at least 1920.
-With such data, we would be able to extend our analysis further back in time and to study how technological progress occurs and combines in time.
-\cite{akcigit2013mechanics} conduct a similar work by looking at recombination and apparition of technological subclasses.
-Using the fact that communities are constructed yearly, one can construct a measure of proximity between two successive classes.
-This could give clear view on how technologies converged over the year and when others became obsolete and replaced by new methods.
-
-%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supporting Information \label{sectionSI}}
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-
-\subsection*{S1 Text : Definition of utility patent}
-
-\textbf{Describes with more details the definition of patents and  context.}
-
-\subsection*{S2 Text : Data collection procedure}
-
-\textbf{Detailed description of data collection}
-
-\subsection*{S3 File : Semantic Network Visualization}
-
-\textbf{Vector file of the semantic network (Fig.\ref{fig:rawnetwork})} available at \texttt{http://37.187.242.99/files/public/network.svg}
-
-\subsection*{S4 Text : Network Sensitivity Analysis\label{app:sensitivity}}
-
-\textbf{Extended figures for Network Sensitivity Analysis}
-
-\subsection*{S5 Text : Statistical definitions and derivations}
-
-\textbf{Extended definitions and derivations for the statistical model}
-
-%%%%%%%%%%%%%%%%%%%%%
-%\section*{Acknowledgments}
-
-%\nolinenumbers
-
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-%\bibliographystyle{plos2015}
-%\bibliography{patents}
-
-\begin{thebibliography}{10}
-
-\bibitem{aghionhowitt1992}
-Aghion P, Howitt P.
-\newblock {A Model of Growth through Creative Destruction}.
-\newblock Econometrica. 1992 March;60(2):323--51.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v60y1992i2p323-51.html}.
-
-\bibitem{romer1990}
-Romer PM.
-\newblock {Endogenous Technological Change}.
-\newblock Journal of Political Economy. 1990 October;98(5):S71--102.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ucp/jpolec/v98y1990i5ps71-102.html}.
-
-\bibitem{RePEc:nbr:nberwo:3301}
-Griliches Z.
-\newblock {Patent Statistics as Economic Indicators: A Survey}.
-\newblock National Bureau of Economic Research, Inc; 1990. 3301.
-\newblock Available from: \url{https://ideas.repec.org/p/nbr/nberwo/3301.html}.
-
-\bibitem{Hall2001}
-Hall BH, Jaffe AB, Trajtenberg M.
-\newblock {The NBER Patent Citations Data File: Lessons, Insights and
-  Methodological Tools}.
-\newblock C.E.P.R. Discussion Papers; 2001. 3094.
-\newblock Available from: \url{https://ideas.repec.org/p/cpr/ceprdp/3094.html}.
-
-\bibitem{Youn:2015fk}
-Youn H, Strumsky D, Bettencourt LMA, Lobo J.
-\newblock Invention as a combinatorial process: evidence from US patents.
-\newblock Journal of The Royal Society Interface. 2015;12(106).
-
-\bibitem{2013arXiv1310.8220N}
-{Newman} MEJ.
-\newblock {Prediction of highly cited papers}.
-\newblock ArXiv e-prints. 2013 Oct;.
-
-\bibitem{2014arXiv1402.7268S}
-{Sarig{\"o}l} E, {Pfitzner} R, {Scholtes} I, {Garas} A, {Schweitzer} F.
-\newblock {Predicting Scientific Success Based on Coauthorship Networks}.
-\newblock ArXiv e-prints. 2014 Feb;.
-
-\bibitem{sorenson2006complexity}
-Sorenson O, Rivkin JW, Fleming L.
-\newblock Complexity, networks and knowledge flow.
-\newblock Research policy. 2006;35(7):994--1017.
-
-\bibitem{kay2014patent}
-Kay L, Newman N, Youtie J, Porter AL, Rafols I.
-\newblock Patent overlay mapping: Visualizing technological distance.
-\newblock Journal of the Association for Information Science and Technology.
-  2014;65(12):2432--2443.
-
-\bibitem{bruck2016recognition}
-Bruck P, R{\'e}thy I, Szente J, Tobochnik J, {\'E}rdi P.
-\newblock Recognition of emerging technology trends: class-selective study of
-  citations in the US Patent Citation Network.
-\newblock Scientometrics. 2016;107(3):1465--1475.
-
-\bibitem{curran2011patent}
-Curran CS, Leker J.
-\newblock Patent indicators for monitoring convergence--examples from NFF and
-  ICT.
-\newblock Technological Forecasting and Social Change. 2011;78(2):256--273.
-
-\bibitem{Katz1996remarks}
-Katz ML.
-\newblock Remarks on the economic implications of convergence.
-\newblock Industrial and Corporate Change. 1996;5(4):1079--1095.
-
-\bibitem{Furman2011shoulders}
-Furman JL, Stern S.
-\newblock Climbing atop the Shoulders of Giants: The Impact of Institutions on
-  Cumulative Research.
-\newblock American Economic Review. 2011 August;101(5):1933--63.
-\newblock Available from:
-  \url{http://www.aeaweb.org/articles?id=10.1257/aer.101.5.1933}.
-
-\bibitem{AAKnetwork2016}
-Acemoglu AU Daron, Kerr W.
-\newblock {Innovation Network}.
-\newblock Proceedings of the National Academy of Sciences (forthcoming). 2016;.
-
-\bibitem{preschitschek2013}
-Preschitschek N, Niemann H, Leker J, Moehrle MG.
-\newblock Anticipating industry convergence: Semantic analyses vs IPC
-  co-classification analyses of patents.
-\newblock Foresight. 2013 11;15(6):446--464.
-
-\bibitem{yoon2004text}
-Yoon B, Park Y.
-\newblock A text-mining-based patent network: Analytical tool for
-  high-technology trend.
-\newblock The Journal of High Technology Management Research.
-  2004;15(1):37--50.
-
-\bibitem{park2014semantic}
-Park I, Yoon B.
-\newblock A semantic analysis approach for identifying patent infringement
-  based on a product--patent map.
-\newblock Technology Analysis \& Strategic Management. 2014;26(8):855--874.
-
-\bibitem{yoon2011detecting}
-Yoon J, Kim K.
-\newblock Detecting signals of new technological opportunities using semantic
-  patent analysis and outlier detection.
-\newblock Scientometrics. 2011;90(2):445--461.
-
-\bibitem{gerken2012new}
-Gerken JM, Moehrle MG.
-\newblock A new instrument for technology monitoring: novelty in patents
-  measured by semantic patent analysis.
-\newblock Scientometrics. 2012;91(3):645--670.
-
-\bibitem{choi2014patent}
-Choi J, Hwang YS.
-\newblock Patent keyword network analysis for improving technology development
-  efficiency.
-\newblock Technological Forecasting and Social Change. 2014;83:170--182.
-
-\bibitem{fattori2003text}
-Fattori M, Pedrazzi G, Turra R.
-\newblock Text mining applied to patent mapping: a practical business case.
-\newblock World Patent Information. 2003;25(4):335--342.
-
-\bibitem{2015arXiv151003797G}
-{Gurciullo} S, {Smallegan} M, {Pereda} M, {Battiston} F, {Patania} A, {Poledna}
-  S, et~al.
-\newblock {Complex Politics: A Quantitative Semantic and Topological Analysis
-  of UK House of Commons Debates}.
-\newblock ArXiv e-prints. 2015 Oct;.
-
-\bibitem{lerner2015use}
-Lerner J, Seru A.
-\newblock The use and misuse of patent data: Issues for corporate finance and
-  beyond.
-\newblock Booth/Harvard Business School Working Paper. 2015;.
-
-\bibitem{oecdpatentmanual}
-OECD.
-\newblock OECD Patent Statistics Manual. 2009;Available from:
-  \url{/content/book/9789264056442-en}.
-
-\bibitem{martin2015}
-Dechezlepretre A, Martin R, Mohnen M.
-\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
-\newblock Centre for Economic Performance, LSE; 2014. dp1300.
-\newblock Available from:
-  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.
-
-\bibitem{tseng2007text}
-Tseng YH, Lin CJ, Lin YI.
-\newblock Text mining techniques for patent analysis.
-\newblock Information Processing \& Management. 2007;43(5):1216--1247.
-
-\bibitem{Adams2010text}
-Adams S.
-\newblock {The text, the full text and nothing but the text: Part 1 - Standards
-  for creating textual information in patent documents and general search
-  implications}.
-\newblock World Patent Information. 2010 March;32(1):22--29.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/eee/worpat/v32y2010i1p22-29.html}.
-
-\bibitem{abbas2014literature}
-Abbas A, Zhang L, Khan SU.
-\newblock A literature review on the state-of-the-art in patent analysis.
-\newblock World Patent Information. 2014;37:3--13.
-
-\bibitem{chavalarias2013phylomemetic}
-Chavalarias D, Cointet JP.
-\newblock Phylomemetic patterns in science evolution---the rise and fall of
-  scientific fields.
-\newblock Plos One. 2013;8(2):e54847.
-
-\bibitem{nltk}
-NLTK. Natural Language Toolkit, Stanford University; 2015.
-
-\bibitem{clauset2004finding}
-Clauset A, Newman ME, Moore C.
-\newblock Finding community structure in very large networks.
-\newblock Physical review E. 2004;70(6):066111.
-
-\bibitem{yang2000improving}
-Yang Y, Ault T, Pierce T, Lattimer CW.
-\newblock Improving text categorization methods for event tracking.
-\newblock In: Proceedings of the 23rd annual international ACM SIGIR conference
-  on Research and development in information retrieval. ACM; 2000. p. 65--72.
-
-\bibitem{blei2003latent}
-Blei DM, Ng AY, Jordan MI.
-\newblock Latent dirichlet allocation.
-\newblock Journal of machine Learning research. 2003;3(Jan):993--1022.
-
-\bibitem{kaplan2015double}
-Kaplan S, Vakili K.
-\newblock The double-edged sword of recombination in breakthrough innovation.
-\newblock Strategic Management Journal. 2015;36(10):1435--1457.
-
-\bibitem{iacovacci2015mesoscopic}
-Iacovacci J, Wu Z, Bianconi G.
-\newblock Mesoscopic Structures Reveal the Network Between the Layers of
-  Multiplex Datasets.
-\newblock arXiv preprint arXiv:150503824. 2015;.
-
-\bibitem{de2015ranking}
-De~Domenico M, Sol{\'e}-Ribalta A, Omodei E, G{\'o}mez S, Arenas A.
-\newblock Ranking in interconnected multilayer networks reveals versatile
-  nodes.
-\newblock Nature communications. 2015;6.
-
-\bibitem{ARCHIBUGI199279}
-Archibugi D, Pianta M.
-\newblock Specialization and size of technological activities in industrial
-  countries: The analysis of patent data.
-\newblock Research Policy. 1992;21(1):79 -- 93.
-\newblock Available from:
-  \url{http://www.sciencedirect.com/science/article/pii/0048733392900283}.
-
-\bibitem{Bloom2005distance}
-Bloom N, Schankerman M, Reenen JV.
-\newblock {Identifying Technology Spillovers and Product Market Rivalry}.
-\newblock Econometrica. 2013 07;81(4):1347--1393.
-\newblock Available from:
-  \url{https://ideas.repec.org/a/ecm/emetrp/v81y2013i4p1347-1393.html}.
-
-\bibitem{ziman2003technological}
-Ziman J.
-\newblock Technological innovation as an evolutionary process.
-\newblock Cambridge University Press; 2003.
-
-\bibitem{holland2012signals}
-Holland JH.
-\newblock Signals and boundaries: Building blocks for complex adaptive systems.
-\newblock Mit Press; 2012.
-
-\bibitem{nicosia2009extending}
-Nicosia V, Mangioni G, Carchiolo V, Malgeri M.
-\newblock Extending the definition of modularity to directed graphs with
-  overlapping communities.
-\newblock Journal of Statistical Mechanics: Theory and Experiment.
-  2009;2009(03):P03024.
-
-\bibitem{decelle2011asymptotic}
-Decelle A, Krzakala F, Moore C, Zdeborov{\'a} L.
-\newblock Asymptotic analysis of the stochastic block model for modular
-  networks and its algorithmic applications.
-\newblock Physical Review E. 2011;84(6):066106.
-
-\bibitem{valles2016multilayer}
-Valles-Catala T, Massucci FA, Guimera R, Sales-Pardo M.
-\newblock Multilayer stochastic block models reveal the multilayer structure of
-  complex networks.
-\newblock Physical Review X. 2016;6(1):011036.
-
-\bibitem{2016arXiv160602319N}
-{Newman} MEJ.
-\newblock {Community detection in networks: Modularity optimization and maximum
-  likelihood are equivalent}.
-\newblock ArXiv e-prints. 2016 Jun;.
-
-\bibitem{akcigit2013mechanics}
-Akcigit U, Kerr WR, Nicholas T.
-\newblock The Mechanics of Endogenous Innovation and Growth: Evidence from
-  Historical US Patents.
-\newblock Citeseer; 2013.
-
-\bibitem{regibeau2010}
-R{\'e}gibeau P, Rockett K.
-\newblock Innovation cycles and learning at the patent office: does the early
-  patent get the delay?
-\newblock Journal of Industrial Economics. 2010;58(2):222--246.
-\newblock Available from:
-  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.
-
-\end{thebibliography}
-
-\newpage
-
-\section*{S1 Text : Definition of utility patent}
-
-A utility patent at the USPTO is a document providing intellectual property and protection of an invention.
-It excludes others to making, using, or selling the invention the same invention in the United States in exchange for a disclosure of the patent content.
-The protection is granted for 20 years since 1995 (it was 17 years before that from 1860) starting from the year the patent application was filled, but can be interrupted before if its owner fails to pay the maintenance fees due after 3.5, 7.5 and 11.5 years.
-Utility patents are by far the most numerous, with more than 90\% of the total universe of USPTO patents.\footnote{Other categories are Plant patents, Design patents and Reissue patents.} According to the Title 35 of the United States Codes (35 USC) section 101: \textit{``Whoever invents or discovers any new and useful process, machine, manufacture, or composition of matter, or any new and useful improvement thereof, may obtain a patent therefor, subject to the conditions and requirements of this title.''}\footnote{%
-Patent laws can be found in http://www.uspto.gov/web/offices/pac/mpep/mpep-9015-appx-l.html\#d0e302376} In practice however, other types of invention including algorithms can also be patented.\footnote{A notable example is the patent \textit{US6285999} protecting the Page Rank algorithm invented by Larry Page in 1998 which was the genesis of Google.} The two following sections of the 35 USC defined the condition an invention must meet to be protected by the USPTO: (i) novelty: the claimed invention cannot be already patented or described in a previous publication (35 USC section 102); (ii) obviousness: \textit{``differences between the claimed invention and the prior art must not be such that the claimed invention as a whole would have been obvious before the effective filing date of the claimed invention to a person having ordinary skill in the art to which the claimed invention pertains''}.
-(35 USC section 103).
-After review from the USPTO experts, an application satisfying these requirements will be accepted and a patent granted.
-The average time lag for such a review is on average a little more than 2 years since 1976, with some patents being granted after much more than two years.\footnote{This time lag, sometimes called the grant lag, is highly heterogeneous across technological fields.
-In addition, it cannot be considered as totally random.
-For example, if the patent is really disruptive some competitors might have some incentive in delaying the process by disputing the validity of the patent, for more details see~\cite{regibeau2010}.}
-
-\paragraph{Sample restriction}
-As explained briefly before, we consider every patent granted by the USPTO between 1976 and 2013.
-For each patent, we gather information on the year of application, the year the patent was granted, the name of the inventors, the name of the assignees and the technological fields in which the patent has been classified (we get back to what these fields are below).
-We restrict attention to patents applied for before 2007.
-The choice of the year 2007 is due to the truncation bias: we only want to use information on granted patents and we get rid of all patents that were rejected by the USPTO.
-However, in order to date them as closely as possible to the date of invention, we use the application date as a reference.
-As a consequence, as we approach the end of the sample, we only observe a fraction of the patents which have been granted by 2013.
-Looking at the distribution of time lag between application and grant in the past and assuming that this distribution is complete in time, we can consider that data prior to 2007 are almost complete and that data for 2007 are complete up to 90\%.
-
-\newpage
-
-\section*{S2 Text : Data collection and Workflow}
-
-\label{supp:data}
-
-\subsubsection*{Data Collection Procedure}
-
-Raw version of USPTO redbook with abstracts are available for years 1976-2014 starting from bulk download page at \url{https://bulkdata.uspto.gov/}.
-A script first automatically downloads files.
-Before being automatically processed, a few error in files (corresponding to missing end of records probably due to line dropping during the concatenation of weekly files) had to be corrected manually.
-Files are then processed with the following filters transforming different format and xml schemes into a uniform dictionary data structure :
-
-\begin{itemize}
-\item \texttt{dat} files (1976-2000): handmade parser
-\item \texttt{xml} files (2001-2012): xml parser, used with different schemas definitions.
-\end{itemize}
-
-Everything is stored into a MongoDB database, which latest dump is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}
-\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % anonymize the db for submission
-
-\subsubsection*{Processing Workflow}
-
-The source code for the full workflow is available at \url{https://github.com/JusteRaimbault/PatentsMining}.
-A simplified shell wrapper is at \texttt{Models/fullpipe.sh}.
-Note that keywords co-occurrence estimation requires a memory amount in $O(N^2)$ (although optimized using dictionaries) and the operation on the full database requires a consequent infrastructure.
-Launch specifications are the following :
-
-\paragraph{Setup}
-
-Install the database and required packages.
-
-\begin{itemize}
-\item Having a running local mongod instance
-\item mongo host, port, user and password to be configured in \texttt{conf/parameters.csv}
-\item raw data import from gz file : use mongorestore -d redbook -c raw --gzip {\$}FILE
-\item specific python packages required : pymongo, python-igraph, nltk (with resources punkt, averaged{\_}perceptron{\_}tagger,porter{\_}test)
-\end{itemize}
-
-\paragraph{Running}
-
-The utility fullpipe.sh launches the successive stages of the processing pipe.
-
-\paragraph{Options}
-
-\textit{this configuration options can be changed in }\texttt{conf/parameters.csv}
-
-\begin{itemize}
-\item window size in years
-\item beginning of first window
-\item beginning of last window
-\item number of parallel runs
-\item \texttt{kwLimit} : total number of keywords $K_W$
-\item \texttt{edge{\_}th} : $\theta_w$ pre-filtering for memory storage purposes
-\item \texttt{dispth} : $\theta_c$
-\item \texttt{ethunit} : $\theta_w^{(0)}$
-\end{itemize}
-
-\paragraph{Tasks}
-
-The tasks to be done in order : keywords extraction, relevance estimation, network construction, semantic probas construction, are launched with the following options :
-%!! keywords and kw-consolidation tested with python3 ; rest with python2 (igraph compatibility issues)
-
-\begin{enumerate}
-\item \texttt{keywords} : extracts keywords
-\item \texttt{kw-consolidation} : consolidate keywords database (techno disp measure)
-\item \texttt{raw-network} : estimates relevance, constructs raw network and perform sensitivity analysis
-\item \texttt{classification} : classify and compute patent probability, keyword measures and patent measures ; here parameters $(\theta_w,\theta_c)$ can be changed in configuration file.
-\end{enumerate}
-
-\paragraph{Classification Data}
-
-The data resulting from the classification process with parameters used here is available as \texttt{csv} files at \url{http://37.187.242.99/files/public/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05.zip}.
-Each files are named according to their content (keywords, patent probabilities, patent measures) and the corresponding time window.
-The format are the following :
-
-\begin{itemize}
-\item Keywords files : keyword ; community ; termhood times inverse document frequency ; technological concentration ; document frequency ; termhood ; degree ; weighted degree ; betweenness centrality ; closeness centrality ; eigenvector centrality
-\item Patents measures : patent id ; total number of potential keywords ; number of classified keywords ; same topological measures as for keywords
-\item Patent probabilities : patent id ; total number of potential keywords ; id of the semantic class ; number of keywords in this class.
-Probabilities have to be reconstructed by extracting all the lines corresponding to a patent and dividing each count by the total number of classified keywords.
-\end{itemize}
-
-\paragraph{Analysis}
-
-The results of classification has to be processed for analysis (construction of sparse matrices for efficiency e.g.), following the steps:
-\begin{itemize}
-\item from classification files to R variables with \texttt{Semantic/semanalfun.R}
-\item from csv technological classes to R-formatted sparse Matrix with \texttt{Techno/prepareData.R} 
-\item from csv citation file to citation network in R-formatted graph and adjacency sparse matrix with \texttt{Citation/constructNW.R}
-\end{itemize}
-
-Analyses are done in \texttt{Semantic/semanalysis.R}.
-
-\newpage
-
-\section*{S4 Text : Network Sensitivity Analysis \label{app:sensitivity}}
-
-\subsubsection*{Network Sensitivity}
-
-The example of Fig.1 in main text for a given year yielded the same qualitative behavior for all years, as shown in Fig.~\ref{fig:ext-sensitivity-1}, \ref{fig:ext-sensitivity-2} and \ref{fig:ext-sensitivity-3} here.
-We also show an other point of view over the Pareto optimization, that is the third plot giving the values of normalized objectives as a function of $\theta_c$.
-
-% Figures :
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears.png}
-\caption{Sensitivity plots for $T_0 = 4$ : Number of communities as a function of $\theta_w$, for each year.}
-\label{fig:ext-sensitivity-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto.png}
-\caption{Sensitivity plots for $T_0 = 4$ : Pareto plots of number of communities and number of vertices, for each year.}
-\label{fig:ext-sensitivity-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_eth4_1e-5.png}
-\caption{Sensitivity plots for $T_0 = 4$ : normalized objective as a function of $\theta_c$, for each year.}
-\label{fig:ext-sensitivity-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Time-window size sensitivity}
-
-% put some graphs for 3-years time window : same qualitative properties but a bit more noisy
-
-We show in Fig.~\ref{fig:sensitivity-window3-1}, \ref{fig:sensitivity-window3-2} and \ref{fig:sensitivity-window3-3} the sensitivity plots used for semantic network construction optimization, for a different time window with $T_0 = 2$.
-The same qualitative behavior is observed (with different quantitative values, as typically $\theta_w^{(0)}$ is for example expected to vary with document number and semantic regime, thus with window size), what confirms that the method is valid across different time windows.
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{commnum_thetaw_byyears_window3.png}
-\caption{Sensitivity plots for $T_0 = 2$ : Number of communities as a function of $\theta_w$, for each year.}
-\label{fig:sensitivity-window3-1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{vcount_comnum_pareto_window3.png}
-\caption{Sensitivity plots for $T_0 = 2$ : Pareto plots of number of communities and number of vertices, for each year.}
-\label{fig:sensitivity-window3-2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\textheight,height=\textwidth,angle=90]{normalizedObjs-dispth_window3_eth4_1e-5.png}
-\caption{Sensitivity plots for $T_0 = 2$ : normalized objective as a function of $\theta_c$, for each year.}
-\label{fig:sensitivity-window3-3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-\newpage
+\input{si.tex}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Information
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S1 Text : Definition of utility patent}
-
-%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%\section*{S2 Text : Data collection and Workflow}
-
-%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
-%\section*{S4 Text : Network Sensitivity Analysis}
-
-%%%%%%%%%%%%%%%%%%%%
-%\bigskip
-%\bigskip
-%\newpage
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\subsection*{Additional plots}
-%
-%% plots that have some info but not included in paper
-%
-%
-%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!ht]
-%% figure : interlayer overlap
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_density_semcounts.png}
-%\includegraphics[width=0.49\textwidth]{figures/norm-patents_interclassif_all_ts_semcounts.png}\\
-%\caption{Inter-classification effective overlaps (normalized by patent count)}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-
-%%%%%%%%%%%%%%%%%%%%%%
-%% Junk
-%%%%%%%%%%%%%%%%%%%%%%
-
-%Data-mining and network analysis~\cite{newman2010networks} can bring different insights.
-As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g.
-in the recent analysis on 20\textsuperscript{th} century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation necessarily involves complex patterns which understanding must have positive feedback on the economy.\par
-
-%%%%%%%%%%%%%%%%%%%%
-%%  Templates
-%%%%%%%%%%%%%%%%%%%%
-
-% For figure citations, please use "Fig." instead of "Figure".
-%\begin{figure}[h]
-%\caption{{\bf Figure Title first bold sentence}
-%Figure Caption}
-%\label{fig1}
-%\end{figure}
-
-%
-%
-%
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-%
-%
-
-%
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-
-%\begin{thebibliography}{10}
-%\bibitem{bib1}
-%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS.
-Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes.
-Mol Immunol.
-2014 Nov 22.
-pii: S0161-5890(14)00313-7.
-doi: 10.1016/j.molimm.2014.11.005
-
-%\bibitem{bib2}
-%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
-
-%\end{thebibliography}
-
 \end{document}
-
-\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
-
-A first insight into innovation dynamics can be drawn from the analysis of semantic communities dynamics.
-Communities are constructed yearly and thus one can define proximity between two successive semantic communities $S_i(t)$ and $S_j(t+1)$ with $i = 1, \cdots, N_{t}^{(sem)}$ and $j = 1, \cdots, N_{t+1}^{(sem)}$ using a similarity index between two respective sets of keywords $K(i, t)$ and $K(j, t+1)$, defined as the normalized intersection:
-\[
-\displaystyle j(K(i, t),K(j, t+1))=2\cdot \frac{\left|K(i, t)\cap K(j, t+1)\right|}{\left|K(i, t)\right|+\left|K(j, t+1)\right|}
-\]
-It enables us to infer flows of topics between communities in time and answer specific questions such as the potential precursors of one specific innovative fields.
-We show in Fig.~\ref{fig:semanticflows} a sample of these flows for the largest classes.
-\comment{En dire un peu plus sur la convergence des technologies. Est ce qu'on observe bien la convergence là dedans?}
-
-% eventually do stats on merging/splitting : distribution of kws overlaps in time ?
-
-\todo{Expected results : succession of classes in time ; maybe "unexpected flows" : ex how \texttt{hydrogen} divides ; birth of classes and dynamics reveal the evolution of technology in time.
-Seems to have some fusions/birth in the preliminary graph ; first need to have a clean graph to then look at some particular aspects.}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\hspace*{-2.5cm}
-\includegraphics[width=1.2\textwidth,height=0.4\textheight]{figures/test_flows_layoutProximity}
-\caption{\textbf{Semantic flows between successive classes in time.} We take each year the 3\% larger classes.
-\comment{(Juste) Cette figure est horrible et provisoire ; je dois creer of scratch un algo de layout parce que le package que j'utilisais est moisi, c'est super galère, pour l'instant c'est un greedy mais du coup il a un biais structurel que les branches tendent à converger ; je vais essayer une optim sur l'ensemble des angles pour minimiser l'angle total des branche pondérés ; pour les noms je ferai apparaitre ceux des plus grosses classes seulement}}
-\label{fig:semanticflows}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-27 Docs/Papers/Technical/overleafv2/Slides.tex

@@
 
-\begin{frame}{Estimation of n-gram relevance}
+\begin{frame}{Estimation of n-gram relevance}\label{slide:relevance}
 
     \begin{itemize}
-        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general})
+        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general}) \hyperlink{slide:filtration}{\beamerbutton{Definition}}
         % bias to keep fixed size of vocabulary ?
@@
 peak in sizes contradicts that, so should not capture this bias significantly (or structure is more important).
-        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 5y$ after sensitivity analysis)
+        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 4y$ after sensitivity analysis)
         \item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
         % potential bias here -> would capture the exogenous classification system ? idem our results suggest that bias does not dominate results
-        \item Low sensibility to the size of the time windows for the network structure % in comparable lengths of course
+        \item Low sensibility to the length of the time window for the network structure  
+\hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}
+% in comparable lengths of course
     \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Technical aspects}
+
+	$\rightarrow$ Temporal complexity: $\mathcal{O}(N_P)$ for keyword extraction and co-occurrences (constant $l_{max}^2$); parallelization on a 60 cores server for a ``reasonable'' computation time.
+
+	\bigskip
+
+	$\rightarrow$ Memory complexity: co-occurrence matrices in $\mathcal{O}(K_W^2)$; necessitates around 600Go RAM when parallelized.
+
+	\bigskip
+
+	$\rightarrow$ Database management: MongoDB (nosql suited to big data).
+
+\end{frame}
+
+\begin{frame}{An application of the method to a scientific corpus}
+	 % illustration de la flexibilite de la methode
+
+	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig6.jpg}
+	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig8.jpg}
+
+	\medskip
+
+	\textit{The method has been applied to a scientific corpus; adaptation of optimization procedures as the topological structure is different.} \cite{raimbault2017exploration}
 
@@
 
+    \hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}
+
 \end{frame}
@@
 
-\justify
+%\justify
 
@@
 \begin{frame}{Evolution of patent diversities}
+
+\label{slide:diversity}
+\hyperlink{slide:measures}{\beamerbutton{Back}}
+
    \centering
@@
 
-    $\rightarrow$ an impact of new information technologies ? (regarding knowledge production: from expert and contextualized to automatized search in references e.g.)
+    $\rightarrow$ an impact of new information technologies (regarding knowledge production: from expert and contextualized to automatized search in references e.g.) ?
+Linked to structural changes in economy (increase in firm concentration since 90s) ?
 
@@
 \end{frame}
+
 \begin{frame}{Other projects}
-    \justify
+    %\justify
 
@@
 
-\begin{frame}{Definition of termhood}
+\begin{frame}{Filtration measures}
+
+\label{slide:filtration}
+\hyperlink{slide:relevance}{\beamerbutton{Back}}
+
+    \textit{1. Unithood: n-gram specific frequency-based filtration ($4\cdot K_W$ keywords)}
+
+	\[
+	u_i = f_i\cdot \log{(1 + l_i)}
+	\]
+
+    \medskip
+
+    \textit{2. Termhood: chi-square statistic for the uniformity of co-occurences}
+
+    \medskip
+
+    \begin{eqnarray}
+\label{termhood}
+t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
+\end{eqnarray}
+
+    \medskip
+
+	\textit{3. Edge weight filtration with a threshold of $\theta_w = \theta_w^{(0)}\cdot N_P$}
+
+	\medskip
+
+	\textit{4. Node filtration with a threshold $\theta_c$ on technological class concentration given by}
+
+    \[
+    c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2}
+    \]
 
@@
 \begin{frame}{Patent measures}
+\label{slide:measures}
+\hyperlink{slide:diversity}{\beamerbutton{Back}}
+
+    \textit{Diversity}
+    \[
+D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}
+	\]
+
+    \medskip
+
+	\textit{Originality and Generality}
+
+	\[
+O_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in I_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in I_i}{p_{i'k}}}}\right)^2}
+\text{ and } G_i^{(z)} = \displaystyle 1 - \sum_{j =1}^{N^{(z)}}{\left(\frac{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'j}}}{\displaystyle \sum_{k =1}^{N^{(z)}}{\displaystyle \sum_{i' \in \tilde{I}_i}{p_{i'k}}}}\right)^2}
+\]
 
@@
 
-    Directed simple modularity:
+    Directed simple modularity \cite{nicosia2009extending}
     \[
@@
 
+\begin{frame}{Network sensitivity analysis}
+\label{slide:sensitivity}
+\hyperlink{slide:relevance}{\beamerbutton{Back}}
+
+	\includegraphics[width=\textwidth]{figures/commnum_thetaw_byyears.png}
+\end{frame}
+
+\begin{frame}{Network sensitivity analysis ($T_W = 2$)}
+	\includegraphics[width=\textwidth]{figures/commnum_thetaw_byyears_window3.png}
+\end{frame}
+
+\begin{frame}{Network sensitivity analysis}
+	\includegraphics[width=\textwidth]{figures/vcount_comnum_pareto.png}
+\end{frame}
+
+\begin{frame}{Network sensitivity analysis ($T_W = 2$)}
+	\includegraphics[width=\textwidth]{figures/vcount_comnum_pareto_window3.png}
+\end{frame}
+
+\begin{frame}{Network sensitivity analysis}
+	\includegraphics[width=\textwidth]{figures/normalizedObjs-dispth_eth4_1e-5.png}
+\end{frame}
+
+\begin{frame}{Network sensitivity analysis ($T_W = 2$)}
+	\includegraphics[width=\textwidth]{figures/normalizedObjs-dispth_window3_eth4_1e-5.png}
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%

### 2018-11-27 Docs/Papers/Technical/overleafv2/todolist.tex

\documentclass{article}

\usepackage{color}
\usepackage[dvipsnames]{xcolor}

% writing utilities

% comments and responses
\usepackage{xparse}
\DeclareDocumentCommand{\comment}{m o o o o}
{%
    \textcolor{red}{#1}
    \IfValueT{#2}{\textcolor{blue}{#2}}
    \IfValueT{#3}{\textcolor{ForestGreen}{#3}}
    \IfValueT{#4}{\textcolor{red!50!blue}{#4}}
    \IfValueT{#5}{\textcolor{Aquamarine}{#5}}
}

% todo
\newcommand{\todo}[1]{\textcolor{red!50!blue}{\textbf{\textit{(TODO) #1}}}}

\begin{document}

\todo{
\begin{itemize}
\item A rebuttal letter that responds to each point raised by the academic editor and reviewer(s). This letter should be uploaded as separate file and labeled 'Response to Reviewers'.
\item A marked-up copy of your manuscript that highlights changes made to the original version. This file should be uploaded as separate file and labeled 'Revised Manuscript with Track Changes'.
\item An unmarked version of your revised paper without tracked changes. This file should be uploaded as separate file and labeled 'Manuscript'.
\end{itemize}
}

\textbf{Reviewer comments : }

\bigskip

\comment{(Editor) Authors extended some usual techniques of classification resulting from a large-scale data-mining and network approach. The analysis is interesting. There are many works about patent network analysis. Authors used co-occurrence of keywords to construct a patent network. Is this a new way? Or at least a discussion of the advantages should be provided. Authors introduced a measure to correct the network topology. But how to properly determine the threshold? Why choose the value 0.06. The research background include complex network analysis, community detection and data analysis, some recent progress in these areas should be reviewed, e.g., Europhysics Letters, 2016, 116: 50001; Scientific Reports, 2016, 6: 20052; Europhysics Letters, 2015, 109: 30005; Scientific Reports, 2015, 5: 8222. All the parameters should be clearly explained.}

\todo{
\begin{itemize}
\item Add a discussion on the advantages of our approaches $\rightarrow$ already here no ?
\item For parameter description and optimization, clarify and highlight more ?
\item Add literature : we already cite what is necessary on the techniques used (modularity), I'm not sure adding what he says is relevant ; we should find a compromise
\end{itemize}
}

\bigskip

\comment{(Reviewer 1)  First authors have defined how they built a network of patents based on a classification method that uses semantic information from patent abstracts. Second, authors provide researchers with materials resulting from their analysis. An evaluation using the correspondence between citation links and classes to provide a measure of accuracy for classifications is performed.}

Nothing to do for this one, no ?

\bigskip

\comment{(Reviewer 2)In this paper, the authors present a semantic approach to patent classification. This is an interesting approach and one I have not seen previously applied to patents. The authors are correct that semantic analysis has been used in other limited studies over scholarly publications. Their decision to test their approach over the entire US Patent database is thus significant in both its scope and subject and lends credibility to the study’s rigor and final appropriability.
The study is both well-crafted and explained in appropriate detail. Although the primary function of a patent is legal protection, as a document they have been used to serve other functions both scholarly and social. Classification of these documents is thus complex and ever-changing. The approach detailed here thus adds to both the theoretical discussion of use of semantic analysis as well as being potentially applicable in the further study of science through patent analysis.
Additionally, the paper is well written and the conclusions drawn by the authors are appropriate given the analysis.
}

Also nothing to do ?

\bigskip

\comment{(Reviewer 3) This is one of the rare occasions that I am quite satisfied reviewing a paper - this paper tackles an interesting challenge in semantic classification of patents based on their text content and meaning of text, it is written in good easy-to-understand English, the dataset/code used is available for reproducibility, and the evaluation methods are appropriately carried out. The appendices also form a useful addition to the manuscript.
Maybe a minor typo in Page 24 - "availability of these data" --> "this data" or "these datasets". I also did not see a caption for the figures and it is quite hard to read the text in the figures due to their current small size. New readers are attracted to tables and figures, and thus it is useful to have descriptive captions - the current caption for Table 1 does not describe the variables being used (I know the text does it) - a brief description of theta being the likelihood estimates (or similar) would be useful.
I like the authors' approach overall, but would also recommend adding some discussion on how a semantic approach enables information integration and reuse - possibly with how their dataset / ontology can be linked to others already existing in Linked Open Data. If such linking already exists, it should be shown - otherwise, this is a strong direction for future work.}

\todo{
\begin{itemize}
\item typos
\item table caption
\item figures caption : are in text. text sizes. for figure 2, explain that the png is an illustration and that the same zoomable svg figure is available as supplementary.
\item discussion on coupling with existing databases.
\end{itemize}
}

\end{document}

### 2018-11-27 Models/DataCollection/dataExport.py
queries

@@ -2,23 +2,37 @@
 # export of data from raw db
 
 import pymongo
+import json
 
 
 #'
 #' This simple request is not implemented by mongo
-def and_text_query(terms,fields,file):
+def and_text_query(terms,fields,f):
     mongo = pymongo.MongoClient('mongodb://root:root@127.0.0.1:29019')
     database = mongo['redbook']
     projection = {}
     for field in fields :
         projection[field]=1
 
+    ids=set()
     for term in terms:
-        data = database.raw.find({"$text":{"$search":terms}},{"id":1})
-        println(len(data))
+        data = database.raw.find({"$text":{"$search":term}},{"id":1})
+        currentids=set([record['id'] for record in list(data)])
+        if len(ids)>0:
+            ids=ids.intersection(currentids)
+        else:
+            ids=currentids
+    #print(ids)
+    ids=list(ids)
+    fulldata= database.raw.find({"id":{"$in":ids}},{"id":1,"abstract":1,"title":1,"year":1,"_id":0})
+    #print(list(fulldata))
+    finaldata=list(fulldata)
+    print(len(finaldata))
+    print(finaldata)
+    json.dump(finaldata,open(f,'w'))
 
 
-def export_redbook_as_csv(fields,file) :
+def export_redbook_as_csv(fields,file):
     mongo = pymongo.MongoClient('localhost', 29019)
     database = mongo['redbook']
 
@@ -30,16 +44,16 @@ def export_redbook_as_csv(fields,file) :
 
     writer = open(file,'w')
 
-    for i in range(len(fields)) :
+    for i in range(len(fields)):
         writer.write(fields[i])
         if i < len(fields)-1:
             writer.write(";")
         else :
             writer.write("\n")
 
-    for row in data :
-        print row
-	for i in range(len(fields)) :
+    for row in data:
+        print(row)
+        for i in range(len(fields)):
             if fields[i] in row : writer.write(row[fields[i]])
             if i < len(fields)-1:
                 writer.write(";")
@@ -56,7 +70,7 @@ def export_classes_as_csv(file,max_year):
     writer.write('id;class;primary\n')
 
     for row in data :
-        print row
+        print(row)
         if 'id' in row :
             patent_id = row['id']
             if 'classes' in row :
@@ -77,4 +91,8 @@ def export_classes_as_csv(file,max_year):
 
[…]

### 2018-12-13 Docs/Papers/Technical/Slides_giessen.tex
slides_cfe

--- 2018-11-27 Docs/Papers/Technical/overleafv2/Slides.tex
@@
 \end{frame}
+
 \begin{frame}{Patents and text-mining}
@@
 \end{frame}
+
+\begin{frame}{An example of classification outcome}
+    \begin{center}
+	\includegraphics[width=0.8\textwidth]{figures/6833896.png}
+	\end{center}
+
+	\medskip
+	\hrule
+
+\medskip
+
+	\textbf{Technological classes:} 349 (Liquid Crystal Cells, Elements and Systems), 257 (electrodes)
+
+	\smallskip
+
+	\textbf{Prior art keywords (Google Patents):} layer, method, gate, electrode, substrate
+
+	\smallskip
+
+	\textbf{Most central keywords (our method):} substrat, semiconductor, insul, gate, transistor
+
+\end{frame}
+
 \section{Background}
@@
 
+\textbf{Paper: } Bergeaud, A., Potiron, Y., & Raimbault, J. (2017). Classifying patents based on their semantic content. PloS one, 12(4), e0176310.
+
+\medskip
+
 \textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\medskip

### 2018-12-13 Docs/Papers/Technical/overleafv2/Slides.tex
slides_cfe

@@
 \institute[]{Banque de France, Keio University and ISC-PIF}
-\date{November 2018}
+\date[14/12/2018]{Computational and Financial Econometrics\\
+Session Text Mining\\
+14 December 2018}
 
@@
 \section{Introduction}
-\begin{frame}{Motivation}
-    %Patenting is increasing, big data blablabla
 
-    \textit{Patenting as a footprint of technology and its coevolution with science and culture~\cite{bais2010praise}}
-
-\bigskip
-\centering
-
-\includegraphics[width=0.35\textwidth,angle=90]{figures/USX1}
-\includegraphics[width=0.45\textwidth]{figures/pageRank}
-
-\end{frame}
+%\begin{frame}{Motivation}
+%    %Patenting is increasing, big data blablabla
+%    
+%    \textit{Patenting as a footprint of technology and its coevolution with science and culture~\cite{bais2010praise}}
+%
+%\bigskip
+%\centering
+%
+%\includegraphics[width=0.35\textwidth,angle=90]{figures/USX1}
+%\includegraphics[width=0.45\textwidth]{figures/pageRank}
+%    
+%\end{frame}
 \begin{frame}{Motivation}
@@
 \end{frame}
-\begin{frame}{Patents and text-mining}
+\begin{frame}{Why study patents ?}
+
+$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
+$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.
+
+\bigskip
+
+\textbf{Patents and text-mining: }
+
     \begin{itemize}
@@
 \end{frame}
-\begin{frame}{Why study patents ?}
+
+%\begin{frame}{Why study patents ?}
+%\textbf{\textcolor{red}{virer ?}}
 %\justify
+%
+%$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
+%$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.
+%\bigskip
 
-$\rightarrow$ Although imperfect, patents are the most commonly used measure of innovation in economics. \\ % return to innovation, matching with firms, citation analysis...
-$\rightarrow$ Applied Epistemology : particular case of the ecology and evolution of knowledge; diffusion of knowledge.
-\bigskip
+%\textbf{Examples :}
 
-\textbf{Examples :}
-
-\begin{itemize}
-\item \cite{griliches1998patent}: patent as an economic indicator
-\item \cite{Youn:2015fk} interaction between technological fields ; combinatorial nature of inventions
-\item \cite{2016arXiv160207928B} citation network analysis to detect emerging research front
-\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis (remains limited to specific fields and time windows)
-\end{itemize}
-
-\end{frame}
+%\begin{itemize}
+%\item \cite{griliches1998patent}: patent as an economic indicator
+%\item \cite{Youn:2015fk} interaction between technological fields ; combinatorial nature of inventions
+%\item \cite{2016arXiv160207928B} citation network analysis to detect emerging research front
+%\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis (remains limited to specific fields and time windows)
+%\end{itemize} 
+%\end{frame}
 
@@
 \end{frame}
+
+\begin{frame}{An example of classification outcome}
+    \begin{center}
+	\includegraphics[width=0.8\textwidth]{figures/6833896.png}
+	\end{center}
+
+	\medskip
+	\hrule
+
+\medskip
+
+	\textbf{Technological classes:} 349 (Liquid Crystal Cells, Elements and Systems), 257 (	Active solid-state devices)
+
+	\smallskip
+
+	\textbf{Prior art keywords (Google Patents):} layer, method, gate, electrode, substrate
+
+	\smallskip
+
+	\textbf{Most central keywords (our method):} substrat, semiconductor, insul, gate, transistor
+
+\end{frame}
+
 \section{Background}
@@
 \item Selection of potential \textit{n-grams} (with $1 \leq n \leq 3$) with the rule $\bigcap \{NN \cup VBG \cup JJ \}$
-\item Database insertion for instantaneous use (several days $\rightarrow$ 1min)
-\item Estimation of \textit{n-grams} relevance, following co-occurrences statistical distribution (\textit{termhood} score as chi-2 score)
+%\item Database insertion for instantaneous use (several days $\rightarrow$ 1min)
+\item Estimation of \textit{n-grams} relevance, following co-occurrences statistical distribution (\textit{termhood} score as chi-2 score), filtering on relevance to construct co-occurence network
+\item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
 \end{itemize}
-\end{frame}
-
-\begin{frame}{Estimation of n-gram relevance}\label{slide:relevance}
-
-    \begin{itemize}
-        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general}) \hyperlink{slide:filtration}{\beamerbutton{Definition}}
-        % bias to keep fixed size of vocabulary ?
-        %  if variable = f(patents) -> arbitrary fixes a number of kws "per patent"; should them optimize regarding an exogenous criteria, which one ?
-        %  if fixed, this number varies, so the resolution of classes varies, thus larger classes more recently ?
-peak in sizes contradicts that, so should not capture this bias significantly (or structure is more important).
-        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 4y$ after sensitivity analysis)
-        \item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
-        % potential bias here -> would capture the exogenous classification system ? idem our results suggest that bias does not dominate results
-        \item Low sensibility to the length of the time window for the network structure  
-\hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}
-% in comparable lengths of course
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Technical aspects}
-
-	$\rightarrow$ Temporal complexity: $\mathcal{O}(N_P)$ for keyword extraction and co-occurrences (constant $l_{max}^2$); parallelization on a 60 cores server for a ``reasonable'' computation time.
-
-	\bigskip
-
-	$\rightarrow$ Memory complexity: co-occurrence matrices in $\mathcal{O}(K_W^2)$; necessitates around 600Go RAM when parallelized.
-
-	\bigskip
-
-	$\rightarrow$ Database management: MongoDB (nosql suited to big data).
-
-\end{frame}
-
-\begin{frame}{An application of the method to a scientific corpus}
-	 % illustration de la flexibilite de la methode
-
-	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig6.jpg}
-	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig8.jpg}
-
-	\medskip
-
-	\textit{The method has been applied to a scientific corpus; adaptation of optimization procedures as the topological structure is different.} \cite{raimbault2017exploration}
-
 \end{frame}
@@
 
-    \hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}
-
 \end{frame}
@@
 \begin{frame}{Classes Examples (2000-2004)}
-
-%\justify
 
@@
 \end{itemize}
- \end{frame}
-
-\begin{frame}{Size of classes}
-   \centering
-    \includegraphics[width=\textwidth]{figures/Fig3.png}
-
-    \medskip
-
-    \textit{A peak in average class size around 1998}
-
  \end{frame}
@@
     % "change in the regime of specialization, the new regime being caused by more single-class patents" => confirms the idea of a new type of more specialized inventions
-
-\end{frame}
-
-\begin{frame}{Originality and generality measures}
-    \centering
-    \includegraphics[width=\textwidth]{figures/Fig6.png}
-
-    \medskip
-
-    \textit{Systematically lower originality and generality (citation-based measures) for the semantic classification (consistent with the higher modularity shown thereafter).}
 
@@
 
-\begin{frame}{Stochastic Block Modeling to evaluate consistency of classifications}
-\begin{itemize}
-    \item   We complete the analysis by developing a statistical model aiming at quantifying performance of both technological and semantic classification systems
-    \item Intuitively, we look at within class citations proportion (for both technological and semantic approaches)
-    \item Question: is the semantic classification better at predicting future within class citations? \\
-    $\longrightarrow$ short answer is \alert{yes}.
-\end{itemize} 
-\end{frame}
-
 \begin{frame}{Summary of outcomes}
@@
 \end{frame}
-
 \begin{frame}{Other projects}
-    %\justify
 
@@
 \bigskip
-\bigskip
 
+%\bigskip
+
+\textbf{Paper: } Bergeaud, A., Potiron, Y., \& Raimbault, J. (2017). Classifying patents based on their semantic content. PloS one, 12(4), e0176310.
+
+\medskip
 \textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/PatentsMining}\\\medskip
@@
     \textbf{Reserve slides}
+
+\end{frame}
+
+\begin{frame}{Previous work on patents and text-mining}
+
+    \begin{itemize}
+\item \cite{griliches1998patent}: patent as an economic indicator
+\item \cite{Youn:2015fk} interaction between technological fields ; combinatorial nature of inventions
+\item \cite{2016arXiv160207928B} citation network analysis to detect emerging research front
+\item \cite{gerken2012new} \cite{tseng2007text} semantic analysis (remains limited to specific fields and time windows)
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Technical aspects}
+
+	$\rightarrow$ Temporal complexity: $\mathcal{O}(N_P)$ for keyword extraction and co-occurrences (constant $l_{max}^2$); parallelization on a 60 cores server for a ``reasonable'' computation time.
+
+	\bigskip
+
+	$\rightarrow$ Memory complexity: co-occurrence matrices in $\mathcal{O}(K_W^2)$; necessitates around 600Go RAM when parallelized.
+
+	\bigskip
+
+	$\rightarrow$ Database management: MongoDB (nosql suited to big data).
+
+\end{frame}
+
+\begin{frame}{An application of the method to a scientific corpus}
+	 % illustration de la flexibilite de la methode
+
+	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig6.jpg}
+	 \includegraphics[width=0.49\textwidth]{figures/cyb_Fig8.jpg}
+
+	\medskip
+
+	\textit{The method has been applied to a scientific corpus; adaptation of optimization procedures as the topological structure is different.} \cite{raimbault2017exploration}
+
+\end{frame}
+
+\begin{frame}{Estimation of n-gram relevance}\label{slide:relevance}
+
+    \begin{itemize}
+        \item Termhood-based selection of a fixed number of keywords $K_W = 100,000$ (\textit{difficulty to select terms in general}) \hyperlink{slide:filtration}{\beamerbutton{Definition}}
+        % bias to keep fixed size of vocabulary ?
+        %  if variable = f(patents) -> arbitrary fixes a number of kws "per patent"; should them optimize regarding an exogenous criteria, which one ?
+        %  if fixed, this number varies, so the resolution of classes varies, thus larger classes more recently ?
+peak in sizes contradicts that, so should not capture this bias significantly (or structure is more important).
+        \item Estimation on temporal moving windows $\left[t - T_w ; t\right]$ (fixed to $T_W = 4y$ after sensitivity analysis)
+        \item Filtering of network edge (parameter $\theta_w$), with an additional exogenous control by technological class keyword concentration to filter nodes (parameter $\theta_c$)
+        % potential bias here -> would capture the exogenous classification system ? idem our results suggest that bias does not dominate results
+        \item Low sensibility to the length of the time window for the network structure  
+\hyperlink{slide:sensitivity}{\beamerbutton{Sensitivity analysis}}
+% in comparable lengths of course
+    \end{itemize}
 
@@
 
-    Directed simple modularity \cite{nicosia2009extending}
+    Directed simple modularity:
     \[
@@
 
+\end{frame}
+
+\begin{frame}{Size of classes}
+   \centering
+    \includegraphics[width=\textwidth]{figures/Fig3.png}
+
+    \medskip
+
+    \textit{A peak in average class size around 1998}
+
+\end{frame}
+
+\begin{frame}{Originality and generality measures}
+    \centering
+    \includegraphics[width=\textwidth]{figures/Fig6.png}
+
+    \medskip
+
+    \textit{Systematically lower originality and generality (citation-based measures) for the semantic classification (consistent with the higher modularity shown thereafter).}
+
+\end{frame}
+
+\begin{frame}{Stochastic Block Modeling to evaluate consistency of classifications}
+\begin{itemize}
+    \item   We complete the analysis by developing a statistical model aiming at quantifying performance of both technological and semantic classification systems
+    \item Intuitively, we look at within class citations proportion (for both technological and semantic approaches)
+    \item Question: is the semantic classification better at predicting future within class citations? \\
+    $\longrightarrow$ short answer is \alert{yes}.
+\end{itemize} 
 \end{frame}

### 2018-12-13 Models/Semantic/example.R

@@ -1,0 +1,101 @@
+
+setwd(paste0(Sys.getenv('CS_HOME'),'/PatentsMining/Models/Semantic'))
+
+library(dplyr)
+
+
+classif04 = as.tbl(read.csv(
+  file='classification/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05/patent_2000-2004_kwLimit100000.0_dispth0.06_ethunit4.1e-05.csv',
+  sep=';',colClasses = c('character',rep('numeric',11)))
+  )
+
+keywords04 = as.tbl(read.csv(
+  file='classification/classification_window5_kwLimit100000_dispth0.06_ethunit4.1e-05/keywords_2000-2004_kwLimit100000.0_dispth0.06_ethunit4.1e-05.csv',
+  sep = ';',colClasses = c('character',rep('numeric',10))
+))
+
+
+data.frame(classif04[classif04$betweennesscentrality==max(classif04$betweennesscentrality),])
+#data.frame(classif04[classif04$classkws==max(classif04$classkws),])
+
+
+#    patent kws classkws     tidf technodispersion docfreq     termhood degree weighteddegree betweennesscentrality
+#1 6833896 172       81 18020.82         18.35517  343389 3.533676e+16  22969        3738107             133189045
+#closenesscentrality eigenvectorcentrality
+#1          0.05285423               7.51915
+
+# Google prior art keywords : (layer) (method) (gate) (electrode) (substrate)
+
+# stems :
+keywords =c("gate insul layer", "amorph silicon", "use third mask", "use third", "pure", 
+"electrod align layer", "activ layer pure", "data", "pattern second metal", "display devic",
+"third mask", "thermal-tr furnac cure", "form gate", "second", "substrat", "have sourc electrod",
+"insul", "metal", "transistor method", "devic", "form gate line", "crystal display", 
+"transistor method form", "gate insul", "first mask", "have gate", "in-plan", "electrod align",
+"first", "plural common", "data line have", "layer use", "pattern second", "electrod gate",
+"layer semiconductor layer", "mask form data", "amorph silicon second", "anneal thin", "amorph",
+"ohmic contact layer", "use second", "display devic have", "line have gate", "align layer",
+"insul layer", "layer semiconductor", "insul layer use", "silicon", "common electrod", "crystal",
+"metal layer semiconductor", "layer impurity-dop amorph", "substrat have", "layer impurity-dop", 
[…]
